### 2020-05-12 maintex.tex
added style files and figures

% AASTeX v6.2
%\documentclass[preprint]{aastex62}

% ApJ Format
\documentclass[iop,revtex4,twocolumn,apj,numberedappendix,appendixfloats]{emulateapj}
\usepackage{apjfonts}
% Hyperlinks & Bookmarks
\usepackage[pagebackref=false,colorlinks=true,citecolor=blue,linkcolor=blue,breaklinks=true,bookmarks=true]{hyperref}
\usepackage{amsmath}
\usepackage{comment}

% Units
\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\msun}{$M_{\odot}$}
\newcommand{\msunyr}{$M_{\odot}~{\rm yr}^{-1}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\ergs}{erg~s$^{-1}$}
\newcommand{\cmsq}{cm$^{-2}$}
\newcommand{\um}{$\mu$m}
\newcommand{\uJy}{$\mu$Jy}
\newcommand{\sqdeg}{deg$^2$}
\newcommand{\lx}{$L_{\rm X}$}
\newcommand{\lmir}{$L_{\rm 12\mu m}$}
\newcommand{\loiii}{$L_{\rm [OIII]}$}
% Emission lines
\newcommand{\Ha}{H$\alpha$}
\newcommand{\Hb}{H$\beta$}
\newcommand{\OII}{[O\,{\sc ii}]}
\newcommand{\OIIlam}{[O\,{\sc ii}]\,$\lambda$3727}
\newcommand{\SII}{[S\,{\sc ii}]}
\newcommand{\OIII}{[O\,{\sc iii}]}
\newcommand{\OIIIlam}{[O\,{\sc iii}]\,$\lambda$5007}
\newcommand{\NII}{[N\,{\sc ii}]}
\newcommand{\NeIII}{[Ne\,{\sc iii}]}
% special 
\newcommand{\nod}{\nodata}

\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\reff}{$R_{\rm eff}$}
\newcommand{\ewha}{EW(H$\alpha$)}
\newcommand{\logm}{log({\it M}/M$_{\odot}$)}

% citations
\defcitealias{Fu18}{Paper I}

\usepackage{epstopdf}

\begin{document}

\title{SDSS-IV MaNGA: Radial Profiles of Specific Star Formation Rate in Nearby Interacting Galaxies}

\author{
Joshua L. Steffen\altaffilmark{1}, 
Hai Fu\altaffilmark{1}, and 
MaNGA Team 
}
\altaffiltext{1}{Department of Physics \& Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}

\begin{abstract}

\end{abstract}

\keywords{galaxies: active --- galaxies: nuclei --- galaxies: interactions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Emission Lines}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pair Sample}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Control Sample}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radial Profiles}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusion}

\acknowledgments

% funding
J.S. and H.F. acknowledge support from the National Science Foundation (NSF) grant AST-1614326 and University of Iowa funds.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
\bibliographystyle{aasjournal}
\bibliography{mergerbib}

%%%%%%%%%%%%
% Appendix
%%%%%%%%%%%%

\end{document}

### 2020-05-12 maintex.tex
added intro

@@
 \newcommand{\logm}{log({\it M}/M$_{\odot}$)}
+%\newcommand{\arcsec}{\prime\prime}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
+
+%%%Galaxy Evolution%%%
+%{\it In $\Lambda$CDM, galaxy evolution is a hierarchical, bottom-up process.
+Galaxies are created in a process where large dark matter halos are formed out of the merging of smaller dark matter pockets and galaxies form within the dark matter halos \citep{White:1978}.
+The subsequent merging of dark matter halos leads to a scenario where a large central galaxy is surrounded by a cluster of smaller satellite galaxies within a single dark matter halo.
+The satellite galaxies lose kinetic energy through dynamical friction \citep{Chandrasekhar:1943} and will eventually merge with the central galaxy.
+The dynamical timescale for a merger event is on the order of 1 Gyr, which means that present day galaxies could have undergone multiple merger events during their lifetimes.
+
+%This means that the massive galaxies in the universe today are the product of the merging of several smaller galaxies.
+In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 (e.g.
+\citet{Rodriguez-Gomez:2016}; \citet{Pillepich:2018}).
+
+%This bottom-up process is still ongoing and can be seen in the Local Group with the Milky Way's collection of satellite galaxies.
+The Milky Way has an ongoing minor merger with its closest companion, the Canis Major dwarf galaxy \citep{Martin:2004} and is on track to merge with the Andromeda galaxy.
+}\\
+
+%%%%%
+In the $\Lambda$CDM model, galaxy evolution is a hierarchical process.
+Over the lifetime of the universe, smaller galaxies have iteratively merged with each other to form more massive galaxies.
+In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 (e.g.
+\citet{Rodriguez-Gomez:2016}; \citet{Pillepich:2018}).
+\\
+%%%%%
+
+%%%Simulations%%%
+%{\it Interacting galaxies were originally known as peculiar galaxies, named for their unusual shapes and morphologies.
+These peculiar galaxies were often seen to have nearby, neighboring galaxies and, because of this, it was suspected that the unusual features such as tails, bridges, or warped disks were the product of the gravitational tidal forces between the galaxies \citep{Zwicky:1959}.
+
+%\citet{Toomre:1972} investigated the idea using N-body simulations to model galaxy interactions.
+They used concentric rings of stars which were gravitationally bound to a central, massive nucleus.
+In their work, \citet{Toomre:1972} were able to demonstrate how the tidal tails found in peculiar galaxies could be the result of galaxy interactions.
+This confirmed the idea that peculiar galaxies are the result of galaxies interactions.
+
+%Since the N-body simulations from \citet{Toomre:1972}, more advanced simulations have been made which model the gas-dynamics within the interacting galaxies.
+These N-body plus gas-dynamics simulations showed how the tidal torques acting on the galaxy disks cause the formation of barred structures \citep{Barnes:1991}.
+As the bars are formed, the gases within the disk lose their angular momentum and get funneled into the center of the galaxy.
+The inflowing gases impact upon the gases already present in the galactic center and trigger a burst of new star formation \citep{Barnes:1996, Mihos:1996}.
+
+%The inflows bring in metal-poor gases from the disk, diluting the nuclear metal content of galaxy's center \citep{Rupke:2010, Perez:2011, Scudder:2012}.
+The inflows can also trigger supermassive black hole (SMBH) accretion \citep{Capelo:2017}.
+
+%Another common feature of peculiar galaxies is that they tend to have much bluer B$-$V color than other galaxy types \citep{Larson:1978}.
+The galaxies within the "Blue Cloud" on the color-magnitude diagram (CMD) are often associated with having active star formation.
+\citet{Larson:1978} identified that the galaxies showing deviations in color from normal galaxies are the galaxies which displayed features like tidal tails.
+This indicated that the violent disturbances subjected to interacting galaxies could trigger a large burst of star formation.} \\
+
+%%%%%
+The internal dynamics of these interacting galaxies were first modeled in the seminal work, \citet{Toomre:1972}.
+Since then, hydrodynamical simulations have expanded upon the N-body simulations of \citet{Toomre:1972} by modeling gas-dynamics within the galaxies.
+These simulations show how barred structures develop within the disks of the interacting galaxies due to the tidal torques between them \citep{Barnes:1991}.
+As the bars form, the gases within the galaxy's disk lose angular momentum and get funneled into the centers of the galaxies.
+
+When the gas-inflows impact upon the gases in the nucleus of galaxy a burst of new star formation in triggered \citep{Barnes:1996, Mihos:1996}.
+These gas inflows will also bring metal-poor gases from the disk into the center of the galaxy which can dilute the central metallicity \citep{Rupke:2010, Perez:2011, Scudder:2012}.
+The gas-inflows may also be able to make it into very center of the galaxy and trigger supermassive black hole (SMBH) accretion \citep{Capelo:2017}.
+\\
+%%%%%
+
+%%%Observations%%%
+%{\it Interacting galaxies have been studied extensively with large spectroscopic surveys.
+It has been shown that interacting galaxies feature higher levels of star formation than isolated galaxies in the surveys; CfA2  \citep{Barton:2000, Woods:2006}, 2dF \citep{Lambas:2003}, AEGIS \citep{Lin:2007}, SDSS \citep{Ellison:2008}, COSMOS \citep{Kartaltepe:2007,Xu:2012}, PRIMUS \citep{Wong:2011}, and GAMA \citep{Robotham:2014}.
+
+%The levels of star formation enhancement was shown to increase with closer projected separations \citep{Ellison:2008, Scudder:2012, Patton:2013}.
+These works indicate that the merger event ignites a burst of star formation after the passage of the first pericenter and that the burst of star formations begins to fade as the galaxies separate.
+\citet{Patton:2013} showed that this burst of star formation lingers as far out as projected separations of 150 kpc.
+The level of enhancement is also tied to the mass ratio, $|\Delta {\rm log}\,M|$, between the galaxies where major mergers, $\left( | \Delta {\rm log}\,M | \le 0.6\right)$, have larger rates of enhancement in comparison to minor mergers, $\left(0.6 < |\Delta {\rm log}\,M| \le 1.0\right)$ \citep{Ellison:2008}.
+
+%These single-fiber spectroscopic studies have been also used to study the nuclear metal content of the galaxy pairs.
+The galaxy pairs show weak levels of metallicity dilution in their centers, $\Delta$log(O/H) $\sim -0.05$ dex \citep{Ellison:2008, Scudder:2012}.
+The central metallicity dilution helps confirm the idea that the merger induced star formation is triggered by gas flows from the metal-poor galactic disks.} \\
+
+%%%%%
+Centrally enhanced star formation has also been observed in large spectroscopic surveys including; CfA2  \citep{Barton:2000, Woods:2006}, 2dF \citep{Lambas:2003}, AEGIS \citep{Lin:2007}, SDSS \citep{Ellison:2008}, COSMOS \citep{Kartaltepe:2007,Xu:2012}, PRIMUS \citep{Wong:2011}, and GAMA \citep{Robotham:2014}.
+
+This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable at wide projected separations of 150 kpc \citep{Patton:2013}.
+The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta log {\it M} |$, between the two galaxies \citep{Ellison:2008}.
+\\
+%%%%%
+
+%%%Integral Field Spectroscopy%%%
+%{\it The advent of large integral field spectroscopic (IFS) surveys has opened a new door in studying nearby galaxies.
+Previous single-fiber spectroscopic studies limit the degree to which we can study galaxy parameters like star formation or metallicity since these surveys are limited to covering only the centers of galaxies.
+IFS surveys allocate an entire bundle of fiber-optic cables, called integral field units (IFUs), to individual galaxies, giving us spectroscopy across the whole disk of the galaxies.
+The current set of IFS surveys include the Calar Alto Legacy Integral Field Area (CALIFA) survey which is based in Spain and covered $\sim$600 galaxies \citep{Sanchez:2012}, the Sydney-AOO Multi-object Integral field spectrograph (SAMI) survey which is based in Australia which plans to cover 3000 galaxies \citep{Croom:2012}, and the Mapping Nearby Galaxies at Apache Point Observatory (MaNGA) survey which is based in New Mexico and plans to cover 10,000 galaxies \citep{Bundy:2015}.
+In this work we will be using the MaNGA survey since it is the largest IFS survey to date.
+
+%Because of these new IFS surveys, parameters like star formation and gas-phase metallicity can be studied spatially in detail.
+These IFS surveys have also been used to study the distribution of star formation in interacting galaxies.
+\citet{Barrera-Ballesteros:2015} utilized the spatial resolution of the CALIFA survey in galaxy pairs by varying the aperture sizes from which SFR is extracted from.
+They found that the SFR is enhanced in the centers of galaxy pairs by a factor of 2$-$3$\times$ and that SFR is moderately suppressed by $\sim$0.74$\times$ in their disks.
+\citet{Barrera-Ballesteros:2015} also found that, in contrast to previous single fiber studies, that the metallicity found in the centers of galaxy pairs are not significantly different from their controls.
+
+%\citet{Pan:2019} used the MaNGA survey to study the radial profiles of specific star-formation rate (sSFR; where sSFR is the SFR of a region divided by the stellar mass of the region) in interacting galaxies.
+The galaxy pairs featured strong central enhancement of sSFR ($\sim$0.35 dex), but also weak enhancement of sSFR in their disks ($\sim$0.1$-$0.2 dex).
+\citet{Pan:2019} also studied the sSFR profiles across different merger stages.
+Galaxies pairs only showed signs of sSFR enhancement after the first pericenter, i.e.
+only pairs with visual morphological disturbances showed sSFR enhancement.
+
+%The MaNGA survey has also been used to study the radial profiles of post merger galaxies (galaxy mergers which have coalesced but still show some tidal features).
+The post mergers featured a central enhancement to SFR surface density of $\sim$ 2.5$\times$ and show a weak metallicity dilution of $\sim$$-$0.04 dex across their disks \citep{Thorp:2019}.
+} \\
+
+%%%%%
+With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can be studied in unprecedented spatial detail.
+Where previous spectroscopic surveys where limited to the nucleus of the interacting galaxies, the new IFS surveys will be able to study both the nuclei and the disks of the interacting galaxies.
+
+\citet{Barrera-Ballesteros:2015} studied star formation in interacting galaxies with the CALIFA\footnote{Calar Alto Legacy Integral Field Area} survey using variable aperture sizes from which the star formation rate (SFR) is extracted from.
+\\
+%%%%%
+
+%%%Purpose%%%
+%{\it In our previous work, \citet{Fu:2018}, we built a sample of galaxies pairs where both galaxies were found within the field of view of a single MaNGA IFU.
+We confirmed the theoretical expectation that the MaNGA pair fraction will increase with higher stellar masses and wider physical spatial coverage.
+We found that $\sim$5.7\% of the MaNGA galaxies have close spectroscopic companions.
+In \citet{Fu:2018} we further analyzed the presence of AGN in galaxy pairs and found that AGN duty cycle is preserved in individual galaxies; however, the population of binary AGN is increased.
+
+%In this work we will expand upon our pair sample from \citet{Fu:2018} with the most recent MaNGA Data Release, DR16, and supplement the sample with MaNGA galaxies which have companions identified outside of their IFUs.
+The galaxy pairs within the fields of view of a single IFU will allow us to study the closest galaxy pairs while the expanded sample of galaxy pairs identified outside of the MaNGA IFUs will allow us to expand the separation coverage of the sample.
+
+%With the expanded pair sample, we will study radial profile of star formation in the galaxy pairs.
+First we will address whether or not galaxy pairs experience enhanced star formation from the merger event.
+Second, we will study if the star formation enhancement is confined to the centers of the paired galaxies or if the enhancement extends into their disks.
+Afterwords, we will address how other parameters pertaining to the galaxy pairs can affect the merger induced star formation.
+
+%\begin{enumerate}
+
+%\item Does the total stellar mass of a galaxy affect the level of enhancement to the specific star-formation rate?
+That is to say, are low mass galaxies enhanced at the same level as high mass galaxies?
+
+%\item Does the stellar mass ratio between the interacting galaxy and its companion affect the rate of enhancement to the specific star-formation rate?
+We will see if galaxy mergers with roughly the same stellar mass are more efficient at inducing star-formation in comparison to massive galaxies absorbing dwarf galaxies.
+
+%\item Does the projected separation between the companion galaxies affect the rate of enhancement to the specific star-formation rate.
+We would expect the companions with the closest separations to have the highest rate of enhancement since they are the most likely to have recently undergone their first pericenter.
+We can also see how separated a set of companions can be and still show enhancement to their star-formation.
+
+%\item Does the merger induced star formation contribute a significant amount of new stellar mass growth to the galaxies?
+
+%\end{enumerate}
+
+%By answering these questions we hope to gain insight on the relevance of individual galaxy merger events in the context of galaxy evolution at low redshift. }\\
+
+% Organization
+This paper is organized as follows; in Section \ref{sec:data} we will discuss the detail of the MaNGA survey, in Section \ref{sec:analysis} we will discuss how we extract emission lines from the MaNGA survey and how we calculate the star formation from them, in Section \ref{sec:pair} we discuss the construction of our pair sample, in Section \ref{sec:control} we discuss the construction of our control sample, in Section \ref{sec:radial} we build the radial profiles for the pair and control galaxies, in Section \ref{sec:results} we discuss the results of the survey, in Section \ref{sec:discussion} we discuss our results in the context of other surveys, and in Section \ref{sec:sum} we summarize and conclude the work.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data}
+\section{Data}\label{sec:data}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Emission Lines}
+\section{Emission Lines}\label{sec:analysis}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pair Sample}
+\section{Pair Sample}\label{sec:pair}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Control Sample}
+\section{Control Sample}\label{sec:control}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Radial Profiles}
+\section{Radial Profiles}\label{sec:radial}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Results}\label{sec:results}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Conclusion}
+\section{Summary and Conclusion}\label{sec:sum}
 
@@
 
+\hbox{}\clearpage
+
+\appendix
+
+\section{Figures}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/Mi-z.pdf}
+\caption[The luminosity - redshift distribution and mass - redshift distribution of the MaNGA sample.]{On the left is the luminosity - redshift distribution of the MaNGA sample.
+The figure illustrates the unique distribution of the MaNGA sample.
+On the right, I replace the luminosity with stellar mass from the NSA catalog.}
+\label{fig:Mi_z}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/color-mag.pdf}
+\caption[Color-magnitude distribution of the MaNGA galaxies]{Color-magnitude diagram for MaNGA galaxies ({\it colored circles}).
+The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+The MaNGA galaxies with close companions are marked with {\it grey diamonds}.
+From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
+The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
+\label{fig:CMD}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/bpt_spax.pdf}
+\caption[BPT classification of MaNGA spaxels.]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
+The color of each bin represents the number density of spaxels, normalized to one.
+The black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001}.
+This shows the capability of the CMD to select star-forming galaxies as most of the spaxels within the selected galaxies fall beneath the starburst line.}
+\label{fig:bpt_spax}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/pair_collage.pdf}
+\caption[A collage of a subset of the inside-IFU pairs.]{A collage of a subset of the inside-IFU pairs.
+Each panel contains a 40$^{\arcsec}$ cutout of the SDSS pseudocolor image for the galaxy pair.
+The minor ticks on each panel's axis represents 2$^{\arcsec}$.
+The green squares highlight the identified galaxy pairs.
+}
+\label{fig:collage}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=3in]{fig/mag_comp.pdf}
+\caption[The comparison between the r-band magnitudes in Simard+11 and NSA catalog]{The comparison between the S\'ersic r-band apparent magnitude in \citet{Simard:2011} and the Elliptical Petrosian r-band apparent magnitude.
+The grey circles represent galaxies in the control sample, the blue squares represent galaxies in the outside-IFU sample, and the red diamonds represent the galaxies in the inside-IFU sample.
+Regardless of the sample, all of the galaxies covered by both of the catalogs have a similar apparent magnitude calculated from either sample.}
+\label{fig:mag_comp}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/8083-12703.pdf}
+\caption[Example of the difference profiles for the mass-redshift selected control sample.]{The process for building the tailored control sample.
+The Left panel shows the paired galaxy's profile for sSFR.
+The Middle panel shows the profiles for sSFR for the selected 20 control galaxies in gray.
+The red profile is the median profile of the 20 control galaxies where the highlighted region about the profile is the standard error of the mean.
+The Right panel shows the difference between pair's profile and the stacked control profile.}
+\label{fig:dex}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/8485-3704.pdf}
+\caption[Example of bootstrapping to quantify the deviation of the random subsample of controls]{An example of the bootstrapping used to quantify the errors associated with the random selection of the control subsample.
+From left to right, the first four panels show the individual dex profiles after a random sub-selection in grey.
+The random sub-selection is run 1000 times and the median profile after the 1000 cycles is given by the colored profile.
+The highlighted region about the colored profiles is the standard error of the mean of the median profile.
+From left to right each panel shows the random selection for a different number of controls to select; 5, 10, 20, and 50 controls.
+The panel on the right end shows the median profiles of all of the preceding panels.
+}
+\label{fig:bootstrap}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
+\caption[The $\Delta$log(sSFR) split by stellar mass.]{The $\Delta$log(sSFR) split into separate stellar mass bins.
+The left column gives the stacked difference profiles.
+The highlighted region about the profiles represents the standard error of the mean of the profile.
+The right column gives the nuclear $\Delta$log(sSFR) values.
+The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
+The vertical error bars on the black squares represent the standard deviation within the bin.
+The top row is the inside-IFU sample, the middle row is the outside-IFU sample, and the bottom row is the combination of the two samples.}
+\label{fig:ssfr_mass}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
+\caption[The $\Delta$log(sSFR) split by mass ratio.]{Same as Figure \ref{fig:ssfr_mass} but split into separate mass ratio bins.}
+\label{fig:ssfr_dm}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
+\caption[The $\Delta$log(sSFR) split by projected separation.]{Same as Figure \ref{fig:ssfr_mass} but split into separate projected separation bins.}
+\label{fig:ssfr_sep}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/mass_gain_1.pdf}
+\caption[Example of the calculation of the fractional mass gain due to merger induced star formation for a single mass bin.]{In the Left panel we fit a model gaussian to the $\Delta$log(sSFR) profiles.
+In the Middle panel we plot the log(sSFR) profile for the stacked profiles of the control galaxies (black).
+We then add the modeled $\Delta$log(sSFR) profile to the control profile (red).
+The error bars represent the standard error of the mean of the profiles.
+In the Right panel we show the fractional mass gain due to star formation in the control galaxies (black) and in the paired galaxies (red).
+The blue profile is the subtraction between the pairs and controls and represents the fractional mass gain due to merger induced star formation.
+The error bars represent the standard error of the mean of the profiles.
+}
+\label{fig:mass_gain}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/mass_gain.pdf}
+\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass gain due to merger induced star formation over a dynamical timescale, $\tau$ $=$ 1 Gyr.
+The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
+}
+\label{fig:mass_gain_sum}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2020-05-13 maintex.tex
data section

--- 2020-05-12 maintex.tex
@@
 \begin{abstract}
-
+We study the spatial profile of the star formation rate (SFR) in a sample of XXX interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
+We find that the specific star formation rate (sSFR) is centrally enhanced in the centers of the interacting galaxies by $\sim$XXX and in their disks by $\sim$XXX.
+We further investigate how these profiles behave as a function of stellar mass, mass ratio, and projected separation.
+We find that the sSFR profiles are unaffected by the stellar masses of the interacting galaxies; however, they are affected by the mass ratio between the galaxies where the galaxies with the smallest mass ratio feature the largest enhancement.
+We also find that, in pairs with large mass ratios (XX$-$XX), the less massive galaxy of the pair has slightly higher levels of sSFR enhancement, $\sim$0.1 dex.
+We also find that the level of sSFR enhancement increases with closer projected separations; however, the closest pairs, $\le$5 kpc, show no signs of sSFR enhancement/suppression.
+We suspect that these close pairs are merging galaxies which have passed their first pericenter, but haven't had enough time pass for the merger-induced gas inflows to trigger new star formation.
+We also set a simple model for the future mass growth of the interacting galaxies due to the merger-induced star formation.
+We predict that the paired galaxies in our sample will see a mass growth rate which is XX$\times$ higher than secular mass growth.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
+
+%%%Galaxy Evolution%%%
+In the $\Lambda$CDM model, galaxy evolution is a hierarchical process.
+Over the lifetime of the universe, smaller galaxies have iteratively merged with each other to form more massive galaxies.
+In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 (e.g.
+\citet{Rodriguez-Gomez:2016}; \citet{Pillepich:2018}).
+
+%%%Simulations%%%
+The internal dynamics of these interacting galaxies were first modeled in the seminal work, \citet{Toomre:1972}.
+Since then, hydrodynamical simulations have expanded upon the N-body simulations of \citet{Toomre:1972} by modeling gas-dynamics within the galaxies.
+These simulations show how barred structures develop within the disks of the interacting galaxies due to the tidal torques between them \citep{Barnes:1991}.
+As the bars form, the gases within the galaxy's disk lose angular momentum and get funneled into the centers of the galaxies.
+
+When the gas-inflows impact upon the gases in the nucleus of galaxy a burst of new star formation in triggered \citep{Barnes:1996, Mihos:1996}.
+These gas inflows will also bring metal-poor gases from the disk into the center of the galaxy which can dilute the central metallicity \citep{Rupke:2010, Perez:2011, Scudder:2012}.
+The gas-inflows may also be able to make it into very center of the galaxy and trigger supermassive black hole (SMBH) accretion \citep{Capelo:2017}.
+
+%%%Observations%%%
+Centrally enhanced star formation has also been observed in large spectroscopic surveys including; CfA2  \citep{Barton:2000, Woods:2006}, 2dF \citep{Lambas:2003}, AEGIS \citep{Lin:2007}, SDSS \citep{Ellison:2008}, COSMOS \citep{Kartaltepe:2007,Xu:2012}, PRIMUS \citep{Wong:2011}, and GAMA \citep{Robotham:2014}.
+
+This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable at wide projected separations of 150 kpc \citep{Patton:2013}.
+The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta log {\it M} |$, between the two galaxies \citep{Ellison:2008}.
+
+%%%Integral Field Spectroscopy%%%
+With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can be studied in unprecedented spatial detail.
+Where previous spectroscopic surveys were limited to the nucleus of the interacting galaxies, the new IFS surveys will be able to study both the nuclei and the disks of the interacting galaxies.
+
+The IFS surveys, CALIFA\footnote{Calar Alto Legacy Integral Field Area} and MaNGA\footnote{Mapping Nearby Galaxies at Apache Point Observatory}, have already been used to study the SFR of interacting galaxies in merging galaxies.
+The SFR was found to be centrally enhanced by a factor of 2$-$3$\times$ \citep{Barrera-Ballesteros:2015, Pan:2019}, which is in agreement with previous single-fiber spectroscopic surveys.
+These surveys also studied the SFR in the disk of the paired galaxies; however, there is a discrepancy between the results.
+\citet{Barrera-Ballesteros:2015} found a suppression to the SFR of $\sim$0.74$\times$ while \citet{Pan:2019} found an enhancement of 1.22$-$1.58$\times$.
+
+{\it can I mention Barrera-Ballesteros+15 and Pan+19 together like this since the BB uses ewha as a proxy for SFR and Pan uses sSFR?}
+
+The MaNGA survey has also been used to study the radial profiles of SFR in post merger galaxies, which are the galaxies which have recently coalesced.
+The post merger galaxies showed a central enhancement to the SFR surface density of 2.5$\times$ and an enhancement in their disks of 1.26$\times$ \citep{Thorp:2019}.
+
+%%%Purpose%%%
+In our previous work, \citet{Fu:2018}, we built a sample of paired galaxies in the MaNGA survey where both components of the pair were contained within field of view of a single IFU.
+We found that approximately 5.7\% of the MaNGA galaxies have a companion galaxies contained with the IFU.
+In this work, we will use a version of this sample updated for the recent MaNGA Data Release 16 (DR16) and further supplement this with a sample of companion galaxies identified outside the field of view of the IFUs.
+
+In this work we will expand upon the previous works by studying how the spatial profile of SFR behaves as a function of the stellar mass of the paired galaxy, the mass ratio between the galaxy pairs, and the projected separation between the galaxies.
+We will also model how the merger-induced star formation will affect the future mass growth of the interacting galaxies.
+
+% Organization
+This paper is organized as follows; in Section \ref{sec:data} we will discuss the detail of the MaNGA survey, in Section \ref{sec:analysis} we will discuss how we extract emission lines from the MaNGA survey and how we calculate the star formation from them, in Section \ref{sec:pair} we discuss the construction of our pair sample, in Section \ref{sec:control} we discuss the construction of our control sample, in Section \ref{sec:radial} we build the radial profiles for the pair and control galaxies, in Section \ref{sec:results} we discuss the results of the survey, in Section \ref{sec:discussion} we discuss our results in the context of other surveys, and in Section \ref{sec:sum} we summarize and conclude the work.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data}
+\section{Data}\label{sec:data}
+
+MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS 2.5 meter telescope along with two dual-channel BOSS spectrographs.
+MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively.
+MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA with a resolution of R $\sim$ 2000 and a median spectra coverage of 2.5\arcsec FWHM \citep{Bundy:2015}.
+
+MaNGA targets galaxies from a subset of 41,154 galaxies with from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the NSA survey's elliptical Petrosian apertures.
+MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
+In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.
+
+The MaNGA sample is split into three subsamples; the Primary Sample, Secondary Sample, and Color-Enhanced Sample.
+The Primary sample contains the galaxies which are covered out to 1.5 \reff\ and makes up 47\% of the survey.
+The Secondary contains the galaxies which are covered out to 2.5 \reff\ and makes up 37\% of the survey.
+The Color-Enhanced sample is designed to select rarer galaxy types with a spatial coverage of 2.5 \reff\ and makes up 16\% of the survey.
+
+Because of the survey's flat stellar mass distribution and uniform spatial coverage, these samples have a unique ``banana" shaped distribution in redshift and luminosity, see Figure \ref{fig:Mi-z}.
+Because the Secondary and Color-Enhanced samples use a wider spatial coverage than the Primary sample, the Secondary and Color-Enhanced Samples will posses galaxies of higher redshifts than galaxies at the same stellar masses in the Primary sample.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Emission Lines}
+\section{Emission Lines}\label{sec:analysis}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pair Sample}
+\section{Pair Sample}\label{sec:pair}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Control Sample}
+\section{Control Sample}\label{sec:control}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Radial Profiles}
+\section{Radial Profiles}\label{sec:radial}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Results}\label{sec:results}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Conclusion}
+\section{Summary and Conclusion}\label{sec:sum}
 
@@
 
+\hbox{}\clearpage
+
+\appendix
+
+\section{Figures}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/Mi-z.pdf}
+\caption[The luminosity - redshift distribution and mass - redshift distribution of the MaNGA sample.]{On the left is the luminosity - redshift distribution of the MaNGA sample.
+The figure illustrates the unique distribution of the MaNGA sample.
+On the right, I replace the luminosity with stellar mass from the NSA catalog.}
+\label{fig:Mi-z}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/color-mag.pdf}
+\caption[Color-magnitude distribution of the MaNGA galaxies]{Color-magnitude diagram for MaNGA galaxies ({\it colored circles}).
+The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+The MaNGA galaxies with close companions are marked with {\it grey diamonds}.
+From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
+The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
+\label{fig:CMD}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/bpt_spax.pdf}
+\caption[BPT classification of MaNGA spaxels.]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
+The color of each bin represents the number density of spaxels, normalized to one.
+The black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001}.
+This shows the capability of the CMD to select star-forming galaxies as most of the spaxels within the selected galaxies fall beneath the starburst line.}
+\label{fig:bpt_spax}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/pair_collage.pdf}
+\caption[A collage of a subset of the inside-IFU pairs.]{A collage of a subset of the inside-IFU pairs.
+Each panel contains a 40$^{\arcsec}$ cutout of the SDSS pseudocolor image for the galaxy pair.
+The minor ticks on each panel's axis represents 2$^{\arcsec}$.
+The green squares highlight the identified galaxy pairs.
+}
+\label{fig:collage}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=3in]{fig/mag_comp.pdf}
+\caption[The comparison between the r-band magnitudes in Simard+11 and NSA catalog]{The comparison between the S\'ersic r-band apparent magnitude in \citet{Simard:2011} and the Elliptical Petrosian r-band apparent magnitude.
+The grey circles represent galaxies in the control sample, the blue squares represent galaxies in the outside-IFU sample, and the red diamonds represent the galaxies in the inside-IFU sample.
+Regardless of the sample, all of the galaxies covered by both of the catalogs have a similar apparent magnitude calculated from either sample.}
+\label{fig:mag_comp}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/8083-12703.pdf}
+\caption[Example of the difference profiles for the mass-redshift selected control sample.]{The process for building the tailored control sample.
+The Left panel shows the paired galaxy's profile for sSFR.
+The Middle panel shows the profiles for sSFR for the selected 20 control galaxies in gray.
+The red profile is the median profile of the 20 control galaxies where the highlighted region about the profile is the standard error of the mean.
+The Right panel shows the difference between pair's profile and the stacked control profile.}
+\label{fig:dex}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/8485-3704.pdf}
+\caption[Example of bootstrapping to quantify the deviation of the random subsample of controls]{An example of the bootstrapping used to quantify the errors associated with the random selection of the control subsample.
+From left to right, the first four panels show the individual dex profiles after a random sub-selection in grey.
+The random sub-selection is run 1000 times and the median profile after the 1000 cycles is given by the colored profile.
+The highlighted region about the colored profiles is the standard error of the mean of the median profile.
+From left to right each panel shows the random selection for a different number of controls to select; 5, 10, 20, and 50 controls.
+The panel on the right end shows the median profiles of all of the preceding panels.
+}
+\label{fig:bootstrap}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
+\caption[The $\Delta$log(sSFR) split by stellar mass.]{The $\Delta$log(sSFR) split into separate stellar mass bins.
+The left column gives the stacked difference profiles.
+The highlighted region about the profiles represents the standard error of the mean of the profile.
+The right column gives the nuclear $\Delta$log(sSFR) values.
+The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
+The vertical error bars on the black squares represent the standard deviation within the bin.
+The top row is the inside-IFU sample, the middle row is the outside-IFU sample, and the bottom row is the combination of the two samples.}
+\label{fig:ssfr_mass}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
+\caption[The $\Delta$log(sSFR) split by mass ratio.]{Same as Figure \ref{fig:ssfr_mass} but split into separate mass ratio bins.}
+\label{fig:ssfr_dm}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
+\caption[The $\Delta$log(sSFR) split by projected separation.]{Same as Figure \ref{fig:ssfr_mass} but split into separate projected separation bins.}
+\label{fig:ssfr_sep}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/mass_gain_1.pdf}
+\caption[Example of the calculation of the fractional mass gain due to merger induced star formation for a single mass bin.]{In the Left panel we fit a model gaussian to the $\Delta$log(sSFR) profiles.
+In the Middle panel we plot the log(sSFR) profile for the stacked profiles of the control galaxies (black).
+We then add the modeled $\Delta$log(sSFR) profile to the control profile (red).
+The error bars represent the standard error of the mean of the profiles.
+In the Right panel we show the fractional mass gain due to star formation in the control galaxies (black) and in the paired galaxies (red).
+The blue profile is the subtraction between the pairs and controls and represents the fractional mass gain due to merger induced star formation.
+The error bars represent the standard error of the mean of the profiles.
+}
+\label{fig:mass_gain}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/mass_gain.pdf}
+\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass gain due to merger induced star formation over a dynamical timescale, $\tau$ $=$ 1 Gyr.
+The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
+}
+\label{fig:mass_gain_sum}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2020-05-13 maintex.tex
started Analysis section

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Emission Lines}\label{sec:analysis}
+\section{Analysis}\label{sec:analysis}
+\subsection{Emission Lines}
+We use our own {\sc IDL} based spectral fitting code, {\sc SPFIT}, to model the spectra from the MaNGA datacubes.
+{\sc SPFIT} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
+Emission line are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
+The algorithm provides us with measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and kinematics of the stellar populations.
+
+\subsection{Stellar Masses}
+
+\subsection{Star Formation Rates}
 

### 2020-05-20 maintex.tex
added pairs sections

@@
 %\newcommand{\arcsec}{\prime\prime}
+\newcommand{\simard}{Simard+11}
 
@@
 
+%%% NSA and Simard+11
+We further use photometric data from the NSA catalog and \citet{Simard:2011} (from now on \simard).
+We use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard\ to quantify the geometry of the outside-IFU and inside-IFU samples respectively.
+We further use the total stellar masses extracted from these apertures to quantify the total stellar masses of the galaxies, the NSA catalog contains their own calculation for stellar mass and we use the stellar mass calculation from \citet{Mendel:2014} for the \simard\ apertures.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Emission Lines}
+
+%%% SPFIT
 We use our own {\sc IDL} based spectral fitting code, {\sc SPFIT}, to model the spectra from the MaNGA datacubes.
@@
 
-\subsection{Stellar Masses}
+%%% Reddening
+We use the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
+The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1 where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ to the expected value of 2.85 for case-B recombination.
+We apply the extinction correction to all of the extracted emission lines.
 
 \subsection{Star Formation Rates}
+We classify galaxies as star forming using both the color-magnitude diagram (CMD) and the BPT diagram \citep{Baldwin:1981}.
+We show the CMD in Figure \ref{fig:cmd} along with demarcation lines which separate the blue cloud, red sequence, and green valley.
+We established the demarcation lines by collapsing the CMD to a color histogram for each of the three regions and then varied the slopes between the regions until we found the slopes which best fit the data.
+These demarcation lines are;
+
+\begin{equation}\label{eq:blue}
+NUV-r = 3.1682 - 0.16 (M_i+18)
+\end{equation}
+\begin{equation}\label{eq:red}
+NUV-r = 4.7866 - 0.04 (M_i+18)
+\end{equation}
+
+Where NUV$-$r is the color and M$_i$ is the i-band magnitude.
+
+The BPT diagnostic uses emission line ratios to separate ionization sources, star formation and active galactic nuclei (AGN).
+The two ionization sources can be separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.
+
+\begin{equation}\label{eq:kewley}
+\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
+\end{equation}
+\begin{equation}\label{eq:kauffmann}
+\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.05} + 1.3}
+\end{equation}
+
+Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes extracted from the spectra within the inner 2 arcseconds of the galaxies.
+It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic HII regions and AGN on the BPT diagram \citep{Stasinska:2008}.
+We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\angstrom to remove these retired galaxies \citet{Cid-Fernandes:2011}.
+In this work, we define star forming galaxies as those which are on the blue cloud in the CMD and which is below the \citet{Kewley:2001} on the BPT diagram.
+
+We measure the SFR from the H$\alpha$ luminosity, L$_{H\alpha}$.
+The H$\alpha$ luminosity is calculated from the flux of the H$\alpha$ emission line.
+We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.
+
+\begin{equation}\label{eq:sfr}
+\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
+\end{equation}
+
+We normalize the SFR by the local stellar mass (the stellar mass contained with a given spaxel), calculated from SPFIT, giving us the specific star formation rate (sSFR).
+
+\begin{equation}
+sSFR = \frac{SFR}{M^*}
+\end{equation}
+
+This will allow us to compare the SFR in high mass regions, like the centers of the galaxies, to the SFR lower mass regions, like the disk of the galaxies.
 
@@
 \section{Pair Sample}\label{sec:pair}
+
+\subsection{Inside-IFU Sample}\label{sec:inside}
+In our previous work, \citet{Fu:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
+In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
+
+We use SDSS photometric objects to create a catalog of objects within the fields of view of the MaNGA IFUs.
+The extract their spectra from the MaNGA datacubes through a 1\arcsec aperture and fit the spectra with {\sc SPFIT}.
+The spectra is then sorted into different categories; ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects.
+The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxies itself or a nearby companion galaxy.
+This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target.
+We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.
+
+From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU and within a relative velocity of $\Delta$v $<$ 500 km s$^{-1}$.
+124 of the galaxies are star forming galaxies (SFGs).
+Finally, 87 SFGs are covered by \simard\ and \citet{Mendel:2014}.
+
+Some of the galaxies in our sample have multiple companions. From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
+
+\subsection{Outside-IFU Sample}\label{sec:outside}
+
+The second pairs sample is the outside-IFU pairs sample.
+This sample includes MaNGA galaxies which have companion galaxies found outside the field of view of its IFU.
+We identify these external pair from the NSA catalog.
+We select galaxies which are within a projected separation, r$_p$ $<$ 50 kpc, and within a relative velocity, $\Delta$v $<$ 500 km s$^{-1}$.
+
+The NSA catalog contains 641,409 galaxies from which we find 509 galaxies which are paired to MaNGA targets.
+169 of the MaNGA target in these pairs are SFGs.
+Eight of these galaxies also had a companion galaxy within the IFU, so they are removed from the outside-IFU sample and left to the inside-IFU sample.
 
@@
 The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
-\label{fig:CMD}
+\label{fig:cmd}
 \end{figure}

### 2020-05-29 maintex.tex
added results section

@@
 \begin{abstract}
-We study the spatial profile of the star formation rate (SFR) in a sample of XXX interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
-We find that the specific star formation rate (sSFR) is centrally enhanced in the centers of the interacting galaxies by $\sim$XXX and in their disks by $\sim$XXX.
+We study the spatial profile of the star formation rate (SFR) in a sample of 202 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
+We find that the specific star formation rate (sSFR) is centrally enhanced in the interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
 We further investigate how these profiles behave as a function of stellar mass, mass ratio, and projected separation.
 We find that the sSFR profiles are unaffected by the stellar masses of the interacting galaxies; however, they are affected by the mass ratio between the galaxies where the galaxies with the smallest mass ratio feature the largest enhancement.
-We also find that, in pairs with large mass ratios (XX$-$XX), the less massive galaxy of the pair has slightly higher levels of sSFR enhancement, $\sim$0.1 dex.
+We also find that, in pairs with large mass ratios ($|\Delta$log(M)$|$ $=$ 0.5 $-$ 1.5), the less massive galaxy of the pair has slightly higher levels of sSFR enhancement, $\sim$0.1 dex.
 We also find that the level of sSFR enhancement increases with closer projected separations; however, the closest pairs, $\le$5 kpc, show no signs of sSFR enhancement/suppression.
-We suspect that these close pairs are merging galaxies which have passed their first pericenter, but haven't had enough time pass for the merger-induced gas inflows to trigger new star formation.
-We also set a simple model for the future mass growth of the interacting galaxies due to the merger-induced star formation.
+We suspect that these close pairs are merging galaxies which have passed their first pericenter, but the merger induced gas-inflows have yet to reach the centers of the galaxies.
+We also set a simple model for the future mass growth of the galaxies due to the merger induced star formation.
 We predict that the paired galaxies in our sample will see a mass growth rate which is XX$\times$ higher than secular mass growth.
@@
 In the $\Lambda$CDM model, galaxy evolution is a hierarchical process.
-Over the lifetime of the universe, smaller galaxies have iteratively merged with each other to form more massive galaxies.
+Over the lifetime of the universe, smaller galaxies have iteratively merged forming more massive galaxies.
 In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 (e.g.
@@
 
-This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable at wide projected separations of 150 kpc \citep{Patton:2013}.
+This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable at projected separations of 150 kpc \citep{Patton:2013}.
 The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta log {\it M} |$, between the two galaxies \citep{Ellison:2008}.
@@
 %%%Integral Field Spectroscopy%%%
-With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can be studied in unprecedented spatial detail.
+With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can be studied with unprecedented spatial detail.
 Where previous spectroscopic surveys were limited to the nucleus of the interacting galaxies, the new IFS surveys will be able to study both the nuclei and the disks of the interacting galaxies.
@@
 \citet{Barrera-Ballesteros:2015} found a suppression to the SFR of $\sim$0.74$\times$ while \citet{Pan:2019} found an enhancement of 1.22$-$1.58$\times$.
-
-{\it can I mention Barrera-Ballesteros+15 and Pan+19 together like this since the BB uses ewha as a proxy for SFR and Pan uses sSFR?}
 
@@
 \subsection{Emission Lines}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
+\caption[]{\textbf{Left:} Color-magnitude diagram for MaNGA galaxies ({\it colored circles}).
+The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+The MaNGA galaxies with close companions are marked with {\it grey diamonds}.
+From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
+The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.
+\textbf{Right:} The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
+The color of each bin represents the number density of spaxels, normalized to one.
+The solid black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001} and the dashed black line is the analytical \citet{Kauffmann:2003} line.
+This shows the capability of the CMD to select star-forming galaxies as most of the spaxels within the selected galaxies fall beneath the starburst line.}
+\label{fig:cmd}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 124 of the galaxies are star forming galaxies (SFGs).
-Finally, 87 SFGs are covered by \simard\ and \citet{Mendel:2014}.
+Finally, 41 SFGs are covered by \simard\ and \citet{Mendel:2014}.
 
 Some of the galaxies in our sample have multiple companions. From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
+
+We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}
 
@@
 The NSA catalog contains 641,409 galaxies from which we find 509 galaxies which are paired to MaNGA targets.
-169 of the MaNGA target in these pairs are SFGs.
-Eight of these galaxies also had a companion galaxy within the IFU, so they are removed from the outside-IFU sample and left to the inside-IFU sample.
+MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
+After restricting the sample to SFGs, we have 161 MaNGA targets with paired galaxies outside of the IFU.
+
+We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample.
+We also use the stellar masses from the NSA catalog for the total stellar mass of the galaxies.
 
@@
 \section{Control Sample}\label{sec:control}
+We build a sample of isolated control galaxies from the remaining MaNGA galaxies.
+Selecting the MaNGA galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
+This gives us a set of 1862 SFGs and 1598 SFGs which are covered by both \simard\ and \citet{Mendel:2014}.
+
+The SFR in galaxies has been shown to be dependent on both stellar mass and redshift \citep{Noeske:2007}.
+To account for this we will need to match pairs with similar mass and redshift controls.
+To do this we build a subset of 20 control galaxies for each paired galaxy.
+
+First we select every control galaxy which is within a stellar mass of 0.1 dex and within in same MaNGA subsample, i.e.
+the Primary or Secondary sample.
+Knowing that MaNGA has a tight ``banana" shaped distribution in stellar mass and redshift, imposing the stellar mass cut and the MaNGA subsample cut will effectively set a $\sim$0.025 dex redshift cut.
+
+We then downselect the control subset down to 20 controls using a random number generator so that each paired galaxies has the same number of selected controls.
+In the few cases where a paired galaxy fails to find at least 20 control galaxies, we iteratively expand the stellar mass limits by 0.1 dex until a set of 20 control galaxies can be made.
+A small set of paired required extra iterations to find 20 controls; 8 paired galaxies need an extra iteration, 1 paired galaxy need two extra iterations, and 1 paired galaxy needed three iterations.
+\\
+
+The control galaxies will be treated using both the \simard\ aperture and \citet{Mendel:2014} masses when comparing them to the inside-IFU sample and the NSA apertures and masses when comparing them to the outside-IFU sample.
 
@@
 
+As mentioned in Sections \ref{sec:pair} and \ref{sec:control} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \simard to define the geometries of the galaxies.
+We calculate the inclination angle, {\it i}, of the galaxies using the major-to-minor axis ratios from the elliptical apertures;
+
+\begin{equation}
+{\rm cos^2}(i) = \frac{(b/a)^2 - q^2}{1 - q^2}
+\end{equation}
+
+The inclination angle is used to deproject the geometries of the galaxies.
+We use our catalog of photometric objects and the \simard\ catalog to mask foregournd/background objects.
+Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \simard\ are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
+
+The distance to each of the spaxels from the center of the MaNGA targets is calculated using the 50\% half light radius to scale the galaxies.
+The spaxels are binned into radius increments of 0.1 \reff\ from 0.0$-$2.4\reff.
+Within each radius bin we take the median of the specific star formation rate.
+The profiles' errors are the standard error of the mean of the data within each radius bin.
+We create one of these individual averaged radial profiles for every MaNGA galaxy.
+
+We then construct difference profiles between the paired galaxies and the control galaxies.
+As mentioned in Section \ref{sec:control}, a paired galaxy is matched to 20 similar control galaxies.
+We take the individual averaged profiles of the control galaxies and take the median value of the profiles at each radius bin giving us a ``stacked" profile of control galaxies.
+The error of the profile is the standard error of the mean of the individual profiles.
+We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of stacked profile over 1000 iterations.
+The difference profile is then the difference between a single paired galaxy's profile and the stacked profile in log space (this means that the difference profiles are ratios in linear space).
+This is done for each of the 202 galaxy pairs.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}\label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_unsplit.pdf}
+\caption[]{\textbf{Left:} The individual difference profiles are shown in light grey while the stacked profile for the whole pair sample is shown in red.
+The highlighted region about the profile is the standard error of the mean of the stacked profile.
+\textbf{Right:} A histogram of the $\delta$log(sSFR) within the inner 0.5 \reff\ of the individual difference profiles.
+The red line shows the median value of the $\Delta$log(sSFR) enhancement, $\sim$0.25 dex.}
+\label{fig:ssfr_all}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We take each of the individual difference profiles for all of the and take the median value of the sSFR within each radius bin.
+This gives a single profile which describes the sSFR enhancements for the whole pair sample.
+We show this profile in the left hand panel of Figure \ref{fig:ssfr_all}.
+The sSFR is centrally enhanced by $\sim$0.25 dex.
+The enhancement falls to zero around 1.0\reff.
+The disks of the paired galaxies feature no enhancement or suppression to the sSFR.
+
+In the right hand panel of Figure \ref{fig:ssfr_all} we show a histogram for the $\Delta$log(sSFR) offset in the centers of the paired galaxies.
+To get this, we extract the values of $\Delta$log(sSFR) in the individual difference profiles within the inner 0.5 R/\reff\ and take the mean of the values.
+
+In the following sections we will break up the stacked profile into separate bins of total stellar mass, mass ratio, and projected separation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_full.pdf}
+\caption[]{The $\Delta$log(sSFR) split into separate stellar mass bins.
+The left column gives the stacked difference profiles.
+The highlighted region about the profiles represents the standard error of the mean of the profile.
+The black dashed line represents the stacked profile of the full pair sample.
+The right column gives the nuclear $\Delta$log(sSFR) values.
+The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
+The vertical error bars on the black squares represent the standard deviation within the bin.
+The horizontal, dashed black lines represent the median central enhancement of the full pair sample.
+The top row shows the paired galaxies split by total stellar mass, the middle panel shows the paired galaxies split by mass ratio, and the bottom panel shows the paired galaxies split by projected separation.
+}
+\label{fig:ssfr_full}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Stellar Mass}
+We show the $\Delta$log(sSFR) profile split by the galaxy's total stellar mass in the top row of Figure \ref{fig:ssfr_full}.
+The level of the central sSFR enhancement is consistent with the level of enhancement for the full sample.
+This effect is better seen in the scatter plot of the central $\Delta$log(sSFR) offsets versus stellar mass where there is a flat distribution.
+
+In the disks of the paired galaxies, there is more scatter to the offsets of the profiles.
+The mass range, \logm\ $=$ 10.0$-$10.5, shows stronger suppression of sSFR in their disks while the mass range, \logm\ $=$ 9.0$-$9.5, show an enhancement to sSFR in their disks.
+There is no trend to sSFR enhancement/suppression with the stellar mass so the scatter in the profiles at large separation is likely due to a combination of the smaller sizes within separate mass bins and lower S/N at larger galactocentric radii.
+
+From this we infer that the total stellar mass of a paired galaxy has no effect on the merger induced star formation within the galaxy.
+Massive galaxies are enhanced to the same degree as low mass galaxies.
+
+\subsection{Mass Ratio}
+While the total stellar mass between the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
+In the middle row of Figure \ref{fig:ssfr_full} we see that the sSFR enhancement is strongest in galaxies with mass ratios close to 1:1, $\delta$log(M) $=$ 0.0.
+These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.15 dex higher than the average central enhancement of the whole sample.
+This enhancement falls with wider mass ratios and pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.2$-$0.25 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.
+
+We also use the mass ratio to explore how the merger induced tidal torques affect paired galaxies with large mass ratios, $|\Delta$log(M)$|$ > 0.5.
+We use the mass ratio to separate the massive central galaxy from satellite galaxies.
+A paired galaxy with a positive mass ratio is the more massive galaxy of the pair while a paired galaxy with negative mass ratio is the less massive galaxy.
+We see that the less massive galaxy of a pair show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to the more massive galaxy.
+This shows us that satellite galaxies are more susceptible to tidal interactions than the central galaxies in the pair system.
+
+\subsection{Projected Separation}
+Finally we look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_full}.
+The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
+
+This effect can be seen most clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
+The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc.
+Within 10 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.5 dex.
+Surprisingly, this central enhancement plummets back to zero at the closest separations, r$_p$ $<$ 5 kpc.
+We will discuss the potential causes of the zero enhancement in the centers of the closest galaxies in Section \ref{sec:discussion}.
+
+\subsection{Future Mass Growth}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/mass_gain_1.pdf}
+\caption[Example of the calculation of the fractional mass gain due to merger induced star formation for a single mass bin.]{In the Left panel we fit a model gaussian to the $\Delta$log(sSFR) profiles.
+In the Middle panel we plot the log(sSFR) profile for the stacked profiles of the control galaxies (black).
+We then add the modeled $\Delta$log(sSFR) profile to the control profile (red).
+The error bars represent the standard error of the mean of the profiles.
+In the Right panel we show the fractional mass gain due to star formation in the control galaxies (black) and in the paired galaxies (red).
+The blue profile is the subtraction between the pairs and controls and represents the fractional mass gain due to merger induced star formation.
+The error bars represent the standard error of the mean of the profiles.
+}
+\label{fig:mass_gain}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/mass_gain.pdf}
+\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass gain due to merger induced star formation over a dynamical timescale, $\tau$ $=$ 1 Gyr.
+The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
+}
+\label{fig:mass_gain_sum}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The merger induced star formation will increase the mass growth rate of the interacting galaxies.
+We will use a simple model to estimate the enhanced mass growth rate due to merger induced star formation.
+
+A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
+
+\begin{equation}
+\frac{\Delta M_{merger}}{M_{total}} = \left(sSFR_{pair} - sSFR_{control}\right) * \tau_{dyn}
+\end{equation}
+
+Where $\tau_{dyn}$ is the dynamical timescale of the merger event.
+For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in hydrodynamical simulations \citep{Boylan-Kolchin:2008}.
+
+To get the difference in sSFR between the pairs and controls, we fit a gaussian to the difference profiles split by stellar mass.
+We then add the modeled difference profile to the stacked control profile in the same mass range in log space.
+We then take the difference between the profiles in linear space and multiple the difference by the 1 Gyr timescale.
+This process is shown for a single mass range in Figure \ref{fig:mass_gain}.
+
+We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
+The mass growth rate is largely restricted to the centers of the galaxies, following the centrally enhanced sSFR.
+The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
+
+The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.065, while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.015.
+This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.
+
+Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth.
+While low mass galaxies may see a more substantial change to their total stellar mass, the more massive galaxies experience higher growth rates.
 
@@
 \label{fig:Mi-z}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/color-mag.pdf}
-\caption[Color-magnitude distribution of the MaNGA galaxies]{Color-magnitude diagram for MaNGA galaxies ({\it colored circles}).
-The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-The MaNGA galaxies with close companions are marked with {\it grey diamonds}.
-From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
-The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
-\label{fig:cmd}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/bpt_spax.pdf}
-\caption[BPT classification of MaNGA spaxels.]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
-The color of each bin represents the number density of spaxels, normalized to one.
-The black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001}.
-This shows the capability of the CMD to select star-forming galaxies as most of the spaxels within the selected galaxies fall beneath the starburst line.}
-\label{fig:bpt_spax}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
-\caption[The $\Delta$log(sSFR) split by stellar mass.]{The $\Delta$log(sSFR) split into separate stellar mass bins.
-The left column gives the stacked difference profiles.
-The highlighted region about the profiles represents the standard error of the mean of the profile.
-The right column gives the nuclear $\Delta$log(sSFR) values.
-The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
-The vertical error bars on the black squares represent the standard deviation within the bin.
-The top row is the inside-IFU sample, the middle row is the outside-IFU sample, and the bottom row is the combination of the two samples.}
-\label{fig:ssfr_mass}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
-\caption[The $\Delta$log(sSFR) split by mass ratio.]{Same as Figure \ref{fig:ssfr_mass} but split into separate mass ratio bins.}
-\label{fig:ssfr_dm}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
-\caption[The $\Delta$log(sSFR) split by projected separation.]{Same as Figure \ref{fig:ssfr_mass} but split into separate projected separation bins.}
-\label{fig:ssfr_sep}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/mass_gain_1.pdf}
-\caption[Example of the calculation of the fractional mass gain due to merger induced star formation for a single mass bin.]{In the Left panel we fit a model gaussian to the $\Delta$log(sSFR) profiles.
-In the Middle panel we plot the log(sSFR) profile for the stacked profiles of the control galaxies (black).
-We then add the modeled $\Delta$log(sSFR) profile to the control profile (red).
-The error bars represent the standard error of the mean of the profiles.
-In the Right panel we show the fractional mass gain due to star formation in the control galaxies (black) and in the paired galaxies (red).
-The blue profile is the subtraction between the pairs and controls and represents the fractional mass gain due to merger induced star formation.
-The error bars represent the standard error of the mean of the profiles.
-}
-\label{fig:mass_gain}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/mass_gain.pdf}
-\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass gain due to merger induced star formation over a dynamical timescale, $\tau$ $=$ 1 Gyr.
-The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
-}
-\label{fig:mass_gain_sum}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2020-06-05 maintex.tex
added discussion and conclusion

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We take each of the individual difference profiles for all of the and take the median value of the sSFR within each radius bin.
-This gives a single profile which describes the sSFR enhancements for the whole pair sample.
-We show this profile in the left hand panel of Figure \ref{fig:ssfr_all}.
-The sSFR is centrally enhanced by $\sim$0.25 dex.
-The enhancement falls to zero around 1.0\reff.
-The disks of the paired galaxies feature no enhancement or suppression to the sSFR.
-
-In the right hand panel of Figure \ref{fig:ssfr_all} we show a histogram for the $\Delta$log(sSFR) offset in the centers of the paired galaxies.
-To get this, we extract the values of $\Delta$log(sSFR) in the individual difference profiles within the inner 0.5 R/\reff\ and take the mean of the values.
-
-In the following sections we will break up the stacked profile into separate bins of total stellar mass, mass ratio, and projected separation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We take each of the individual difference profiles for all of the and take the median value of the sSFR within each radius bin.
+This gives a single profile which describes the sSFR enhancements for the whole pair sample.
+We show this profile in the left hand panel of Figure \ref{fig:ssfr_all}.
+The sSFR is centrally enhanced by $\sim$0.25 dex.
+The enhancement falls to zero around 1.0\reff.
+The disks of the paired galaxies feature no enhancement or suppression to the sSFR.
+
+In the right hand panel of Figure \ref{fig:ssfr_all} we show a histogram for the $\Delta$log(sSFR) offset in the centers of the paired galaxies.
+To get this, we extract the values of $\Delta$log(sSFR) in the individual difference profiles within the inner 0.5 R/\reff\ and take the mean of the values.
+
+In the following sections we will break up the stacked profile into separate bins of total stellar mass, mass ratio, and projected separation.
 
@@
 
+% Nuclear comp with prev works
+The enhancement to the sSFR in the centers of the whole pair sample is consistent with previous galaxy merger studies \citet{Ellison:2008, Barrera-Ballesteros:2015, Pan:2019}.
+
+Different IFS studies have found different sSFR offsets in the disks of the paired galaxies.
+\citet{Barrera-Ballesteros:2015} found that the sSFR (using \ewha\ as a proxy) is suppressed in the disks of paired galaxies by $\sim$-0.13 dex.
+In contrast, \citet{Pan:2019} found that the sSFR is enhanced by 0.15 dex.
+In this work, we see that  $\Delta$log(sSFR) is roughly zero but leans towards being suppressed, $\Delta$log(sSFR) $=$ -0.1$-$0.0 dex.
+
+In previous studies it was noted that the enhancement to the SFR is strongest in galaxy pairs with small mass ratios \citet{Ellison:2008}.
+We see the same effect; however, we have also shown that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement.
+Further, within these galaxy pairs with wide mass ratios we see that the less massive galaxy in the pair shows higher levels of sSFR enhancement.
+This implies that satellite galaxies are more affected by interaction induced star formation than the central galaxy.
+
+ We saw that the $\Delta$log(sSFR) enhancement increases with closer projected separations \citet{Ellison:2008, Scudder:2012, Patton:2013}.
+This is unsurprising as nearby galaxy pairs will have just completed a close interaction.
+This enhancement persists out to wide separations where galaxy pairs separated by 50 kpc still show a substantial enhancement to the sSFR.
+\citet{Patton:2013} showed that the central enhancements to sSFR persists out to 150 kpc.
+
+The closest pairs in our sample, pairs closer than 5 kpc, show no enhancement to the sSFR.
+This seems odd as one would think that these galaxies should show the strongest enhancements.
+The first thing to consider is that the sample contains no post-merger galaxies so we will not see the second large burst of star formation when the two galaxies are coalescing.
+The closest paired galaxies will either be pairs which are about to go through their first pericenter or galaxies which have just passed their first pericenter.
+In the galaxies which have passed their first pericenter, we believe that the timescale is still too small for the interaction induced gas inflows to travel from the galaxy's disk to its nucleus.
+Since the gas inflows haven't impacted the galaxy's nucleus, no enhancements to the sSFR will be seen.
+\citet{Scudder:2012} also found a delay in the burst of merger induced star formation in their hydrodynamical simulations.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary and Conclusion}\label{sec:sum}
+
+We studied a sample of paired, star forming galaxies using the MaNGA IFS survey.
+We have made a sample of 913 paired galaxies of which 202 are SFGs.
+We compared the radial profiles of the paired galaxies with 1862 isolated MaNGA SFGs.
+We found the following;
+
+\begin{enumerate}
+\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.25 $\pm$ 0.1 dex. 
+\item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show no signs of either sSFR enhancement or sSFR suppression. 
+\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies, Massive galaxies experience the same level of sSFR enhancement as low mass galaxies.
+\item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies.
+Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.4 $\pm$ 0.1 dex, which is 0.15 dex higher than the average paired galaxies in the survey.
+We have also showed that paired galaxies with large mass ratios, 1.0 $<$ $|\Delta$log(M)$|$ $<$ 2.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex.
+\item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair, $\sim$0.1 dex.
+\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$10 kpc have their sSFR enhanced by 0.5 $\pm$ 0.1 dex.
+The galaxies within 5 kpc experience no central enhancement to their sSFR.
+We believe that these galaxies have just passed their first pericenter and the merger induced gas-inflow have yet to reach the centers of these galaxies.
+\item The paired galaxies will experience a faster mass growth rate of secular evolution of 1.6$-$2.3$\times$.
+The growth rate is highest for massive galaxies; however, the the low mass galaxies will see the stellar mass in their center more substantially increased over a 1 Gyr timescale.
+
+\end{enumerate}
 
@@
 
-\hbox{}\clearpage
+%\hbox{}\clearpage
 
-\appendix
+%\appendix
 
-\section{Figures}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/Mi-z.pdf}
-\caption[The luminosity - redshift distribution and mass - redshift distribution of the MaNGA sample.]{On the left is the luminosity - redshift distribution of the MaNGA sample.
-The figure illustrates the unique distribution of the MaNGA sample.
-On the right, I replace the luminosity with stellar mass from the NSA catalog.}
-\label{fig:Mi-z}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/pair_collage.pdf}
-\caption[A collage of a subset of the inside-IFU pairs.]{A collage of a subset of the inside-IFU pairs.
-Each panel contains a 40$^{\arcsec}$ cutout of the SDSS pseudocolor image for the galaxy pair.
-The minor ticks on each panel's axis represents 2$^{\arcsec}$.
-The green squares highlight the identified galaxy pairs.
-}
-\label{fig:collage}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=3in]{fig/mag_comp.pdf}
-\caption[The comparison between the r-band magnitudes in Simard+11 and NSA catalog]{The comparison between the S\'ersic r-band apparent magnitude in \citet{Simard:2011} and the Elliptical Petrosian r-band apparent magnitude.
-The grey circles represent galaxies in the control sample, the blue squares represent galaxies in the outside-IFU sample, and the red diamonds represent the galaxies in the inside-IFU sample.
-Regardless of the sample, all of the galaxies covered by both of the catalogs have a similar apparent magnitude calculated from either sample.}
-\label{fig:mag_comp}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Figures}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/8485-3704.pdf}
-\caption[Example of bootstrapping to quantify the deviation of the random subsample of controls]{An example of the bootstrapping used to quantify the errors associated with the random selection of the control subsample.
-From left to right, the first four panels show the individual dex profiles after a random sub-selection in grey.
-The random sub-selection is run 1000 times and the median profile after the 1000 cycles is given by the colored profile.
-The highlighted region about the colored profiles is the standard error of the mean of the median profile.
-From left to right each panel shows the random selection for a different number of controls to select; 5, 10, 20, and 50 controls.
-The panel on the right end shows the median profiles of all of the preceding panels.
-}
-\label{fig:bootstrap}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2020-06-17 maintex.tex
added SDSS acknowledgement

@@
 We study the spatial profile of the star formation rate (SFR) in a sample of 202 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
-We find that the specific star formation rate (sSFR) is centrally enhanced in the interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
-We further investigate how these profiles behave as a function of stellar mass, mass ratio, and projected separation.
-We find that the sSFR profiles are unaffected by the stellar masses of the interacting galaxies; however, they are affected by the mass ratio between the galaxies where the galaxies with the smallest mass ratio feature the largest enhancement.
-We also find that, in pairs with large mass ratios ($|\Delta$log(M)$|$ $=$ 0.5 $-$ 1.5), the less massive galaxy of the pair has slightly higher levels of sSFR enhancement, $\sim$0.1 dex.
+We find that the specific star formation rate (sSFR) is centrally enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
+We further investigate how these profiles behave as a function of their stellar mass, mass ratio, and projected separation.
+We find that the sSFR profiles are unaffected by the stellar masses of the interacting galaxies; however, they are affected by the mass ratio between the galaxies where the galaxies with the smallest mass ratios feature the largest enhancement to their sSFR.
+We also find that, in pairs with large mass ratios ($|\Delta$log(M)$|$ $=$ 0.5 $-$ 1.5), the less massive galaxy of the pair has slightly higher levels of sSFR enhancement, $\sim$0.1 dex, than the more massive galaxies in the pair.
 We also find that the level of sSFR enhancement increases with closer projected separations; however, the closest pairs, $\le$5 kpc, show no signs of sSFR enhancement/suppression.
-We suspect that these close pairs are merging galaxies which have passed their first pericenter, but the merger induced gas-inflows have yet to reach the centers of the galaxies.
-We also set a simple model for the future mass growth of the galaxies due to the merger induced star formation.
-We predict that the paired galaxies in our sample will see a mass growth rate which is XX$\times$ higher than secular mass growth.
+We suspect that these close pairs are merging galaxies which have passed their first pericenter, but the merger induced gas-inflows have yet to reach the centers of these galaxies.
+We make a simple model for the future mass growth of the galaxies due to the merger induced star formation.
+We predict that the paired galaxies in our sample will see a mass growth rate in their centers which is 1.6$-$2.3$\times$ higher than secular mass growth, showing that the merger induced star formation can significantly alter the stellar mass distribution.
 \end{abstract}
@@
 In the $\Lambda$CDM model, galaxy evolution is a hierarchical process.
-Over the lifetime of the universe, smaller galaxies have iteratively merged forming more massive galaxies.
+In this model, massive galaxies are the product of several past merger events of smaller galaxies.
 In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 (e.g.
@@
 %%%Observations%%%
-Centrally enhanced star formation has also been observed in large spectroscopic surveys including; CfA2  \citep{Barton:2000, Woods:2006}, 2dF \citep{Lambas:2003}, AEGIS \citep{Lin:2007}, SDSS \citep{Ellison:2008}, COSMOS \citep{Kartaltepe:2007,Xu:2012}, PRIMUS \citep{Wong:2011}, and GAMA \citep{Robotham:2014}.
+Centrally enhanced star formation has also been observed in galaxy pairs with large spectroscopic surveys including; CfA2  \citep{Barton:2000, Woods:2006}, 2dF \citep{Lambas:2003}, AEGIS \citep{Lin:2007}, SDSS \citep{Ellison:2008}, COSMOS \citep{Kartaltepe:2007,Xu:2012}, PRIMUS \citep{Wong:2011}, and GAMA \citep{Robotham:2014}.
 
-This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable at projected separations of 150 kpc \citep{Patton:2013}.
-The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta log {\it M} |$, between the two galaxies \citep{Ellison:2008}.
+This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable out to projected separations of 150 kpc \citep{Patton:2013}.
+The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta {\rm log} {\it M} |$, between the two galaxies \citep{Ellison:2008}.
+Similar mass galaxies show the strongest sSFR effects while large central galaxies interacting with small satellite galaxies show weaker sSFR effects.
+Because of this, most surveys will split their sample into major mergers, $|\Delta$log($M$)$|$ $\le$ 0.5, and minor mergers, 0.5 $\le$ $|\Delta$log($M$)$|$ $\le$ 1.0, where major mergers are expected to show the strongest interaction induced effects.
 
@@
 With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can be studied with unprecedented spatial detail.
-Where previous spectroscopic surveys were limited to the nucleus of the interacting galaxies, the new IFS surveys will be able to study both the nuclei and the disks of the interacting galaxies.
+These surveys allow astronomers to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture.
+These IFS surveys will also allow us to see the extent of the centrally induced star formation and to see how the star formation in the disks of the galaxies are affected.
 
 The IFS surveys, CALIFA\footnote{Calar Alto Legacy Integral Field Area} and MaNGA\footnote{Mapping Nearby Galaxies at Apache Point Observatory}, have already been used to study the SFR of interacting galaxies in merging galaxies.
-The SFR was found to be centrally enhanced by a factor of 2$-$3$\times$ \citep{Barrera-Ballesteros:2015, Pan:2019}, which is in agreement with previous single-fiber spectroscopic surveys.
-These surveys also studied the SFR in the disk of the paired galaxies; however, there is a discrepancy between the results.
+The SFR was found to be centrally enhanced by a factor of 2$-$3$\times$ \citep{Barrera-Ballesteros:2015, Pan:2019}, which is in agreement with the previous single-fiber spectroscopic surveys.
+These surveys also studied the SFR in the disk of the paired galaxies; however, there is a standing discrepancy between the different works.
 \citet{Barrera-Ballesteros:2015} found a suppression to the SFR of $\sim$0.74$\times$ while \citet{Pan:2019} found an enhancement of 1.22$-$1.58$\times$.
 
-The MaNGA survey has also been used to study the radial profiles of SFR in post merger galaxies, which are the galaxies which have recently coalesced.
-The post merger galaxies showed a central enhancement to the SFR surface density of 2.5$\times$ and an enhancement in their disks of 1.26$\times$ \citep{Thorp:2019}.
+The MaNGA survey has also been used to study the radial profiles of SFR in post-merger galaxies, which are the galaxies which have recently coalesced.
+Hydrodynamical simulations predict a second burst of star formation as the two galaxies coalesce.
+This effect has been observed in a sample of post-merger galaxies which showed a central enhancement to the SFR surface density of 2.5$\times$ and an enhancement in their disks of 1.26$\times$ \citep{Thorp:2019}.
 
 %%%Purpose%%%
-In our previous work, \citet{Fu:2018}, we built a sample of paired galaxies in the MaNGA survey where both components of the pair were contained within field of view of a single IFU.
-We found that approximately 5.7\% of the MaNGA galaxies have a companion galaxies contained with the IFU.
-In this work, we will use a version of this sample updated for the recent MaNGA Data Release 16 (DR16) and further supplement this with a sample of companion galaxies identified outside the field of view of the IFUs.
+In our previous work, \citet{Fu:2018}, we built a sample of paired galaxies in the MaNGA survey where both components of the pair were contained within field of view of a single integral field unit (IFU).
+We found that approximately 5.7\% of the MaNGA galaxies have a companion galaxy contained within the field-of-view of a single IFU.
+In this work, we will use a version of this sample updated for the recent MaNGA Data Release 16 (DR16) and we will further supplement this with a sample of companion galaxies identified outside the field-of-view of the MaNGA IFUs.
 
-In this work we will expand upon the previous works by studying how the spatial profile of SFR behaves as a function of the stellar mass of the paired galaxy, the mass ratio between the galaxy pairs, and the projected separation between the galaxies.
-We will also model how the merger-induced star formation will affect the future mass growth of the interacting galaxies.
+In this work we will study how the radial profiles of star formation in our pair sample is effected by tidal interactions.
+We will expand upon the previous studies of star formation in merging galaxies by studying how the spatial profile of the SFR behaves as a function of the stellar mass of the paired galaxy, the mass ratio between the galaxy pairs, and the projected separation between the galaxies.
+
+Changes in the star formation rate will also affect the future mass growth in the interacting galaxies.
+We will model the fractional mass growth rate of the galaxies in our sample to see how the merger event influences the mass evolution of the paired galaxies.
+Since merging galaxies are already known to have centrally enhanced star formation rates, we would expect this to produce higher concentrations of stellar mass in their centers.
 
 % Organization
-This paper is organized as follows; in Section \ref{sec:data} we will discuss the detail of the MaNGA survey, in Section \ref{sec:analysis} we will discuss how we extract emission lines from the MaNGA survey and how we calculate the star formation from them, in Section \ref{sec:pair} we discuss the construction of our pair sample, in Section \ref{sec:control} we discuss the construction of our control sample, in Section \ref{sec:radial} we build the radial profiles for the pair and control galaxies, in Section \ref{sec:results} we discuss the results of the survey, in Section \ref{sec:discussion} we discuss our results in the context of other surveys, and in Section \ref{sec:sum} we summarize and conclude the work.
+This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the photometric catalogs which we use characterize the stellar masses and geometries or our galaxies, in Section \ref{sec:analysis} we will discuss how we extract emission lines from the MaNGA survey and how we calculate star formation rates from them, in Section \ref{sec:pair} we discuss the construction of our pair samples, in Section \ref{sec:control} we discuss the construction of a sample of isolated, control galaxies, in Section \ref{sec:radial} we build the radial profiles for both the paired and control galaxies, in Section \ref{sec:results} we discuss the results of the constructed radial profiles, and in Section \ref{sec:sum} we discuss and summarize the finding of the work.
 
@@
 
-MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS 2.5 meter telescope along with two dual-channel BOSS spectrographs.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/Mi-z.pdf}
+\caption[]{\textbf{Left:} The luminosity $-$ redshift distribution of the three MaNGA subsamples; The Primary Sample (blue), the Secondary Sample (red) and the Color-Enhanced Sample (green).
+\textbf{Right:} The stellar mass $-$ redshift distribution of the three samples.
+}
+\label{fig:Mi-z}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs.
 MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively.
-MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA with a resolution of R $\sim$ 2000 and a median spectra coverage of 2.5\arcsec FWHM \citep{Bundy:2015}.
+MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a median spectra coverage of 2.5\arcsec\ FWHM \citep{Bundy:2015}.
 
-MaNGA targets galaxies from a subset of 41,154 galaxies with from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the NSA survey's elliptical Petrosian apertures.
+MaNGA targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
 MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
@@
 
-Because of the survey's flat stellar mass distribution and uniform spatial coverage, these samples have a unique ``banana" shaped distribution in redshift and luminosity, see Figure \ref{fig:Mi-z}.
+Because of the survey's flat stellar mass distribution and uniform spatial coverage, these samples have a unique ``banana" shaped distribution in redshift and luminosity, seen in Figure \ref{fig:Mi-z}.
 Because the Secondary and Color-Enhanced samples use a wider spatial coverage than the Primary sample, the Secondary and Color-Enhanced Samples will posses galaxies of higher redshifts than galaxies at the same stellar masses in the Primary sample.
+This distribution will be important later when we match control galaxies to paired galaxies based on their stellar masses and redshifts.
 
 %%% NSA and Simard+11
-We further use photometric data from the NSA catalog and \citet{Simard:2011} (from now on \simard).
-We use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard\ to quantify the geometry of the outside-IFU and inside-IFU samples respectively.
-We further use the total stellar masses extracted from these apertures to quantify the total stellar masses of the galaxies, the NSA catalog contains their own calculation for stellar mass and we use the stellar mass calculation from \citet{Mendel:2014} for the \simard\ apertures.
+We use photometric data from the NSA catalog and \citet{Simard:2011} (from now on \simard).
+We use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard\ to characterize the geometry of galaxies with pairs identified outside of the IFU (the outside-IFU sample) and galaxies identified within the IFU (the inside-IFU sample) respectively.
+We further use the total stellar masses extracted from these apertures to quantify the total stellar masses of the galaxies, the NSA catalog contains its own calculation for stellar mass and we use the stellar mass calculation from \citet{Mendel:2014} for the \simard\ apertures.
+
+We use two different photometric catalogs here because the NSA catalog covers the entirety of the MaNGA sample, but does not adequately fit the geometry of galaxies with close companions.
+In many of the cases where we have a MaNGA target with an inside-IFU pair, the NSA catalog's algorithm fails to model the geometry of the MANGA target as the algorithm fails to separately deblend the two galaxies.
+We found that the algorithm used in the \simard\ catalog models the galaxies with close companions much better; however, the catalog does not completely cover our sample.
+We use both of the catalogs as a compromise to maintain the sample size in the outside-IFU sample, where the NSA catalog models the paired galaxies' geometry well, and to obtain better geometry in our inside-IFU sample, which is poorly fitted by the NSA catalog's algorithm.
 
@@
 {\sc SPFIT} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
-Emission line are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
-The algorithm provides us with measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and kinematics of the stellar populations.
+Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
+The algorithm provides us with measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
 
 %%% Reddening
-We use the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
-The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1 where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ to the expected value of 2.85 for case-B recombination.
+We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
+The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
 We apply the extinction correction to all of the extracted emission lines.
@@
 \subsection{Star Formation Rates}
-We classify galaxies as star forming using both the color-magnitude diagram (CMD) and the BPT diagram \citep{Baldwin:1981}.
+To ensure that the observed emission lines are created by HII regions, we classify galaxies as star forming using both the color-magnitude diagram (CMD) and the BPT diagram \citep{Baldwin:1981}.
 We show the CMD in Figure \ref{fig:cmd} along with demarcation lines which separate the blue cloud, red sequence, and green valley.
-We established the demarcation lines by collapsing the CMD to a color histogram for each of the three regions and then varied the slopes between the regions until we found the slopes which best fit the data.
+We established the demarcation lines by collapsing the CMD to a color histogram for each of the three regions.
+We then varied the slopes between the regions until we found the slopes which best fit the data.
 These demarcation lines are;
@@
 
-Where NUV$-$r is the color and M$_i$ is the i-band magnitude.
+Where NUV$-$r is the color and M$_i$ is the i-band magnitude from the NSA catalog.
 
-The BPT diagnostic uses emission line ratios to separate ionization sources, star formation and active galactic nuclei (AGN).
-The two ionization sources can be separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.
+The BPT diagnostic uses emission line ratios to separate ionization sources; star formation and active galactic nuclei (AGN).
+The two ionization sources are often separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.
 
@@
 
-Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes extracted from the spectra within the inner 2 arcseconds of the galaxies.
+Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes extracted from the MaNGA spectra within the inner 2 arcseconds of the galaxies.
 It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic HII regions and AGN on the BPT diagram \citep{Stasinska:2008}.
-We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\angstrom to remove these retired galaxies \citet{Cid-Fernandes:2011}.
-In this work, we define star forming galaxies as those which are on the blue cloud in the CMD and which is below the \citet{Kewley:2001} on the BPT diagram.
+We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to remove these retired galaxies \citet{Cid-Fernandes:2011}.
+In this work, we define star forming galaxies as those which are in the blue cloud in the CMD and which are below the theoretical maximum starburst line from \citet{Kewley:2001} on the BPT diagram.
 
-We measure the SFR from the H$\alpha$ luminosity, L$_{H\alpha}$.
-The H$\alpha$ luminosity is calculated from the flux of the H$\alpha$ emission line.
+We measure the SFR from the H$\alpha$ luminosity, L$_{H\alpha}$, calculated from the H$\alpha$ flux.
 We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.
@@
 
-We normalize the SFR by the local stellar mass (the stellar mass contained with a given spaxel), calculated from SPFIT, giving us the specific star formation rate (sSFR).
+Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, giving us the specific star formation rate (sSFR).
+The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum with each spaxel.
 
 \begin{equation}
-sSFR = \frac{SFR}{M^*}
+{\rm sSFR} = \frac{\rm SFR}{M^*}
 \end{equation}
@@
 \section{Pair Sample}\label{sec:pair}
+We build two different pair samples in this work; the inside-IFU sample which contains paired galaxies where both galaxies are contained within a single MaNGA IFU and the outside-IFU sample where a MaNGA target galaxies is coupled with another galaxies found outside of the MaNGA IFU.
 
@@
 We use SDSS photometric objects to create a catalog of objects within the fields of view of the MaNGA IFUs.
-The extract their spectra from the MaNGA datacubes through a 1\arcsec aperture and fit the spectra with {\sc SPFIT}.
+We extract their spectra from the MaNGA datacubes through a 1\arcsec\ aperture and fit the spectra with {\sc SPFIT} assuming the MaNGA target's redshift.
 The spectra is then sorted into different categories; ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects.
-The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxies itself or a nearby companion galaxy.
+The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
 This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target.
@@
 
-From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU and within a relative velocity of $\Delta$v $<$ 500 km s$^{-1}$.
-124 of the galaxies are star forming galaxies (SFGs).
-Finally, 41 SFGs are covered by \simard\ and \citet{Mendel:2014}.
+From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU.
+We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions and we also require that the galaxies are classified as star forming as described in Section \ref{sec:analysis}.
+These requirements reduce our sample down to 124 star forming galaxies (SFGs).
 
-Some of the galaxies in our sample have multiple companions. From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
+Several of the target galaxies in our sample have multiple companions. From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
 
-We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}
+We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}.
+The Simard+11 and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample.
+Out of the 124 SFGs in the inside-IFU sample, 41 of the SFGs are covered by both \simard\ and \citet{Mendel:2014}.
 
@@
 
-The second pairs sample is the outside-IFU pairs sample.
-This sample includes MaNGA galaxies which have companion galaxies found outside the field of view of its IFU.
-We identify these external pair from the NSA catalog.
-We select galaxies which are within a projected separation, r$_p$ $<$ 50 kpc, and within a relative velocity, $\Delta$v $<$ 500 km s$^{-1}$.
+We supplement the inside-IFU sample with a set of pairs identified outside of the field of view of the MaNGA IFU.
+We select these outside-IFU pairs from the NSA catalog.
+We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of r$_p$ $<$ 50 kpc using the MaNGA target's redshift.
+We further use a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.
 
-The NSA catalog contains 641,409 galaxies from which we find 509 galaxies which are paired to MaNGA targets.
+From the NSA catalog's 641,409 galaxies, we find 509 galaxies which are paired to MaNGA targets.
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
@@
 We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample.
-We also use the stellar masses from the NSA catalog for the total stellar mass of the galaxies.
+We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.
 
@@
 \section{Control Sample}\label{sec:control}
-We build a sample of isolated control galaxies from the remaining MaNGA galaxies.
-Selecting the MaNGA galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
+We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
 This gives us a set of 1862 SFGs and 1598 SFGs which are covered by both \simard\ and \citet{Mendel:2014}.
 
-The SFR in galaxies has been shown to be dependent on both stellar mass and redshift \citep{Noeske:2007}.
-To account for this we will need to match pairs with similar mass and redshift controls.
-To do this we build a subset of 20 control galaxies for each paired galaxy.
+The SFR in galaxies has been shown to be dependent on both stellar mass and redshift of the galaxies \citep{Noeske:2007}.
+This effect needs to be controlled for when comparing the paired and control galaxies to isolate the changes in the sSFR due to merger induced effects.
+For each galaxy pair we will build a subset of 20 control galaxies which are matched on stellar mass and redshift.
 
-First we select every control galaxy which is within a stellar mass of 0.1 dex and within in same MaNGA subsample, i.e.
-the Primary or Secondary sample.
-Knowing that MaNGA has a tight ``banana" shaped distribution in stellar mass and redshift, imposing the stellar mass cut and the MaNGA subsample cut will effectively set a $\sim$0.025 dex redshift cut.
+To control for stellar mass, we set a 0.1 dex stellar mass cut between a paired galaxy and the potential control galaxies.
+To restrict the redshift between the control and paired galaxies, we select control galaxies which are drawn from the same MaNGA subsample (e.g.
+Primary or Secondary) as the paired galaxy.
+The MaNGA sample has a tight ``banana" shaped distribution in stellar mass and redshift, seen in Figure \ref{fig:Mi-z}.
+By setting a 0.1 dex stellar mass cut and requiring that the galaxies be in the same MaNGA subsample, we effectively set a z $\le$ $\sim$0.025 redshift cut.
+We note that the MaNGA galaxies with stellar masses above \logm\ $\ge$ 11.0 have a wide redshift distribution.
+In this work, we focus on the galaxies below that mass range.
 
-We then downselect the control subset down to 20 controls using a random number generator so that each paired galaxies has the same number of selected controls.
-In the few cases where a paired galaxy fails to find at least 20 control galaxies, we iteratively expand the stellar mass limits by 0.1 dex until a set of 20 control galaxies can be made.
+Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies.
+Since we want each paired galaxy to be treated in a similar manner, we will downselect the total number of acquired control galaxies down to 20 controls.
+We select the 20 controls using a random number generator.
+In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.
+
 A small set of paired required extra iterations to find 20 controls; 8 paired galaxies need an extra iteration, 1 paired galaxy need two extra iterations, and 1 paired galaxy needed three iterations.
-\\
 
-The control galaxies will be treated using both the \simard\ aperture and \citet{Mendel:2014} masses when comparing them to the inside-IFU sample and the NSA apertures and masses when comparing them to the outside-IFU sample.
+The control galaxies have their radial profiles of sSFR made with both the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard.
+We use the geometries and stellar masses from \simard\ and \citet{Mendel:2014} when the controls are being matched to pairs in the inside-IFU sample and we use the geometries and stellar masses from the NSA catalog when the controls are being matched to pairs in the outside-IFU sample.
 
@@
 
-As mentioned in Sections \ref{sec:pair} and \ref{sec:control} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \simard to define the geometries of the galaxies.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/8083-12703.pdf}
+\caption[Example of the difference profiles for the mass-redshift selected control sample.]{The process for building the tailored control sample.
+The Left panel shows the paired galaxy's profile for sSFR.
+The Middle panel shows the profiles for sSFR for the selected 20 control galaxies in gray.
+The red profile is the median profile of the 20 control galaxies where the highlighted region about the profile is the standard error of the mean.
+The Right panel shows the difference between pair's profile and the stacked control profile.}
+\label{fig:dex}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR.
+As mentioned in Sections \ref{sec:pair} and \ref{sec:control} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \simard\ to define the geometries of the galaxies.
 We calculate the inclination angle, {\it i}, of the galaxies using the major-to-minor axis ratios from the elliptical apertures;
@@
 
-The inclination angle is used to deproject the geometries of the galaxies.
-We use our catalog of photometric objects and the \simard\ catalog to mask foregournd/background objects.
-Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \simard\ are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
+Where $q$ is the intrinsic oblateness. We use the empirically determined oblateness of $q = 0.13$, from \citet{Giovanelli:1994}.
 
-The distance to each of the spaxels from the center of the MaNGA targets is calculated using the 50\% half light radius to scale the galaxies.
-The spaxels are binned into radius increments of 0.1 \reff\ from 0.0$-$2.4\reff.
+The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies.
+The distance to each of the spaxels from the center of the MaNGA target is calculated using the 50\% half light radius to scale the size of the galaxy.
+The r-band elliptical S\'ersic apertures from \simard\ are used for the inside-IFU sample and their controls and the r-band elliptical Petrosian apertures from the NSA catalog are used for the outside-IFU sample and their controls.
+
+The spaxels are binned into radius increments of 0.1 \reff\ from 0.0$-$2.5 \reff.
 Within each radius bin we take the median of the specific star formation rate.
@@
 We create one of these individual averaged radial profiles for every MaNGA galaxy.
+
+We use our catalog of photometric objects and the \simard\ catalog to mask foregournd/background objects which may contaminate the data.
+Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \simard\ are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
 
@@
 We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of stacked profile over 1000 iterations.
-The difference profile is then the difference between a single paired galaxy's profile and the stacked profile in log space (this means that the difference profiles are ratios in linear space).
-This is done for each of the 202 galaxy pairs.
+This random selection contributes an error of about 0.1 dex.
+
+Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space (this means that the profiles really represents a ratio between the pairs and controls in linear space).
+An example of the construction of a difference profile is shown in Figure \ref{fig:dex}.
+We do this process for each of the 202 paired galaxies.
+
+The difference profiles at this stage have now been controlled for stellar mass, redshift, and galaxy size so we can freely stack these profiles to study the global properties of the merging galaxies.
+We take all of the $\Delta$log(sSFR) profiles and take the median within each radius bin to create a stacked profile which represents the whole pair sample, shown in Figure \ref{fig:ssfr_all}.
+We can also split the pair sample along different parameters; stellar mass, mass ratio, and projected separation to study how these profiles behave as a function of these parameters, shown in Figure \ref{fig:ssfr_full}.
+The results of the profiles will discussed in detail in Section \ref{sec:results}.
 
@@
 
-We take each of the individual difference profiles for all of the and take the median value of the sSFR within each radius bin.
+We take each of the individual difference profiles for all of the galaxy pairs and take the median value of the sSFR within each radius bin.
 This gives a single profile which describes the sSFR enhancements for the whole pair sample.
 We show this profile in the left hand panel of Figure \ref{fig:ssfr_all}.
-The sSFR is centrally enhanced by $\sim$0.25 dex.
-The enhancement falls to zero around 1.0\reff.
+The sSFR is centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex which falls to zero around 1.0 \reff.
 The disks of the paired galaxies feature no enhancement or suppression to the sSFR.
+The figure also shows that there is a large amount of scatter between the individual difference profiles, so while the trend is for the paired galaxies to show central enhancement, there are several paired galaxies which feature sSFR suppression in their centers.
 
 In the right hand panel of Figure \ref{fig:ssfr_all} we show a histogram for the $\Delta$log(sSFR) offset in the centers of the paired galaxies.
-To get this, we extract the values of $\Delta$log(sSFR) in the individual difference profiles within the inner 0.5 R/\reff\ and take the mean of the values.
+To get this, we extract the values of $\Delta$log(sSFR) in the individual difference profiles from the inner 0.5 R/\reff\ and take the mean of the values.
+Again, this shows the preference for paired galaxies to show an enhancement to the star formation in their centers.
 
 In the following sections we will break up the stacked profile into separate bins of total stellar mass, mass ratio, and projected separation.
+The radial profiles of $\Delta$log(sSFR) along with the nuclear $\Delta$log(sSFR) values from the inner 0.5 \reff\ broken up across each of the three parameters are shown in Figure \ref{fig:ssfr_full}.
 
@@
 We show the $\Delta$log(sSFR) profile split by the galaxy's total stellar mass in the top row of Figure \ref{fig:ssfr_full}.
-The level of the central sSFR enhancement is consistent with the level of enhancement for the full sample.
+The level of the central sSFR enhancement for each of the stellar mass ranges is consistent with the level of enhancement for the full sample.
 This effect is better seen in the scatter plot of the central $\Delta$log(sSFR) offsets versus stellar mass where there is a flat distribution.
@@
 The mass range, \logm\ $=$ 10.0$-$10.5, shows stronger suppression of sSFR in their disks while the mass range, \logm\ $=$ 9.0$-$9.5, show an enhancement to sSFR in their disks.
-There is no trend to sSFR enhancement/suppression with the stellar mass so the scatter in the profiles at large separation is likely due to a combination of the smaller sizes within separate mass bins and lower S/N at larger galactocentric radii.
+There is no trend to sSFR enhancement/suppression with the stellar mass so the scatter in the profiles at large separation is likely due to a combination of the smaller sample sizes within each of the separate mass bins and due to the lower S/N at larger galactocentric radii.
 
-From this we infer that the total stellar mass of a paired galaxy has no effect on the merger induced star formation within the galaxy.
-Massive galaxies are enhanced to the same degree as low mass galaxies.
+From this we see that the total stellar mass of a paired galaxy has no effect on the merger induced star formation within the galaxy.
+Massive galaxies have their specific star formation rate enhanced to the same degree as low mass galaxies.
 
@@
 While the total stellar mass between the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
-In the middle row of Figure \ref{fig:ssfr_full} we see that the sSFR enhancement is strongest in galaxies with mass ratios close to 1:1, $\delta$log(M) $=$ 0.0.
+The mass ratio is calculated as the difference between stellar masses contained within the 50\% half light radius,
+
+\begin{equation}
+\Delta {\rm log}(M) = {\rm log}(M_{target}) - {\rm log}(M_{comp}) 
+\end{equation}
+
+Where M$_{target}$ is the mass of the MaNGA target galaxy and M$_{comp}$ is the mass of the companion galaxy.
+Note that we do not use the absolute value of the difference like how the mass ratio is typically used.
+We do this so that we can independently study how the star formation large central galaxies behave in comparison to small satellite galaxies.
+
+For the outside-IFU sample we use the stellar masses calculated from the r-band elliptical Petrosian apertures from the NSA catalog.
+For the inside-IFU sample, the neither the NSA catalog or \citet{Mendel:2014} will cover both galaxies.
+Instead we use stellar masses calculated from {\sc SPFIT} from the inner 2\arcsec\ of the galaxies.
+
+In the middle row of Figure \ref{fig:ssfr_full} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log(M) $=$ 0.0.
 These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.15 dex higher than the average central enhancement of the whole sample.
@@
 \subsection{Projected Separation}
+
 Finally we look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_full}.
 The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
+The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are $\sim$0.1 dex below the median.
 
@@
 The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc.
+While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex.
 Within 10 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.5 dex.
-Surprisingly, this central enhancement plummets back to zero at the closest separations, r$_p$ $<$ 5 kpc.
-We will discuss the potential causes of the zero enhancement in the centers of the closest galaxies in Section \ref{sec:discussion}.
+
+For the galaxies with the closest separations, r$_p$ $<$ 5 kpc, $\Delta$log(sSFR) drops to zero.
+This is strange as we would expect that the closest pairs would show the strongest enhancements to their star formation as they are currently or have just passed the first pericenter.
+We will discuss the potential causes of the zero enhancement in the centers of the closest galaxies in Section \ref{sec:sum}.
 
@@
 
-The merger induced star formation will increase the mass growth rate of the interacting galaxies.
+The higher rate of star formation in interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
+The question is whether or not the advanced mass growth rate is significant.
+
 We will use a simple model to estimate the enhanced mass growth rate due to merger induced star formation.
-
 A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}\label{sec:discussion}
+\section{Discussion and Summary}\label{sec:sum}
+%\label{sec:discussion}
 
 % Nuclear comp with prev works
-The enhancement to the sSFR in the centers of the whole pair sample is consistent with previous galaxy merger studies \citet{Ellison:2008, Barrera-Ballesteros:2015, Pan:2019}.
+In this study we saw that the sSFR is centrally enhanced in the centers of paired galaxies by $\sim$0.25 dex ($\sim$1.78$\times$) in comparison to isolated galaxies.
+This enhancement is consistent with what is predicted by hydrodynamical simulations \citep{Scudder:2012} and is also consistent with previous observational surveys \citep{Ellison:2008, Barrera-Ballesteros:2015, Pan:2019}.
 
-Different IFS studies have found different sSFR offsets in the disks of the paired galaxies.
-\citet{Barrera-Ballesteros:2015} found that the sSFR (using \ewha\ as a proxy) is suppressed in the disks of paired galaxies by $\sim$-0.13 dex.
-In contrast, \citet{Pan:2019} found that the sSFR is enhanced by 0.15 dex.
-In this work, we see that  $\Delta$log(sSFR) is roughly zero but leans towards being suppressed, $\Delta$log(sSFR) $=$ -0.1$-$0.0 dex.
+When looking at the disks of our paired galaxies, we found zero enhancement or suppression to the sSFR.
+A sample of galaxy pairs from the CALIFA survey featured a suppression to the sSFR (using the H$\alpha$ equivalent width as a proxy for the sSFR) of $\sim$-0.13 dex \citep{Barrera-Ballesteros:2015}.
+\citet{Pan:2019} built radial profiles for galaxy pairs in MaNGA and found that the sSFR is enhancement by 0.15 dex.
+We note that in our work that there is a large amount of scatter seen in the $\Delta$log(sSFR) in the disks of the paired galaxies, so many paired galaxies feature enhanced sSFR and while other feature suppressed sSFR but that the $\Delta$log(sSFR) averages to zero over our sample.
 
@@
 We see the same effect; however, we have also shown that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement.
+It has been a convention to split galaxy pairs in major mergers, $|$log(M)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log(M)$|$ $\le$ 1.0.
+In this work, we can see that the mass ratio range used in galaxy pair studies can safely be widened to at least $|$log(M)$|$ $\le$ 2.0 so that larger pair samples can be constructed.
+
 Further, within these galaxy pairs with wide mass ratios we see that the less massive galaxy in the pair shows higher levels of sSFR enhancement.
@@
 This is unsurprising as nearby galaxy pairs will have just completed a close interaction.
-This enhancement persists out to wide separations where galaxy pairs separated by 50 kpc still show a substantial enhancement to the sSFR.
+This enhancement persists out to wide separations, where galaxy pairs separated by 50 kpc, still show a substantial enhancement to the sSFR.
 \citet{Patton:2013} showed that the central enhancements to sSFR persists out to 150 kpc.
@@
 The closest pairs in our sample, pairs closer than 5 kpc, show no enhancement to the sSFR.
-This seems odd as one would think that these galaxies should show the strongest enhancements.
-The first thing to consider is that the sample contains no post-merger galaxies so we will not see the second large burst of star formation when the two galaxies are coalescing.
+This seems odd as one would think that these galaxies should show the strongest enhancements to the sSFR.
+It is important to remember that this sample contains no post-merger galaxies so we will not see the second large burst of star formation when the two galaxies are coalescing.
 The closest paired galaxies will either be pairs which are about to go through their first pericenter or galaxies which have just passed their first pericenter.
 In the galaxies which have passed their first pericenter, we believe that the timescale is still too small for the interaction induced gas inflows to travel from the galaxy's disk to its nucleus.
-Since the gas inflows haven't impacted the galaxy's nucleus, no enhancements to the sSFR will be seen.
-\citet{Scudder:2012} also found a delay in the burst of merger induced star formation in their hydrodynamical simulations.
+Since the gas inflows haven't yet impacted the galaxy's nucleus, no enhancements to the sSFR will be seen.
+This delay between the first pericenter of the merger event and the burst of star formation has been shown in the hydrodynamical simulations of \citet{Scudder:2012}.
+
+We have also modeled the future mass growth of our sample of paired galaxies.
+Our model shows that the merger induced star formation could substantially accelerate the mass growth in the centers of the interacting galaxies in comparison to secular mass growth.
+Since the enhanced star formation and thereby mass growth is largely restricted to the centers of the interacting galaxies, these close interactions will produce galaxies with higher concentrations of stellar mass in their centers.
+\\
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Conclusion}\label{sec:sum}
+%\section{Summary and Conclusion}\label{sec:sum}
 
-We studied a sample of paired, star forming galaxies using the MaNGA IFS survey.
+In this work, we studied a sample of paired, star forming galaxies using the MaNGA IFS survey.
 We have made a sample of 913 paired galaxies of which 202 are SFGs.
@@
 % funding
-J.S. and H.F. acknowledge support from the National Science Foundation (NSF) grant AST-1614326 and University of Iowa funds.
+J.S.
+and H.F.
+acknowledge support from the National Science Foundation (NSF) grant AST-1614326 and University of Iowa funds.
+Funding for the Sloan Digital Sky Survey IV has been provided by the Alfred P.
+Sloan Foundation, the U.S.
+Department of Energy Office of Science, and the Participating Institutions.
+SDSS acknowledges support and resources from the Center for High-Performance Computing at the University of Utah.
+The SDSS web site is www.sdss.org.
+
+SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions of the SDSS Collaboration including the Brazilian Participation Group, the Carnegie Institution for Science, Carnegie Mellon University, the Chilean Participation Group, the French Participation Group, Harvard-Smithsonian Center for Astrophysics, Instituto de Astrofísica de Canarias, The Johns Hopkins University, Kavli Institute for the Physics and Mathematics of the Universe (IPMU) / University of Tokyo, the Korean Participation Group, Lawrence Berkeley National Laboratory, Leibniz Institut für Astrophysik Potsdam (AIP), Max-Planck-Institut für Astronomie (MPIA Heidelberg), Max-Planck-Institut für Astrophysik (MPA Garching), Max-Planck-Institut für Extraterrestrische Physik (MPE), National Astronomical Observatories of China, New Mexico State University, New York University, University of Notre Dame, Observatório Nacional / MCTI, The Ohio State University, Pennsylvania State University, Shanghai Astronomical Observatory, United Kingdom Participation Group, Universidad Nacional Autónoma de México, University of Arizona, University of Colorado Boulder, University of Oxford, University of Portsmouth, University of Utah, University of Virginia, University of Washington, University of Wisconsin, Vanderbilt University, and Yale University.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/8083-12703.pdf}
-\caption[Example of the difference profiles for the mass-redshift selected control sample.]{The process for building the tailored control sample.
-The Left panel shows the paired galaxy's profile for sSFR.
-The Middle panel shows the profiles for sSFR for the selected 20 control galaxies in gray.
-The red profile is the median profile of the 20 control galaxies where the highlighted region about the profile is the standard error of the mean.
-The Right panel shows the difference between pair's profile and the stacked control profile.}
-\label{fig:dex}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2020-07-15 maintex.tex
next draft

@@
 \begin{abstract}
-We study the spatial profile of the star formation rate (SFR) in a sample of 202 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
+We study the spatial profile of the star formation rate (SFR) in a sample of 160 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
 We find that the specific star formation rate (sSFR) is centrally enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
-We further investigate how these profiles behave as a function of their stellar mass, mass ratio, and projected separation.
-We find that the sSFR profiles are unaffected by the stellar masses of the interacting galaxies; however, they are affected by the mass ratio between the galaxies where the galaxies with the smallest mass ratios feature the largest enhancement to their sSFR.
-We also find that, in pairs with large mass ratios ($|\Delta$log(M)$|$ $=$ 0.5 $-$ 1.5), the less massive galaxy of the pair has slightly higher levels of sSFR enhancement, $\sim$0.1 dex, than the more massive galaxies in the pair.
-We also find that the level of sSFR enhancement increases with closer projected separations; however, the closest pairs, $\le$5 kpc, show no signs of sSFR enhancement/suppression.
-We suspect that these close pairs are merging galaxies which have passed their first pericenter, but the merger induced gas-inflows have yet to reach the centers of these galaxies.
-We make a simple model for the future mass growth of the galaxies due to the merger induced star formation.
-We predict that the paired galaxies in our sample will see a mass growth rate in their centers which is 1.6$-$2.3$\times$ higher than secular mass growth, showing that the merger induced star formation can significantly alter the stellar mass distribution.
+We find that the level of the central enhancement is independent of galaxy mass.
+Low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
+Assuming a constant burst merger induced star formation over a 1 Gyr period, the mass growth rate in the centers of the paired galaxies will be 1.6$-$2.3$\times$ higher than secular mass growth.
+Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate which is $\sim$4.3 higher than that of high mass galaxies.
+This indicates that merger induced star formation has a significant impact on the mass evolution of low mass galaxies.
+
 \end{abstract}
 
-\keywords{galaxies: active --- galaxies: nuclei --- galaxies: interactions}
+\keywords{galaxies: star formation --- galaxies: nuclei --- galaxies: interactions --- galaxies: mass evolution}
 
@@
 % Organization
-This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the photometric catalogs which we use characterize the stellar masses and geometries or our galaxies, in Section \ref{sec:analysis} we will discuss how we extract emission lines from the MaNGA survey and how we calculate star formation rates from them, in Section \ref{sec:pair} we discuss the construction of our pair samples, in Section \ref{sec:control} we discuss the construction of a sample of isolated, control galaxies, in Section \ref{sec:radial} we build the radial profiles for both the paired and control galaxies, in Section \ref{sec:results} we discuss the results of the constructed radial profiles, and in Section \ref{sec:sum} we discuss and summarize the finding of the work.
+This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we discuss the results of the constructed radial profiles, and in Section \ref{sec:sum} we discuss and summarize the findings of the work.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data}\label{sec:data}
+\section{Data and Sample}\label{sec:data}
 
@@
 \centering
-\includegraphics[width=\linewidth]{fig/Mi-z.pdf}
-\caption[]{\textbf{Left:} The luminosity $-$ redshift distribution of the three MaNGA subsamples; The Primary Sample (blue), the Secondary Sample (red) and the Color-Enhanced Sample (green).
-\textbf{Right:} The stellar mass $-$ redshift distribution of the three samples.
-}
-\label{fig:Mi-z}
+\includegraphics[width=\linewidth]{fig/color-mag.pdf}
+\caption[]{Color-magnitude diagram for MaNGA galaxies ({\it colored circles}).
+The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+The MaNGA galaxies with close companions are marked with {\it grey diamonds}.
+From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
+The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
+\label{fig:cmd}
 \end{figure}
@@
 
-MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs.
-MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively.
+MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}.
+MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citet{Law:2015}.
 MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a median spectra coverage of 2.5\arcsec\ FWHM \citep{Bundy:2015}.
 
-MaNGA targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
+The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
 MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
@@
 
-The MaNGA sample is split into three subsamples; the Primary Sample, Secondary Sample, and Color-Enhanced Sample.
-The Primary sample contains the galaxies which are covered out to 1.5 \reff\ and makes up 47\% of the survey.
-The Secondary contains the galaxies which are covered out to 2.5 \reff\ and makes up 37\% of the survey.
-The Color-Enhanced sample is designed to select rarer galaxy types with a spatial coverage of 2.5 \reff\ and makes up 16\% of the survey.
-
-Because of the survey's flat stellar mass distribution and uniform spatial coverage, these samples have a unique ``banana" shaped distribution in redshift and luminosity, seen in Figure \ref{fig:Mi-z}.
-Because the Secondary and Color-Enhanced samples use a wider spatial coverage than the Primary sample, the Secondary and Color-Enhanced Samples will posses galaxies of higher redshifts than galaxies at the same stellar masses in the Primary sample.
-This distribution will be important later when we match control galaxies to paired galaxies based on their stellar masses and redshifts.
-
-%%% NSA and Simard+11
-We use photometric data from the NSA catalog and \citet{Simard:2011} (from now on \simard).
-We use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard\ to characterize the geometry of galaxies with pairs identified outside of the IFU (the outside-IFU sample) and galaxies identified within the IFU (the inside-IFU sample) respectively.
-We further use the total stellar masses extracted from these apertures to quantify the total stellar masses of the galaxies, the NSA catalog contains its own calculation for stellar mass and we use the stellar mass calculation from \citet{Mendel:2014} for the \simard\ apertures.
-
-We use two different photometric catalogs here because the NSA catalog covers the entirety of the MaNGA sample, but does not adequately fit the geometry of galaxies with close companions.
-In many of the cases where we have a MaNGA target with an inside-IFU pair, the NSA catalog's algorithm fails to model the geometry of the MANGA target as the algorithm fails to separately deblend the two galaxies.
-We found that the algorithm used in the \simard\ catalog models the galaxies with close companions much better; however, the catalog does not completely cover our sample.
-We use both of the catalogs as a compromise to maintain the sample size in the outside-IFU sample, where the NSA catalog models the paired galaxies' geometry well, and to obtain better geometry in our inside-IFU sample, which is poorly fitted by the NSA catalog's algorithm.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analysis}\label{sec:analysis}
-\subsection{Emission Lines}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
-\caption[]{\textbf{Left:} Color-magnitude diagram for MaNGA galaxies ({\it colored circles}).
-The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-The MaNGA galaxies with close companions are marked with {\it grey diamonds}.
-From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
-The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.
-\textbf{Right:} The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
-The color of each bin represents the number density of spaxels, normalized to one.
-The solid black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001} and the dashed black line is the analytical \citet{Kauffmann:2003} line.
-This shows the capability of the CMD to select star-forming galaxies as most of the spaxels within the selected galaxies fall beneath the starburst line.}
-\label{fig:cmd}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% SPFIT
-We use our own {\sc IDL} based spectral fitting code, {\sc SPFIT}, to model the spectra from the MaNGA datacubes.
-{\sc SPFIT} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
-Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
-The algorithm provides us with measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
-
-%%% Reddening
-We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
-The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
-We apply the extinction correction to all of the extracted emission lines.
-
-\subsection{Star Formation Rates}
-To ensure that the observed emission lines are created by HII regions, we classify galaxies as star forming using both the color-magnitude diagram (CMD) and the BPT diagram \citep{Baldwin:1981}.
-We show the CMD in Figure \ref{fig:cmd} along with demarcation lines which separate the blue cloud, red sequence, and green valley.
+We classify galaxies in this survey as star forming galaxies using the color-magnitude diagram (CMD).
+We show the CMD for the MaNGA survey and our pair sample in Figure \ref{fig:cmd} along with demarcation lines which separate the blue cloud, red sequence, and green valley.
 We established the demarcation lines by collapsing the CMD to a color histogram for each of the three regions.
@@
 
-The BPT diagnostic uses emission line ratios to separate ionization sources; star formation and active galactic nuclei (AGN).
-The two ionization sources are often separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.
+After the star formation cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}. We also set a stellar mass range of \logm\ $=$ 9.0$-$11.0.
 
-\begin{equation}\label{eq:kewley}
-\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
-\end{equation}
-\begin{equation}\label{eq:kauffmann}
-\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.05} + 1.3}
-\end{equation}
+We build two different pair samples in this work; the inside-IFU sample which contains paired galaxies where both galaxies are covered by a single MaNGA IFU and the outside-IFU sample where a MaNGA target galaxy is coupled with another galaxies found outside of its MaNGA IFU.
 
-Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes extracted from the MaNGA spectra within the inner 2 arcseconds of the galaxies.
-It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic HII regions and AGN on the BPT diagram \citep{Stasinska:2008}.
-We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to remove these retired galaxies \citet{Cid-Fernandes:2011}.
-In this work, we define star forming galaxies as those which are in the blue cloud in the CMD and which are below the theoretical maximum starburst line from \citet{Kewley:2001} on the BPT diagram.
+\subsection{Inside-IFU Sample}\label{sec:inside}
+
+In our previous work, \citet{Fu:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
+In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
+
+We use SDSS photometric objects to create a catalog of objects within the fields of view of the MaNGA IFUs.
+We extract their spectra from the MaNGA datacubes through a 1\arcsec\ aperture and fit the spectra with {\sc SPFIT} assuming the MaNGA target's redshift.
+The spectra is then sorted into different categories; ``good" galaxy spectra, broad-line AGN (active galactic nuclei), foreground star, foreground/background galaxies, or poor S/N objects.
+The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
+This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target.
+We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.
+
+From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU.
+We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions and we also require that the galaxies are classified as star forming by the CMD diagram.
+These requirements reduce our sample down to 124 star forming galaxies (SFGs).
+
+Several of the target galaxies in our sample have multiple companions. From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
+
+We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures from \citet{Simard:2011} and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}.
+We use \citet{Simard:2011} instead of the apertures from the NSA catalog, which the MaNGA sample is drawn from, because the apertures in the NSA catalog often fail to fit the MaNGA galaxies when there is another nearby, bright object.
+
+The \citet{Simard:2011} and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample.
+Out of the 124 SFGs in the inside-IFU sample, 33 of the SFGs are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
+
+\subsection{Outside-IFU Sample}\label{sec:outside}
+
+We supplement the inside-IFU sample with a set of pairs identified outside of the field of view of the MaNGA IFU.
+We select these outside-IFU pairs from the NSA catalog.
+We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of r$_p$ $<$ 50 kpc using the MaNGA target's redshift.
+We further use a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.
+
+From the NSA catalog's 641,409 galaxies, we find 361 galaxies which are paired to MaNGA targets.
+MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
+After restricting the sample to SFGs, we have 127 MaNGA targets with paired galaxies outside of the IFU.
+
+We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample.
+For cases where the identified galaxy pair is outside of the MaNGA IFU, the NSA catalog's algorithm is able to fit the MaNGA target's geometry well.
+We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.
+
+\subsection{Control Sample}\label{sec:control}
+We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
+This gives us a set of 1891 SFGs and 1528 SFGs which are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
+
+The SFR in galaxies has been shown to be dependent on both stellar mass and redshift of the galaxies \citep{Noeske:2007}.
+This effect needs to be controlled for when comparing the paired and control galaxies to isolate the changes in the sSFR due to merger induced effects.
+For each galaxy pair we build a subset of 20 control galaxies which are matched in stellar mass and redshift.
+
+To control for stellar mass, we set a 0.1 dex stellar mass limit between a paired galaxy and the potential control galaxies.
+To restrict the redshift between the control and paired galaxies, we select control galaxies which are drawn from the same MaNGA subsample (e.g.
+Primary or Secondary) as the paired galaxy.
+The MaNGA sample has a tight ``banana" shaped distribution in stellar mass and redshift.
+By setting a 0.1 dex stellar mass cut and requiring that the galaxies be in the same MaNGA subsample, we effectively set a z $\le$ $\sim$0.025 redshift cut.
+We note that the MaNGA galaxies with stellar masses above \logm\ $\ge$ 11.0 have a wide redshift distribution, our galaxy samples are restricted to a stellar mass range between \logm\ $=$ 9.0$-$11.0.
+
+Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies.
+Since we want each paired galaxy to be treated in a similar manner, we will downselect the total number of acquired control galaxies down to 20 controls using a random number generator.
+In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.
+
+A small set of paired required extra iterations to find 20 controls; 8 paired galaxies need an extra iteration, 1 paired galaxy need two extra iterations, and 1 paired galaxy needed three iterations.
+
+The control galaxies have their radial profiles of sSFR made with both the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \citet{Simard:2011}.
+We use the geometries and stellar masses from \citet{Simard:2011} and \citet{Mendel:2014} when the controls are being matched to pairs in the inside-IFU sample and we use the geometries and stellar masses from the NSA catalog when the controls are being matched to pairs in the outside-IFU sample.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Radial Profiles of Star Formation}\label{sec:analysis}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/bpt_spax.pdf}
+\caption[]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
+The color of each bin represents the number density of spaxels, normalized to one.
+The solid black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001} and the dashed black line is the analytical \citet{Kauffmann:2003} line.}
+\label{fig:bpt}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Emission Line Extraction}
+
+%%% SPFIT
+We use our own {\sc IDL} based spectral fitting code, {\sc SPFIT}, to model the spectra from the MaNGA datacubes.
+{\sc SPFIT} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
+Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
+The algorithm provides us with measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
+
+%%% Reddening
+We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
+The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
+The extinction correction is applied to all of the extracted emission lines.
+
+\subsection{Star Formation Rate}
 
@@
 Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, giving us the specific star formation rate (sSFR).
-The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum with each spaxel.
+The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each spaxel (spatial pixel).
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pair Sample}\label{sec:pair}
-We build two different pair samples in this work; the inside-IFU sample which contains paired galaxies where both galaxies are contained within a single MaNGA IFU and the outside-IFU sample where a MaNGA target galaxies is coupled with another galaxies found outside of the MaNGA IFU.
+We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation.
+Ionization sources are often separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.
 
-\subsection{Inside-IFU Sample}\label{sec:inside}
-In our previous work, \citet{Fu:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
-In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
+\begin{equation}\label{eq:kewley}
+\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
+\end{equation}
+\begin{equation}\label{eq:kauffmann}
+\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.05} + 1.3}
+\end{equation}
 
-We use SDSS photometric objects to create a catalog of objects within the fields of view of the MaNGA IFUs.
-We extract their spectra from the MaNGA datacubes through a 1\arcsec\ aperture and fit the spectra with {\sc SPFIT} assuming the MaNGA target's redshift.
-The spectra is then sorted into different categories; ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects.
-The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
-This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target.
-We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.
+Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel.
+We depict the BPT diagram for each spaxel in the MaNGA survey in Figure \ref{fig:bpt} along with the demarcations for star formation from \citet{Kewley:2001} and \citet{Kauffmann:2003}.
+We use the \citet{Kewley:2001} demarcation line as the limit for classifying star formation in the MaNGA spaxels.
 
-From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU.
-We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions and we also require that the galaxies are classified as star forming as described in Section \ref{sec:analysis}.
-These requirements reduce our sample down to 124 star forming galaxies (SFGs).
-
-Several of the target galaxies in our sample have multiple companions. From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
-
-We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}.
-The Simard+11 and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample.
-Out of the 124 SFGs in the inside-IFU sample, 41 of the SFGs are covered by both \simard\ and \citet{Mendel:2014}.
-
-\subsection{Outside-IFU Sample}\label{sec:outside}
-
-We supplement the inside-IFU sample with a set of pairs identified outside of the field of view of the MaNGA IFU.
-We select these outside-IFU pairs from the NSA catalog.
-We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of r$_p$ $<$ 50 kpc using the MaNGA target's redshift.
-We further use a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.
-
-From the NSA catalog's 641,409 galaxies, we find 509 galaxies which are paired to MaNGA targets.
-MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-After restricting the sample to SFGs, we have 161 MaNGA targets with paired galaxies outside of the IFU.
-
-We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample.
-We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.
+It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic HII regions and AGN on the BPT diagram \citep{Stasinska:2008}.
+We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to mask retired spaxels \citet{Cid-Fernandes:2011}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Control Sample}\label{sec:control}
-We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
-This gives us a set of 1862 SFGs and 1598 SFGs which are covered by both \simard\ and \citet{Mendel:2014}.
-
-The SFR in galaxies has been shown to be dependent on both stellar mass and redshift of the galaxies \citep{Noeske:2007}.
-This effect needs to be controlled for when comparing the paired and control galaxies to isolate the changes in the sSFR due to merger induced effects.
-For each galaxy pair we will build a subset of 20 control galaxies which are matched on stellar mass and redshift.
-
-To control for stellar mass, we set a 0.1 dex stellar mass cut between a paired galaxy and the potential control galaxies.
-To restrict the redshift between the control and paired galaxies, we select control galaxies which are drawn from the same MaNGA subsample (e.g.
-Primary or Secondary) as the paired galaxy.
-The MaNGA sample has a tight ``banana" shaped distribution in stellar mass and redshift, seen in Figure \ref{fig:Mi-z}.
-By setting a 0.1 dex stellar mass cut and requiring that the galaxies be in the same MaNGA subsample, we effectively set a z $\le$ $\sim$0.025 redshift cut.
-We note that the MaNGA galaxies with stellar masses above \logm\ $\ge$ 11.0 have a wide redshift distribution.
-In this work, we focus on the galaxies below that mass range.
-
-Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies.
-Since we want each paired galaxy to be treated in a similar manner, we will downselect the total number of acquired control galaxies down to 20 controls.
-We select the 20 controls using a random number generator.
-In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.
-
-A small set of paired required extra iterations to find 20 controls; 8 paired galaxies need an extra iteration, 1 paired galaxy need two extra iterations, and 1 paired galaxy needed three iterations.
-
-The control galaxies have their radial profiles of sSFR made with both the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard.
-We use the geometries and stellar masses from \simard\ and \citet{Mendel:2014} when the controls are being matched to pairs in the inside-IFU sample and we use the geometries and stellar masses from the NSA catalog when the controls are being matched to pairs in the outside-IFU sample.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Radial Profiles}\label{sec:radial}
+\subsection{Geometry}\label{sec:radial}
 
@@
 \centering
-\includegraphics[width=\linewidth]{fig/8083-12703.pdf}
-\caption[Example of the difference profiles for the mass-redshift selected control sample.]{The process for building the tailored control sample.
-The Left panel shows the paired galaxy's profile for sSFR.
-The Middle panel shows the profiles for sSFR for the selected 20 control galaxies in gray.
-The red profile is the median profile of the 20 control galaxies where the highlighted region about the profile is the standard error of the mean.
-The Right panel shows the difference between pair's profile and the stacked control profile.}
-\label{fig:dex}
+\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
+\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
+The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel.
+The dashed black profile represents the mean of the difference profiles).
+The colors of the profiles represent the mass range of the selected galaxies and the highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.}
+\label{fig:ssfr_prof}
 \end{figure*}
@@
 In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR.
-As mentioned in Sections \ref{sec:pair} and \ref{sec:control} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \simard\ to define the geometries of the galaxies.
+As mentioned in Section \ref{sec:data} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies.
 We calculate the inclination angle, {\it i}, of the galaxies using the major-to-minor axis ratios from the elliptical apertures;
@@
 The distance to each of the spaxels from the center of the MaNGA target is calculated using the 50\% half light radius to scale the size of the galaxy.
-The r-band elliptical S\'ersic apertures from \simard\ are used for the inside-IFU sample and their controls and the r-band elliptical Petrosian apertures from the NSA catalog are used for the outside-IFU sample and their controls.
+The r-band elliptical S\'ersic apertures from \citet{Simard:2011} are used for the inside-IFU sample and their controls and the r-band elliptical Petrosian apertures from the NSA catalog are used for the outside-IFU sample and their controls.
 
-The spaxels are binned into radius increments of 0.1 \reff\ from 0.0$-$2.5 \reff.
+The spaxels are binned into radius increments of 0.1 R/\reff\ from 0.0$-$2.5 R/\reff.
 Within each radius bin we take the median of the specific star formation rate.
@@
 
-We use our catalog of photometric objects and the \simard\ catalog to mask foregournd/background objects which may contaminate the data.
-Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \simard\ are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
+We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foregournd/background objects which may contaminate the data.
+Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
 
-We then construct difference profiles between the paired galaxies and the control galaxies.
-As mentioned in Section \ref{sec:control}, a paired galaxy is matched to 20 similar control galaxies.
-We take the individual averaged profiles of the control galaxies and take the median value of the profiles at each radius bin giving us a ``stacked" profile of control galaxies.
+With individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies.
+The first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins.
+In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset 20 control galaxies which have a similar stellar mass and redshift.
+
+\subsection{Mass-Binned Difference Profiles}\label{sec:mass-bin}
+
+In the first method, paired and control galaxies are grouped into four evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.0.
+Within each stellar mass bin, we create a median profile of log(sSFR) as a function of galactocentric radius for both paired and control galaxies.
+The control profiles are constructed using all available control galaxies within each mass bin.
+The error associated with the profile is the standard error of mean of the data at each radius bin.
+We show these ``stacked" profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}.
+
+Once the stacked profiles are made, we take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the profiles really represents a ratio between the pairs and controls in linear space).
+This gives us difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
+We will discuss the results of the difference profiles later in Section \ref{sec:results}.
+
+\subsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
+
+In the second method, we match each paired galaxy to a set of 20 control galaxies of a similar stellar mass and redshift, as mentioned in Section \ref{sec:control}.
+We take the individual averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin giving us a stacked profile of control galaxies.
 The error of the profile is the standard error of the mean of the individual profiles.
-We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of stacked profile over 1000 iterations.
+We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of the stacked profiles over 1000 iterations.
 This random selection contributes an error of about 0.1 dex.
 
-Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space (this means that the profiles really represents a ratio between the pairs and controls in linear space).
-An example of the construction of a difference profile is shown in Figure \ref{fig:dex}.
-We do this process for each of the 202 paired galaxies.
+Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space.
+We do this process for each of the 160 paired galaxies.
 
-The difference profiles at this stage have now been controlled for stellar mass, redshift, and galaxy size so we can freely stack these profiles to study the global properties of the merging galaxies.
-We take all of the $\Delta$log(sSFR) profiles and take the median within each radius bin to create a stacked profile which represents the whole pair sample, shown in Figure \ref{fig:ssfr_all}.
-We can also split the pair sample along different parameters; stellar mass, mass ratio, and projected separation to study how these profiles behave as a function of these parameters, shown in Figure \ref{fig:ssfr_full}.
+The difference profiles at this stage have now been controlled for stellar mass, redshift, and galaxy size.
+We can freely stack these profiles to study the global properties of the merging galaxies.
+We take all of the $\Delta$log(sSFR) profiles and take the median value within each radius bin to create a stacked profile of the individual difference profiles.
+We split the individual difference profiles into four evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.0 and stack the difference profiles within each mass bin.
+This gives us four difference profiles covering four different stellar mass ranges shown in the left hand panel of Figure \ref{fig:ssfr_mass}.
 The results of the profiles will discussed in detail in Section \ref{sec:results}.
+
+To study how the star formation in the centers of paired galaxies are affected by merger events, we extract the $\Delta$log(sSFR) from the individual difference profiles.
+We extract the value of $\Delta$log(sSFR) from the inner 0.5 R/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture.
+We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
 
@@
 \section{Results}\label{sec:results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_unsplit.pdf}
-\caption[]{\textbf{Left:} The individual difference profiles are shown in light grey while the stacked profile for the whole pair sample is shown in red.
-The highlighted region about the profile is the standard error of the mean of the stacked profile.
-\textbf{Right:} A histogram of the $\delta$log(sSFR) within the inner 0.5 \reff\ of the individual difference profiles.
-The red line shows the median value of the $\Delta$log(sSFR) enhancement, $\sim$0.25 dex.}
-\label{fig:ssfr_all}
-\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=\linewidth]{fig/ssfr_full.pdf}
-\caption[]{The $\Delta$log(sSFR) split into separate stellar mass bins.
-The left column gives the stacked difference profiles.
-The highlighted region about the profiles represents the standard error of the mean of the profile.
-The black dashed line represents the stacked profile of the full pair sample.
-The right column gives the nuclear $\Delta$log(sSFR) values.
+\includegraphics[width=\linewidth]{fig/ssfr_all_mass.pdf}
+\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
+The profiles are split into four different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile.
+The black dashed line represents the mean profile between the four difference mass ranges.
+In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown.
 The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
 The vertical error bars on the black squares represent the standard deviation within the bin.
-The horizontal, dashed black lines represent the median central enhancement of the full pair sample.
-The top row shows the paired galaxies split by total stellar mass, the middle panel shows the paired galaxies split by mass ratio, and the bottom panel shows the paired galaxies split by projected separation.
-}
-\label{fig:ssfr_full}
+The horizontal, dashed black line represents the median central enhancement of the pair sample.
+Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
+\label{fig:ssfr_mass}
 \end{figure*}
@@
 
-We take each of the individual difference profiles for all of the galaxy pairs and take the median value of the sSFR within each radius bin.
-This gives a single profile which describes the sSFR enhancements for the whole pair sample.
-We show this profile in the left hand panel of Figure \ref{fig:ssfr_all}.
-The sSFR is centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex which falls to zero around 1.0 \reff.
-The disks of the paired galaxies feature no enhancement or suppression to the sSFR.
-The figure also shows that there is a large amount of scatter between the individual difference profiles, so while the trend is for the paired galaxies to show central enhancement, there are several paired galaxies which feature sSFR suppression in their centers.
+\subsection{Stellar Mass}
 
-In the right hand panel of Figure \ref{fig:ssfr_all} we show a histogram for the $\Delta$log(sSFR) offset in the centers of the paired galaxies.
-To get this, we extract the values of $\Delta$log(sSFR) in the individual difference profiles from the inner 0.5 R/\reff\ and take the mean of the values.
-Again, this shows the preference for paired galaxies to show an enhancement to the star formation in their centers.
+In Figures \ref{fig:ssfr_prof} and \ref{fig:ssfr_mass}, we show the profile of $\Delta$log(sSFR) as a function of galactocentric radius between two different methods of comparing paired galaxies to control galaxies.
+In the first method (Section \ref{sec:mass-bin}) where pair and control galaxies are compared within different stellar mass bins.
+The difference profiles from this method show a central enhancement to the log(sSFR) of $\sim$0.3 $\pm$ 0.1 dex.
+The enhancement linearly falls to zero at 1.0 \reff\ after which the disks of the paired galaxies have zero enhancement/suppression to their sSFR.
 
-In the following sections we will break up the stacked profile into separate bins of total stellar mass, mass ratio, and projected separation.
-The radial profiles of $\Delta$log(sSFR) along with the nuclear $\Delta$log(sSFR) values from the inner 0.5 \reff\ broken up across each of the three parameters are shown in Figure \ref{fig:ssfr_full}.
+The $\Delta$log(sSFR) profile following the second method shows the same central sSFR enhancement albeit with smaller variances.
+Within the inner 1.0 \reff, there is a variance between the profile of 0.1 dex.
+Beyond 1.0 \reff, the variance increases 0.2 dex.
+This indicates that the second method of pair$-$ control comparison is superior to the first method.
 
-\subsection{Stellar Mass}
-We show the $\Delta$log(sSFR) profile split by the galaxy's total stellar mass in the top row of Figure \ref{fig:ssfr_full}.
-The level of the central sSFR enhancement for each of the stellar mass ranges is consistent with the level of enhancement for the full sample.
-This effect is better seen in the scatter plot of the central $\Delta$log(sSFR) offsets versus stellar mass where there is a flat distribution.
-
-In the disks of the paired galaxies, there is more scatter to the offsets of the profiles.
-The mass range, \logm\ $=$ 10.0$-$10.5, shows stronger suppression of sSFR in their disks while the mass range, \logm\ $=$ 9.0$-$9.5, show an enhancement to sSFR in their disks.
-There is no trend to sSFR enhancement/suppression with the stellar mass so the scatter in the profiles at large separation is likely due to a combination of the smaller sample sizes within each of the separate mass bins and due to the lower S/N at larger galactocentric radii.
-
-From this we see that the total stellar mass of a paired galaxy has no effect on the merger induced star formation within the galaxy.
-Massive galaxies have their specific star formation rate enhanced to the same degree as low mass galaxies.
-
-\subsection{Mass Ratio}
-While the total stellar mass between the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
-The mass ratio is calculated as the difference between stellar masses contained within the 50\% half light radius,
-
-\begin{equation}
-\Delta {\rm log}(M) = {\rm log}(M_{target}) - {\rm log}(M_{comp}) 
-\end{equation}
-
-Where M$_{target}$ is the mass of the MaNGA target galaxy and M$_{comp}$ is the mass of the companion galaxy.
-Note that we do not use the absolute value of the difference like how the mass ratio is typically used.
-We do this so that we can independently study how the star formation large central galaxies behave in comparison to small satellite galaxies.
-
-For the outside-IFU sample we use the stellar masses calculated from the r-band elliptical Petrosian apertures from the NSA catalog.
-For the inside-IFU sample, the neither the NSA catalog or \citet{Mendel:2014} will cover both galaxies.
-Instead we use stellar masses calculated from {\sc SPFIT} from the inner 2\arcsec\ of the galaxies.
-
-In the middle row of Figure \ref{fig:ssfr_full} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log(M) $=$ 0.0.
-These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.15 dex higher than the average central enhancement of the whole sample.
-This enhancement falls with wider mass ratios and pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.2$-$0.25 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.
-
-We also use the mass ratio to explore how the merger induced tidal torques affect paired galaxies with large mass ratios, $|\Delta$log(M)$|$ > 0.5.
-We use the mass ratio to separate the massive central galaxy from satellite galaxies.
-A paired galaxy with a positive mass ratio is the more massive galaxy of the pair while a paired galaxy with negative mass ratio is the less massive galaxy.
-We see that the less massive galaxy of a pair show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to the more massive galaxy.
-This shows us that satellite galaxies are more susceptible to tidal interactions than the central galaxies in the pair system.
-
-\subsection{Projected Separation}
-
-Finally we look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_full}.
-The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
-The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are $\sim$0.1 dex below the median.
-
-This effect can be seen most clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
-The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc.
-While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex.
-Within 10 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.5 dex.
-
-For the galaxies with the closest separations, r$_p$ $<$ 5 kpc, $\Delta$log(sSFR) drops to zero.
-This is strange as we would expect that the closest pairs would show the strongest enhancements to their star formation as they are currently or have just passed the first pericenter.
-We will discuss the potential causes of the zero enhancement in the centers of the closest galaxies in Section \ref{sec:sum}.
+The profiles of either method show no dependence on the stellar mass of the galaxies.
+This effect is better seen in the right hand panel of Figure \ref{fig:ssfr_mass} where the nuclear $\Delta$log(sSFR) of the paired galaxies fall within 0.1 dex of the mean nuclear sSFR enhancement.
+Low mass galaxies have their star formation enhanced at the same level as high mass galaxies.
+The similar level of $\Delta$log(sSFR) in high and low mass galaxies will mean that the fractional mass growth between high and low mass galaxies will be different.
 
 \subsection{Future Mass Growth}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/mass_gain_1.pdf}
-\caption[Example of the calculation of the fractional mass gain due to merger induced star formation for a single mass bin.]{In the Left panel we fit a model gaussian to the $\Delta$log(sSFR) profiles.
-In the Middle panel we plot the log(sSFR) profile for the stacked profiles of the control galaxies (black).
-We then add the modeled $\Delta$log(sSFR) profile to the control profile (red).
-The error bars represent the standard error of the mean of the profiles.
-In the Right panel we show the fractional mass gain due to star formation in the control galaxies (black) and in the paired galaxies (red).
-The blue profile is the subtraction between the pairs and controls and represents the fractional mass gain due to merger induced star formation.
-The error bars represent the standard error of the mean of the profiles.
-}
-\label{fig:mass_gain}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/mass_gain.pdf}
-\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass gain due to merger induced star formation over a dynamical timescale, $\tau$ $=$ 1 Gyr.
-The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
-}
-\label{fig:mass_gain_sum}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The higher rate of star formation in interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
+The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
 The question is whether or not the advanced mass growth rate is significant.
 
-We will use a simple model to estimate the enhanced mass growth rate due to merger induced star formation.
+To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given dynamic timescale, $\tau_{dyn}$.
 A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
@@
 
-Where $\tau_{dyn}$ is the dynamical timescale of the merger event.
 For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in hydrodynamical simulations \citep{Boylan-Kolchin:2008}.
@@
 We then add the modeled difference profile to the stacked control profile in the same mass range in log space.
-We then take the difference between the profiles in linear space and multiple the difference by the 1 Gyr timescale.
-This process is shown for a single mass range in Figure \ref{fig:mass_gain}.
+We then take the difference between the profiles in linear space and multiply the difference by the 1 Gyr timescale.
 
 We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
-The mass growth rate is largely restricted to the centers of the galaxies, following the centrally enhanced sSFR.
+The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 \reff, following profile of the $\Delta$log(sSFR).
 The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
@@
 
+In the context of galaxy evolution, where less massive galaxies merge to form larger galaxies, the merger induced star formation contributes a significant amount of stellar mass on top of the stellar mass contribution from the mixing of the two galaxies.
+Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion and Summary}\label{sec:sum}
-%\label{sec:discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/mass_gain.pdf}
+\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over a dynamical timescale, $\tau$ $=$ 1 Gyr.
+The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
+}
+\label{fig:mass_gain_sum}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Nuclear comp with prev works
-In this study we saw that the sSFR is centrally enhanced in the centers of paired galaxies by $\sim$0.25 dex ($\sim$1.78$\times$) in comparison to isolated galaxies.
-This enhancement is consistent with what is predicted by hydrodynamical simulations \citep{Scudder:2012} and is also consistent with previous observational surveys \citep{Ellison:2008, Barrera-Ballesteros:2015, Pan:2019}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
+\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
+\label{fig:ssfr_dmsep}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-When looking at the disks of our paired galaxies, we found zero enhancement or suppression to the sSFR.
-A sample of galaxy pairs from the CALIFA survey featured a suppression to the sSFR (using the H$\alpha$ equivalent width as a proxy for the sSFR) of $\sim$-0.13 dex \citep{Barrera-Ballesteros:2015}.
-\citet{Pan:2019} built radial profiles for galaxy pairs in MaNGA and found that the sSFR is enhancement by 0.15 dex.
-We note that in our work that there is a large amount of scatter seen in the $\Delta$log(sSFR) in the disks of the paired galaxies, so many paired galaxies feature enhanced sSFR and while other feature suppressed sSFR but that the $\Delta$log(sSFR) averages to zero over our sample.
+In this work, we primarily focused on how the $\Delta$log(sSFR) in paired galaxies behaves as a function of stellar mass.
+We also explored how the $\Delta$log(sSFR) behaves as a function of the mass ratio between the paired galaxies and the projected separation between the paired galaxies.
+While we see hints that the $\Delta$log(sSFR) is affected by the mass ratio and projected separation, these results are less definitive than the $\Delta$log(sSFR) profile's lack of dependence on stellar mass.
+
+\subsection{Mass Ratio}
+While the total stellar mass between the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
+The mass ratio here is calculated as the difference between stellar masses contained within the 50\% half light radius,
+
+\begin{equation}
+\Delta {\rm log}(M) = {\rm log}(M_{target}) - {\rm log}(M_{comp}) 
+\end{equation}
+
+Where M$_{target}$ is the stellar mass of the MaNGA target galaxy and M$_{comp}$ is the stellar mass of the companion galaxy.
+Note that we do not use the absolute value of the difference like how the mass ratio is typically used.
+We do this so that we can independently study how the star formation large central galaxies behave in comparison to small satellite galaxies.
+
+For the outside-IFU sample we use the stellar masses calculated from the r-band elliptical Petrosian apertures from the NSA catalog.
+For the inside-IFU sample, neither the NSA catalog nor \citet{Mendel:2014} will cover both galaxies.
+Instead we use stellar masses calculated from {\sc SPFIT} from the inner 2\arcsec\ of the galaxies.
+
+In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log(M) $=$ 0.0.
+These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.15 dex higher than the average central enhancement of the whole sample.
+This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.2$-$0.25 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.
+
+We also use the mass ratio to explore how the merger induced tidal torques affect paired galaxies with large mass ratios, $|\Delta$log(M)$|$ > 0.5.
+We use the mass ratio to separate the massive central galaxy from satellite galaxies.
+A paired galaxy with a positive mass ratio is the more massive galaxy of the pair while a paired galaxy with negative mass ratio is the less massive galaxy.
+We see that the less massive galaxy of a pair show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to the more massive galaxy.
+This shows us that satellite galaxies may be more susceptible to tidal interactions than the central galaxies in the pair system.
 
@@
 It has been a convention to split galaxy pairs in major mergers, $|$log(M)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log(M)$|$ $\le$ 1.0.
-In this work, we can see that the mass ratio range used in galaxy pair studies can safely be widened to at least $|$log(M)$|$ $\le$ 2.0 so that larger pair samples can be constructed.
+In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log(M)$|$ $\le$ 2.0 so that larger pair samples can be constructed.
 
@@
 
-We saw that the $\Delta$log(sSFR) enhancement increases with closer projected separations \citet{Ellison:2008, Scudder:2012, Patton:2013}.
-This is unsurprising as nearby galaxy pairs will have just completed a close interaction.
-This enhancement persists out to wide separations, where galaxy pairs separated by 50 kpc, still show a substantial enhancement to the sSFR.
-\citet{Patton:2013} showed that the central enhancements to sSFR persists out to 150 kpc.
+\subsection{Projected Separation}\label{sec:sep}
 
-The closest pairs in our sample, pairs closer than 5 kpc, show no enhancement to the sSFR.
+We also look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_dmsep}.
+The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
+The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are $\sim$0.1 dex below the median.
+
+This effect can be seen most clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
+The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc.
+While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex.
+Within 15 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.5$-$0.6 dex.
+
+The sSFR enhancement increasing with closer projected separations is to be expected and has been shown in previous studies \citep{Ellison:2008, Scudder:2012, Patton:2013}.
+The passage of the first pericenter is predicted to trigger a burst of star formation which falls as the two galaxies separate \citep{Scudder:2012}.
+The sSFR enhancement in our sample persists out to 50 kpc, \citet{Patton:2013} showed that the burst of star formation can persist out to 150 kpc.
+
+For the galaxies with the closest separations, r$_p$ $<$ 5 kpc, $\Delta$log(sSFR) drops to zero.
+This is strange as we would expect that the closest pairs would show the strongest enhancements to their star formation as they are currently or have just passed the first pericenter.
 This seems odd as one would think that these galaxies should show the strongest enhancements to the sSFR.
-It is important to remember that this sample contains no post-merger galaxies so we will not see the second large burst of star formation when the two galaxies are coalescing.
-The closest paired galaxies will either be pairs which are about to go through their first pericenter or galaxies which have just passed their first pericenter.
-In the galaxies which have passed their first pericenter, we believe that the timescale is still too small for the interaction induced gas inflows to travel from the galaxy's disk to its nucleus.
-Since the gas inflows haven't yet impacted the galaxy's nucleus, no enhancements to the sSFR will be seen.
-This delay between the first pericenter of the merger event and the burst of star formation has been shown in the hydrodynamical simulations of \citet{Scudder:2012}.
 
-We have also modeled the future mass growth of our sample of paired galaxies.
-Our model shows that the merger induced star formation could substantially accelerate the mass growth in the centers of the interacting galaxies in comparison to secular mass growth.
-Since the enhanced star formation and thereby mass growth is largely restricted to the centers of the interacting galaxies, these close interactions will produce galaxies with higher concentrations of stellar mass in their centers.
+This lack of $\Delta$log(sSFR) could be due to a couple of reasons.
+First, it may be due to the limited sampling of this separation range, there are only 6 paired galaxies in this range.
+A second explanation could be that we are observing merging galaxies which are just going though their first pericenter, but have yet to have the burst of star formation.
+Not enough time has elapsed for the gas inflows from the disks of the galaxies to reach the centers of the galaxies.
+The hydrodynamical simulations of \citet{Scudder:2012} show this delay in the burst of star formation, where the burst of star formation only reaches its peak after 0.3 Gyr after the passage of the first pericenter.
+
+\subsection{Comparison with Previous Works}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/nuc_sep.pdf}
+\caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Patton:2013} (Green), \citet{Scudder:2012} (Blue), and \citet{Bustamante:2020} (Purple).
+}
+\label{fig:nuc_sep}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/prof_comp.pdf}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work (red) compared against those of \citet{Pan:2019} (Blue) and \citet{Thorp:2019} (Green).}
+\label{fig:prof_comp}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Patton:2013, Scudder:2012, Bustamante:2020}.
+We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}.
+We find that our pairs generally feature higher level of SFR enhancement in their centers, by $\sim$0.0$-$0.2 dex.
+Further, we probe galaxies with projected separations below 5 kpc, a projected separation range not covered in previous works.
+As mentioned in Section \ref{sec:sep}, we find a $\Delta$log(SFR) of zero implying that we are viewing galaxies that are about to or have just passed their first pericenter.
+
+Our sample only covers projected separations within 50 kpc, while previous surveys cover out to 100$-$200 kpc.
+While our sample covers a smaller separation range, the $\Delta$log(SFR) of our sample at 50 kpc is roughly the same level as \citet{Scudder:2012} and \citet{Patton:2013} at the same projected separation.
+This shows that the central SFR enhancement of our sample is consistent with with what has been found in previous works.
+
+In Figure \ref{fig:prof_comp} we look at the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
+\citet{Pan:2019} examines a set of paired galaxies in the MaNGA survey while \citet{Thorp:2019} examines a set of post-merger galaxies in the MaNGA survey.
+The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughtly $\sim$0.05$-$0.2 dex higher than our sample.
+The $\Delta$log(sSFR) profile is closest to our work at the centers of the galaxy pairs but then begins to diverge further out into the galaxies' disks.
+Our paired galaxies show zero sSFR enhancement in their disks past \reff\ $=$ 1.0 while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+
+The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.15 higher than our sample of paired galaxies.
+Their $\Delta$log(sSFR) profile follows our sample's profile closely between 0.25$-$1.0 \reff.
+The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
+The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 \reff\ of $\sim$0.1$-$0.15 dex.
+The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
+
+\citet{Barrera-Ballesteros:2015} studied the sSFR in paired galaxies in the CALIFA IFS survey using the H$\alpha$ equivalent width (\ewha) as a proxy.
+They compared the sSFR in the centers of paired galaxies to their disks by varying the aperture diameters from which they extract the \ewha.
+They found that the sSFR is enhanced in the centers of the paired galaxies but suppressed in their disks.
+Between our work, \citet{Barrera-Ballesteros:2015}, and \citet{Pan:2019} there three is different scenarios; one where the disks of the paired galaxies see no change to the sSFR, one where the sSFR is suppressed, and one where the sSFR is enhanced.
+
+Looking at individual difference profiles in our work, we see that there is a large variance in the $\Delta$log(sSFR) where there are as many paired galaxies with sSFR enhancement in their disks as there are paired galaxies with suppression in there disks.
+The end result is that the average of the $\Delta$log(sSFR) is zero.
+The merger induced effects seen in the disks of the paired galaxies may be more complicated than what is seen in the centers of the galaxies.
 \\
@@
 In this work, we studied a sample of paired, star forming galaxies using the MaNGA IFS survey.
-We have made a sample of 913 paired galaxies of which 202 are SFGs.
-We compared the radial profiles of the paired galaxies with 1862 isolated MaNGA SFGs.
-We found the following;
+We have made a sample of 160 star forming galaxy pairs along with a set of 1891 star forming control galaxies.
+We compared the radial profiles of the paired galaxies with those of the controls galaxies and found the follwing;
 
 \begin{enumerate}
-\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.25 $\pm$ 0.1 dex. 
+\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.30 $\pm$ 0.1 dex. 
 \item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show no signs of either sSFR enhancement or sSFR suppression. 
@@
 \item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair, $\sim$0.1 dex.
-\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$10 kpc have their sSFR enhanced by 0.5 $\pm$ 0.1 dex.
+\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.5$-$0.6 $\pm$ 0.1 dex.
 The galaxies within 5 kpc experience no central enhancement to their sSFR.
@@
 \item The paired galaxies will experience a faster mass growth rate of secular evolution of 1.6$-$2.3$\times$.
-The growth rate is highest for massive galaxies; however, the the low mass galaxies will see the stellar mass in their center more substantially increased over a 1 Gyr timescale.
+The growth rate is highest for massive galaxies; however, the the low mass galaxies will see a higher fractional mass increase in comparison to the preexisting stellar mass.
 

### 2020-07-17 maintex.tex
title change

@@
 
-\title{SDSS-IV MaNGA: Radial Profiles of Specific Star Formation Rate in Nearby Interacting Galaxies}
+\title{SDSS-IV MaNGA: The Universal Profile of Enhanced Star Formation in Close Galaxy Pairs}
 
@@
 We study the spatial profile of the star formation rate (SFR) in a sample of 160 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
-We find that the specific star formation rate (sSFR) is centrally enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
-We find that the level of the central enhancement is independent of galaxy mass.
+We find that the specific star formation rate (sSFR) is centrally (e.g.
+within a single effective radius) enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
+We split the radial profile into four separate stellar mass bins from \logm\ $=$ 9.0$-$11.0 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies.
+Within one effective radius, the sSFR enhancement in each of the mass bins falls within $\sim$0.1 dex of the median profile for the whole pair sample.
 Low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.

### 2020-07-17 maintex.tex
minor edits

@@
 This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable out to projected separations of 150 kpc \citep{Patton:2013}.
-The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta {\rm log} {\it M} |$, between the two galaxies \citep{Ellison:2008}.
+The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta$log($M$)$|$, between the two galaxies \citep{Ellison:2008}.
 Similar mass galaxies show the strongest sSFR effects while large central galaxies interacting with small satellite galaxies show weaker sSFR effects.
@@
 We found that approximately 5.7\% of the MaNGA galaxies have a companion galaxy contained within the field-of-view of a single IFU.
-In this work, we will use a version of this sample updated for the recent MaNGA Data Release 16 (DR16) and we will further supplement this with a sample of companion galaxies identified outside the field-of-view of the MaNGA IFUs.
+In this work, we will use a version of this sample updated for the recent MaNGA Data Release 16 (DR16) \citep{Ahumada:2020} and we will further supplement this with a sample of companion galaxies identified outside the field-of-view of the MaNGA IFUs.
 
@@
 The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
-MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
+MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 R/\reff\ and 2.5 R/\reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
 In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.
@@
 We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foregournd/background objects which may contaminate the data.
-Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
+Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
 
@@
 The difference profiles from this method show a central enhancement to the log(sSFR) of $\sim$0.3 $\pm$ 0.1 dex.
-The enhancement linearly falls to zero at 1.0 \reff\ after which the disks of the paired galaxies have zero enhancement/suppression to their sSFR.
+The enhancement linearly falls to zero at 1.0 R/\reff\ after which the disks of the paired galaxies have zero enhancement/suppression to their sSFR.
 
 The $\Delta$log(sSFR) profile following the second method shows the same central sSFR enhancement albeit with smaller variances.
-Within the inner 1.0 \reff, there is a variance between the profile of 0.1 dex.
-Beyond 1.0 \reff, the variance increases 0.2 dex.
+Within the inner 1.0 R/\reff, there is a variance between the profile of 0.1 dex.
+Beyond 1.0 R/\reff, the variance increases 0.2 dex.
 This indicates that the second method of pair$-$ control comparison is superior to the first method.
@@
 We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
-The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 \reff, following profile of the $\Delta$log(sSFR).
+The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 R/\reff, following profile of the $\Delta$log(sSFR).
 The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
@@
 The $\Delta$log(sSFR) profile is closest to our work at the centers of the galaxy pairs but then begins to diverge further out into the galaxies' disks.
-Our paired galaxies show zero sSFR enhancement in their disks past \reff\ $=$ 1.0 while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+Our paired galaxies show zero sSFR enhancement in their disks past 1.0 R/\reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
 
 The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.15 higher than our sample of paired galaxies.
-Their $\Delta$log(sSFR) profile follows our sample's profile closely between 0.25$-$1.0 \reff.
+Their $\Delta$log(sSFR) profile follows our sample's profile closely between 0.25$-$1.0 R/\reff.
 The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
-The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 \reff\ of $\sim$0.1$-$0.15 dex.
+The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 R/\reff\ of $\sim$0.1$-$0.15 dex.
 The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
@@
 \begin{enumerate}
-\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.30 $\pm$ 0.1 dex. 
+\item The sSFR is centrally enhanced within the inner 1.0 R/\reff\ by 0.30 $\pm$ 0.1 dex. 
 \item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show no signs of either sSFR enhancement or sSFR suppression. 

### 2020-07-27 maintex.tex
updated Figures

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/bpt_spax.pdf}
-\caption[]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
+%\begin{figure}
+%\centering
+%\includegraphics[width=\linewidth]{fig/bpt_spax.pdf}
+%\caption[]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
 The color of each bin represents the number density of spaxels, normalized to one.
 The solid black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001} and the dashed black line is the analytical \citet{Kauffmann:2003} line.}
-\label{fig:bpt}
-\end{figure}
+%\label{fig:bpt}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=\linewidth]{fig/ssfr_all_mass.pdf}
+\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
 \caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=\linewidth]{fig/nuc_sep.pdf}
+\includegraphics[width=3in]{fig/nuc_sep.pdf}
 \caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Patton:2013} (Green), \citet{Scudder:2012} (Blue), and \citet{Bustamante:2020} (Purple).
@@
 \label{fig:nuc_sep}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-07-28 maintex.tex
edits based on Hai's suggestions in Sections 1-2

@@
 
-\title{SDSS-IV MaNGA: The Universal Profile of Enhanced Star Formation in Close Galaxy Pairs}
+\title{
+SDSS-IV MaNGA: Mass Independent Star Formation Enhancement in Close Galaxy Pairs
+}
 
@@
 \begin{abstract}
-We study the spatial profile of the star formation rate (SFR) in a sample of 160 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey.
+We study the spatial profile of the star formation rate (SFR) in a sample of {\it 160} interacting galaxies within the SDSS-IV MaNGA survey.
 We find that the specific star formation rate (sSFR) is centrally (e.g.
 within a single effective radius) enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
-We split the radial profile into four separate stellar mass bins from \logm\ $=$ 9.0$-$11.0 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies.
+We split the radial profile into five separate stellar mass bins from \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies.
 Within one effective radius, the sSFR enhancement in each of the mass bins falls within $\sim$0.1 dex of the median profile for the whole pair sample.
-Low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
-Assuming a constant burst merger induced star formation over a 1 Gyr period, the mass growth rate in the centers of the paired galaxies will be 1.6$-$2.3$\times$ higher than secular mass growth.
-Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate which is $\sim$4.3 higher than that of high mass galaxies.
+We then use a second method to compare paired galaxies and control galaxies where each paired galaxies is matched to a set of 20 control galaxies based on stellar mass and redshift.
+The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
+Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate of 1$-$7\%, assuming a constant burst merger induced star formation over a 1 Gyr period.
 This indicates that merger induced star formation has a significant impact on the mass evolution of low mass galaxies.
@@
 %%%Observations%%%
-Centrally enhanced star formation has also been observed in galaxy pairs with large spectroscopic surveys including; CfA2  \citep{Barton:2000, Woods:2006}, 2dF \citep{Lambas:2003}, AEGIS \citep{Lin:2007}, SDSS \citep{Ellison:2008}, COSMOS \citep{Kartaltepe:2007,Xu:2012}, PRIMUS \citep{Wong:2011}, and GAMA \citep{Robotham:2014}.
+Centrally enhanced star formation has also been observed in galaxy pairs with large spectroscopic surveys including; CfA2 (Center of Astrophysics Redshift Survey)  \citep{Barton:2000, Woods:2006}, 2dF (Two Degree Field) \citep{Lambas:2003}, AEGIS (All-Wavelength Extended Groth Strip International Survey) \citep{Lin:2007}, SDSS (Sloan Digital Sky Survey) \citep{Ellison:2008}, COSMOS (Cosmic Evolution Survey) \citep{Kartaltepe:2007,Xu:2012}, PRIMUS (Prism Multi-Object Survey) \citep{Wong:2011}, and GAMA (Galaxy and Mass Assembly) \citep{Robotham:2014}.
 
@@
 % Organization
-This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we discuss the results of the constructed radial profiles, and in Section \ref{sec:sum} we discuss and summarize the findings of the work.
+This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we discuss the mass independence of the constructed radial profiles, in Section \ref{sec:disc} we explore the radial profiles as a function of the mass ratio and projected separation and we compare our work against previous works, and in Section \ref{sec:sum} we summarize the findings of the work.
 
@@
 The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-The MaNGA galaxies with close companions are marked with {\it grey diamonds}.
+Inside and outside-IFU pairs are marked with {\it grey diamonds}.
 From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
@@
 
-The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
+The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
 MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 R/\reff\ and 2.5 R/\reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
@@
 \begin{equation}\label{eq:blue}
-NUV-r = 3.1682 - 0.16 (M_i+18)
+NUV-r = 3.1682 - 0.16 (\mathcal{M}_i+18)
 \end{equation}
 \begin{equation}\label{eq:red}
-NUV-r = 4.7866 - 0.04 (M_i+18)
+NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18)
 \end{equation}
@@
 
-After the star formation cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}. We also set a stellar mass range of \logm\ $=$ 9.0$-$11.0.
+After the star formation cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}.
+The resulting sample cover a stellar mass range of \logm\ $=$ 9.0$-$11.5.
 
@@
 
-In our previous work, \citet{Fu:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
+In our previous work, \citet{Fu:2018}, using the 2168 unique galaxies form DR14 \citep{Abolfathi:2018} we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
 In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
@@
 
-We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures from \citet{Simard:2011} and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}.
-We use \citet{Simard:2011} instead of the apertures from the NSA catalog, which the MaNGA sample is drawn from, because the apertures in the NSA catalog often fail to fit the MaNGA galaxies when there is another nearby, bright object.
-
-The \citet{Simard:2011} and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample.
-Out of the 124 SFGs in the inside-IFU sample, 33 of the SFGs are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
-
 \subsection{Outside-IFU Sample}\label{sec:outside}
@@
 After restricting the sample to SFGs, we have 127 MaNGA targets with paired galaxies outside of the IFU.
-
-We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample.
-For cases where the identified galaxy pair is outside of the MaNGA IFU, the NSA catalog's algorithm is able to fit the MaNGA target's geometry well.
-We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.
 
@@
 We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation.
-Ionization sources are often separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.
+To separate ionization sources, we use the theoretical maximum starburst line from \citet{Kewley:2001} (Equation \ref{eq:kewley}).
 
@@
 \end{equation}
-\begin{equation}\label{eq:kauffmann}
-\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.05} + 1.3}
-\end{equation}
 
 Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel.
-We depict the BPT diagram for each spaxel in the MaNGA survey in Figure \ref{fig:bpt} along with the demarcations for star formation from \citet{Kewley:2001} and \citet{Kauffmann:2003}.
 We use the \citet{Kewley:2001} demarcation line as the limit for classifying star formation in the MaNGA spaxels.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures from \citet{Simard:2011} and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}.
+We use \citet{Simard:2011} instead of the apertures from the NSA catalog, which the MaNGA sample is drawn from, because the apertures in the NSA catalog often fail to fit the MaNGA galaxies when there is another nearby, bright object.
+
+The \citet{Simard:2011} and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample.
+Out of the 124 SFGs in the inside-IFU sample, 33 of the SFGs are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
+
+We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample.
+For cases where the identified galaxy pair is outside of the MaNGA IFU, the NSA catalog's algorithm is able to fit the MaNGA target's geometry well.
+We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.
+\\
 
@@
 In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset 20 control galaxies which have a similar stellar mass and redshift.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{sec:results}
 
@@
 We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{sec:results}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Summary}\label{sec:sum}
+\section{Discussion}\label{sec:disc}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The merger induced effects seen in the disks of the paired galaxies may be more complicated than what is seen in the centers of the galaxies.
-\\
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Summary and Conclusion}\label{sec:sum}
+\section{Summary and Conclusion}\label{sec:sum}
 

### 2020-08-04 maintex.tex
next draft

@@
 \begin{abstract}
-We study the spatial profile of the star formation rate (SFR) in a sample of {\it 160} interacting galaxies within the SDSS-IV MaNGA survey.
+We study the spatial profile of the star formation rate (SFR) in a sample of {\it 220} interacting galaxies within the SDSS-IV MaNGA survey.
 We find that the specific star formation rate (sSFR) is centrally (e.g.
@@
 
-After the star formation cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}.
+On top of the color selection cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}.
 The resulting sample cover a stellar mass range of \logm\ $=$ 9.0$-$11.5.
@@
 
-In our previous work, \citet{Fu:2018}, using the 2168 unique galaxies form DR14 \citep{Abolfathi:2018} we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
+In our previous work, \citet{Fu:2018}, using the 2168 unique galaxies form DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
 In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
 
-We use SDSS photometric objects to create a catalog of objects within the fields of view of the MaNGA IFUs.
-We extract their spectra from the MaNGA datacubes through a 1\arcsec\ aperture and fit the spectra with {\sc SPFIT} assuming the MaNGA target's redshift.
-The spectra is then sorted into different categories; ``good" galaxy spectra, broad-line AGN (active galactic nuclei), foreground star, foreground/background galaxies, or poor S/N objects.
+We identify potential paired galaxies by overlaying SDSS photometric objects over the MaNGA fields of view.
+We manually inspect each MaNGA field, removing photometric objects which are over-deblended galaxy fragments and adding any objects missed by the SDSS photometric catalog.
+At this stage the object catalog includes any foreground stars and foreground/background galaxies along with the potential paired galaxies.
+
+To select paired galaxies out of our object catalog, we inspect the spectra of each object.
+We use our own {\sc IDL} based spectral fitting code, {\sc SPFIT}, to model the spectra from the MaNGA datacubes.
+{\sc SPFIT} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
+Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
+
+The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories; ``good" galaxy spectra, broad-line AGN (active galactic nuclei), foreground star, foreground/background galaxies, or poor S/N objects.
 The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
@@
 From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU.
-We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions and we also require that the galaxies are classified as star forming by the CMD diagram.
-These requirements reduce our sample down to 124 star forming galaxies (SFGs).
+We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions.
+Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples.
+We also require that the galaxies are classified as star forming by the CMD diagram.
+These requirements reduce our sample down to 87 star forming galaxies (SFGs).
 
@@
 
-From the NSA catalog's 641,409 galaxies, we find 361 galaxies which are paired to MaNGA targets.
+From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets.
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-After restricting the sample to SFGs, we have 127 MaNGA targets with paired galaxies outside of the IFU.
+After restricting the sample to SFGs, we have 133 MaNGA targets with paired galaxies outside of the IFU.
 
 \subsection{Control Sample}\label{sec:control}
-We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
-This gives us a set of 1891 SFGs and 1528 SFGs which are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
 
@@
 
-To control for stellar mass, we set a 0.1 dex stellar mass limit between a paired galaxy and the potential control galaxies.
-To restrict the redshift between the control and paired galaxies, we select control galaxies which are drawn from the same MaNGA subsample (e.g.
+We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
+This gives us a set of 1891 SFGs and 1528 SFGs which are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
+
+We then set two separate methods for comparing the paired galaxies with the control galaxies.
+In the first method, we simply split the galaxies into separate stellar mass bins.
+We then compare paired galaxies and control galaxies within each stellar mass bin.
+
+In the second method, we control for both stellar mass and redshift.
+To do this, we set a 0.1 dex stellar mass limit between a paired galaxy and the potential control galaxies.
+Then we restrict the redshift between the control and paired galaxies, by selecting control galaxies which are drawn from the same MaNGA subsample (e.g.
 Primary or Secondary) as the paired galaxy.
@@
 By setting a 0.1 dex stellar mass cut and requiring that the galaxies be in the same MaNGA subsample, we effectively set a z $\le$ $\sim$0.025 redshift cut.
-We note that the MaNGA galaxies with stellar masses above \logm\ $\ge$ 11.0 have a wide redshift distribution, our galaxy samples are restricted to a stellar mass range between \logm\ $=$ 9.0$-$11.0.
 
@@
 
-The control galaxies have their radial profiles of sSFR made with both the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \citet{Simard:2011}.
-We use the geometries and stellar masses from \citet{Simard:2011} and \citet{Mendel:2014} when the controls are being matched to pairs in the inside-IFU sample and we use the geometries and stellar masses from the NSA catalog when the controls are being matched to pairs in the outside-IFU sample.
+While the first method is very basic in comparison to the second method, we will see in Section \ref{sec:results} that the first method is sufficient to see the central enhancement to the star formation rate and the mass independence of the star formation enhancement.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=\linewidth]{fig/bpt_spax.pdf}
-%\caption[]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples.
-The color of each bin represents the number density of spaxels, normalized to one.
-The solid black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001} and the dashed black line is the analytical \citet{Kauffmann:2003} line.}
-%\label{fig:bpt}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Emission Line Extraction}
@@
 %%% SPFIT
-We use our own {\sc IDL} based spectral fitting code, {\sc SPFIT}, to model the spectra from the MaNGA datacubes.
-{\sc SPFIT} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
-Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
-The algorithm provides us with measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
+We use {\sc SPFIT} to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
 
@@
 The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
-The extinction correction is applied to all of the extracted emission lines.
+
+\begin{equation}
+A_V = 6.78\ {\rm log} \left[(H\alpha/H\beta)/2.85 \right]
+\end{equation}
+
+The V-band extinction is then used to calculate the wavelength dependent extinciton A$_{\lambda}$;
+
+\begin{equation}
+A_{\lambda}(x) = A_V \left(a(x) + b(x) / R_v \right)
+\end{equation}
+
+where $x = 1/\lambda$ and $a(x)$ and $b(x)$ are the coefficients for the extinction curve from \citet{ODonnell:1994}. The extinction corrected flux is then;
+
+\begin{equation}
+F'(\lambda) = F(\lambda) * 10^{0.4 A_{\lambda}(x)}
+\end{equation}
+
+This extinction correction is applied to all of the extracted emission lines.
 
@@
 
-We measure the SFR from the H$\alpha$ luminosity, L$_{H\alpha}$, calculated from the H$\alpha$ flux.
+We measure the SFR from the H$\alpha$ luminosity, L$_{{\rm H}\alpha}$, calculated from the H$\alpha$ flux.
 We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.
@@
 \begin{equation}\label{eq:sfr}
-\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
+\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{{\rm L}_{H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
 \end{equation}
@@
 This will allow us to compare the SFR in high mass regions, like the centers of the galaxies, to the SFR lower mass regions, like the disk of the galaxies.
+We have also found a strong correlation between sSFR and \ewha and have found the same results using \ewha.
+This is useful to check as \ewha\ is an observable and independent on {\sc SPFIT}'s measurement of the stellar mass.
 
@@
 
-It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic HII regions and AGN on the BPT diagram \citep{Stasinska:2008}.
-We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to mask retired spaxels \citet{Cid-Fernandes:2011}.
+It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
+We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to mask retired spaxels \citep{Cid-Fernandes:2011}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Geometry}\label{sec:radial}
+\subsection{Geometry of Galaxies}\label{sec:radial}
 
@@
 
-We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures from \citet{Simard:2011} and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}.
-We use \citet{Simard:2011} instead of the apertures from the NSA catalog, which the MaNGA sample is drawn from, because the apertures in the NSA catalog often fail to fit the MaNGA galaxies when there is another nearby, bright object.
+In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR.
+First, the geometry of the galaxies need to be defined.
+We use the $r$-band elliptical Petrosian apertures from the NSA catalog and the $r$-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies.
 
-The \citet{Simard:2011} and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample.
-Out of the 124 SFGs in the inside-IFU sample, 33 of the SFGs are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
+The NSA catalog has complete coverage over the MaNGA sample (since MaNGA selects its targets from this catalog); however, it tends to fail to properly fit paired galaxies with close on-sky separations.
+We found that the apertures from \citet{Simard:2011} work better for these close galaxies, but the catalog does not completely cover the MaNGA sample.
+We use NSA catalog for the outside-IFU pair sample because they are well separated on the sky and the \citet{Simard:2011} catalog on the inside-IFU sample.
+In the cases where an Inside-IFU paired galaxy is not covered by \citet{Simard:2011}, we use the ellipse from the NSA catalog.
 
-We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample.
-For cases where the identified galaxy pair is outside of the MaNGA IFU, the NSA catalog's algorithm is able to fit the MaNGA target's geometry well.
-We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.
-\\
+We fit the geometry with aperture from both catalog when available.
+When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
+When making the comparison with the second method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
 
-In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR.
-As mentioned in Section \ref{sec:data} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies.
+We compared the magnitudes extracted from the two apertures for the control galaxies and found that they are in close agreement.
+This means that the geometries between the two surveys must be in close agreement and the profiles of a galaxy fitted with a NSA aperture can be confidently compared against a galaxy fitted with an aperture from \citet{Simard:2011}.
+
 We calculate the inclination angle, {\it i}, of the galaxies using the major-to-minor axis ratios from the elliptical apertures;
@@
 The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies.
-The distance to each of the spaxels from the center of the MaNGA target is calculated using the 50\% half light radius to scale the size of the galaxy.
-The r-band elliptical S\'ersic apertures from \citet{Simard:2011} are used for the inside-IFU sample and their controls and the r-band elliptical Petrosian apertures from the NSA catalog are used for the outside-IFU sample and their controls.
+We use the 50\% half light radius, the effective radius (\reff) to scale the sizes of the galaxies.
+Doing this will allow use the compare galaxies of different sizes against each other.
 
+\subsection{Radial Profiles}
+
+Once the geometry of the galaxies are set, we can build the radial profiles.
 The spaxels are binned into radius increments of 0.1 R/\reff\ from 0.0$-$2.5 R/\reff.
@@
 
-We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foregournd/background objects which may contaminate the data.
+We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects which may contaminate the data.
 Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{sec:results}
+
+\subsection{Star Formation Enhancement}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{sec:results}
+\subsubsection{Mass-Binned Difference Profiles}\label{sec:mass-bin}
 
-\subsection{Mass-Binned Difference Profiles}\label{sec:mass-bin}
-
-In the first method, paired and control galaxies are grouped into four evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.0.
+In the first method, paired and control galaxies are grouped into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5.
 Within each stellar mass bin, we create a median profile of log(sSFR) as a function of galactocentric radius for both paired and control galaxies.
@@
 This gives us difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
-We will discuss the results of the difference profiles later in Section \ref{sec:results}.
 
-\subsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
+This method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls.
+On the other hand, this method only controls for a single galaxy parameter, stellar mass.
+Further the profiles can only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.
+
+We show the mass-binned profiles in Figure \ref{fig:ssfr_prof}.
+Between the median profiles of the control galaxies and paired galaxies, we can see that the paired profiles are flatted in their centers in comparison to the control profiles.
+The paired profiles are centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
+This enhancement linearly falls to zero around 1.0 \reff.
+In the disks the profiles feature a weak suppression to the sSFR of 0.05$-$0.1 dex.
+
+The sSFR enhancement show no dependence on the stellar mass, the profiles of the different mass bins fall within $\sim$0.2 dex of median profile.
+This means that low mass galaxies are enhanced at the same level as high mass galaxies.
+It is also notable that while this method of pair-control comparison is not rigorous as the next method, the central star formation enhancement is clearly present.
+
+\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
 
@@
 We take all of the $\Delta$log(sSFR) profiles and take the median value within each radius bin to create a stacked profile of the individual difference profiles.
-We split the individual difference profiles into four evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.0 and stack the difference profiles within each mass bin.
+We split the individual difference profiles into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5 and stack the difference profiles within each mass bin.
 This gives us four difference profiles covering four different stellar mass ranges shown in the left hand panel of Figure \ref{fig:ssfr_mass}.
-The results of the profiles will discussed in detail in Section \ref{sec:results}.
 
-To study how the star formation in the centers of paired galaxies are affected by merger events, we extract the $\Delta$log(sSFR) from the individual difference profiles.
+The difference profiles are shown to be centrally enhanced by $\sim$0.30 $\pm$ 0.1 dex.
+The enhancement falls to zero around 1.0 \reff\ and is slightly suppressed in their disks by $\sim$0.1 dex.
+The profiles of the pair stellar masses of \logm\ $=$ 9.0$-$9.5 show a strong enhancement in their disks of $\sim$0.1$-$0.2 $\pm$ 0.1 dex.
+
+The profiles are largely consistent with the results of the previous mass binning method.
+The profiles of this method have less scatter, which may be due to how the paired are more closely matched in stellar mass and redshift.
+This method also has the added benefit that the profiles can be separated by other parameters instead of just the stellar mass.
+
+We can also inspect the star formation enhancement within individual paired galaxies.
+We extract the $\Delta$log(sSFR) from the individual difference profiles.
 We extract the value of $\Delta$log(sSFR) from the inner 0.5 R/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture.
 We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
+The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.3 dex $\Delta$log(sSFR) median.
 
@@
 
-\subsection{Stellar Mass}
-
-In Figures \ref{fig:ssfr_prof} and \ref{fig:ssfr_mass}, we show the profile of $\Delta$log(sSFR) as a function of galactocentric radius between two different methods of comparing paired galaxies to control galaxies.
-In the first method (Section \ref{sec:mass-bin}) where pair and control galaxies are compared within different stellar mass bins.
-The difference profiles from this method show a central enhancement to the log(sSFR) of $\sim$0.3 $\pm$ 0.1 dex.
-The enhancement linearly falls to zero at 1.0 R/\reff\ after which the disks of the paired galaxies have zero enhancement/suppression to their sSFR.
-
-The $\Delta$log(sSFR) profile following the second method shows the same central sSFR enhancement albeit with smaller variances.
-Within the inner 1.0 R/\reff, there is a variance between the profile of 0.1 dex.
-Beyond 1.0 R/\reff, the variance increases 0.2 dex.
-This indicates that the second method of pair$-$ control comparison is superior to the first method.
-
-The profiles of either method show no dependence on the stellar mass of the galaxies.
-This effect is better seen in the right hand panel of Figure \ref{fig:ssfr_mass} where the nuclear $\Delta$log(sSFR) of the paired galaxies fall within 0.1 dex of the mean nuclear sSFR enhancement.
-Low mass galaxies have their star formation enhanced at the same level as high mass galaxies.
-The similar level of $\Delta$log(sSFR) in high and low mass galaxies will mean that the fractional mass growth between high and low mass galaxies will be different.
-
 \subsection{Future Mass Growth}
@@
 
-To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given dynamic timescale, $\tau_{dyn}$.
+To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given timescale, $\tau$.
 A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
@@
 \begin{equation}
-\frac{\Delta M_{merger}}{M_{total}} = \left(sSFR_{pair} - sSFR_{control}\right) * \tau_{dyn}
+\frac{\Delta M_{merger}}{M_{total}} = \left({\rm sSFR}_{\rm pair} - {\rm sSFR}_{\rm control}\right) * \tau
 \end{equation}
 
-For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in hydrodynamical simulations \citep{Boylan-Kolchin:2008}.
+For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
 
@@
 \includegraphics[width=3in]{fig/mass_gain.pdf}
-\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over a dynamical timescale, $\tau$ $=$ 1 Gyr.
+\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over 1 Gyr.
 The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
@@
 
-In this work, we primarily focused on how the $\Delta$log(sSFR) in paired galaxies behaves as a function of stellar mass.
-We also explored how the $\Delta$log(sSFR) behaves as a function of the mass ratio between the paired galaxies and the projected separation between the paired galaxies.
+We primarily focused on how the $\Delta$log(sSFR) in paired galaxies behaves as a function of stellar mass, but we also explored how the $\Delta$log(sSFR) behaves as a function of the mass ratio between the paired galaxies and the projected separation between the paired galaxies.
 While we see hints that the $\Delta$log(sSFR) is affected by the mass ratio and projected separation, these results are less definitive than the $\Delta$log(sSFR) profile's lack of dependence on stellar mass.
 
-\subsection{Mass Ratio}
+\subsection{Dependency on Mass Ratio}
 While the total stellar mass between the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
@@
 
-\subsection{Projected Separation}\label{sec:sep}
+\subsection{Dependency on Projected Separation}\label{sec:sep}
 
@@
 and H.F.
-acknowledge support from the National Science Foundation (NSF) grant AST-1614326 and University of Iowa funds.
+acknowledge support from the National Science Foundation (NSF) grant AST-1614326.
 Funding for the Sloan Digital Sky Survey IV has been provided by the Alfred P.

### 2020-08-18 maintex.tex
more edits
updated values

@@
 \title{
-SDSS-IV MaNGA: Mass Independent Star Formation Enhancement in Close Galaxy Pairs
+SDSS-IV MaNGA: Mass-Independent Star Formation Enhancement in Close Galaxy Pairs
 }
@@
 \begin{abstract}
-We study the spatial profile of the star formation rate (SFR) in a sample of {\it 220} interacting galaxies within the SDSS-IV MaNGA survey.
+We study the spatial profile of the star formation rate (SFR) in a sample of 220 interacting galaxies within the SDSS-IV MaNGA survey.
 We find that the specific star formation rate (sSFR) is centrally (e.g.
@@
 The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
-Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate of 1$-$7\%, assuming a constant burst merger induced star formation over a 1 Gyr period.
+Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate of 1$-$6\%, assuming a constant burst merger induced star formation over a 1 Gyr period.
 This indicates that merger induced star formation has a significant impact on the mass evolution of low mass galaxies.
@@
 Where NUV$-$r is the color and M$_i$ is the i-band magnitude from the NSA catalog.
+We have checked the selected star forming galaxies on the BPT diagram \citep{Baldwin:1981} and confirmed that there is not a significant number of AGN in our sample.
 
 On top of the color selection cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}.
-The resulting sample cover a stellar mass range of \logm\ $=$ 9.0$-$11.5.
+The stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.
 
@@
 
-We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation.
+%We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation.
 To separate ionization sources, we use the theoretical maximum starburst line from \citet{Kewley:2001} (Equation \ref{eq:kewley}).
 
-\begin{equation}\label{eq:kewley}
-\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
-\end{equation}
+%\begin{equation}\label{eq:kewley}
+%\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
+%\end{equation}
 
-Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel.
+%Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel.
 We use the \citet{Kewley:2001} demarcation line as the limit for classifying star formation in the MaNGA spaxels.
 
-It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
-We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to mask retired spaxels \citep{Cid-Fernandes:2011}.
+It has been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
+To mask retired spaxels, we implement a H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ \citep{Cid-Fernandes:2011}.
 
@@
 First, the geometry of the galaxies need to be defined.
+Specifically we will need position angle, inclination angle, and the effective radius of each of the MaNGA targets.
 We use the $r$-band elliptical Petrosian apertures from the NSA catalog and the $r$-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies.
@@
 Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space.
-We do this process for each of the 160 paired galaxies.
+We do this process for each of the 220 paired galaxies.
 
@@
 
-The difference profiles are shown to be centrally enhanced by $\sim$0.30 $\pm$ 0.1 dex.
+The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
 The enhancement falls to zero around 1.0 \reff\ and is slightly suppressed in their disks by $\sim$0.1 dex.
@@
 We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
-The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.3 dex $\Delta$log(sSFR) median.
+The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.2 dex $\Delta$log(sSFR) median.
 
@@
 For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
+The actual timescale for star formation enhancement is likely shorter; however, we use the 1 Gyr value as an order of magnitude guess.
 
@@
 
-The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.065, while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.015.
+The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%).
 This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.
 
-Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth.
+%Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth.
 While low mass galaxies may see a more substantial change to their total stellar mass, the more massive galaxies experience higher growth rates.
@@
 \includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
-\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
+\caption[]{{\it Use larger bins here.} Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
 \label{fig:ssfr_dmsep}
@@
 For the outside-IFU sample we use the stellar masses calculated from the r-band elliptical Petrosian apertures from the NSA catalog.
-For the inside-IFU sample, neither the NSA catalog nor \citet{Mendel:2014} will cover both galaxies.
-Instead we use stellar masses calculated from {\sc SPFIT} from the inner 2\arcsec\ of the galaxies.
+Most of the companion galaxies in the inside-IFU sample are not covered by either the NSA catalog or \citet{Simard:2011}.
+Because of this, the inside-IFU galaxies are left out of this analysis.
 
 In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log(M) $=$ 0.0.
-These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.15 dex higher than the average central enhancement of the whole sample.
-This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.2$-$0.25 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.
+These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
+This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.
 
@@
 It has been a convention to split galaxy pairs in major mergers, $|$log(M)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log(M)$|$ $\le$ 1.0.
-In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log(M)$|$ $\le$ 2.0 so that larger pair samples can be constructed.
+In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log(M)$|$ $\le$ 1.5 so that larger pair samples can be constructed.
 
@@
 The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
-The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are $\sim$0.1 dex below the median.
+The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.
 
@@
 While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex.
-Within 15 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.5$-$0.6 dex.
+Within 15 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex.
 
@@
 
-For the galaxies with the closest separations, r$_p$ $<$ 5 kpc, $\Delta$log(sSFR) drops to zero.
-This is strange as we would expect that the closest pairs would show the strongest enhancements to their star formation as they are currently or have just passed the first pericenter.
-This seems odd as one would think that these galaxies should show the strongest enhancements to the sSFR.
-
-This lack of $\Delta$log(sSFR) could be due to a couple of reasons.
-First, it may be due to the limited sampling of this separation range, there are only 6 paired galaxies in this range.
-A second explanation could be that we are observing merging galaxies which are just going though their first pericenter, but have yet to have the burst of star formation.
-Not enough time has elapsed for the gas inflows from the disks of the galaxies to reach the centers of the galaxies.
-The hydrodynamical simulations of \citet{Scudder:2012} show this delay in the burst of star formation, where the burst of star formation only reaches its peak after 0.3 Gyr after the passage of the first pericenter.
+For galaxies with separations of r$_p$ $<$ 5 kpc and r$_p$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero.
+For the r$_p$ $<$ 5 kpc galaxy, about half of the pairs show signs of tidal features while the others do not.
+The pairs without the tidal features may be approaching their first pericenter, meaning that the merger-induced gas-inflows have not been triggered yet.
+The dips in $\Delta$log(sSFR) may also just be due to statistical error from the relatively limited sample size.
 
@@
 We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}.
-We find that our pairs generally feature higher level of SFR enhancement in their centers, by $\sim$0.0$-$0.2 dex.
-Further, we probe galaxies with projected separations below 5 kpc, a projected separation range not covered in previous works.
-As mentioned in Section \ref{sec:sep}, we find a $\Delta$log(SFR) of zero implying that we are viewing galaxies that are about to or have just passed their first pericenter.
+We find that our central SFR enhancements are higher than many of the previous studies, the enhancements are $\sim$0.15 dex higher than \citet{Scudder:2012} and $\sim$0.25 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}.
+Our $\Delta$log(SFR) as a function of projected separation is very consistent to what was found in \citet{Patton:2013}.
 
@@
 \citet{Pan:2019} examines a set of paired galaxies in the MaNGA survey while \citet{Thorp:2019} examines a set of post-merger galaxies in the MaNGA survey.
-The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughtly $\sim$0.05$-$0.2 dex higher than our sample.
+The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughtly $\sim$0.1$-$0.2 dex higher than our sample.
 The $\Delta$log(sSFR) profile is closest to our work at the centers of the galaxy pairs but then begins to diverge further out into the galaxies' disks.
-Our paired galaxies show zero sSFR enhancement in their disks past 1.0 R/\reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+Our paired galaxies show a slight sSFR suppression in their disks past 1.0 R/\reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
 
-The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.15 higher than our sample of paired galaxies.
-Their $\Delta$log(sSFR) profile follows our sample's profile closely between 0.25$-$1.0 R/\reff.
+The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 higher than our sample of paired galaxies.
 The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
@@
 In this work, we studied a sample of paired, star forming galaxies using the MaNGA IFS survey.
-We have made a sample of 160 star forming galaxy pairs along with a set of 1891 star forming control galaxies.
+We have made a sample of 220 star forming galaxy pairs along with a set of 1891 star forming control galaxies.
 We compared the radial profiles of the paired galaxies with those of the controls galaxies and found the follwing;
@@
 \begin{enumerate}
-\item The sSFR is centrally enhanced within the inner 1.0 R/\reff\ by 0.30 $\pm$ 0.1 dex. 
-\item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show no signs of either sSFR enhancement or sSFR suppression. 
+\item The sSFR is centrally enhanced within the inner 1.0 R/\reff\ by 0.25 $\pm$ 0.1 dex. 
+\item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show limited suppression in their disks, $\sim$0.1 dex.
 \item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies, Massive galaxies experience the same level of sSFR enhancement as low mass galaxies.
 \item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies.
-Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.4 $\pm$ 0.1 dex, which is 0.15 dex higher than the average paired galaxies in the survey.
-We have also showed that paired galaxies with large mass ratios, 1.0 $<$ $|\Delta$log(M)$|$ $<$ 2.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex.
+Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.3 $\pm$ 0.1 dex, which is 0.1 dex higher than the average paired galaxies in the survey.
+We have also showed that paired galaxies with large mass ratios, $|\Delta$log(M)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.15$-$0.2 dex.
 \item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair, $\sim$0.1 dex.
-\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.5$-$0.6 $\pm$ 0.1 dex.
-The galaxies within 5 kpc experience no central enhancement to their sSFR.
-We believe that these galaxies have just passed their first pericenter and the merger induced gas-inflow have yet to reach the centers of these galaxies.
-\item The paired galaxies will experience a faster mass growth rate of secular evolution of 1.6$-$2.3$\times$.
-The growth rate is highest for massive galaxies; however, the the low mass galaxies will see a higher fractional mass increase in comparison to the preexisting stellar mass.
+\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4 $\pm$ 0.1 dex. 
+\item The paired galaxies will experience a fractional mass growth rate of 1$-$6\%, where the growth in mass in largest in low mass galaxies.
 

### 2020-08-19 maintex.tex
Next draft for submission to MaNGA team

@@
 \title{
-SDSS-IV MaNGA: Mass-Independent Star Formation Enhancement in Close Galaxy Pairs
+SDSS-IV MaNGA: The Universal Profile of Enhanced Star Formation in Close Galaxy Pairs
 }
@@
 The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
+We describe the profiles of the $\Delta$log(sSFR) enhancement as a universal profile because the general shape of the profile is unchanged by parameters like stellar mass, mass ratio, or projected separation.
+The shape of the profile is a central peak in $\Delta$log(sSFR) which linearly falls to zero around 1.0 R/\reff.
+Parameters like the mass ratio or projected separation may scale the height of the profile's central peak, but the general shape of the profile is preserved.
 Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate of 1$-$6\%, assuming a constant burst merger induced star formation over a 1 Gyr period.
@@
 
-This star formation enhancement increases with closer projected separations between the two galaxies \citep{Ellison:2008, Scudder:2012} but has still shown to be detectable out to projected separations of 150 kpc \citep{Patton:2013}.
+This star formation enhancement increases with closer projected separations between the two galaxies \citep{Li:2008, Ellison:2008, Scudder:2012} but has still shown to be detectable out to projected separations of 150 kpc \citep{Patton:2013}.
 The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta$log($M$)$|$, between the two galaxies \citep{Ellison:2008}.
@@
 
-Where NUV$-$r is the color and M$_i$ is the i-band magnitude from the NSA catalog.
+Where NUV$-$r is the color and $\mathcal{M}_i$ is the i-band magnitude from the NSA catalog.
 We have checked the selected star forming galaxies on the BPT diagram \citep{Baldwin:1981} and confirmed that there is not a significant number of AGN in our sample.
 
-On top of the color selection cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}.
-The stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.
+On top of the color selection cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}, and that the stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.
 
@@
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-After restricting the sample to SFGs, we have 133 MaNGA targets with paired galaxies outside of the IFU.
+After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU.
+This give use a total of 220 MaNGA targets in our pair sample.
 
@@
 This effect needs to be controlled for when comparing the paired and control galaxies to isolate the changes in the sSFR due to merger induced effects.
-For each galaxy pair we build a subset of 20 control galaxies which are matched in stellar mass and redshift.
 
 We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
-This gives us a set of 1891 SFGs and 1528 SFGs which are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.
+This gives us a set of 1891 star forming control galaxies to work with.
 
@@
 This will allow us to compare the SFR in high mass regions, like the centers of the galaxies, to the SFR lower mass regions, like the disk of the galaxies.
-We have also found a strong correlation between sSFR and \ewha and have found the same results using \ewha.
-This is useful to check as \ewha\ is an observable and independent on {\sc SPFIT}'s measurement of the stellar mass.
+We have also found a strong correlation between sSFR and \ewha\ and have found the same results using \ewha.
+This is useful to check as \ewha\ is an observable and independent of {\sc SPFIT}'s measurement of the stellar mass.
 
@@
 We found that the apertures from \citet{Simard:2011} work better for these close galaxies, but the catalog does not completely cover the MaNGA sample.
-We use NSA catalog for the outside-IFU pair sample because they are well separated on the sky and the \citet{Simard:2011} catalog on the inside-IFU sample.
+We use NSA catalog for the outside-IFU pair sample because they are well separated on the sky and the \citet{Simard:2011} catalog for the inside-IFU sample.
 In the cases where an Inside-IFU paired galaxy is not covered by \citet{Simard:2011}, we use the ellipse from the NSA catalog.
@@
 
-We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects which may contaminate the data.
+We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects within the MaNGA IFUs which may contaminate the data.
 Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
@@
 We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of the stacked profiles over 1000 iterations.
-This random selection contributes an error of about 0.1 dex.
+We estimate that this random selection contributes an error of about 0.1 dex.
 
@@
 We split the individual difference profiles into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5 and stack the difference profiles within each mass bin.
-This gives us four difference profiles covering four different stellar mass ranges shown in the left hand panel of Figure \ref{fig:ssfr_mass}.
+This gives us five difference profiles covering five different stellar mass ranges shown in the left hand panel of Figure \ref{fig:ssfr_mass}.
 
@@
 The enhancement falls to zero around 1.0 \reff\ and is slightly suppressed in their disks by $\sim$0.1 dex.
-The profiles of the pair stellar masses of \logm\ $=$ 9.0$-$9.5 show a strong enhancement in their disks of $\sim$0.1$-$0.2 $\pm$ 0.1 dex.
+While all of the other paired galaxies show a sSFR suppression in their disks, the profiles of the pairs in the stellar mass range of \logm\ $=$ 9.0$-$9.5 show an enhancement in their disks of $\sim$0.1$-$0.2 $\pm$ 0.1 dex.
 
@@
 The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.2 dex $\Delta$log(sSFR) median.
+
+Between the two different pair-control comparison methods, we conclude that the $\Delta$log(sSFR) is independent of the paired galaxies' stellar mass.
+Low mass galaxies are having their sSFR enhanced at a similar rate as high mass galaxies.
 
@@
 For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
-The actual timescale for star formation enhancement is likely shorter; however, we use the 1 Gyr value as an order of magnitude guess.
+The actual timescale for star formation enhancement is likely shorter; however, we will use the 1 Gyr value as an order of magnitude estimate.
 
@@
 
-The sSFR enhancement increasing with closer projected separations is to be expected and has been shown in previous studies \citep{Ellison:2008, Scudder:2012, Patton:2013}.
+The sSFR enhancement increasing with closer projected separations is to be expected and has been shown in previous studies \citep{Li:2008, Ellison:2008, Scudder:2012, Patton:2013}.
 The passage of the first pericenter is predicted to trigger a burst of star formation which falls as the two galaxies separate \citep{Scudder:2012}.
@@
 For galaxies with separations of r$_p$ $<$ 5 kpc and r$_p$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero.
-For the r$_p$ $<$ 5 kpc galaxy, about half of the pairs show signs of tidal features while the others do not.
+For the r$_p$ $<$ 5 kpc galaxies, about half of the pairs show signs of tidal features while the others do not.
 The pairs without the tidal features may be approaching their first pericenter, meaning that the merger-induced gas-inflows have not been triggered yet.
 The dips in $\Delta$log(sSFR) may also just be due to statistical error from the relatively limited sample size.
+
+Between the three parameters, stellar mass, mass ratio, and projected separation, the projected separation has the strongest effect on the $\Delta$log(sSFR) enhancement, followed by the mass ratio.
+From this we see that the paired galaxies with the strongest enhancements to the central sSFR are paired galaxies with 1:1 mass ratios and  which are within 10 kpc.
+
+Between the splitting the $\Delta$log(sSFR) profile by stellar mass, mass ratio, and projected separation, we see that the general shape of the profile within the inner 1.0 R/\reff\ is unchanged.
+The profile is peaked in the center of the paired galaxies and linearly (in log space) to zero around 1.0 R/\reff.
+Different projected separations and mass ratios may elevate or suppress the level of the enhancement in the profile's center; however, the shape of the profile is largely unchanged.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\citet{Li:2008} studied the star formation enhancement over different stellar masses and saw that low mass galaxies experience greater levels of enhancement than high mass galaxies.
+Galaxies in the mass range \logm\ $=$ 9.72 were shown to experience an enhancement $\sim$0.4 dex higher than galaxies in the mass range \logm\ $=$ 10.6.
+In this work, we find that $\Delta$log(sSFR) has no dependence on the stellar mass of the galaxy.
+The galaxies with stellar masses above \logm\ $\ge$ 10.5 do show slightly lower levels of enhancement compared to the lower mass galaxies; however, the pairs still do not significantly deviate from the average $\Delta$log(sSFR) of the sample.
 
@@
 \item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4 $\pm$ 0.1 dex. 
+\item When splitting the sSFR enhancement profiles by stellar mass, mass ratio, or projected separation, the general shape of the enhancement profile is unchanged.
+While lower projected separations or mass ratios closer to 1:1 may raise the level of the central enhancement to the profiles, the profiles still linearly fall to zero enhancement around 1.0 R/\reff\ with roughly the same gradient.
 \item The paired galaxies will experience a fractional mass growth rate of 1$-$6\%, where the growth in mass in largest in low mass galaxies.

### 2020-08-19 maintex.tex
minor edit to abstract

@@
 Within one effective radius, the sSFR enhancement in each of the mass bins falls within $\sim$0.1 dex of the median profile for the whole pair sample.
-We then use a second method to compare paired galaxies and control galaxies where each paired galaxies is matched to a set of 20 control galaxies based on stellar mass and redshift.
+We then use a second method to compare paired galaxies and control galaxies where each paired galaxy is matched to a set of 20 control galaxies based on stellar mass and redshift.
 The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.

### 2020-08-28 maintex.tex
Revised Abstract to fit APJ word count

@@
 We study the spatial profile of the star formation rate (SFR) in a sample of 220 interacting galaxies within the SDSS-IV MaNGA survey.
-We find that the specific star formation rate (sSFR) is centrally (e.g.
-within a single effective radius) enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks.
+We find that the specific star formation rate (sSFR) is centrally (within one effective radius) enhanced in interacting galaxies by $\sim$0.25$\pm$0.1 but that there is no enhancement or suppression in their disks.
 We split the radial profile into five separate stellar mass bins from \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies.
 Within one effective radius, the sSFR enhancement in each of the mass bins falls within $\sim$0.1 dex of the median profile for the whole pair sample.
-We then use a second method to compare paired galaxies and control galaxies where each paired galaxy is matched to a set of 20 control galaxies based on stellar mass and redshift.
+We then use a second method to compare paired galaxies and control galaxies where each paired galaxy is matched to a set of control galaxies based on stellar mass and redshift.
 The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
@@
 Parameters like the mass ratio or projected separation may scale the height of the profile's central peak, but the general shape of the profile is preserved.
-Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate of 1$-$6\%, assuming a constant burst merger induced star formation over a 1 Gyr period.
-This indicates that merger induced star formation has a significant impact on the mass evolution of low mass galaxies.
 
@@
 \includegraphics[width=3in]{fig/nuc_sep.pdf}
-\caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Patton:2013} (Green), \citet{Scudder:2012} (Blue), and \citet{Bustamante:2020} (Purple).
+\caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Li:2008} (Orange), \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
 }
@@
 
-The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Patton:2013, Scudder:2012, Bustamante:2020}.
+The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Li:2008, Patton:2013, Scudder:2012, Bustamante:2020}.
 We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}.
 We find that our central SFR enhancements are higher than many of the previous studies, the enhancements are $\sim$0.15 dex higher than \citet{Scudder:2012} and $\sim$0.25 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}.
+The central enhancement to sSFR is $\sim$0.1 dex higher in our pairs compared to \citet{Li:2008} past 35 kpc, but \citet{Li:2008} is $\sim$0.1 dex higher than our pairs at 20 kpc.
 Our $\Delta$log(SFR) as a function of projected separation is very consistent to what was found in \citet{Patton:2013}.

### 2020-09-05 maintex.tex
Revised abstract and Introduction

@@
 \title{
-SDSS-IV MaNGA: The Universal Profile of Enhanced Star Formation in Close Galaxy Pairs
+SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs
 }
@@
 We study the spatial profile of the star formation rate (SFR) in a sample of 220 interacting galaxies within the SDSS-IV MaNGA survey.
-We find that the specific star formation rate (sSFR) is centrally (within one effective radius) enhanced in interacting galaxies by $\sim$0.25$\pm$0.1 but that there is no enhancement or suppression in their disks.
+We find that the specific star formation rate (sSFR) is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25$\pm$0.1 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of about $\sim$0.1$\pm$0.1 dex.
 We split the radial profile into five separate stellar mass bins from \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies.
@@
 The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
-We describe the profiles of the $\Delta$log(sSFR) enhancement as a universal profile because the general shape of the profile is unchanged by parameters like stellar mass, mass ratio, or projected separation.
-The shape of the profile is a central peak in $\Delta$log(sSFR) which linearly falls to zero around 1.0 R/\reff.
-Parameters like the mass ratio or projected separation may scale the height of the profile's central peak, but the general shape of the profile is preserved.
-
+We also find that that the central sSFR is enhanced by smaller mass ratios and closer projected separations; however, the gradients of the profiles within 1.0 $R$/\reff\ are unchanged by the parameters.
 \end{abstract}
@@
 \citet{Rodriguez-Gomez:2016}; \citet{Pillepich:2018}).
+As the galaxies undergo the merging process, the gas within the galaxies are subject to gravitational torques which perturb the morphology of the galaxies.
 
@@
 %%%Observations%%%
-Centrally enhanced star formation has also been observed in galaxy pairs with large spectroscopic surveys including; CfA2 (Center of Astrophysics Redshift Survey)  \citep{Barton:2000, Woods:2006}, 2dF (Two Degree Field) \citep{Lambas:2003}, AEGIS (All-Wavelength Extended Groth Strip International Survey) \citep{Lin:2007}, SDSS (Sloan Digital Sky Survey) \citep{Ellison:2008}, COSMOS (Cosmic Evolution Survey) \citep{Kartaltepe:2007,Xu:2012}, PRIMUS (Prism Multi-Object Survey) \citep{Wong:2011}, and GAMA (Galaxy and Mass Assembly) \citep{Robotham:2014}.
-
-This star formation enhancement increases with closer projected separations between the two galaxies \citep{Li:2008, Ellison:2008, Scudder:2012} but has still shown to be detectable out to projected separations of 150 kpc \citep{Patton:2013}.
-The level of the star formation enhancement also increases with smaller stellar mass ratios, $|\Delta$log($M$)$|$, between the two galaxies \citep{Ellison:2008}.
-Similar mass galaxies show the strongest sSFR effects while large central galaxies interacting with small satellite galaxies show weaker sSFR effects.
-Because of this, most surveys will split their sample into major mergers, $|\Delta$log($M$)$|$ $\le$ 0.5, and minor mergers, 0.5 $\le$ $|\Delta$log($M$)$|$ $\le$ 1.0, where major mergers are expected to show the strongest interaction induced effects.
+Interaction induced star formation was first seen observationally in the bluer colors of peculiar galaxies in \citet{Larson:1978}.
+This observation has also been shown in more recent works using the single-fiber spectroscopic survey, SDSS (Sloan Digital Sky Survey) \citet{Ellison:2008, Li:2008, Scudder:2012, Patton:2013, Bustamante:2020}.
+From these previous works it has been shown that the strength of the star formation enhancement in the centers of paired galaxies is dependent on the stellar mass of the pairs \citet{Li:2008}, the projected separation between the pairs \citet{Ellison:2008, Li:2008, Scudder:2012}, and the mass ratio between the pairs \citet{Ellison:2008}.
 
 %%%Integral Field Spectroscopy%%%
-With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can be studied with unprecedented spatial detail.
+The previous mentioned works using SDSS were restricted to studying the centers of the paired galaxies through a 2\arcsec\ diameter optical fiber.
+With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail.
 These surveys allow astronomers to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture.
@@
 
-The IFS surveys, CALIFA\footnote{Calar Alto Legacy Integral Field Area} and MaNGA\footnote{Mapping Nearby Galaxies at Apache Point Observatory}, have already been used to study the SFR of interacting galaxies in merging galaxies.
-The SFR was found to be centrally enhanced by a factor of 2$-$3$\times$ \citep{Barrera-Ballesteros:2015, Pan:2019}, which is in agreement with the previous single-fiber spectroscopic surveys.
-These surveys also studied the SFR in the disk of the paired galaxies; however, there is a standing discrepancy between the different works.
-\citet{Barrera-Ballesteros:2015} found a suppression to the SFR of $\sim$0.74$\times$ while \citet{Pan:2019} found an enhancement of 1.22$-$1.58$\times$.
+Astronomers have already begun to take advantage of IFS surveys in galaxy pair studies.
+\citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted from.
+In the study, \citet{Barrera-Ballesteros:2015} found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.
 
-The MaNGA survey has also been used to study the radial profiles of SFR in post-merger galaxies, which are the galaxies which have recently coalesced.
-Hydrodynamical simulations predict a second burst of star formation as the two galaxies coalesce.
-This effect has been observed in a sample of post-merger galaxies which showed a central enhancement to the SFR surface density of 2.5$\times$ and an enhancement in their disks of 1.26$\times$ \citep{Thorp:2019}.
+\citet{Pan:2019} used the MaNGA survey to study radial profiles of a sample of 205 paired galaxies.
+The enhancement to the sSFR was shown to be the strongest in the centers of the paired galaxies.
+This central enhancement linearly fell with increasing galactocentric radii; however, a moderate enhancement to the sSFR remain in the outskirts of the galaxies.
+\citet{Pan:2019} further studied the paired galaxies as a function of merger stage; from well separated pairs to post-merger galaxies.
+Across the different merger stages, the sSFR enhancement was greatest in close pairs with tidal features and in post-merger galaxies.
+This was in agreement with previous hydrodynamical simulations which showed that a burst of star formation is triggered after the first pericenter and as the two galaxies begin to coalesce \citep{Scudder:2012}.
 
-%%%Purpose%%%
+The radial profile of sSFR in post-merger galaxies has also been studied with the MaNGA survey by \citet{Thorp:2019}.
+The post-merger galaxies were shown to have a strong enhancement to the sSFR in their centers as well as a moderate enhancement in their outskirts.
+
+Where previous studies on the radial profile of the sSFR offsets in paired galaxies have focused on studying the profiles as a function of interaction stage, we will focus on the radial profile as a function of the stellar mass, projected separation, and mass ratio.
+As mentioned previously, these parameters have been covered by studies restricted to the nuclear region of the paired galaxies.
+With the MaNGA survey, we will be able to expand upon these previous studies in greater spatial detail.
+We will be able to see how these three parameters affect the both the level of the sSFR offsets in the centers of the paired galaxies and the offsets in the outskirts of the galaxies.
+We will also be able to study if any of three parameters influence the gradient of the sSFR enhancement profiles or if the gradient is preserved between different configurations.
+
 In our previous work, \citet{Fu:2018}, we built a sample of paired galaxies in the MaNGA survey where both components of the pair were contained within field of view of a single integral field unit (IFU).
@@
 
-In this work we will study how the radial profiles of star formation in our pair sample is effected by tidal interactions.
-We will expand upon the previous studies of star formation in merging galaxies by studying how the spatial profile of the SFR behaves as a function of the stellar mass of the paired galaxy, the mass ratio between the galaxy pairs, and the projected separation between the galaxies.
-
-Changes in the star formation rate will also affect the future mass growth in the interacting galaxies.
-We will model the fractional mass growth rate of the galaxies in our sample to see how the merger event influences the mass evolution of the paired galaxies.
-Since merging galaxies are already known to have centrally enhanced star formation rates, we would expect this to produce higher concentrations of stellar mass in their centers.
-
 % Organization
-This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we discuss the mass independence of the constructed radial profiles, in Section \ref{sec:disc} we explore the radial profiles as a function of the mass ratio and projected separation and we compare our work against previous works, and in Section \ref{sec:sum} we summarize the findings of the work.
+This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we study the radial profiles as a function of stellar mass, projected separation, and the mass ratio, in Section \ref{sec:disc} we compare our work against previous works, and in Section \ref{sec:sum} we summarize the findings of the work.
 

### 2020-09-07 maintex.tex
various edits in abs and intro

@@
 % citations
-\defcitealias{Fu18}{Paper I}
+\defcitealias{Fu:2018}{Paper I}
 
@@
 \begin{abstract}
-We study the spatial profile of the star formation rate (SFR) in a sample of 220 interacting galaxies within the SDSS-IV MaNGA survey.
-We find that the specific star formation rate (sSFR) is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25$\pm$0.1 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of about $\sim$0.1$\pm$0.1 dex.
-We split the radial profile into five separate stellar mass bins from \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass of the paired galaxies.
-Within one effective radius, the sSFR enhancement in each of the mass bins falls within $\sim$0.1 dex of the median profile for the whole pair sample.
-We then use a second method to compare paired galaxies and control galaxies where each paired galaxy is matched to a set of control galaxies based on stellar mass and redshift.
-The sSFR enhancements found are still mass independent, reinforcing the idea that low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies.
-We also find that that the central sSFR is enhanced by smaller mass ratios and closer projected separations; however, the gradients of the profiles within 1.0 $R$/\reff\ are unchanged by the parameters.
+We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 220 star-forming galaxies in close pairs with those of mass-matched isolated galaxies in the SDSS-IV MaNGA survey.
+We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.3 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
+We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass.
+The same result is obtained when the comparison galaxies are matched to each paired galaxy in both stellar mass and redshift.
+In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy.
 \end{abstract}
@@
 In this model, massive galaxies are the product of several past merger events of smaller galaxies.
-In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 (e.g.
-\citet{Rodriguez-Gomez:2016}; \citet{Pillepich:2018}).
+In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 \citep[e.g.,][]{Rodriguez-Gomez:2016,Pillepich:2018}.
 As the galaxies undergo the merging process, the gas within the galaxies are subject to gravitational torques which perturb the morphology of the galaxies.
@@
 Interaction induced star formation was first seen observationally in the bluer colors of peculiar galaxies in \citet{Larson:1978}.
-This observation has also been shown in more recent works using the single-fiber spectroscopic survey, SDSS (Sloan Digital Sky Survey) \citet{Ellison:2008, Li:2008, Scudder:2012, Patton:2013, Bustamante:2020}.
-From these previous works it has been shown that the strength of the star formation enhancement in the centers of paired galaxies is dependent on the stellar mass of the pairs \citet{Li:2008}, the projected separation between the pairs \citet{Ellison:2008, Li:2008, Scudder:2012}, and the mass ratio between the pairs \citet{Ellison:2008}.
+This observation has also been shown in more recent works using the single-fiber spectroscopic survey, SDSS (Sloan Digital Sky Survey) \citep{Ellison:2008, Li:2008, Scudder:2012, Patton:2013, Bustamante:2020}.
+From these previous works it has been shown that the strength of the star formation enhancement in the centers of paired galaxies is dependent on the stellar mass of the pairs \citep{Li:2008}, the projected separation between the pairs \citep{Ellison:2008, Li:2008, Scudder:2012}, and the mass ratio between the pairs \citep{Ellison:2008}.
 
 %%%Integral Field Spectroscopy%%%
-The previous mentioned works using SDSS were restricted to studying the centers of the paired galaxies through a 2\arcsec\ diameter optical fiber.
+The previous mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 2\arcsec\ diameter optical fibers.
 With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail.
-These surveys allow astronomers to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture.
+These surveys allow us to study the centers of merging galaxies more rigorously since apertures can be set to the physical scale of the galaxies instead of being bound by a fixed sky aperture.
 These IFS surveys will also allow us to see the extent of the centrally induced star formation and to see how the star formation in the disks of the galaxies are affected.
 
-Astronomers have already begun to take advantage of IFS surveys in galaxy pair studies.
-\citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted from.
+Indeed, \citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted from.
 In the study, \citet{Barrera-Ballesteros:2015} found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.
-
+%
 \citet{Pan:2019} used the MaNGA survey to study radial profiles of a sample of 205 paired galaxies.
@@
 This was in agreement with previous hydrodynamical simulations which showed that a burst of star formation is triggered after the first pericenter and as the two galaxies begin to coalesce \citep{Scudder:2012}.
-
+%
 The radial profile of sSFR in post-merger galaxies has also been studied with the MaNGA survey by \citet{Thorp:2019}.
@@
 
-In our previous work, \citet{Fu:2018}, we built a sample of paired galaxies in the MaNGA survey where both components of the pair were contained within field of view of a single integral field unit (IFU).
+In our previous work, we built a sample of paired galaxies in the MaNGA survey where both components of the pair were contained within field of view of a single integral field unit \citep[][hereafter \citetalias{Fu:2018}]{Fu:2018}.
 We found that approximately 5.7\% of the MaNGA galaxies have a companion galaxy contained within the field-of-view of a single IFU.
@@
 This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we study the radial profiles as a function of stellar mass, projected separation, and the mass ratio, in Section \ref{sec:disc} we compare our work against previous works, and in Section \ref{sec:sum} we summarize the findings of the work.
+% cosmology
+Throughout we adopt the $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.3$, $\Omega_\Lambda=0.7$, and $h=0.7$.
 

### 2020-09-08 maintex.tex
edits to the data and samples section

--- 2020-09-05 maintex.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data and Sample}\label{sec:data}
+\section{Data and Samples}\label{sec:data}
 
@@
 
-MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}.
-MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citet{Law:2015}.
-MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a median spectra coverage of 2.5\arcsec\ FWHM \citep{Bundy:2015}.
+MaNGA is an IFS survey at the Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}.
+MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citep{Law:2015}.
+MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a PSF of 2.5\arcsec\ FWHM \citep{Bundy:2015}.
 
-The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
-MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 R/\reff\ and 2.5 R/\reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
+The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
+MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 $R$/\reff\ and 2.5 $R$/\reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
 In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.
@@
 
-Where NUV$-$r is the color and $\mathcal{M}_i$ is the i-band magnitude from the NSA catalog.
-We have checked the selected star forming galaxies on the BPT diagram \citep{Baldwin:1981} and confirmed that there is not a significant number of AGN in our sample.
+Where $NUV-r$ is the color from SDSS's k-corrected absolute magnitude and $\mathcal{M}_i$ is the i-band magnitude from the NSA catalog.
+We have checked the selected star forming galaxies on the BPT diagram \citep{Baldwin:1981} to confirm that AGN (active galactic nuclei) will have a minimal impact on our SFG sample.
 
@@
 
-We build two different pair samples in this work; the inside-IFU sample which contains paired galaxies where both galaxies are covered by a single MaNGA IFU and the outside-IFU sample where a MaNGA target galaxy is coupled with another galaxies found outside of its MaNGA IFU.
+We build two different pair samples in this work; the inside-IFU sample which contains paired galaxies where both galaxies are covered by a single MaNGA IFU and the outside-IFU sample where a MaNGA target galaxy is coupled with another galaxy found outside of its MaNGA IFU.
 
@@
 To select paired galaxies out of our object catalog, we inspect the spectra of each object.
-We use our own {\sc IDL} based spectral fitting code, {\sc SPFIT}, to model the spectra from the MaNGA datacubes.
-{\sc SPFIT} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
+We use our own {\sc idl} based spectral fitting code, {\sc spfit}, to model the spectra from the MaNGA datacubes.
+{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
 Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
 
-The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories; ``good" galaxy spectra, broad-line AGN (active galactic nuclei), foreground star, foreground/background galaxies, or poor S/N objects.
-The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
+The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories; ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects.
+The ``good" galaxy spectra are the objects whose spectra are well modeled by {\sc spfit} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
 This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target.
@@
 From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU.
-We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions.
+We further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected companions.
+Given redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc.
 Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples.
@@
 We select these outside-IFU pairs from the NSA catalog.
-We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of r$_p$ $<$ 50 kpc using the MaNGA target's redshift.
-We further use a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.
+We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of $r_p$ $<$ 50 kpc using the MaNGA target's redshift.
+We further use a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.
 
@@
 
-The SFR in galaxies has been shown to be dependent on both stellar mass and redshift of the galaxies \citep{Noeske:2007}.
-This effect needs to be controlled for when comparing the paired and control galaxies to isolate the changes in the sSFR due to merger induced effects.
+To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of isolated galaxies in the MaNGA survey.
+We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_p$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
+This gives us a control sample of 1891 star forming control galaxies.
 
-We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
-This gives us a set of 1891 star forming control galaxies to work with.
+It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep{Noeske:2007}.
+We will compare our interacting galaxies with isolated galaxies of a similar stellar mass and redshift, to account for these other dependencies.
+To do this, we will use two different methods of pair - control comparison.
 
-We then set two separate methods for comparing the paired galaxies with the control galaxies.
-In the first method, we simply split the galaxies into separate stellar mass bins.
-We then compare paired galaxies and control galaxies within each stellar mass bin.
+In the first method, we only control for the stellar mass between the pairs and controls.
+We split both the pair and control samples into five evenly spaced stellar mass bins over the range, \logm\ $=$ 9.0$-$11.5.
+The pairs are then compared to their respective controls within each stellar mass bins.
+While the redshift in not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
 
-In the second method, we control for both stellar mass and redshift.
-To do this, we set a 0.1 dex stellar mass limit between a paired galaxy and the potential control galaxies.
-Then we restrict the redshift between the control and paired galaxies, by selecting control galaxies which are drawn from the same MaNGA subsample (e.g.
+In the second method, we wish to account for both stellar mass and redshift.
+To do this we select a subsample of 20 control galaxies for each paired galaxy.
+We first select all of the control galaxies which are within a 0.1 dex stellar mass limit and within the same MaNGA subsample (e.g.
 Primary or Secondary) as the paired galaxy.
-The MaNGA sample has a tight ``banana" shaped distribution in stellar mass and redshift.
-By setting a 0.1 dex stellar mass cut and requiring that the galaxies be in the same MaNGA subsample, we effectively set a z $\le$ $\sim$0.025 redshift cut.
+Since the MaNGA sample has a tight distribution in stellar mass and redshift, the stellar mass and MaNGA subsample restriction effectively sets a $z$ $\lesssim$ $\sim$0.025 redshift cut.
 
 Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies.
-Since we want each paired galaxy to be treated in a similar manner, we will downselect the total number of acquired control galaxies down to 20 controls using a random number generator.
+Since we want each paired galaxy to be treated in a similar manner, we will down-select the total number of acquired control galaxies down to 20 controls randomly.
 In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.
+A small set of paired galaxies required extra iterations to find 20 controls; 8 needed an extra iteration, 1 needed two extra iterations, and 1 needed three iterations.
 
-A small set of paired required extra iterations to find 20 controls; 8 paired galaxies need an extra iteration, 1 paired galaxy need two extra iterations, and 1 paired galaxy needed three iterations.
-
-While the first method is very basic in comparison to the second method, we will see in Section \ref{sec:results} that the first method is sufficient to see the central enhancement to the star formation rate and the mass independence of the star formation enhancement.
+While the first method is less sophisticated in comparison to the second method, we will see in Section \ref{sec:results} that the first method is sufficient to see the central enhancement to the star formation rate and the mass independence of the star formation enhancement.
 
@@
 The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
-The profiles in the galaxy pairs in the separation range, r$_p$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, r$_p$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.
+The profiles in the galaxy pairs in the separation range, $r_p$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, $r_p$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.
 
@@
 
-For galaxies with separations of r$_p$ $<$ 5 kpc and r$_p$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero.
-For the r$_p$ $<$ 5 kpc galaxies, about half of the pairs show signs of tidal features while the others do not.
+For galaxies with separations of $r_p$ $<$ 5 kpc and $r_p$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero.
+For the $r_p$ $<$ 5 kpc galaxies, about half of the pairs show signs of tidal features while the others do not.
 The pairs without the tidal features may be approaching their first pericenter, meaning that the merger-induced gas-inflows have not been triggered yet.

### 2020-09-09 maintex.tex
updated the radial profile section

@@
 
-\subsection{Emission Line Extraction}
+\subsection{Specific Star Formation Rate}
 
 %%% SPFIT
-We use {\sc SPFIT} to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
+We use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
 
@@
 
-The V-band extinction is then used to calculate the wavelength dependent extinciton A$_{\lambda}$;
-
-\begin{equation}
-A_{\lambda}(x) = A_V \left(a(x) + b(x) / R_v \right)
-\end{equation}
-
-where $x = 1/\lambda$ and $a(x)$ and $b(x)$ are the coefficients for the extinction curve from \citet{ODonnell:1994}. The extinction corrected flux is then;
-
-\begin{equation}
-F'(\lambda) = F(\lambda) * 10^{0.4 A_{\lambda}(x)}
-\end{equation}
-
-This extinction correction is applied to all of the extracted emission lines.
-
-\subsection{Star Formation Rate}
-
-We measure the SFR from the H$\alpha$ luminosity, L$_{{\rm H}\alpha}$, calculated from the H$\alpha$ flux.
+We measure the SFR from the extinction corrected H$\alpha$ luminosity, L$_{{\rm H}\alpha}$, calculated from the H$\alpha$ flux.
 We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.
@@
 
-Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, giving us the specific star formation rate (sSFR).
+Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, $M_*$, giving us the specific star formation rate (sSFR).
 The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each spaxel (spatial pixel).
@@
 
-This will allow us to compare the SFR in high mass regions, like the centers of the galaxies, to the SFR lower mass regions, like the disk of the galaxies.
-We have also found a strong correlation between sSFR and \ewha\ and have found the same results using \ewha.
-This is useful to check as \ewha\ is an observable and independent of {\sc SPFIT}'s measurement of the stellar mass.
+This will allow us to compare regions to high mass surface density to regions of low mass surface density.
 
-%We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation.
-To separate ionization sources, we use the theoretical maximum starburst line from \citet{Kewley:2001} (Equation \ref{eq:kewley}).
+We check the results of the radial profiles of this sSFR against the radial profiles of \ewha\ and find that they are in good agreement.
+\ewha\ is an observable while our measurement of the sSFR is dependent on both the H$\alpha$ luminosity and {\sc spfit}'s calculation of the stellar mass, so this check helps confirm the quality of our sSFR measurement.
 
-%\begin{equation}\label{eq:kewley}
-%\rm{log\Big(\frac{[O\,\textsc{iii}]\lambda 5007}{H\beta}\Big) = \frac{0.61}{log([N\,\textsc{ii}]\lambda 6584 / H\alpha) - 0.47} + 1.19}
-%\end{equation}
-
-%Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel.
-We use the \citet{Kewley:2001} demarcation line as the limit for classifying star formation in the MaNGA spaxels.
-
-It has been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
+%It has been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
 To mask retired spaxels, we implement a H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ \citep{Cid-Fernandes:2011}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Geometry of Galaxies}\label{sec:radial}
+\subsection{Radial Profiles}\label{sec:radial}
 
@@
 In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR.
-First, the geometry of the galaxies need to be defined.
+First, the geometry of the galaxies needs to be defined.
 Specifically we will need position angle, inclination angle, and the effective radius of each of the MaNGA targets.
@@
 The NSA catalog has complete coverage over the MaNGA sample (since MaNGA selects its targets from this catalog); however, it tends to fail to properly fit paired galaxies with close on-sky separations.
-We found that the apertures from \citet{Simard:2011} work better for these close galaxies, but the catalog does not completely cover the MaNGA sample.
-We use NSA catalog for the outside-IFU pair sample because they are well separated on the sky and the \citet{Simard:2011} catalog for the inside-IFU sample.
-In the cases where an Inside-IFU paired galaxy is not covered by \citet{Simard:2011}, we use the ellipse from the NSA catalog.
+We found that the apertures from \citet{Simard:2011} work better for these close paired galaxies; however, the catalog does not completely cover the MaNGA sample.
+We use the NSA catalog for the outside-IFU pair sample because they are well separated on the sky.
+The \citet{Simard:2011} catalog is used for the inside-IFU sample.
+If the paired galaxy is not covered by \citet{Simard:2011}, we use the ellipse from the NSA catalog.
 
-We fit the geometry with aperture from both catalog when available.
+We fit the geometry with apertures from both catalog when available.
 When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
@@
 
-Where $q$ is the intrinsic oblateness. We use the empirically determined oblateness of $q = 0.13$, from \citet{Giovanelli:1994}.
+Where $b/a$ is the major-to-minor axis ratio and $q$ is the intrinsic oblateness. We use the empirically determined oblateness of $q = 0.13$, from \citet{Giovanelli:1994}.
 
 The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies.
-We use the 50\% half light radius, the effective radius (\reff) to scale the sizes of the galaxies.
-Doing this will allow use the compare galaxies of different sizes against each other.
-
-\subsection{Radial Profiles}
+We use the 50\% half light radius (i.e.
+the effective radius, \reff) to scale the sizes of the galaxies.
+Doing this will allow us to compare galaxies of different sizes against each other.
 
@@
 Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
+This gives us an individual radial profile of the sSFR for all paired and control galaxies.
 
@@
 
-\subsection{Future Mass Growth}
-
-The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
-The question is whether or not the advanced mass growth rate is significant.
-
-To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given timescale, $\tau$.
-A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
-
-\begin{equation}
-\frac{\Delta M_{merger}}{M_{total}} = \left({\rm sSFR}_{\rm pair} - {\rm sSFR}_{\rm control}\right) * \tau
-\end{equation}
-
-For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
-The actual timescale for star formation enhancement is likely shorter; however, we will use the 1 Gyr value as an order of magnitude estimate.
-
-To get the difference in sSFR between the pairs and controls, we fit a gaussian to the difference profiles split by stellar mass.
-We then add the modeled difference profile to the stacked control profile in the same mass range in log space.
-We then take the difference between the profiles in linear space and multiply the difference by the 1 Gyr timescale.
-
-We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
-The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 R/\reff, following profile of the $\Delta$log(sSFR).
-The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
-
-The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%).
-This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.
-
-%Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth.
-While low mass galaxies may see a more substantial change to their total stellar mass, the more massive galaxies experience higher growth rates.
-
-In the context of galaxy evolution, where less massive galaxies merge to form larger galaxies, the merger induced star formation contributes a significant amount of stellar mass on top of the stellar mass contribution from the mixing of the two galaxies.
-Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}\label{sec:disc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/mass_gain.pdf}
-\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over 1 Gyr.
-The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
-}
-\label{fig:mass_gain_sum}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
-\caption[]{{\it Use larger bins here.} Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
-\label{fig:ssfr_dmsep}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We primarily focused on how the $\Delta$log(sSFR) in paired galaxies behaves as a function of stellar mass, but we also explored how the $\Delta$log(sSFR) behaves as a function of the mass ratio between the paired galaxies and the projected separation between the paired galaxies.
-While we see hints that the $\Delta$log(sSFR) is affected by the mass ratio and projected separation, these results are less definitive than the $\Delta$log(sSFR) profile's lack of dependence on stellar mass.
-
 \subsection{Dependency on Mass Ratio}
@@
 Different projected separations and mass ratios may elevate or suppress the level of the enhancement in the profile's center; however, the shape of the profile is largely unchanged.
+
+\subsection{Future Mass Growth}
+
+The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
+The question is whether or not the advanced mass growth rate is significant.
+
+To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given timescale, $\tau$.
+A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
+
+\begin{equation}
+\frac{\Delta M_{merger}}{M_{total}} = \left({\rm sSFR}_{\rm pair} - {\rm sSFR}_{\rm control}\right) * \tau
+\end{equation}
+
+For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
+The actual timescale for star formation enhancement is likely shorter; however, we will use the 1 Gyr value as an order of magnitude estimate.
+
+To get the difference in sSFR between the pairs and controls, we fit a gaussian to the difference profiles split by stellar mass.
+We then add the modeled difference profile to the stacked control profile in the same mass range in log space.
+We then take the difference between the profiles in linear space and multiply the difference by the 1 Gyr timescale.
+
+We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
+The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 R/\reff, following profile of the $\Delta$log(sSFR).
+The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
+
+The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%).
+This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.
+
+%Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth.
+While low mass galaxies may see a more substantial change to their total stellar mass, the more massive galaxies experience higher growth rates.
+
+In the context of galaxy evolution, where less massive galaxies merge to form larger galaxies, the merger induced star formation contributes a significant amount of stellar mass on top of the stellar mass contribution from the mixing of the two galaxies.
+Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}\label{sec:disc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/mass_gain.pdf}
+\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over 1 Gyr.
+The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
+}
+\label{fig:mass_gain_sum}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
+\caption[]{{\it Use larger bins here.} Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
+\label{fig:ssfr_dmsep}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We primarily focused on how the $\Delta$log(sSFR) in paired galaxies behaves as a function of stellar mass, but we also explored how the $\Delta$log(sSFR) behaves as a function of the mass ratio between the paired galaxies and the projected separation between the paired galaxies.
+While we see hints that the $\Delta$log(sSFR) is affected by the mass ratio and projected separation, these results are less definitive than the $\Delta$log(sSFR) profile's lack of dependence on stellar mass.
 

### 2020-09-11 maintex.tex
updated Results section

@@
 
-%It has been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
+It has been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
 To mask retired spaxels, we implement a H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ \citep{Cid-Fernandes:2011}.
@@
 The first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins.
-In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset 20 control galaxies which have a similar stellar mass and redshift.
+In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which have a similar stellar mass and redshift.
 
@@
 
+The dashed regions of the profiles in Figure \ref{fig:ssfr_prof} represent regions which have been ``trimmed" due to a low percent of data coverage in the region.
+A radial bin is trimmed if less than 70\% of the galaxies in that bin have data.
+There are a few reasons why galaxy's profile may not have data points at a given radial bin.
+First, the MaNGA IFU may not cover the radius range; only $\sim$37\% of MaNGA galaxies are covered out to 2.5 $R$/\reff.
+This radial coverage limitation primarily affect the lower mass galaxies in the \logm\ $=$ 9.0$-$9.5.
+Second, foreground and background objects have been masked out which can create gaps in the data of an individual galaxies profile.
+This case does not significantly affect the stacked profiles here since the masked out regions will be spread out across the whole radius range.
+Third, retired regions within galaxies have been masked out with the \ewha\ $\ge$ 3\AA\ cut.
+It is well known that high mass galaxies tend to be passive (as seen in our CMD diagram in Figure \ref{fig:cmd}).
+As a consequence, the highest mass galaxies in our sample (\logm\ $=$ 11.0$-$11.5) have much of their profiles trimmed due to absence of star forming spaxels.
+
 This method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls.
@@
 
-We show the mass-binned profiles in Figure \ref{fig:ssfr_prof}.
-Between the median profiles of the control galaxies and paired galaxies, we can see that the paired profiles are flatted in their centers in comparison to the control profiles.
+Between the median profiles of the control galaxies and paired galaxies, we can see that the paired profiles are flattened in their centers in comparison to the control profiles.
 The paired profiles are centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
-This enhancement linearly falls to zero around 1.0 \reff.
+This enhancement linearly falls to zero around 1.0 $R$/\reff.
 In the disks the profiles feature a weak suppression to the sSFR of 0.05$-$0.1 dex.
 
-The sSFR enhancement show no dependence on the stellar mass, the profiles of the different mass bins fall within $\sim$0.2 dex of median profile.
+The sSFR in the pair sample shows no dependence on their stellar mass.
+The profiles from all of the mass ranges fall within $\sim$0.2 of the median profile.
 This means that low mass galaxies are enhanced at the same level as high mass galaxies.
-It is also notable that while this method of pair-control comparison is not rigorous as the next method, the central star formation enhancement is clearly present.
+It is also notable that while this method of pair-control comparison is not rigorous as the next method, the central star formation enhancement is clearly present at all stellar masses.
+
+The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
+The fractional mass growth rate is simply the difference between the sSFR profiles of the paired and control galaxies (pairs - controls) multiplied by at timescale.
+We chose a timescale of 1 Gyr as an order of magnitude estimate of the interaction event \citep{Boylan-Kolchin:2008}, though the actual timescale of the merger induced starburst is likely somewhat shorter ($\sim$0.4 Gyr; \citet{Feng:2019}).
+
+Since the $\Delta$log(sSFR) is independent of galaxy mass, the fractional mass change will depend on the stellar mass of the paired galaxy.
+Low mass galaxies, \logm\ $=$ 9.0$-$9.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.06 (6\%) while massive galaxies, \logm\ $=$ 11.0$-$11.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.005 (0.5\%).
+This show that the merger induced mass growth is greatest in low mass galaxies.
+Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
 
@@
 
-In the second method, we match each paired galaxy to a set of 20 control galaxies of a similar stellar mass and redshift, as mentioned in Section \ref{sec:control}.
-We take the individual averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin giving us a stacked profile of control galaxies.
-The error of the profile is the standard error of the mean of the individual profiles.
+In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}.
+We take the individual azimuthally averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin to produce the average profile of the control galaxies.
+
+% Is this necessary
+%The error of the profile is the standard error of the mean of the individual profiles.
 We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of the stacked profiles over 1000 iterations.
@@
 
-Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space.
+Once the average profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the average control profile in log space.
 We do this process for each of the 220 paired galaxies.
 
-The difference profiles at this stage have now been controlled for stellar mass, redshift, and galaxy size.
-We can freely stack these profiles to study the global properties of the merging galaxies.
-We take all of the $\Delta$log(sSFR) profiles and take the median value within each radius bin to create a stacked profile of the individual difference profiles.
+The difference profiles at this stage have now been controlled for stellar mass and redshift.
+We can freely stack these difference profiles to study their dependence on other parameter like the mass ratio and projected separation.
 We split the individual difference profiles into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5 and stack the difference profiles within each mass bin.
 This gives us five difference profiles covering five different stellar mass ranges shown in the left hand panel of Figure \ref{fig:ssfr_mass}.
+The errors of the stacked profiles are the standard error of the mean of the difference profiles within each bin.
 
@@
 The profiles are largely consistent with the results of the previous mass binning method.
-The profiles of this method have less scatter, which may be due to how the paired are more closely matched in stellar mass and redshift.
-This method also has the added benefit that the profiles can be separated by other parameters instead of just the stellar mass.
+The profiles of this method have less scatter as a result of how the paired are more closely matched in stellar mass and redshift.
+This method also has the added benefit that the profiles can be separated by parameters other than stellar mass.
+We will discuss how these profiles behave as a function of the mass ratio and projected separation in the following sections.
 
@@
 We extract the $\Delta$log(sSFR) from the individual difference profiles.
-We extract the value of $\Delta$log(sSFR) from the inner 0.5 R/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture.
+We extract the value of $\Delta$log(sSFR) from the inner 0.5 $R$/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture.
 We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
@@
 Low mass galaxies are having their sSFR enhanced at a similar rate as high mass galaxies.
+
+%\subsection{Future Mass Growth}
+
+%The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
+The question is whether or not the advanced mass growth rate is significant.
+
+%To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given timescale, $\tau$.
+A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
+
+%\begin{equation}
+%\frac{\Delta M_{merger}}{M_{total}} = \left({\rm sSFR}_{\rm pair} - {\rm sSFR}_{\rm control}\right) * \tau
+%\end{equation}
+
+%For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
+The actual timescale for star formation enhancement is likely shorter; however, we will use the 1 Gyr value as an order of magnitude estimate.
+
+%To get the difference in sSFR between the pairs and controls, we fit a gaussian to the difference profiles split by stellar mass.
+We then add the modeled difference profile to the stacked control profile in the same mass range in log space.
+We then take the difference between the profiles in linear space and multiply the difference by the 1 Gyr timescale.
+
+%We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
+The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 R/\reff, following profile of the $\Delta$log(sSFR).
+The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
+
+%The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%).
+This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.
+
+%In the context of galaxy evolution, where less massive galaxies merge to form larger galaxies, the merger induced star formation contributes a significant amount of stellar mass on top of the stellar mass contribution from the mixing of the two galaxies.
+Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
 
@@
 
-\subsection{Future Mass Growth}
-
-The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
-The question is whether or not the advanced mass growth rate is significant.
-
-To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given timescale, $\tau$.
-A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
-
-\begin{equation}
-\frac{\Delta M_{merger}}{M_{total}} = \left({\rm sSFR}_{\rm pair} - {\rm sSFR}_{\rm control}\right) * \tau
-\end{equation}
-
-For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
-The actual timescale for star formation enhancement is likely shorter; however, we will use the 1 Gyr value as an order of magnitude estimate.
-
-To get the difference in sSFR between the pairs and controls, we fit a gaussian to the difference profiles split by stellar mass.
-We then add the modeled difference profile to the stacked control profile in the same mass range in log space.
-We then take the difference between the profiles in linear space and multiply the difference by the 1 Gyr timescale.
-
-We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
-The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 R/\reff, following profile of the $\Delta$log(sSFR).
-The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
-
-The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%).
-This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.
-
-%Galaxies in the mass range \logm\ $=$ 9.0$-$10.0 have a mass growth of $\sim$1.6$\times$ that of secular mass growth and galaxies in the mass range \logm\ $=$ 10.0$-$11.0 have a mass growth of $\sim$2.3$\times$ that of secular mass growth.
-While low mass galaxies may see a more substantial change to their total stellar mass, the more massive galaxies experience higher growth rates.
-
-In the context of galaxy evolution, where less massive galaxies merge to form larger galaxies, the merger induced star formation contributes a significant amount of stellar mass on top of the stellar mass contribution from the mixing of the two galaxies.
-Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/mass_gain.pdf}
-\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over 1 Gyr.
+%\begin{figure}
+%\centering
+%\includegraphics[width=3in]{fig/mass_gain.pdf}
+%\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over 1 Gyr.
 The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
 }
-\label{fig:mass_gain_sum}
-\end{figure}
+%\label{fig:mass_gain_sum}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-09-22 maintex.tex
updated mass ratio and separation sections

@@
 \subsection{Dependency on Mass Ratio}
-While the total stellar mass between the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
+While the total stellar mass of the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
 The mass ratio here is calculated as the difference between stellar masses contained within the 50\% half light radius,
@@
 \begin{equation}
-\Delta {\rm log}(M) = {\rm log}(M_{target}) - {\rm log}(M_{comp}) 
+\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}) 
 \end{equation}
 
-Where M$_{target}$ is the stellar mass of the MaNGA target galaxy and M$_{comp}$ is the stellar mass of the companion galaxy.
-Note that we do not use the absolute value of the difference like how the mass ratio is typically used.
-We do this so that we can independently study how the star formation large central galaxies behave in comparison to small satellite galaxies.
+Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
 
@@
 
-In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log(M) $=$ 0.0.
+In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0.
 These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
-This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log(M)$|$ $=$ 1.0.
+This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0.
 
-We also use the mass ratio to explore how the merger induced tidal torques affect paired galaxies with large mass ratios, $|\Delta$log(M)$|$ > 0.5.
+We also use the mass ratio to explore how the merger induced tidal torques affect paired galaxies with large mass ratios, $|\Delta$log($M$)$|$ > 0.5.
 We use the mass ratio to separate the massive central galaxy from satellite galaxies.
@@
 In previous studies it was noted that the enhancement to the SFR is strongest in galaxy pairs with small mass ratios \citet{Ellison:2008}.
-We see the same effect; however, we have also shown that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement.
-It has been a convention to split galaxy pairs in major mergers, $|$log(M)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log(M)$|$ $\le$ 1.0.
-In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log(M)$|$ $\le$ 1.5 so that larger pair samples can be constructed.
+We see the same effect; however, we have also found that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement.
+It has been a convention to split galaxy pairs in major mergers, $|$log($M$)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log($M$)$|$ $\le$ 1.0.
+In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log($M$)$|$ $\le$ 1.5 so that larger pair samples can be constructed.
 
-Further, within these galaxy pairs with wide mass ratios we see that the less massive galaxy in the pair shows higher levels of sSFR enhancement.
+Further, within these galaxy pairs with wide mass ratios we see that the less massive galaxy in the pair ($\Delta$log($M$) $<$ 0) shows higher levels of sSFR enhancement.
 This implies that satellite galaxies are more affected by interaction induced star formation than the central galaxy.
@@
 The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
-The profiles in the galaxy pairs in the separation range, $r_p$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the the profiles of the galaxy pairs in the separation range, $r_p$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.
+The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.
 
@@
 The passage of the first pericenter is predicted to trigger a burst of star formation which falls as the two galaxies separate \citep{Scudder:2012}.
-The sSFR enhancement in our sample persists out to 50 kpc, \citet{Patton:2013} showed that the burst of star formation can persist out to 150 kpc.
+The sSFR enhancement in our sample persists out to 50 kpc.
+\citet{Patton:2013} showed that the burst of star formation can persist out to 150 kpc.
 
-For galaxies with separations of $r_p$ $<$ 5 kpc and $r_p$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero.
-For the $r_p$ $<$ 5 kpc galaxies, about half of the pairs show signs of tidal features while the others do not.
+For galaxies with separations of $r_{\rm p}$ $<$ 5 kpc and $r_{\rm p}$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero.
+For the $r_{\rm p}$ $<$ 5 kpc galaxies, about half of the pairs show signs of tidal features while the others do not.
 The pairs without the tidal features may be approaching their first pericenter, meaning that the merger-induced gas-inflows have not been triggered yet.
 The dips in $\Delta$log(sSFR) may also just be due to statistical error from the relatively limited sample size.
-
-Between the three parameters, stellar mass, mass ratio, and projected separation, the projected separation has the strongest effect on the $\Delta$log(sSFR) enhancement, followed by the mass ratio.
-From this we see that the paired galaxies with the strongest enhancements to the central sSFR are paired galaxies with 1:1 mass ratios and  which are within 10 kpc.
-
-Between the splitting the $\Delta$log(sSFR) profile by stellar mass, mass ratio, and projected separation, we see that the general shape of the profile within the inner 1.0 R/\reff\ is unchanged.
-The profile is peaked in the center of the paired galaxies and linearly (in log space) to zero around 1.0 R/\reff.
-Different projected separations and mass ratios may elevate or suppress the level of the enhancement in the profile's center; however, the shape of the profile is largely unchanged.
 
@@
 
-We primarily focused on how the $\Delta$log(sSFR) in paired galaxies behaves as a function of stellar mass, but we also explored how the $\Delta$log(sSFR) behaves as a function of the mass ratio between the paired galaxies and the projected separation between the paired galaxies.
-While we see hints that the $\Delta$log(sSFR) is affected by the mass ratio and projected separation, these results are less definitive than the $\Delta$log(sSFR) profile's lack of dependence on stellar mass.
+Among the three parameters, stellar mass, mass ratio, and projected separation, the projected separation has the strongest effect on the $\Delta$log(sSFR) enhancement, followed by the mass ratio.
+From this we see that the paired galaxies with the strongest enhancements to the central sSFR are paired galaxies with 1:1 mass ratios and  which are within 10 kpc.
+
+Between the splitting the $\Delta$log(sSFR) profile by stellar mass, mass ratio, and projected separation, we see that the general shape of the profile within the inner 1.0 $R$/\reff\ is unchanged.
+The profile is peaked in the center of the paired galaxies and linearly (in log space) to zero around 1.0 $R$/\reff.
+Different projected separations and mass ratios may elevate or suppress the level of the enhancement in the profile's center; however, the shape of the profile is largely unchanged.
 

### 2020-09-25 maintex.tex
updated discussion

@@
 \centering
-\includegraphics[width=3in]{fig/nuc_sep.pdf}
-\caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Li:2008} (Orange), \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
-}
-\label{fig:nuc_sep}
+\includegraphics[width=3in]{fig/prof_comp.pdf}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
+\label{fig:prof_comp}
 \end{figure}
@@
 \centering
-\includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work (red) compared against those of \citet{Pan:2019} (Blue) and \citet{Thorp:2019} (Green).}
-\label{fig:prof_comp}
+\includegraphics[width=3in]{fig/nuc_sep.pdf}
+\caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Li:2008} (Orange), \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
+}
+\label{fig:nuc_sep}
 \end{figure}
@@
 
-In Figure \ref{fig:prof_comp} we look at the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
+In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
 \citet{Pan:2019} examines a set of paired galaxies in the MaNGA survey while \citet{Thorp:2019} examines a set of post-merger galaxies in the MaNGA survey.
-The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughtly $\sim$0.1$-$0.2 dex higher than our sample.
-The $\Delta$log(sSFR) profile is closest to our work at the centers of the galaxy pairs but then begins to diverge further out into the galaxies' disks.
+The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughly $\sim$0.1$-$0.2 dex higher than our sample.
 Our paired galaxies show a slight sSFR suppression in their disks past 1.0 R/\reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+The reason for the discrepancies between our samples is that \citet{Pan:2019} includes a set of post-merger galaxies while our sample has no post-merger galaxies.
+These post-merger galaxies are predicted to have higher levels of star formation over other paired galaxies due to a second larger burst of star formation which is triggered as the merging galaxies coalesce.
 
-The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 higher than our sample of paired galaxies.
+The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 dex higher than our sample of paired galaxies.
 The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
-The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 R/\reff\ of $\sim$0.1$-$0.15 dex.
+The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 $R$/\reff\ of $\sim$0.1$-$0.15 dex.
 The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
 
-\citet{Barrera-Ballesteros:2015} studied the sSFR in paired galaxies in the CALIFA IFS survey using the H$\alpha$ equivalent width (\ewha) as a proxy.
+\citet{Barrera-Ballesteros:2015} studied the sSFR in paired galaxies in the CALIFA IFS survey using the H$\alpha$ equivalent width (\ewha) as a proxy for the sSFR.
 They compared the sSFR in the centers of paired galaxies to their disks by varying the aperture diameters from which they extract the \ewha.
-They found that the sSFR is enhanced in the centers of the paired galaxies but suppressed in their disks.
-Between our work, \citet{Barrera-Ballesteros:2015}, and \citet{Pan:2019} there three is different scenarios; one where the disks of the paired galaxies see no change to the sSFR, one where the sSFR is suppressed, and one where the sSFR is enhanced.
-
-Looking at individual difference profiles in our work, we see that there is a large variance in the $\Delta$log(sSFR) where there are as many paired galaxies with sSFR enhancement in their disks as there are paired galaxies with suppression in there disks.
-The end result is that the average of the $\Delta$log(sSFR) is zero.
-The merger induced effects seen in the disks of the paired galaxies may be more complicated than what is seen in the centers of the galaxies.
+They found that the sSFR is enhanced in the centers of the paired galaxies but suppressed in their disks, which is similar to what we find.
 

### 2020-10-01 maintex.tex
minor updates

@@
 \begin{abstract}
-We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 220 star-forming galaxies in close pairs with those of mass-matched isolated galaxies in the SDSS-IV MaNGA survey.
+We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 175 star-forming galaxies in close pairs with those of mass-matched isolated galaxies in the SDSS-IV MaNGA survey.
 We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.3 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
@@
 
-We classify galaxies in this survey as star forming galaxies using the color-magnitude diagram (CMD).
+We classify galaxies in this survey as star forming galaxies by selecting galaxies in the blue cloud on the color-magnitude diagram (CMD).
 We show the CMD for the MaNGA survey and our pair sample in Figure \ref{fig:cmd} along with demarcation lines which separate the blue cloud, red sequence, and green valley.
@@
 Where $NUV-r$ is the color from SDSS's k-corrected absolute magnitude and $\mathcal{M}_i$ is the i-band magnitude from the NSA catalog.
-We have checked the selected star forming galaxies on the BPT diagram \citep{Baldwin:1981} to confirm that AGN (active galactic nuclei) will have a minimal impact on our SFG sample.
+We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0 \reff\ aperture to remove any passive galaxies which may have passed the CMD cut \citep{Cid-Fernandes:2011}.
+We further use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with an AGN from our sample.
+We use the emission line ratios, log([O\textsc{III}]/H$\beta$) and log([N\textsc{II}]/H$\alpha$), extracted from a 1.3 kpc aperture along with the maximum starburst line from \citet{Kewley:2001} as the demarcation between star forming branch and the AGN branch.
 
-On top of the color selection cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}, and that the stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.
+On top of the star formation cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}, and that the stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.
+We use masses calculated from the elliptical Petrosian apertures in the NSA catalog for our total stellar masses.
 
@@
 
-Several of the target galaxies in our sample have multiple companions. From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
+Several of the target galaxies in our sample have multiple companions.
+From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
+In cases where a MaNGA target has multiple viable companions galaxies, we chose the closest companion when measuring the mass ratio and projected separation.
 
@@
 After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU.
-This give use a total of 220 MaNGA targets in our pair sample.
+This give use a total of 175 MaNGA targets in our pair sample.
 
@@
 We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_p$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
-This gives us a control sample of 1891 star forming control galaxies.
+This gives us a control sample of 1888 star forming control galaxies.
 
@@
 Since we want each paired galaxy to be treated in a similar manner, we will down-select the total number of acquired control galaxies down to 20 controls randomly.
+Control galaxies may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times.
 In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.
-A small set of paired galaxies required extra iterations to find 20 controls; 8 needed an extra iteration, 1 needed two extra iterations, and 1 needed three iterations.
+Only 5 of the paired galaxies required an extra iteration to find 20 controls.
 
@@
 
-It has been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic H\,{\sc ii} regions and AGN on the BPT diagram \citep{Stasinska:2008}.
-To mask retired spaxels, we implement a H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ \citep{Cid-Fernandes:2011}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We fit the geometry with apertures from both catalog when available.
+We fit the geometry with apertures from both catalogs when available.
 When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
 When making the comparison with the second method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
-
-We compared the magnitudes extracted from the two apertures for the control galaxies and found that they are in close agreement.
-This means that the geometries between the two surveys must be in close agreement and the profiles of a galaxy fitted with a NSA aperture can be confidently compared against a galaxy fitted with an aperture from \citet{Simard:2011}.
+Further, when defining the a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
 
@@
 
-Between the median profiles of the control galaxies and paired galaxies, we can see that the paired profiles are flattened in their centers in comparison to the control profiles.
-The paired profiles are centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
+The profiles of the control galaxies are centrally quenched, which was previously seen in the MaNGA sample in \citet{Belfiore:2018}.
+The profiles of the paired galaxies flat across the whole galaxy accept for galaxies with masses above \logm\ $=$ 10.5 which show some central quenching.
+When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
 This enhancement linearly falls to zero around 1.0 $R$/\reff.
@@
 Once the average profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the average control profile in log space.
-We do this process for each of the 220 paired galaxies.
+We do this process for each of the 175 paired galaxies.
 
@@
 In this work, we studied a sample of paired, star forming galaxies using the MaNGA IFS survey.
-We have made a sample of 220 star forming galaxy pairs along with a set of 1891 star forming control galaxies.
-We compared the radial profiles of the paired galaxies with those of the controls galaxies and found the follwing;
+We have made a sample of 175 star forming galaxy pairs along with a set of 1888 star forming control galaxies.
+We compared the radial profiles of the paired galaxies with those of the controls galaxies and found the following;
 
@@
 \item The sSFR is centrally enhanced within the inner 1.0 R/\reff\ by 0.25 $\pm$ 0.1 dex. 
-\item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show limited suppression in their disks, $\sim$0.1 dex.
+\item The outskirts of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show limited suppression in their disks of $\sim$0.1 dex.
 \item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies, Massive galaxies experience the same level of sSFR enhancement as low mass galaxies.
@@
 We have also showed that paired galaxies with large mass ratios, $|\Delta$log(M)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.15$-$0.2 dex.
-\item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair, $\sim$0.1 dex.
-\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4 $\pm$ 0.1 dex. 
+\item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair by $\sim$0.1 dex.
+\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4 which is consistent with previous single fiber studies. 
 \item When splitting the sSFR enhancement profiles by stellar mass, mass ratio, or projected separation, the general shape of the enhancement profile is unchanged.
-While lower projected separations or mass ratios closer to 1:1 may raise the level of the central enhancement to the profiles, the profiles still linearly fall to zero enhancement around 1.0 R/\reff\ with roughly the same gradient.
-\item The paired galaxies will experience a fractional mass growth rate of 1$-$6\%, where the growth in mass in largest in low mass galaxies.
+While lower projected separations or mass ratios closer to 1:1 may raise the level of the central enhancement, the profiles still linearly fall to zero enhancement around 1.0 R/\reff.
+\item The paired galaxies will experience a fractional mass growth rate of 1$-$6\%, where the growth in mass is largest in low mass galaxies.
 

### 2020-10-02 maintex.tex
added simulations to the previous works comparisons

@@
 \includegraphics[width=3in]{fig/nuc_sep.pdf}
-\caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Li:2008} (Orange), \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
+\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red),  \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
+(\textbf{Bottom}) $\Delta$log(sSFR) over projected separation for this sample (Black), \citet{Li:2008} (Red), and \citet{Patton:2020} (Blue).
 }
@@
 They found that the sSFR is enhanced in the centers of the paired galaxies but suppressed in their disks, which is similar to what we find.
+
+\citet{Moreno:2015} used {\sc Gadget}-3, a smoothed particle hydrodynamics code, to study the spatial extend of the star formation enhancement.
+The merger simulations showed that the star formation enhancement was largely concentrated in the centers (R $<$ 1 kpc) of the paired galaxies and that the off-nuclear regions (1 $<$ R $<$ 10 kpc) showed a suppression to the star formation.
+\citet{Moreno:2015} also found that star formation offsets in lower mass secondary galaxies (in mergers with stellar mass ratios of 2.5:1) have a stronger radial dependence with respect to the more massive primary companion.
+This is in good agreement with our work, we found that secondary companions show moderately higher levels of sSFR enhancement in their centers in comparison to primary companions at the same mass ratio.
+Further, the outskirts of the primary companions feature no enhancement or suppression to their sSFR while the secondary companions show a strong suppression to the sSFR at large radii.
+
+The sSFR as a function of separation was studied with the cosmological hydrodynamical simulations of IllustrisTNG \citep{Patton:2020}.
+In Figure \ref{fig:nuc_sep} we show the $\Delta$log(sSFR) enhancements across 2D separation (projected separation) from the TNG300-1 simulation.
+\citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2d separation of $\sim$250 kpc.
+This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in \ref{fig:nuc_sep} was extracted from a 0.5\reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius.
+This means that our extraction radius is effectively twice a small and is more restricted to the central burst of star formation.
 

### 2020-10-09 maintex.tex
Updated Results

@@
 \includegraphics[width=\linewidth]{fig/color-mag.pdf}
-\caption[]{Color-magnitude diagram for MaNGA galaxies ({\it colored circles}).
-The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-Inside and outside-IFU pairs are marked with {\it grey diamonds}.
+\caption[]{Color-magnitude diagram for MaNGA galaxies.
+The grey circles represent the whole MaNGA sample and reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+Inside-IFU pairs are marked with red diamonds and the outside-IFU pairs are marked with red squares.
 From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
@@
 \section{Radial Profiles of Star Formation}\label{sec:analysis}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
+\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
+The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel.
+The dashed black profile represents the mean of the difference profiles.
+The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses.
+The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.
+The parts of the profiles with dashed lines represent regions where less than 50\% of the galaxies in the bin are covered at that radii.
+}
+\label{fig:ssfr_prof}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Specific Star Formation Rate}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
-\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
-The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel.
-The dashed black profile represents the mean of the difference profiles).
-The colors of the profiles represent the mass range of the selected galaxies and the highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.}
-\label{fig:ssfr_prof}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR.
@@
 Once the geometry of the galaxies are set, we can build the radial profiles.
-The spaxels are binned into radius increments of 0.1 R/\reff\ from 0.0$-$2.5 R/\reff.
+The spaxels are binned into radius increments of 0.2 R/\reff\ from 0.0$-$2.6 R/\reff.
 Within each radius bin we take the median of the specific star formation rate.
@@
 
-We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects within the MaNGA IFUs which may contaminate the data.
+%We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects within the MaNGA IFUs which may contaminate the data.
 Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
@@
 
+The radial extent of our profiles go out to 2.6 $R$/\reff; however,  67\% of the MaNGA sample is designed to cover only 1.5 $R$/\reff\ of the galaxy.
+Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall into the 0.2 $R$\reff\ bin.
+Because of these issues, the centers or the outskirts of the stacked profiles may only represent a small subset of the galaxies in that mass bin.
+To account for this, we ``trim" the stacked profiles where radii bins contain data for less than 50\% of the total set of galaxies.
+We represent the trimmed regions in our figures with dashed lines.
+In Figure \ref{fig:ssfr_prof}, this is shown in the centers of the lower mass galaxies, \logm\ $\le$ 10.0.
+
 Once the stacked profiles are made, we take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the profiles really represents a ratio between the pairs and controls in linear space).
@@
 
-The dashed regions of the profiles in Figure \ref{fig:ssfr_prof} represent regions which have been ``trimmed" due to a low percent of data coverage in the region.
+%The dashed regions of the profiles in Figure \ref{fig:ssfr_prof} represent regions which have been ``trimmed" due to a low percent of data coverage in the region.
 A radial bin is trimmed if less than 70\% of the galaxies in that bin have data.
@@
 
-This method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls.
-On the other hand, this method only controls for a single galaxy parameter, stellar mass.
-Further the profiles can only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.
+The profiles of the control galaxies are lower in their centers, which was previously seen in the MaNGA sample in \citet{Belfiore:2018}.
+The profiles of the paired galaxies flat across the whole galaxy accept for galaxies with masses above \logm\ $\ge$ 10.5 which show some central quenching.
+Because of this, it may be more accurate to describe the control galaxies as centrally suppressed or quenched in comparison to the paired galaxies which feature flat profiles of star formation.
+The difference in the pair and control profiles seems to indicate that the mechanism for quenching in galaxies is the depletion of gases in their centers.
+The gas inflows from the merger events can then refuel the centers of these quenched galaxies and allow new star formation to occur.
 
-The profiles of the control galaxies are centrally quenched, which was previously seen in the MaNGA sample in \citet{Belfiore:2018}.
-The profiles of the paired galaxies flat across the whole galaxy accept for galaxies with masses above \logm\ $=$ 10.5 which show some central quenching.
-When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
-This enhancement linearly falls to zero around 1.0 $R$/\reff.
-In the disks the profiles feature a weak suppression to the sSFR of 0.05$-$0.1 dex.
-
-The sSFR in the pair sample shows no dependence on their stellar mass.
-The profiles from all of the mass ranges fall within $\sim$0.2 of the median profile.
-This means that low mass galaxies are enhanced at the same level as high mass galaxies.
-It is also notable that while this method of pair-control comparison is not rigorous as the next method, the central star formation enhancement is clearly present at all stellar masses.
+When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.35 $\pm$ 0.1 dex which then falls to zero around 1.2 R/\reff.
+In the outskirts of the pairs beyond 1.2 R/\reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex.
+All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile.
+The most massive galaxies in the range, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 R/\reff\ is higher than the median profile at 0.5$-$0.6 dex.
+The sSFR enhancement in the sample seems to mass independent except for the most massive galaxies which feature higher levels of enhancement.
 
@@
 Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
+
+This method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls.
+On the other hand, this method only controls for a single galaxy parameter, stellar mass, though it is still relevant that the central enhancement of the sSFR in pairs is able to be observed.
+Further the profiles can only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
+\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
+The profiles are split into four different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile.
+The black dashed line represents the mean profile between the four difference mass ranges.
+The number of paired galaxies in each mass range is given in the legend in parentheses.
+In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown.
+The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
+The vertical error bars on the black squares represent the standard deviation within the bin.
+The horizontal, dashed black line represents the median central enhancement of the pair sample.
+Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
+\label{fig:ssfr_mass}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/sep_hist.pdf}
+\caption[]{The projected separation distribution of the whole sample (blue) against the projected separation distribution for the highest mass galaxies, \logm\ $=$ 11.0$-$11.5 (Red). }
+\label{fig:sep_hist}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Once the average profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the average control profile in log space.
+Once the median profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the median control profile in log space.
 We do this process for each of the 175 paired galaxies.
@@
 
+To focus on the sSFR offsets in the centers of the galaxies, we take the median sSFR within 0.5 \reff\ for all galaxies.
+We then calculate the offsets in the centers of the pairs by taking the difference between the sSFR in the centers of the pairs and the median sSFR of their 20 controls.
+We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}
+
 The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
-The enhancement falls to zero around 1.0 \reff\ and is slightly suppressed in their disks by $\sim$0.1 dex.
-While all of the other paired galaxies show a sSFR suppression in their disks, the profiles of the pairs in the stellar mass range of \logm\ $=$ 9.0$-$9.5 show an enhancement in their disks of $\sim$0.1$-$0.2 $\pm$ 0.1 dex.
+Similar to what was seen in Section \ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.15$-$0.25 dex higher than the sample average.
 
-The profiles are largely consistent with the results of the previous mass binning method.
-The profiles of this method have less scatter as a result of how the paired are more closely matched in stellar mass and redshift.
-This method also has the added benefit that the profiles can be separated by parameters other than stellar mass.
-We will discuss how these profiles behave as a function of the mass ratio and projected separation in the following sections.
+To understand why these high mass galaxies behave differently from the rest of the sample, we compare the distribution of the projected separation between the whole sample and the galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.
+The whole sample has a relatively flat separation distribution while 70\% of the highest mass galaxies in the sample are within 20 kpc.
+As we will show in Section \ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.
 
-We can also inspect the star formation enhancement within individual paired galaxies.
-We extract the $\Delta$log(sSFR) from the individual difference profiles.
-We extract the value of $\Delta$log(sSFR) from the inner 0.5 $R$/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture.
-We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
-The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.2 dex $\Delta$log(sSFR) median.
+The central enhancement to the sSFR falls to zero around 1.2 $R$/\reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex.
+The paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, feature enhanced sSFR in their disks of 0.1$-$0.2 dex.
+As we will show in the next section, Section \ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.
 
-Between the two different pair-control comparison methods, we conclude that the $\Delta$log(sSFR) is independent of the paired galaxies' stellar mass.
-Low mass galaxies are having their sSFR enhanced at a similar rate as high mass galaxies.
+The results we obtain from the tailored-control method is largely consistent with the mass-binning method.
+Between the two methods we see that the $\Delta$log(sSFR) profile is independent of the total stellar mass of the galaxies.
+In the next two sections, we will use the tailored-control method to study how the profiles behave as a function of the mass ratio (Section \ref{sec:dm}) and projected separation (Section \ref{sec:sep}).
 
-%\subsection{Future Mass Growth}
-
-%The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
-The question is whether or not the advanced mass growth rate is significant.
-
-%To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given timescale, $\tau$.
-A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;
-
-%\begin{equation}
-%\frac{\Delta M_{merger}}{M_{total}} = \left({\rm sSFR}_{\rm pair} - {\rm sSFR}_{\rm control}\right) * \tau
-%\end{equation}
-
-%For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}.
-The actual timescale for star formation enhancement is likely shorter; however, we will use the 1 Gyr value as an order of magnitude estimate.
-
-%To get the difference in sSFR between the pairs and controls, we fit a gaussian to the difference profiles split by stellar mass.
-We then add the modeled difference profile to the stacked control profile in the same mass range in log space.
-We then take the difference between the profiles in linear space and multiply the difference by the 1 Gyr timescale.
-
-%We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}.
-The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 R/\reff, following profile of the $\Delta$log(sSFR).
-The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.
-
-%The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%).
-This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.
-
-%In the context of galaxy evolution, where less massive galaxies merge to form larger galaxies, the merger induced star formation contributes a significant amount of stellar mass on top of the stellar mass contribution from the mixing of the two galaxies.
-Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
-
+\subsection{Dependency on Mass Ratio}\label{sec:dm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
-\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
-The profiles are split into four different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile.
-The black dashed line represents the mean profile between the four difference mass ranges.
-In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown.
-The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
-The vertical error bars on the black squares represent the standard deviation within the bin.
-The horizontal, dashed black line represents the median central enhancement of the pair sample.
-Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
-\label{fig:ssfr_mass}
+\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
+\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. }
+\label{fig:ssfr_dm}
 \end{figure*}
@@
 
-\subsection{Dependency on Mass Ratio}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}
+%\centering
+%\includegraphics[width=\linewidth]{fig/ssfr_massdm.pdf}
+%\caption[]{Same as the left hand panel of Figure \ref{fig:ssfr_mass} except primary companions are shown on the \textbf{Left} and secondary companions are shown on the \textbf{Right}.
+The \logm\ $=$ 11.0$-$11.5 mass bin is left out of left hand panel since it only contains two galaxies.
+}
+%\label{fig:ssfr_massdm}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 While the total stellar mass of the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
@@
 Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
+We will define the more massive galaxies of a pair, $\Delta$log(M) $>$ 0.0, the primary companion and the less massive galaxy of a pair, $\Delta$log(M) $<$ 0.0, the secondary companion.
 
@@
 
-In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0.
+In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log(M)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log(M)$|$ $>$ 0.5.
+Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex.
+Secondary companions also feature slightly higher levels of enhancement than primary companions at the same mass ratios by $\sim$0.1 dex.
+
+The sSFR offsets in the outskirts of the galaxy pairs show a dependence on the mass ratio.
+Primary companions show a zero to positive enhancement, 0.0$-$ 0.4 dex, to the sSFR in their outskirts.
+Secondary companions feature a suppression to the sSFR in their outskirts of about 0.1$-$0.4 dex.
+
+In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0.
 These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
 This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0.
+We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.
 
-We also use the mass ratio to explore how the merger induced tidal torques affect paired galaxies with large mass ratios, $|\Delta$log($M$)$|$ > 0.5.
-We use the mass ratio to separate the massive central galaxy from satellite galaxies.
-A paired galaxy with a positive mass ratio is the more massive galaxy of the pair while a paired galaxy with negative mass ratio is the less massive galaxy.
-We see that the less massive galaxy of a pair show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to the more massive galaxy.
-This shows us that satellite galaxies may be more susceptible to tidal interactions than the central galaxies in the pair system.
+%To emphasize the difference between primary and secondary companions and to further investigate the sSFR enhancement seen in the outskirts of low mass galaxies (\logm\ $=$ 9.0$-$9.5), we plot the difference profiles split both by stellar mass and mass ratio in Figure \ref{fig:ssfr_massdm}.
+The difference profile of primary companions is centrally enhanced by 0.25 dex and remains enhanced across their disks with an enhancement of 0.1-0.3 dex.
+The difference profile of secondary companions is centrally enhanced by 0.3 dex and is suppressed by 0.1 dex in their outskirts.
+Specifically looking at the paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, the primary companions in the mass range show strong enhancements to their outskirts while the primary companions in the mass range show a weak suppression to their outskirts.
 
-In previous studies it was noted that the enhancement to the SFR is strongest in galaxy pairs with small mass ratios \citet{Ellison:2008}.
-We see the same effect; however, we have also found that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement.
-It has been a convention to split galaxy pairs in major mergers, $|$log($M$)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log($M$)$|$ $\le$ 1.0.
-In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log($M$)$|$ $\le$ 1.5 so that larger pair samples can be constructed.
-
-Further, within these galaxy pairs with wide mass ratios we see that the less massive galaxy in the pair ($\Delta$log($M$) $<$ 0) shows higher levels of sSFR enhancement.
-This implies that satellite galaxies are more affected by interaction induced star formation than the central galaxy.
+From the mass ratio, we see two different effects.
+First, we see that the central enhancement to the sSFR is strongest for pairs with 1:1 mass ratios.
+Second, we see that secondary companions show steeper enhancement profiles with higher levels of sSFR enhancement in their centers and stronger sSFR suppression in their disks with respect to primary companions.
+It is interesting to note that the central enhancement to sSFR is dependent on both the mass ratio and the projected separation (which we will demonstrate in the next section) while the sSFR offsets in their outskirts primarily depends on whether the galaxy is the primary or secondary companion of the pair.
 
@@
 
-We also look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_dmsep}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
+\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by projected separation. }
+\label{fig:ssfr_sep}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in Figure \ref{fig:ssfr_sep}.
 The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
-The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.
+The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.05$-$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.
 
@@
 
-For galaxies with separations of $r_{\rm p}$ $<$ 5 kpc and $r_{\rm p}$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero.
-For the $r_{\rm p}$ $<$ 5 kpc galaxies, about half of the pairs show signs of tidal features while the others do not.
-The pairs without the tidal features may be approaching their first pericenter, meaning that the merger-induced gas-inflows have not been triggered yet.
-The dips in $\Delta$log(sSFR) may also just be due to statistical error from the relatively limited sample size.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}\label{sec:disc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering
-%\includegraphics[width=3in]{fig/mass_gain.pdf}
-%\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over 1 Gyr.
-The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles.
-}
-%\label{fig:mass_gain_sum}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
-\caption[]{{\it Use larger bins here.} Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
-\label{fig:ssfr_dmsep}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
 \label{fig:prof_comp}
@@
 \includegraphics[width=3in]{fig/nuc_sep.pdf}
-\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red),  \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
+\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation for this sample using the tailored control method (Black), \citet{Ellison:2008} (Red),  \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
 (\textbf{Bottom}) $\Delta$log(sSFR) over projected separation for this sample (Black), \citet{Li:2008} (Red), and \citet{Patton:2020} (Blue).

### 2020-10-14 maintex.tex
Next round of revisions

@@
 We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 175 star-forming galaxies in close pairs with those of mass-matched isolated galaxies in the SDSS-IV MaNGA survey.
-We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.3 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
+We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
 We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass.
@@
 In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy.
+We also find that the sSFR offsets in the outskirts of the paired galaxies is dependent on whether the galaxy is the more massive or less massive companion in the pair.
+The more massive companion experiences no to a positive sSFR enhancement while the less massive companion experiences a sSFR suppression in their outskirts.
 \end{abstract}
@@
 The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
-MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 $R$/\reff\ and 2.5 $R$/\reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
+MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
 In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.
@@
 
-Where $NUV-r$ is the color from SDSS's k-corrected absolute magnitude and $\mathcal{M}_i$ is the i-band magnitude from the NSA catalog.
-We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0 \reff\ aperture to remove any passive galaxies which may have passed the CMD cut \citep{Cid-Fernandes:2011}.
-We further use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with an AGN from our sample.
+Where $NUV-r$ is the color from SDSS's k-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the i-band magnitude from the NSA catalog.
+We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0 \reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
+We further use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with an AGN in their centers from our sample.
 We use the emission line ratios, log([O\textsc{III}]/H$\beta$) and log([N\textsc{II}]/H$\alpha$), extracted from a 1.3 kpc aperture along with the maximum starburst line from \citet{Kewley:2001} as the demarcation between star forming branch and the AGN branch.
@@
 
-In our previous work, \citet{Fu:2018}, using the 2168 unique galaxies form DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
+In our previous work, \citet{Fu:2018}, using the 2168 unique galaxies from DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
 In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
@@
 The ``good" galaxy spectra are the objects whose spectra are well modeled by {\sc spfit} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
-This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target.
+This means that the companion galaxy can be within approximately $\pm$3000 km s$^{-1}$ of the MaNGA target.
 We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.
 
-From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU.
+From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple galaxy objects within the IFU.
 We further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected companions.
@@
 Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples.
-We also require that the galaxies are classified as star forming by the CMD diagram.
+We also require that the galaxies are classified as star forming as described in Section \ref{sec:data}.
 These requirements reduce our sample down to 87 star forming galaxies (SFGs).
@@
 From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets.
+After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU.
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU.
 This give use a total of 175 MaNGA targets in our pair sample.
@@
 Since we want each paired galaxy to be treated in a similar manner, we will down-select the total number of acquired control galaxies down to 20 controls randomly.
-Control galaxies may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times.
+A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times.
 In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.
@@
 
-While the first method is less sophisticated in comparison to the second method, we will see in Section \ref{sec:results} that the first method is sufficient to see the central enhancement to the star formation rate and the mass independence of the star formation enhancement.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Radial Profiles of Star Formation}\label{sec:analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
-\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
-The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel.
-The dashed black profile represents the mean of the difference profiles.
-The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses.
-The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.
-The parts of the profiles with dashed lines represent regions where less than 50\% of the galaxies in the bin are covered at that radii.
-}
-\label{fig:ssfr_prof}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Specific Star Formation Rate}
@@
 We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
-The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
+The extinction is parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
 
-\begin{equation}
-A_V = 6.78\ {\rm log} \left[(H\alpha/H\beta)/2.85 \right]
-\end{equation}
-
-We measure the SFR from the extinction corrected H$\alpha$ luminosity, L$_{{\rm H}\alpha}$, calculated from the H$\alpha$ flux.
+We measure the SFR from the extinction corrected H$\alpha$ luminosity, L$_{{\rm H}\alpha}$.
 We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.
@@
 Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, $M_*$, giving us the specific star formation rate (sSFR).
-The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each spaxel (spatial pixel).
+The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each MaNGA spaxel (spatial pixel).
 
@@
 
-This will allow us to compare regions to high mass surface density to regions of low mass surface density.
-
-We check the results of the radial profiles of this sSFR against the radial profiles of \ewha\ and find that they are in good agreement.
-\ewha\ is an observable while our measurement of the sSFR is dependent on both the H$\alpha$ luminosity and {\sc spfit}'s calculation of the stellar mass, so this check helps confirm the quality of our sSFR measurement.
+This will allow us to compare regions of high mass surface density to regions of low mass surface density.
 
@@
 First, the geometry of the galaxies needs to be defined.
-Specifically we will need position angle, inclination angle, and the effective radius of each of the MaNGA targets.
+Specifically we will need the position angle, the inclination angle, and the effective radius of each of the MaNGA targets.
 We use the $r$-band elliptical Petrosian apertures from the NSA catalog and the $r$-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies.
@@
 Once the geometry of the galaxies are set, we can build the radial profiles.
-The spaxels are binned into radius increments of 0.2 R/\reff\ from 0.0$-$2.6 R/\reff.
+The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
 Within each radius bin we take the median of the specific star formation rate.
@@
 
-With individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
+\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
+The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel.
+The dashed black profile represents the mean of the difference profiles.
+The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses.
+The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.
+The parts of the profiles with dashed lines represent regions where less than 50\% of the galaxies in the bin are covered at that radii.
+}
+\label{fig:ssfr_prof}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+With the individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies.
 The first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins.
-In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which have a similar stellar mass and redshift.
+In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which are matched in stellar mass and redshift.
 
@@
 
-The radial extent of our profiles go out to 2.6 $R$/\reff; however,  67\% of the MaNGA sample is designed to cover only 1.5 $R$/\reff\ of the galaxy.
-Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall into the 0.2 $R$\reff\ bin.
+The radial extent of our profiles go out to 2.6 \reff; however,  67\% of the MaNGA sample is designed to cover only 1.5 \reff\ of the galaxy.
+Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall outside of the innermost radii bin.
 Because of these issues, the centers or the outskirts of the stacked profiles may only represent a small subset of the galaxies in that mass bin.
-To account for this, we ``trim" the stacked profiles where radii bins contain data for less than 50\% of the total set of galaxies.
+To account for this, we ``trim" the stacked profiles where a radius bin contains data for less than 50\% of the total set of galaxies.
 We represent the trimmed regions in our figures with dashed lines.
-In Figure \ref{fig:ssfr_prof}, this is shown in the centers of the lower mass galaxies, \logm\ $\le$ 10.0.
+In Figure \ref{fig:ssfr_prof}, galaxies below \logm\ $\le$ 10.0 have their innermost radii bin trimmed due to insufficient coverage.
 
-Once the stacked profiles are made, we take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the profiles really represents a ratio between the pairs and controls in linear space).
+Once the stacked profiles are made, we take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space).
 This gives us difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
 
-%The dashed regions of the profiles in Figure \ref{fig:ssfr_prof} represent regions which have been ``trimmed" due to a low percent of data coverage in the region.
-A radial bin is trimmed if less than 70\% of the galaxies in that bin have data.
-There are a few reasons why galaxy's profile may not have data points at a given radial bin.
-First, the MaNGA IFU may not cover the radius range; only $\sim$37\% of MaNGA galaxies are covered out to 2.5 $R$/\reff.
-This radial coverage limitation primarily affect the lower mass galaxies in the \logm\ $=$ 9.0$-$9.5.
-Second, foreground and background objects have been masked out which can create gaps in the data of an individual galaxies profile.
-This case does not significantly affect the stacked profiles here since the masked out regions will be spread out across the whole radius range.
-Third, retired regions within galaxies have been masked out with the \ewha\ $\ge$ 3\AA\ cut.
-It is well known that high mass galaxies tend to be passive (as seen in our CMD diagram in Figure \ref{fig:cmd}).
-As a consequence, the highest mass galaxies in our sample (\logm\ $=$ 11.0$-$11.5) have much of their profiles trimmed due to absence of star forming spaxels.
-
-The profiles of the control galaxies are lower in their centers, which was previously seen in the MaNGA sample in \citet{Belfiore:2018}.
-The profiles of the paired galaxies flat across the whole galaxy accept for galaxies with masses above \logm\ $\ge$ 10.5 which show some central quenching.
-Because of this, it may be more accurate to describe the control galaxies as centrally suppressed or quenched in comparison to the paired galaxies which feature flat profiles of star formation.
-The difference in the pair and control profiles seems to indicate that the mechanism for quenching in galaxies is the depletion of gases in their centers.
-The gas inflows from the merger events can then refuel the centers of these quenched galaxies and allow new star formation to occur.
-
-When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.35 $\pm$ 0.1 dex which then falls to zero around 1.2 R/\reff.
-In the outskirts of the pairs beyond 1.2 R/\reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex.
+When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.35 $\pm$ 0.1 dex which then falls to zero around 1.2 \reff.
+In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex.
 All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile.
-The most massive galaxies in the range, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 R/\reff\ is higher than the median profile at 0.5$-$0.6 dex.
-The sSFR enhancement in the sample seems to mass independent except for the most massive galaxies which feature higher levels of enhancement.
+For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is higher than the median profile at 0.5$-$0.6 dex.
+The sSFR enhancement in the sample seems to be mass independent except for the most massive galaxies which feature higher levels of sSFR enhancement.
 
 The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
-The fractional mass growth rate is simply the difference between the sSFR profiles of the paired and control galaxies (pairs - controls) multiplied by at timescale.
-We chose a timescale of 1 Gyr as an order of magnitude estimate of the interaction event \citep{Boylan-Kolchin:2008}, though the actual timescale of the merger induced starburst is likely somewhat shorter ($\sim$0.4 Gyr; \citet{Feng:2019}).
+The fractional mass growth rate is simply the difference between the sSFR profiles of the paired and control galaxies in linear space (pairs - controls) multiplied by a given timescale.
+We chose a timescale of 0.4 Gyr which is estimated to be the average timescale for the merger induced starburst \citep{Feng:2019}.
 
 Since the $\Delta$log(sSFR) is independent of galaxy mass, the fractional mass change will depend on the stellar mass of the paired galaxy.
-Low mass galaxies, \logm\ $=$ 9.0$-$9.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.06 (6\%) while massive galaxies, \logm\ $=$ 11.0$-$11.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.005 (0.5\%).
-This show that the merger induced mass growth is greatest in low mass galaxies.
+That is, since the amount of new stellar mass from merger induced interactions is roughly constant across galaxies of different stellar masses, lower mass galaxies will experience a greater change to their total stellar mass.
+Low mass galaxies, \logm\ $=$ 9.0$-$9.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.03 (3\%) while massive galaxies, \logm\ $=$ 11.0$-$11.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.001 (0.1\%).
+This shows that the merger induced mass growth is greatest in low mass galaxies.
 Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
 
-This method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls.
+This mass-binning method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls.
 On the other hand, this method only controls for a single galaxy parameter, stellar mass, though it is still relevant that the central enhancement of the sSFR in pairs is able to be observed.
-Further the profiles can only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.
+The profiles can also only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.
 
@@
 \subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
+\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. }
+\label{fig:ssfr_dm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}.
-We take the individual azimuthally averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin to produce the average profile of the control galaxies.
-
-% Is this necessary
-%The error of the profile is the standard error of the mean of the individual profiles.
-We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of the stacked profiles over 1000 iterations.
-We estimate that this random selection contributes an error of about 0.1 dex.
+We take the individual azimuthally averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin to produce the median profile of the control galaxies.
 
@@
 
-The difference profiles at this stage have now been controlled for stellar mass and redshift.
+The difference profiles at this stage have now been controlled for both stellar mass and redshift.
 We can freely stack these difference profiles to study their dependence on other parameter like the mass ratio and projected separation.
+
+First, we split the profiles by stellar mass to see how this method compares to the previous mass-binning method.
 We split the individual difference profiles into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5 and stack the difference profiles within each mass bin.
@@
 
-To understand why these high mass galaxies behave differently from the rest of the sample, we compare the distribution of the projected separation between the whole sample and the galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.
-The whole sample has a relatively flat separation distribution while 70\% of the highest mass galaxies in the sample are within 20 kpc.
-As we will show in Section \ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.
-
-The central enhancement to the sSFR falls to zero around 1.2 $R$/\reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex.
+The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex.
 The paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, feature enhanced sSFR in their disks of 0.1$-$0.2 dex.
 As we will show in the next section, Section \ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.
+
+To understand why these high mass galaxies behave differently from the rest of the sample, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.
+The whole sample has a v-shaped separation distribution.
+This is the result of the combination of the two different samples, the inside-IFU and outside-IFU samples.
+The outside-IFU sample should find more pairs at wide projected separations due to the larger volume to find companions in.
+The separation distribution of the inside-IFU sample is limited by MaNGA's IFU sizes and the sample's redshift distribution; the maximum possible projected separation for a MaNGA target with $z$ $=$ 0.15 and a 127 spaxel IFU is about 40 kpc.
+The highest mass galaxies in the sample are at closer projected separations in comparison to the rest of the sample with 70\% of the highest mass galaxies being within 20 kpc.
+As we will show in Section \ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.
 
@@
 \subsection{Dependency on Mass Ratio}\label{sec:dm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
-\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. }
-\label{fig:ssfr_dm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log(M)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log(M)$|$ $>$ 0.5.
-Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex.
-Secondary companions also feature slightly higher levels of enhancement than primary companions at the same mass ratios by $\sim$0.1 dex.
+Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex over minor mergers.
+Secondary companions also feature slightly higher levels of enhancement in their centers than primary companions at the same mass ratios by $\sim$0.1 dex.
 
 The sSFR offsets in the outskirts of the galaxy pairs show a dependence on the mass ratio.
-Primary companions show a zero to positive enhancement, 0.0$-$ 0.4 dex, to the sSFR in their outskirts.
+Primary companions show a zero to positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts.
 Secondary companions feature a suppression to the sSFR in their outskirts of about 0.1$-$0.4 dex.
@@
 First, we see that the central enhancement to the sSFR is strongest for pairs with 1:1 mass ratios.
-Second, we see that secondary companions show steeper enhancement profiles with higher levels of sSFR enhancement in their centers and stronger sSFR suppression in their disks with respect to primary companions.
+Second, we see that secondary companions show steeper enhancement profiles with higher levels of sSFR enhancement in their centers and stronger levels of sSFR suppression in their disks with respect to primary companions.
 It is interesting to note that the central enhancement to sSFR is dependent on both the mass ratio and the projected separation (which we will demonstrate in the next section) while the sSFR offsets in their outskirts primarily depends on whether the galaxy is the primary or secondary companion of the pair.
@@
 We look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in Figure \ref{fig:ssfr_sep}.
-The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations.
+The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations.
 The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.05$-$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.
 
-This effect can be seen most clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
+This effect can be seen more clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
 The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc.
 While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex.
-Within 15 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex.
+Within 20 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex.
 
@@
 The passage of the first pericenter is predicted to trigger a burst of star formation which falls as the two galaxies separate \citep{Scudder:2012}.
-The sSFR enhancement in our sample persists out to 50 kpc.
-\citet{Patton:2013} showed that the burst of star formation can persist out to 150 kpc.
+The sSFR enhancement in our sample persists out to 50 kpc and previous works have shown that the burst of star formation can persist out to 150 kpc \citep{Patton:2013}.
 
@@
 
-Among the three parameters, stellar mass, mass ratio, and projected separation, the projected separation has the strongest effect on the $\Delta$log(sSFR) enhancement, followed by the mass ratio.
+%Among the three parameters, stellar mass, mass ratio, and projected separation, the projected separation has the strongest effect on the $\Delta$log(sSFR) enhancement, followed by the mass ratio.
 From this we see that the paired galaxies with the strongest enhancements to the central sSFR are paired galaxies with 1:1 mass ratios and  which are within 10 kpc.
 
-Between the splitting the $\Delta$log(sSFR) profile by stellar mass, mass ratio, and projected separation, we see that the general shape of the profile within the inner 1.0 $R$/\reff\ is unchanged.
-The profile is peaked in the center of the paired galaxies and linearly (in log space) to zero around 1.0 $R$/\reff.
+%Between the splitting the $\Delta$log(sSFR) profile by stellar mass, mass ratio, and projected separation, we see that the general shape of the profile within the inner 1.0 \reff\ is unchanged.
+The profile is peaked in the center of the paired galaxies and linearly (in log space) to zero around 1.0 \reff.
 Different projected separations and mass ratios may elevate or suppress the level of the enhancement in the profile's center; however, the shape of the profile is largely unchanged.
@@
 \subsection{Comparison with Previous Works}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
-\label{fig:prof_comp}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\citet{Li:2008} studied the star formation enhancement over different stellar masses and saw that low mass galaxies experience greater levels of enhancement than high mass galaxies.
-Galaxies in the mass range \logm\ $=$ 9.72 were shown to experience an enhancement $\sim$0.4 dex higher than galaxies in the mass range \logm\ $=$ 10.6.
-In this work, we find that $\Delta$log(sSFR) has no dependence on the stellar mass of the galaxy.
-The galaxies with stellar masses above \logm\ $\ge$ 10.5 do show slightly lower levels of enhancement compared to the lower mass galaxies; however, the pairs still do not significantly deviate from the average $\Delta$log(sSFR) of the sample.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/prof_comp.pdf}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
+\label{fig:prof_comp}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}.
-We find that our central SFR enhancements are higher than many of the previous studies, the enhancements are $\sim$0.15 dex higher than \citet{Scudder:2012} and $\sim$0.25 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}.
-The central enhancement to sSFR is $\sim$0.1 dex higher in our pairs compared to \citet{Li:2008} past 35 kpc, but \citet{Li:2008} is $\sim$0.1 dex higher than our pairs at 20 kpc.
-Our $\Delta$log(SFR) as a function of projected separation is very consistent to what was found in \citet{Patton:2013}.
-
-Our sample only covers projected separations within 50 kpc, while previous surveys cover out to 100$-$200 kpc.
-While our sample covers a smaller separation range, the $\Delta$log(SFR) of our sample at 50 kpc is roughly the same level as \citet{Scudder:2012} and \citet{Patton:2013} at the same projected separation.
-This shows that the central SFR enhancement of our sample is consistent with with what has been found in previous works.
-
-In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
-\citet{Pan:2019} examines a set of paired galaxies in the MaNGA survey while \citet{Thorp:2019} examines a set of post-merger galaxies in the MaNGA survey.
-The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughly $\sim$0.1$-$0.2 dex higher than our sample.
-Our paired galaxies show a slight sSFR suppression in their disks past 1.0 R/\reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
-The reason for the discrepancies between our samples is that \citet{Pan:2019} includes a set of post-merger galaxies while our sample has no post-merger galaxies.
-These post-merger galaxies are predicted to have higher levels of star formation over other paired galaxies due to a second larger burst of star formation which is triggered as the merging galaxies coalesce.
-
-The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 dex higher than our sample of paired galaxies.
-The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
-The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 $R$/\reff\ of $\sim$0.1$-$0.15 dex.
-The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
-
-\citet{Barrera-Ballesteros:2015} studied the sSFR in paired galaxies in the CALIFA IFS survey using the H$\alpha$ equivalent width (\ewha) as a proxy for the sSFR.
-They compared the sSFR in the centers of paired galaxies to their disks by varying the aperture diameters from which they extract the \ewha.
-They found that the sSFR is enhanced in the centers of the paired galaxies but suppressed in their disks, which is similar to what we find.
-
-\citet{Moreno:2015} used {\sc Gadget}-3, a smoothed particle hydrodynamics code, to study the spatial extend of the star formation enhancement.
-The merger simulations showed that the star formation enhancement was largely concentrated in the centers (R $<$ 1 kpc) of the paired galaxies and that the off-nuclear regions (1 $<$ R $<$ 10 kpc) showed a suppression to the star formation.
-\citet{Moreno:2015} also found that star formation offsets in lower mass secondary galaxies (in mergers with stellar mass ratios of 2.5:1) have a stronger radial dependence with respect to the more massive primary companion.
-This is in good agreement with our work, we found that secondary companions show moderately higher levels of sSFR enhancement in their centers in comparison to primary companions at the same mass ratio.
-Further, the outskirts of the primary companions feature no enhancement or suppression to their sSFR while the secondary companions show a strong suppression to the sSFR at large radii.
+We find that our central SFR enhancements for closely separated pairs are higher than many of the previous studies, our sSFR enhancement is $\sim$0.2 dex higher than \citet{Scudder:2012} and $\sim$0.3 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}.
+The central enhancement to the sSFR for closely separated pairs in our sample is $\sim$0.1 dex higher than \citet{Patton:2013}.
+The sSFR enhancement function from \citet{Li:2008} follows closely to our own and remains $\sim$0.05 dex above our sample out to 40 kpc.
 
@@
 
+Our sample only covers projected separations within 50 kpc, while previous surveys cover out to 100$-$200 kpc.
+While our sample covers a smaller separation range, the $\Delta$log(SFR) of our sample at 50 kpc is roughly the same level as \citet{Scudder:2012} and \citet{Patton:2013} at the same projected separation.
+From this we see that our sSFR enhancement as a function of projected separation is consistent with with what has been found in previous works.
+
+\citet{Li:2008} studied the star formation enhancement over different stellar masses and saw that low mass galaxies experience greater levels of enhancement than high mass galaxies.
+Galaxies in the mass range \logm\ $=$ 9.72 were shown to experience an enhancement $\sim$0.4 dex higher than galaxies in the mass range \logm\ $=$ 10.6.
+In this work, we find that $\Delta$log(sSFR) has no dependence on the stellar mass of the galaxy.
+The source of the difference is unclear; between our works we utilize different methods for determining the sSFR enhancement in galaxy pairs.
+\citet{Li:2008} defines their enhancement function as the average sSFR of the paired galaxies at a given separation, weighted by the number of companions, subtracted by the average sSFR of the whole sample.
+While we don't find the same dependency between the sSFR enhancement and stellar mass, the sSFR enhancement as a function of projected separation between our studies is in good agreement.
+
+The dependency of the SFR enhancement on the mass ratio was studied in \citet{Ellison:2008}.
+They found that pairs with mass ratios of 2:1 have higher SFR enhancements of $\sim$0.1 dex over pairs with wider 10:1 mass ratios.
+We find that pairs with mass ratios of $\Delta$log(M) $=$ 0.25 (1.8:1) are 0.2 dex over pairs with mass ratios of $\Delta$log(M) $=$ 1.0 (10:1).
+\citet{Ellison:2008} also saw tentative evidence for SFR enhancement in the secondary companions of minor pairs.
+We not only confirm that secondary companions of minor pairs feature SFR enhancement, but also that the enhancement is higher than the primary component of pairs at the same mass ratios.
+
+In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
+The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 dex higher than our sample of paired galaxies.
+The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
+The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 \reff\ of $\sim$0.1$-$0.15 dex.
+The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
+
+The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughly $\sim$0.1$-$0.2 dex higher than our sample.
+Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of post-merger galaxies while our sample has no post-merger galaxies.
+These post-merger galaxies are predicted to have higher levels of star formation over other paired galaxies due to a second larger burst of star formation which is triggered as the merging galaxies coalesce and may be able to increase the sample's average sSFR enhancement .
+
+\citet{Barrera-Ballesteros:2015} studied the sSFR in paired galaxies in the CALIFA IFS survey using the H$\alpha$ equivalent width (\ewha) as a proxy for the sSFR.
+They compared the sSFR in the centers of paired galaxies to their disks by varying the aperture diameters from which they extract the \ewha.
+They found that the sSFR is enhanced in the centers of the paired galaxies but suppressed in their disks, which is similar to what we find.
+
+\citet{Moreno:2015} used {\sc Gadget}-3, a smoothed particle hydrodynamics code, to study the spatial extent of the star formation enhancement.
+The merger simulations showed that the star formation enhancement was largely concentrated in the centers (R $<$ 1 kpc) of the paired galaxies and that the off-nuclear regions (1 $<$ R $<$ 10 kpc) showed a suppression to the star formation.
+\citet{Moreno:2015} also found that lower mass secondary galaxies (in mergers with stellar mass ratios of 2.5:1) have higher levels of sSFR enhancement in their centers and have stronger levels of sSFR suppression in their disks.
+This is in good agreement with our work, we found that secondary companions show moderately higher levels of sSFR enhancement in their centers in comparison to primary companions at the same mass ratio.
+Further, the outskirts of the primary companions feature positive to zero enhancement to their sSFR while the secondary companions show a strong suppression to the sSFR in their outskirts.
+
+\subsection{Enhanced Pairs or Quenched Controls}
+
+In Figure \ref{fig:ssfr_prof}, we showed the stacked sSFR profiles of control galaxies and paired galaxies.
+The control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with higher stellar masses (which was previously seen in the MaNGA survey in \citet{Belfiore:2018}).
+The paired galaxies show flattened star formation profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5 which still show some central quenching.
+This indicates that the central offsets viewed in the difference profiles is largely driven by the centrally quenched controls.
+Because of this it may be more proper to describe isolated galaxies as being centrally quenched or that the profiles of paired galaxies are flattened in their centers with respect to their controls.
+
+The flattening of the paired galaxies' profiles seems to indicate that the merger event can ``un-quench" the centers of the galaxies.
+The mode of inside-out quenching that seems most consistent with our results is the gas depletion model where the galaxy runs out of cold gas in their centers.
+In the merger event, new gases are brought into the centers of the galaxies by the merger induced gas inflows which are then able to facilitate new star formation.
+
+After the merger induced starburst, it is unclear whether the galaxy will return to the same level of central quenching or if the resulting galaxy is more quenched.
+From Figure \ref{fig:ssfr_prof}, we see that more massive galaxies are more quenched than less massive galaxies.
+Since the resulting galaxy after the merger process will be more massive than it was before and since the most massive galaxies have likely gone through multiple past merging events \citep{Rodriguez-Gomez:2016, Pillepich:2018}, it is reasonable to believe that the long term result of the merger event is a more quenched galaxy.
+In this situation, the merger event temporarily alleviates the galaxy from its quenched state; however, when starburst ends the galaxy is more quenched than it was before.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this work, we studied a sample of paired, star forming galaxies using the MaNGA IFS survey.
-We have made a sample of 175 star forming galaxy pairs along with a set of 1888 star forming control galaxies.
-We compared the radial profiles of the paired galaxies with those of the controls galaxies and found the following;
+In this work.
+we have made a sample of 175 star forming galaxy pairs along with a set of 1888 star forming control galaxies in the MaNGA IFS survey.
+We compared the radial profiles of sSFR between the paired galaxies and controls galaxies and found the following;
 
 \begin{enumerate}
-\item The sSFR is centrally enhanced within the inner 1.0 R/\reff\ by 0.25 $\pm$ 0.1 dex. 
-\item The outskirts of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show limited suppression in their disks of $\sim$0.1 dex.
-\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies, Massive galaxies experience the same level of sSFR enhancement as low mass galaxies.
+\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.25 $\pm$ 0.1 dex. 
+\item The outskirts of the paired galaxies, \reff\ $=$ 1.0$-$2.5, show limited suppression in their disks of $\sim$0.1 dex.
+\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies.
 \item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies.
-Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.3 $\pm$ 0.1 dex, which is 0.1 dex higher than the average paired galaxies in the survey.
-We have also showed that paired galaxies with large mass ratios, $|\Delta$log(M)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.15$-$0.2 dex.
-\item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair by $\sim$0.1 dex.
-\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4 which is consistent with previous single fiber studies. 
-\item When splitting the sSFR enhancement profiles by stellar mass, mass ratio, or projected separation, the general shape of the enhancement profile is unchanged.
-While lower projected separations or mass ratios closer to 1:1 may raise the level of the central enhancement, the profiles still linearly fall to zero enhancement around 1.0 R/\reff.
-\item The paired galaxies will experience a fractional mass growth rate of 1$-$6\%, where the growth in mass is largest in low mass galaxies.
+Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.35 dex, which is 0.1 dex higher than the average paired galaxies in the survey.
+Paired galaxies with large mass ratios, $|\Delta$log(M)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex.
+\item The secondary companions of a galaxy pair, the less massive galaxy, show higher sSFR enhancements, by $\sim$0.1 dex in comparison to primary companions at the same mass ratio.
+Further, primary companions have zero to positive sSFR offsets in their ouskirts, $\Delta$log(sSFR) $=$ 0.0$-$0.3 dex.
+Secondary companions feature a sSFR suppression in their outskirts of 0.0$-$0.3 dex.
+\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4.
 
@@
 
-%%%%%%%%%%%%
-% Appendix
-%%%%%%%%%%%%
-
-%\hbox{}\clearpage
-
-%\appendix
-
-%\section{Figures}
-
 \end{document}

### 2020-10-19 maintex.tex
Fixed typos/Revised Future work

@@
 \newcommand{\ewha}{EW(H$\alpha$)}
-\newcommand{\logm}{log({\it M}/M$_{\odot}$)}
+\newcommand{\logm}{log($M/M_{\odot}$)}
 %\newcommand{\arcsec}{\prime\prime}
@@
 \author{
-Joshua L. Steffen\altaffilmark{1}, 
-Hai Fu\altaffilmark{1}, and 
-MaNGA Team 
+Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1}, J.~M.~Comerford\altaffilmark{2}, Shuai~Feng\altaffilmark{3}, Cheng~Li\altaffilmark{4}, Y.~Sophia~Dai\altaffilmark{5}, and Rui~Xue\altaffilmark{1}
 }
-\altaffiltext{1}{Department of Physics \& Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
+\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
+\altaffiltext{2}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
+\altaffiltext{3}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical University, Chinese Academy of Sciences}
+\altaffiltext{4}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}
+\altaffiltext{5}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
 
@@
 We also find that the sSFR offsets in the outskirts of the paired galaxies is dependent on whether the galaxy is the more massive or less massive companion in the pair.
-The more massive companion experiences no to a positive sSFR enhancement while the less massive companion experiences a sSFR suppression in their outskirts.
+The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.
 \end{abstract}
@@
 \begin{equation}\label{eq:blue}
-NUV-r = 3.1682 - 0.16 (\mathcal{M}_i+18)
+NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
 \end{equation}
 \begin{equation}\label{eq:red}
-NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18)
+NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18)
 \end{equation}
@@
 We select these outside-IFU pairs from the NSA catalog.
-We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of $r_p$ $<$ 50 kpc using the MaNGA target's redshift.
+We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of $r_{\rm p}$ $<$ 50 kpc using the MaNGA target's redshift.
 We further use a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.
@@
 To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of isolated galaxies in the MaNGA survey.
-We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_p$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
+We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_{\rm p}$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
 This gives us a control sample of 1888 star forming control galaxies.
@@
 We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
-The extinction is parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
+The extinction is parameterized as $R_{\rm V}$ $\equiv$ $A_{\rm V}/E(B-V)$ $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
 
-We measure the SFR from the extinction corrected H$\alpha$ luminosity, L$_{{\rm H}\alpha}$.
+We measure the SFR from the extinction corrected H$\alpha$ luminosity, $L_{{\rm H}\alpha}$.
 We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.
@@
 \begin{equation}\label{eq:sfr}
-\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{{\rm L}_{H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
+\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
 \end{equation}
@@
 \begin{equation}
-{\rm sSFR} = \frac{\rm SFR}{M^*}
+{\rm sSFR} = \frac{\rm SFR}{M_*}
 \end{equation}
@@
 
+The control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with higher stellar masses (which was previously seen in the MaNGA survey in \citet{Belfiore:2018}).
+The paired galaxies show flattened star formation profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5 which still show some central quenching.
+
 When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.35 $\pm$ 0.1 dex which then falls to zero around 1.2 \reff.
@@
 The sSFR enhancement in the sample seems to be mass independent except for the most massive galaxies which feature higher levels of sSFR enhancement.
+
+It is also relevant to note that the driving factor behind the central enhancement to the sSFR in the difference profiles is really the quenching in the centers of the controls.
+While the mechanism for the quenching in galaxies is in dispute, the merger process seems to be capable of rejuvenating star formation in the centers of these galaxies resulting in the flatter sSFR profiles seen in the paired galaxies.
+Further, since the sSFR enhancement in the difference profiles is largely driven by the quenched controls, it may be more appropriate to describe isolated galaxies as being centrally quenched in comparison to paired galaxies or that the profiles of paired galaxies are flattened in their centers with respect to their controls.
 
@@
 \caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
-The profiles are split into four different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile.
+The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile.
 The black dashed line represents the mean profile between the four difference mass ranges.
@@
 \includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
-\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. }
+\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. The inside-IFU sample is left out of this analysis as their mass ratios are unreliable.}
 \label{fig:ssfr_dm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}
-%\centering
-%\includegraphics[width=\linewidth]{fig/ssfr_massdm.pdf}
-%\caption[]{Same as the left hand panel of Figure \ref{fig:ssfr_mass} except primary companions are shown on the \textbf{Left} and secondary companions are shown on the \textbf{Right}.
-The \logm\ $=$ 11.0$-$11.5 mass bin is left out of left hand panel since it only contains two galaxies.
-}
-%\label{fig:ssfr_massdm}
-%\end{figure*}
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
+\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by projected separation. }
+\label{fig:ssfr_sep}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
-We will define the more massive galaxies of a pair, $\Delta$log(M) $>$ 0.0, the primary companion and the less massive galaxy of a pair, $\Delta$log(M) $<$ 0.0, the secondary companion.
+We will define the more massive galaxies of a pair, $\Delta$log($M$) $>$ 0.0, the primary companion and the less massive galaxy of a pair, $\Delta$log($M$) $<$ 0.0, the secondary companion.
 
@@
 
-In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log(M)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log(M)$|$ $>$ 0.5.
+In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log($M$)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log($M$)$|$ $>$ 0.5.
 Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex over minor mergers.
@@
 In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0.
-These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
+These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
 This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0.
@@
 \subsection{Dependency on Projected Separation}\label{sec:sep}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
-\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by projected separation. }
-\label{fig:ssfr_sep}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
-\label{fig:prof_comp}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Li:2008, Patton:2013, Scudder:2012, Bustamante:2020}.
@@
 They found that pairs with mass ratios of 2:1 have higher SFR enhancements of $\sim$0.1 dex over pairs with wider 10:1 mass ratios.
-We find that pairs with mass ratios of $\Delta$log(M) $=$ 0.25 (1.8:1) are 0.2 dex over pairs with mass ratios of $\Delta$log(M) $=$ 1.0 (10:1).
+We find that pairs with mass ratios of $\Delta$log($M$) $=$ 0.25 (1.8:1) are 0.2 dex over pairs with mass ratios of $\Delta$log($M$) $=$ 1.0 (10:1).
 \citet{Ellison:2008} also saw tentative evidence for SFR enhancement in the secondary companions of minor pairs.
@@
 
-\subsection{Enhanced Pairs or Quenched Controls}
-
-In Figure \ref{fig:ssfr_prof}, we showed the stacked sSFR profiles of control galaxies and paired galaxies.
-The control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with higher stellar masses (which was previously seen in the MaNGA survey in \citet{Belfiore:2018}).
-The paired galaxies show flattened star formation profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5 which still show some central quenching.
-This indicates that the central offsets viewed in the difference profiles is largely driven by the centrally quenched controls.
-Because of this it may be more proper to describe isolated galaxies as being centrally quenched or that the profiles of paired galaxies are flattened in their centers with respect to their controls.
-
-The flattening of the paired galaxies' profiles seems to indicate that the merger event can ``un-quench" the centers of the galaxies.
-The mode of inside-out quenching that seems most consistent with our results is the gas depletion model where the galaxy runs out of cold gas in their centers.
-In the merger event, new gases are brought into the centers of the galaxies by the merger induced gas inflows which are then able to facilitate new star formation.
-
-After the merger induced starburst, it is unclear whether the galaxy will return to the same level of central quenching or if the resulting galaxy is more quenched.
-From Figure \ref{fig:ssfr_prof}, we see that more massive galaxies are more quenched than less massive galaxies.
-Since the resulting galaxy after the merger process will be more massive than it was before and since the most massive galaxies have likely gone through multiple past merging events \citep{Rodriguez-Gomez:2016, Pillepich:2018}, it is reasonable to believe that the long term result of the merger event is a more quenched galaxy.
-In this situation, the merger event temporarily alleviates the galaxy from its quenched state; however, when starburst ends the galaxy is more quenched than it was before.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary and Conclusion}\label{sec:sum}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/prof_comp.pdf}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
+\label{fig:prof_comp}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \item The outskirts of the paired galaxies, \reff\ $=$ 1.0$-$2.5, show limited suppression in their disks of $\sim$0.1 dex.
-\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies.
+\item The sSFR enhancement in paired galaxies is independent of their total stellar mass.
 \item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies.
-Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.35 dex, which is 0.1 dex higher than the average paired galaxies in the survey.
-Paired galaxies with large mass ratios, $|\Delta$log(M)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex.
+Galaxies with small mass ratios, $|\Delta$log($M$)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.35 dex, which is 0.1 dex higher than the average paired galaxies in the survey.
+Paired galaxies with large mass ratios, $|\Delta$log($M$)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex.
 \item The secondary companions of a galaxy pair, the less massive galaxy, show higher sSFR enhancements, by $\sim$0.1 dex in comparison to primary companions at the same mass ratio.
-Further, primary companions have zero to positive sSFR offsets in their ouskirts, $\Delta$log(sSFR) $=$ 0.0$-$0.3 dex.
-Secondary companions feature a sSFR suppression in their outskirts of 0.0$-$0.3 dex.
-\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4.
+Further, primary companions have zero to positive sSFR offsets in their ouskirts, $\Delta$log(sSFR) $=$ 0.0$-$0.4 dex.
+Secondary companions feature a sSFR suppression in their outskirts of 0.1$-$0.4 dex.
+\item The sSFR enhancement increases with closer projected separations where galaxies within 20 kpc have their sSFR enhanced by 0.3$-$0.4. 
+\end{enumerate}
 
-\end{enumerate}
+There is still much to be understood about these galaxy pairs.
+We see that there is a great diversity in the difference profiles of individual galaxies.
+In particular there are galaxy pairs which feature a strong suppression to the sSFR in their centers while others feature a central enhancement to the sSFR which is much greater than the median enhancement.
+The depth of our analysis here would benefit by studying other merger parameters like the interaction stage or the gas fraction.
+
+As of August 24, 2020, MaNGA has finished observing its goal of 10,000 galaxies.
+The completion of the final sample will mean that we will have access to a larger sample of paired and control galaxies.
+We also plan to fit the light profiles of the inside-IFU companion galaxies which will allow us to roughly double the size of the inside-IFU sample.
+With this and the completion of MaNGA's observations, we may be able to expand our pair sample to include nearly 500 galaxy pairs.
+
+With the larger sample size we will be better able to separate how the stellar mass, mass ratio, and projected separation effect the enhancement profile along with new parameters like the merger stage and gas fraction.
+Also, by constructing enhancement profiles for the inside-IFU companions to the MaNGA targets, we can better study how primary companions behave in comparison to their secondary companions.
 

### 2020-10-20 authors.tex
updated authors list

\author{
Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5}, Cheng~Li\altaffilmark{6}, and Rui~Xue\altaffilmark{1}
}
\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
\altaffiltext{2}{Insititute for Astronomy, University of Hawaii, Honolulu, HI 96822}
\altaffiltext{3}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
\altaffiltext{4}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
\altaffiltext{5}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical University, Chinese Academy of Sciences}
\altaffiltext{6}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}

### 2020-10-20 maintex.tex
updated authors list

@@
 
-\author{
-Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1}, J.~M.~Comerford\altaffilmark{2}, Shuai~Feng\altaffilmark{3}, Cheng~Li\altaffilmark{4}, Y.~Sophia~Dai\altaffilmark{5}, and Rui~Xue\altaffilmark{1}
-}
-\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
-\altaffiltext{2}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
-\altaffiltext{3}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical University, Chinese Academy of Sciences}
-\altaffiltext{4}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}
-\altaffiltext{5}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
+\include{authors}
 

### 2020-10-21 authors.tex
updated authorlist

@@
 \author{
-Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5}, Cheng~Li\altaffilmark{6}, and Rui~Xue\altaffilmark{1}
+Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Cheng~Li\altaffilmark{8}, and Rui~Xue\altaffilmark{1}
 }
@@
 \altaffiltext{4}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
-\altaffiltext{5}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical University, Chinese Academy of Sciences}
-\altaffiltext{6}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}
+\altaffiltext{5}{Department of Physics, Hebei Normal University, 20 South Erhuan Road, Shijiazhuang, 050024, China}
+\altaffiltext{6}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical Observatory, Chinese Academy of Sciences, 80 Nandan Road, Shanghai 200030, China}
+\altaffiltext{7}{University of the Chinese Academy of Sciences, No.19A Yuquan Road, Beijing 100049, China}
+\altaffiltext{8}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}

### 2020-10-21 authors.tex
moved Cheng Li to acknowledgements

@@
 \author{
-Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Cheng~Li\altaffilmark{8}, and Rui~Xue\altaffilmark{1}
+Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, and Rui~Xue\altaffilmark{1}
 }
@@
 \altaffiltext{7}{University of the Chinese Academy of Sciences, No.19A Yuquan Road, Beijing 100049, China}
-\altaffiltext{8}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}

### 2020-10-21 maintex.tex
moved Cheng Li to acknowledgements
minor edits up to Sec 2

@@
 These gas inflows will also bring metal-poor gases from the disk into the center of the galaxy which can dilute the central metallicity \citep{Rupke:2010, Perez:2011, Scudder:2012}.
-The gas-inflows may also be able to make it into very center of the galaxy and trigger supermassive black hole (SMBH) accretion \citep{Capelo:2017}.
+The gas-inflows may also be able to reach the very center of the galaxy and trigger supermassive black hole (SMBH) accretion \citep{Capelo:2017}.
 
@@
 Indeed, \citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted from.
-In the study, \citet{Barrera-Ballesteros:2015} found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.
+In this study, they found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.
 %
-\citet{Pan:2019} used the MaNGA survey to study radial profiles of a sample of 205 paired galaxies.
+\citet{Pan:2019} used the SDSS-IV MaNGA survey to study radial profiles of a sample of 205 paired galaxies.
 The enhancement to the sSFR was shown to be the strongest in the centers of the paired galaxies.
@@
 With the MaNGA survey, we will be able to expand upon these previous studies in greater spatial detail.
-We will be able to see how these three parameters affect the both the level of the sSFR offsets in the centers of the paired galaxies and the offsets in the outskirts of the galaxies.
+We will be able to see how these three parameters affect both the level of the sSFR offsets in the centers of the paired galaxies and the offsets in the outskirts of the galaxies.
 We will also be able to study if any of three parameters influence the gradient of the sSFR enhancement profiles or if the gradient is preserved between different configurations.
 
-In our previous work, we built a sample of paired galaxies in the MaNGA survey where both components of the pair were contained within field of view of a single integral field unit \citep[][hereafter \citetalias{Fu:2018}]{Fu:2018}.
+In our previous work using the MaNGA data included in the 14th Public Data Release \citep[DR14;][]{Abolfathi:2018}, we built a sample of close galaxy pairs where both components of the pair were contained within the field of view of a single integral field unit \citep[][hereafter \citetalias{Fu:2018}]{Fu:2018}.
 We found that approximately 5.7\% of the MaNGA galaxies have a companion galaxy contained within the field-of-view of a single IFU.
-In this work, we will use a version of this sample updated for the recent MaNGA Data Release 16 (DR16) \citep{Ahumada:2020} and we will further supplement this with a sample of companion galaxies identified outside the field-of-view of the MaNGA IFUs.
+In this work, we update this sample and supplement it with a sample of companion galaxies identified outside the field-of-view of the MaNGA IFUs.
 
@@
 
-The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures.
+The MaNGA survey targets galaxies from a subset of 41,154 galaxies in the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_i}$ $<$ -24.0, where $\mathcal{M_i}$ is the rest frame $i$-band magnitude within the survey's elliptical Petrosian apertures.
 MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
@@
 \begin{equation}\label{eq:blue}
-NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
+NUV-r = 3.1682 - 0.16 (\mathcal{M}_i+18)
 \end{equation}
 \begin{equation}\label{eq:red}
-NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18)
+NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18)
 \end{equation}
 
-Where $NUV-r$ is the color from SDSS's k-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the i-band magnitude from the NSA catalog.
-We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0 \reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
-We further use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with an AGN in their centers from our sample.
-We use the emission line ratios, log([O\textsc{III}]/H$\beta$) and log([N\textsc{II}]/H$\alpha$), extracted from a 1.3 kpc aperture along with the maximum starburst line from \citet{Kewley:2001} as the demarcation between star forming branch and the AGN branch.
+Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_i$ is the $i$-band magnitude from the NSA catalog.
+We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
+Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers.
+Specifically, we use the emission line ratios, log([O~\sc{iii}]/H$\beta$) and log([N~\sc{ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.
 
@@
 We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
-The extinction is parameterized as $R_{\rm V}$ $\equiv$ $A_{\rm V}/E(B-V)$ $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
+The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
 
@@
 
-For the outside-IFU sample we use the stellar masses calculated from the r-band elliptical Petrosian apertures from the NSA catalog.
+For the outside-IFU sample we use the stellar masses calculated from the $r$-band elliptical Petrosian apertures from the NSA catalog.
 Most of the companion galaxies in the inside-IFU sample are not covered by either the NSA catalog or \citet{Simard:2011}.
@@
 % funding
+We thank Cheng Li for our useful discussion on how the sSFR enhancement in galaxy pairs relates to their stellar mass and mass ratio.
 J.S.

### 2020-10-21 maintex.tex
M_* -> M for consistency

@@
 
-Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, $M_*$, giving us the specific star formation rate (sSFR).
+Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, $M$, giving us the specific star formation rate (sSFR).
 The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each MaNGA spaxel (spatial pixel).
@@
 \begin{equation}
-{\rm sSFR} = \frac{\rm SFR}{M_*}
+{\rm sSFR} = \frac{\rm SFR}{M}
 \end{equation}

### 2020-10-21 maintex.tex
corrected {\sc } error, use \citealias for paper I

@@
 Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers.
-Specifically, we use the emission line ratios, log([O~\sc{iii}]/H$\beta$) and log([N~\sc{ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.
+Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.
 
@@
 
-In our previous work, \citet{Fu:2018}, using the 2168 unique galaxies from DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
+In our previous work, \citetalias{Fu:2018}, using the 2168 unique galaxies from DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
 In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
@@
 We use our own {\sc idl} based spectral fitting code, {\sc spfit}, to model the spectra from the MaNGA datacubes.
-{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}.
+{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}.
 Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).

### 2020-10-21 maintex.tex
defined MPL-8, removed redundant paragraph in S2.1

@@
 MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
-In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.
+In this work we use the data from the 8th MaNGA Product Launch (MPL-8), which covers 6142 unique galaxies observed by July 3, 2018.
 
@@
 \subsection{Inside-IFU Sample}\label{sec:inside}
-
-In our previous work, \citetalias{Fu:2018}, using the 2168 unique galaxies from DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU.
-In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.
 

### 2020-10-21 maintex.tex
further edits up to page 5

@@
 
-We identify potential paired galaxies by overlaying SDSS photometric objects over the MaNGA fields of view.
-We manually inspect each MaNGA field, removing photometric objects which are over-deblended galaxy fragments and adding any objects missed by the SDSS photometric catalog.
-At this stage the object catalog includes any foreground stars and foreground/background galaxies along with the potential paired galaxies.
+To identify potential paired galaxies covered by individual IFUs, we start by overlaying SDSS photometric objects over each MaNGA fields of view.
+We manually inspect each MaNGA field, removing photometric objects which are over-deblended galaxy fragments and, very rarely, adding any objects missed in the SDSS photometric catalog.
+At this stage the object catalog includes foreground stars and foreground/background galaxies along with the potential paired galaxies.
 
@@
 
-From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple galaxy objects within the IFU.
+Among 6142 MaNGA IFUs considered here, 404 have multiple galaxy objects within the IFU.
 We further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected companions.
@@
 We also require that the galaxies are classified as star forming as described in Section \ref{sec:data}.
-These requirements reduce our sample down to 87 star forming galaxies (SFGs).
+These requirements reduce our sample down to 87 star forming pairs.
 
@@
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-This give use a total of 175 MaNGA targets in our pair sample.
+This give us a total of 175 close pairs.
 
@@
 
-It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep{Noeske:2007}.
+It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep[e.g.,][]{Noeske:2007}.
 We will compare our interacting galaxies with isolated galaxies of a similar stellar mass and redshift, to account for these other dependencies.
@@
 The pairs are then compared to their respective controls within each stellar mass bins.
-While the redshift in not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
+While the redshift is not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
 
@@
 To do this we select a subsample of 20 control galaxies for each paired galaxy.
-We first select all of the control galaxies which are within a 0.1 dex stellar mass limit and within the same MaNGA subsample (e.g.
+We first select all of the control galaxies which are within a 0.1~dex stellar mass limit and within the same MaNGA subsample (e.g.
 Primary or Secondary) as the paired galaxy.
-Since the MaNGA sample has a tight distribution in stellar mass and redshift, the stellar mass and MaNGA subsample restriction effectively sets a $z$ $\lesssim$ $\sim$0.025 redshift cut.
+Since the MaNGA sample has a tight distribution in stellar mass and redshift, the stellar mass and MaNGA subsample restriction effectively sets a $\Delta z$ $\lesssim$ $\sim$0.025 redshift tolerance.
 
 Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies.
-Since we want each paired galaxy to be treated in a similar manner, we will down-select the total number of acquired control galaxies down to 20 controls randomly.
+Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20.
 A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Radial Profiles of Star Formation}\label{sec:analysis}
+\section{Analysis Methods}\label{sec:analysis}
 
@@
 %%% SPFIT
-We use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
+For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
 
@@
 We measure the SFR from the extinction corrected H$\alpha$ luminosity, $L_{{\rm H}\alpha}$.
-We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.
-
+We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination:
 \begin{equation}\label{eq:sfr}
-\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
+\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}.
 \end{equation}
 
-Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, $M$, giving us the specific star formation rate (sSFR).
-The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each MaNGA spaxel (spatial pixel).
-
+Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the stellar mass in the same spaxel, giving us the specific star formation rate (sSFR):
 \begin{equation}
@@
 \end{equation}
-
-This will allow us to compare regions of high mass surface density to regions of low mass surface density.
+The local stellar masses used here is derived from {\sc SPFIT}'s best-fit stellar continuum.
+Utilizing sSFR, instead of SFR, allows us to compare regions of high mass surface density to regions of low mass surface density.
 
@@
 When making the comparison with the second method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
-Further, when defining the a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
+Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
+Note that although we carefully treat the two catalogs separately whenever possible, we find excellent agreement in the geometry parameters of isolated galaxies in both catalogs.
 
@@
 
-Once the geometry of the galaxies are set, we can build the radial profiles.
+Once the geometry of the galaxies are set, we can build azimuthally averaged radial profiles.
 The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
@@
 The profiles' errors are the standard error of the mean of the data within each radius bin.
-We create one of these individual averaged radial profiles for every MaNGA galaxy.
+We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.
 
@@
 In the first method, paired and control galaxies are grouped into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5.
-Within each stellar mass bin, we create a median profile of log(sSFR) as a function of galactocentric radius for both paired and control galaxies.
+Within each stellar mass bin, we create a median profile of log(sSFR) as a function of \reff-scaled galactocentric distance for both paired and control galaxies.
 The control profiles are constructed using all available control galaxies within each mass bin.
-The error associated with the profile is the standard error of mean of the data at each radius bin.
-We show these ``stacked" profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}.
+The error associated with the ``stacked'' profile is the standard error of mean of the data at each radius bin.
+We show these stacked profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}.
+{\bf QUESTION: for the inside-IFU pairs, did you use only the primaries to build these stacked profiles?
+If so, this needs to made clear in the text.} Star formation in the control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with stellar mass, consistent with previously published results using the MaNGA survey \citep{Belfiore:2018}.
+In contrast, the paired galaxies show flatter sSFR profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5, which still show some central quenching.
 
-The radial extent of our profiles go out to 2.6 \reff; however,  67\% of the MaNGA sample is designed to cover only 1.5 \reff\ of the galaxy.
+{\bf COMMENT: I am not sure the trimmed regions could be so limited.
+If this is indeed correct, then we don't need to spend a paragraph on something so negligible and not to highlight the trimed regions in the plots.}
+The radial extent of our profiles reaches 2.6 \reff; however, 67\% of the MaNGA sample (i.e., the Primary subsample) is designed to cover only 1.5 \reff\ of the galaxy.
 Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall outside of the innermost radii bin.
@@
 
-Once the stacked profiles are made, we take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space).
+We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space).
 This gives us difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
-
-The control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with higher stellar masses (which was previously seen in the MaNGA survey in \citet{Belfiore:2018}).
-The paired galaxies show flattened star formation profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5 which still show some central quenching.
-
-When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.35 $\pm$ 0.1 dex which then falls to zero around 1.2 \reff.
+Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.35$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff.
 In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex.
@@
 
-It is also relevant to note that the driving factor behind the central enhancement to the sSFR in the difference profiles is really the quenching in the centers of the controls.
-While the mechanism for the quenching in galaxies is in dispute, the merger process seems to be capable of rejuvenating star formation in the centers of these galaxies resulting in the flatter sSFR profiles seen in the paired galaxies.
-Further, since the sSFR enhancement in the difference profiles is largely driven by the quenched controls, it may be more appropriate to describe isolated galaxies as being centrally quenched in comparison to paired galaxies or that the profiles of paired galaxies are flattened in their centers with respect to their controls.
+Alternatively, the central enhancement of the sSFR in the paired galaxies can be interpreted as the quenching of star formation in the centers of isolated galaxies.
+While the mechanism for quenching in galaxies remains under debate, the merger process seems to be capable of rejuvenating star formation in the centers of these galaxies, resulting in the flatter sSFR profiles.
+%Further, since the sSFR enhancement in the difference profiles is largely driven by the quenched controls, it may be more appropriate to describe isolated galaxies as being centrally quenched in comparison to paired galaxies or that the profiles of paired galaxies are flattened in their centers with respect to their controls.
 

### 2020-10-22 maintex.tex
fixed typos

--- 2020-10-21 maintex.tex
@@
 In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy.
-We also find that the sSFR offsets in the outskirts of the paired galaxies is dependent on whether the galaxy is the more massive or less massive companion in the pair.
+We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair.
 The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.
@@
 
-On top of the star formation cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}, and that the stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.
+On top of the star formation cuts, we require that all galaxies are in either the Primary or Secondary MaNGA subsamples \citep{Wake:2017}, and that the stellar mass range of the galaxy sample is between \logm\ $=$ 9.0$-$11.5.
 We use masses calculated from the elliptical Petrosian apertures in the NSA catalog for our total stellar masses.
@@
 From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
-In cases where a MaNGA target has multiple viable companions galaxies, we chose the closest companion when measuring the mass ratio and projected separation.
+In cases where a MaNGA target has multiple viable companions galaxies, we chose the closest companion when measuring the pair's mass ratio and projected separation.
 
@@
 From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets.
-After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU.
+After restricting the sample to SFGs, we have 133 MaNGA targets with paired galaxies outside of the IFU.
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
@@
 We split both the pair and control samples into five evenly spaced stellar mass bins over the range, \logm\ $=$ 9.0$-$11.5.
-The pairs are then compared to their respective controls within each stellar mass bins.
+The pairs are then compared to their respective controls within each stellar mass bin.
 While the redshift in not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
@@
 When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
-When making the comparison with the second method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
+When making the comparison with the second tailored control method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
 Further, when defining the a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
@@
 \citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2d separation of $\sim$250 kpc.
-This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in \ref{fig:nuc_sep} was extracted from a 0.5\reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius.
+This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in Figure \ref{fig:nuc_sep} was extracted from a 0.5 \reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius.
 This means that our extraction radius is effectively twice a small and is more restricted to the central burst of star formation.

### 2020-10-22 maintex.tex

--- 2020-10-21 maintex.tex
@@
-% AASTeX v6.2
-%\documentclass[preprint]{aastex62}
-
 % ApJ Format
@@
 In this study, they found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.
-%
+
 \citet{Pan:2019} used the SDSS-IV MaNGA survey to study radial profiles of a sample of 205 paired galaxies.
@@
 This was in agreement with previous hydrodynamical simulations which showed that a burst of star formation is triggered after the first pericenter and as the two galaxies begin to coalesce \citep{Scudder:2012}.
-%
+
 The radial profile of sSFR in post-merger galaxies has also been studied with the MaNGA survey by \citet{Thorp:2019}.
@@
 We also require that the galaxies are classified as star forming as described in Section \ref{sec:data}.
-These requirements reduce our sample down to 87 star forming pairs.
+These requirements reduce our sample down to 87 star forming MaNGA targets with inside-IFU companions.
+While the companions to the inside-IFU MaNGA targets contained are within the MaNGA IFUs, we only use the MaNGA targets when building radial profiles.
+We leave out the identified companions from the analysis because the MaNGA targets are covered by the NSA catalog with geometries and total stellar masses while the companions are not covered by the NSA catalog.
 
@@
 We further use a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.
+
+From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets.
+After restricting the sample to SFGs, we have 133 MaNGA targets with paired galaxies outside of the IFU.
+MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
+This give use a total of 175 MaNGA targets in our pair sample.
 
@@
 This gives us a control sample of 1888 star forming control galaxies.
+
+It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep{Noeske:2007}.
+We will compare our interacting galaxies with isolated galaxies of a similar stellar mass and redshift, to account for these other dependencies.
+To do this, we will use two different methods of pair - control comparison.
+
+In the first method, we only control for the stellar mass between the pairs and controls.
+We split both the pair and control samples into five evenly spaced stellar mass bins over the range, \logm\ $=$ 9.0$-$11.5.
+The pairs are then compared to their respective controls within each stellar mass bin.
+While the redshift in not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
 
@@
 
-%%% SPFIT
 For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
 
-%%% Reddening
 We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
@@
 When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
+When making the comparison with the second tailored control method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
+Further, when defining the a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
+
+We fit the geometry with apertures from both catalogs when available.
+When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
 When making the comparison with the second method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
@@
 We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.
-
-%We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects within the MaNGA IFUs which may contaminate the data.
-Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.
-This gives us an individual radial profile of the sSFR for all paired and control galaxies.
 
@@
 We show these stacked profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}.
-{\bf QUESTION: for the inside-IFU pairs, did you use only the primaries to build these stacked profiles?
-If so, this needs to made clear in the text.} Star formation in the control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with stellar mass, consistent with previously published results using the MaNGA survey \citep{Belfiore:2018}.
+Star formation in the control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with stellar mass, consistent with previously published results using the MaNGA survey \citep{Belfiore:2018}.
 In contrast, the paired galaxies show flatter sSFR profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5, which still show some central quenching.
@@
 While the mechanism for quenching in galaxies remains under debate, the merger process seems to be capable of rejuvenating star formation in the centers of these galaxies, resulting in the flatter sSFR profiles.
-%Further, since the sSFR enhancement in the difference profiles is largely driven by the quenched controls, it may be more appropriate to describe isolated galaxies as being centrally quenched in comparison to paired galaxies or that the profiles of paired galaxies are flattened in their centers with respect to their controls.
 
@@
 
-%To emphasize the difference between primary and secondary companions and to further investigate the sSFR enhancement seen in the outskirts of low mass galaxies (\logm\ $=$ 9.0$-$9.5), we plot the difference profiles split both by stellar mass and mass ratio in Figure \ref{fig:ssfr_massdm}.
-The difference profile of primary companions is centrally enhanced by 0.25 dex and remains enhanced across their disks with an enhancement of 0.1-0.3 dex.
-The difference profile of secondary companions is centrally enhanced by 0.3 dex and is suppressed by 0.1 dex in their outskirts.
-Specifically looking at the paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, the primary companions in the mass range show strong enhancements to their outskirts while the primary companions in the mass range show a weak suppression to their outskirts.
-
 From the mass ratio, we see two different effects.
@@
 
-%Among the three parameters, stellar mass, mass ratio, and projected separation, the projected separation has the strongest effect on the $\Delta$log(sSFR) enhancement, followed by the mass ratio.
-From this we see that the paired galaxies with the strongest enhancements to the central sSFR are paired galaxies with 1:1 mass ratios and  which are within 10 kpc.
-
-%Between the splitting the $\Delta$log(sSFR) profile by stellar mass, mass ratio, and projected separation, we see that the general shape of the profile within the inner 1.0 \reff\ is unchanged.
-The profile is peaked in the center of the paired galaxies and linearly (in log space) to zero around 1.0 \reff.
-Different projected separations and mass ratios may elevate or suppress the level of the enhancement in the profile's center; however, the shape of the profile is largely unchanged.
-
 \subsection{Comparison with Previous Works}

### 2020-10-22 maintex.tex
major revision to Sec 4.1.1

@@
 
-In the first method, we only control for the stellar mass between the pairs and controls.
+In the first method, we simply control for the stellar mass between the pairs and controls.
 We split both the pair and control samples into five evenly spaced stellar mass bins over the range, \logm\ $=$ 9.0$-$11.5.
@@
 
-In the second method, we wish to account for both stellar mass and redshift.
-To do this we select a subsample of 20 control galaxies for each paired galaxy.
+In the second method, we select a ``tailored'' control sample for each paired galaxy from the full sample of isolated galaxies.
+We select a subsample of 20 control galaxies for each paired galaxy.
 We first select all of the control galaxies which are within a 0.1~dex stellar mass limit and within the same MaNGA subsample (e.g.
@@
 Since the MaNGA sample has a tight distribution in stellar mass and redshift, the stellar mass and MaNGA subsample restriction effectively sets a $\Delta z$ $\lesssim$ $\sim$0.025 redshift tolerance.
-
-Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies.
+With these requirements, most paired galaxies will find between 20$-$100 control galaxies.
 Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20.
@@
 All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile.
-For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is higher than the median profile at 0.5$-$0.6 dex.
-The sSFR enhancement in the sample seems to be mass independent except for the most massive galaxies which feature higher levels of sSFR enhancement.
+For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is significantly higher than the median profile (reaching 0.5$-$0.6 dex).
+As will be discussed in \S~\ref{sec:tailored}, we believe this elevated enhancement in the highest mass bin is driven by more compact mergers instead of stellar mass.
 
-Alternatively, the central enhancement of the sSFR in the paired galaxies can be interpreted as the quenching of star formation in the centers of isolated galaxies.
-While the mechanism for quenching in galaxies remains under debate, the merger process seems to be capable of rejuvenating star formation in the centers of these galaxies, resulting in the flatter sSFR profiles.
+In summary, Figure~\ref{fig:ssfr_prof} shows that the merger process is capable of rejuvenating star formation in the centers of these galaxies, resulting in almost flat sSFR radial profiles.
+In addition, the sSFR enhancement is mass independent -- star formation proceeds at $\sim$2$\times$ (0.3~dex) greater rates in galaxies with close companions than in more isolated galaxies, across a wide mass range between 9.0 $\leq$ \logm\ $\leq$ 11.5.
 
-The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth.
-The fractional mass growth rate is simply the difference between the sSFR profiles of the paired and control galaxies in linear space (pairs - controls) multiplied by a given timescale.
-We chose a timescale of 0.4 Gyr which is estimated to be the average timescale for the merger induced starburst \citep{Feng:2019}.
-
-Since the $\Delta$log(sSFR) is independent of galaxy mass, the fractional mass change will depend on the stellar mass of the paired galaxy.
-That is, since the amount of new stellar mass from merger induced interactions is roughly constant across galaxies of different stellar masses, lower mass galaxies will experience a greater change to their total stellar mass.
-Low mass galaxies, \logm\ $=$ 9.0$-$9.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.03 (3\%) while massive galaxies, \logm\ $=$ 11.0$-$11.5, experience a fractional mass change of $\Delta M_{\rm merger}$/$M_{\rm total}$ $=$ 0.001 (0.1\%).
-This shows that the merger induced mass growth is greatest in low mass galaxies.
-Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.
-
-This mass-binning method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls.
-On the other hand, this method only controls for a single galaxy parameter, stellar mass, though it is still relevant that the central enhancement of the sSFR in pairs is able to be observed.
-The profiles can also only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.
+This method of stacking sSFR profiles by a single parameter (stellar mass) has the advantage of simplicity and large statistical samples.
+It has revealed the first order result of mass-independent, centrally enhanced star formation in close galaxy pairs.
+To proceed with exploring the dependency of $\Delta$sSFR on merger parameters such as separation and mass ratio, we will utilize a more sophisticated method of selecting control samples for individual paired galaxies based on stellar mass and redshift in the following subsections.
 

### 2020-10-22 maintex.tex
shortened paragraphs in Sec 4.1.2

@@
 In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}.
-We take the individual azimuthally averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin to produce the median profile of the control galaxies.
+We then take the median of the azimuthally averaged profiles of the tailored control sample.
+Finally, we obtain the $\Delta\log$sSFR profile for each of the 175 paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.
 
-Once the median profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the median control profile in log space.
-We do this process for each of the 175 paired galaxies.
-
-The difference profiles at this stage have now been controlled for both stellar mass and redshift.
-We can freely stack these difference profiles to study their dependence on other parameter like the mass ratio and projected separation.
-
-First, we split the profiles by stellar mass to see how this method compares to the previous mass-binning method.
+Before delving into merger parameters, we decided to stack the profiles by stellar mass to see how this method compares to the previous mass-binning method.
 We split the individual difference profiles into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5 and stack the difference profiles within each mass bin.
@@
 
-To focus on the sSFR offsets in the centers of the galaxies, we take the median sSFR within 0.5 \reff\ for all galaxies.
-We then calculate the offsets in the centers of the pairs by taking the difference between the sSFR in the centers of the pairs and the median sSFR of their 20 controls.
-We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}
+To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff.
+We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
 
@@
 Between the two methods we see that the $\Delta$log(sSFR) profile is independent of the total stellar mass of the galaxies.
-In the next two sections, we will use the tailored-control method to study how the profiles behave as a function of the mass ratio (Section \ref{sec:dm}) and projected separation (Section \ref{sec:sep}).
+In the next two sections, we will use the tailored-control method to study how the difference profiles behave as a function of the mass ratio (Section \ref{sec:dm}) and projected separation (Section \ref{sec:sep}).
 

### 2020-10-22 maintex.tex
major revisions to Sec 5 & 6

@@
 \centering
-\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
+\includegraphics[width=0.8\linewidth]{fig/ssfr_mass.pdf}
 \caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
@@
 \centering
-\includegraphics[width=\linewidth]{fig/sep_hist.pdf}
+\includegraphics[width=0.8\linewidth]{fig/sep_hist.pdf}
 \caption[]{The projected separation distribution of the whole sample (blue) against the projected separation distribution for the highest mass galaxies, \logm\ $=$ 11.0$-$11.5 (Red). }
@@
 \centering
-\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
-\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. The inside-IFU sample is left out of this analysis as their mass ratios are unreliable.}
+\includegraphics[width=0.8\linewidth]{fig/ssfr_dm.pdf}
+\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair.
+The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
 \label{fig:ssfr_dm}
@@
 \centering
-\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
+\includegraphics[width=0.8\linewidth]{fig/ssfr_sep.pdf}
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by projected separation. }
@@
 
-While the total stellar mass of the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does.
-The mass ratio here is calculated as the difference between stellar masses contained within the 50\% half light radius,
+While the centrally enhanced star formation in close galaxy pairs seems mostly mass-independent, the mass ratio of the galaxy pair, like the projected separation, may be an important parameter that controls the level of enhancement \citep{Ellison:2008}.
 
+The mass ratio here is defined as, 
 \begin{equation}
-\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}) 
+\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
 \end{equation}
+where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
+We will define the more massive galaxy of a pair the primary companion and the less massive one the secondary companion.
 
-Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
-We will define the more massive galaxies of a pair, $\Delta$log($M$) $>$ 0.0, the primary companion and the less massive galaxy of a pair, $\Delta$log($M$) $<$ 0.0, the secondary companion.
-
-For the outside-IFU sample we use the stellar masses calculated from the $r$-band elliptical Petrosian apertures from the NSA catalog.
-Most of the companion galaxies in the inside-IFU sample are not covered by either the NSA catalog or \citet{Simard:2011}.
-Because of this, the inside-IFU galaxies are left out of this analysis.
+For the outside-IFU pair sample we use the stellar masses enclosed by the $r$-band elliptical Petrosian apertures from the NSA catalog.
+The inside-IFU pair sample is left out of this analysis, because most of the secondary companions in these pairs are missing in the NSA catalog and the \citet{Simard:2011} catalog.
 
@@
 
-In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0.
+In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
 These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
@@
 
-We look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in Figure \ref{fig:ssfr_sep}.
+A number of previous studies have shown that the sSFR enhancement increases as projected separation decreases \citep[e.g.,][]{Li:2008, Ellison:2008, Scudder:2012, Patton:2013}, in agreement with simulations \citep{Scudder:2012}.
+
+Figure \ref{fig:ssfr_sep} shows the profile and the central level of sSFR enhancement as a function of the projected separation ($r_{\rm p}$) from our MaNGA data.
 The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations.
@@
 
-This effect can be seen more clearly in the scatter plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
+This effect can be seen more clearly in the plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
 The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc.
@@
 Within 20 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex.
-
-The sSFR enhancement increasing with closer projected separations is to be expected and has been shown in previous studies \citep{Li:2008, Ellison:2008, Scudder:2012, Patton:2013}.
-The passage of the first pericenter is predicted to trigger a burst of star formation which falls as the two galaxies separate \citep{Scudder:2012}.
-The sSFR enhancement in our sample persists out to 50 kpc and previous works have shown that the burst of star formation can persist out to 150 kpc \citep{Patton:2013}.
+Our data shows that the sSFR enhancement persists out to at least $r_{\rm p} = 50$~kpc, which is the limit of our pair selection.
+In the next section, we will compare our results with those from previous studies.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}\label{sec:disc}
+\section{Comparison with Previous Work}\label{sec:disc}
 
-\subsection{Comparison with Previous Works}
+\subsection{Difference Radial Profiles}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=3in]{fig/prof_comp.pdf}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}) and \citet{Thorp:2019} ({\it Blue}).}
+\label{fig:prof_comp}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
+The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 dex higher than our sample of paired galaxies.
+The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
+The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 \reff\ of $\sim$0.1$-$0.15 dex.
+The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
+
+The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughly $\sim$0.1$-$0.2 dex higher than our sample.
+Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of post-merger galaxies while our sample has no post-merger galaxies.
+These post-merger galaxies are predicted to have higher levels of star formation over other paired galaxies due to a second larger burst of star formation which is triggered as the merging galaxies coalesce and may be able to increase the sample's average sSFR enhancement.
+
+While in this work we find that $\Delta$log(sSFR) has essentially no dependence on the stellar mass of the galaxy, \citet{Li:2008} found that lower mass galaxies experience greater levels of enhancement than higher mass galaxies.
+Galaxies in the mass range \logm\ $=$ 9.72 were shown to experience an enhancement $\sim$0.4 dex higher than galaxies in the mass range \logm\ $=$ 10.6.
+The source of the difference is unclear; between our works we utilize different methods for determining the sSFR enhancement in galaxy pairs.
+\citet{Li:2008} defines their enhancement function as the average sSFR of the paired galaxies at a given separation, weighted by the number of companions, subtracted by the average sSFR of the whole sample.
+While we do not find the same dependency between the sSFR enhancement and stellar mass, the sSFR enhancement as a function of projected separation between our studies is in good agreement (see Figure~\ref{fig:nuc_sep}).
+
+\subsection{Dependency on Merger Parameters}
+
+The dependency of the SFR enhancement on the mass ratio was studied in \citet{Ellison:2008}.
+They found that pairs with mass ratios of 2:1 have higher SFR enhancements of $\sim$0.1 dex over pairs with wider 10:1 mass ratios.
+We find that pairs with mass ratios of $\Delta$log($M$) $=$ 0.25 (1.8:1) are 0.2 dex over pairs with mass ratios of $\Delta$log($M$) $=$ 1.0 (10:1).
+\citet{Ellison:2008} also saw tentative evidence for SFR enhancement in the secondary companions of minor pairs.
+We not only confirm that secondary companions of minor pairs feature SFR enhancement, but also that the enhancement is higher than the primary component of pairs at the same mass ratios.
+
+The observations are also consistent with simulations.
+\citet{Moreno:2015} used {\sc Gadget}-3, a smoothed particle hydrodynamics code, to study the spatial extent of the star formation enhancement.
+The merger simulations showed that the star formation enhancement was largely concentrated in the centers (R $<$ 1 kpc) of the paired galaxies and that the off-nuclear regions (1 $<$ R $<$ 10 kpc) showed a suppression to the star formation.
+\citet{Moreno:2015} also found that lower mass secondary galaxies (in mergers with stellar mass ratios of 2.5:1) have higher levels of sSFR enhancement in their centers and have stronger levels of sSFR suppression in their disks.
+This is in good agreement with our work, we found that secondary companions show moderately higher levels of sSFR enhancement in their centers in comparison to primary companions at the same mass ratio.
+Further, the outskirts of the primary companions feature positive to zero enhancement to their sSFR while the secondary companions show a strong suppression to the sSFR in their outskirts.
 
@@
 \includegraphics[width=3in]{fig/nuc_sep.pdf}
-\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation for this sample using the tailored control method (Black), \citet{Ellison:2008} (Red),  \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).
-(\textbf{Bottom}) $\Delta$log(sSFR) over projected separation for this sample (Black), \citet{Li:2008} (Red), and \citet{Patton:2020} (Blue).
-}
+\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
+(\textbf{Bottom}) $\Delta$log(sSFR) over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).}
 \label{fig:nuc_sep}
@@
 
-The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Li:2008, Patton:2013, Scudder:2012, Bustamante:2020}.
+Figure~\ref{fig:nuc_sep} compares the enhancement in both SFR and sSFR as a function of projected separation.
+For our data points, we use the mean $\Delta\log{\rm SFR}$ and $\Delta\log{\rm sSFR}$ measured within a deprojected radius of 0.5~\reff\ (i.e., the black data points in the right side panel of Figure~\ref{fig:ssfr_sep}).
+The literature data are either measured from single 1-1.5\arcsec-radius SDSS fibers \citep{Ellison:2008,Scudder:2012,Patton:2013} or XX\arcsec-radius apertures from CALIFA IFS data \citep{Bustamante:2020}.
+%The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Li:2008, Patton:2013, Scudder:2012, Bustamante:2020}.
 We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}.
@@
 
-\citet{Li:2008} studied the star formation enhancement over different stellar masses and saw that low mass galaxies experience greater levels of enhancement than high mass galaxies.
-Galaxies in the mass range \logm\ $=$ 9.72 were shown to experience an enhancement $\sim$0.4 dex higher than galaxies in the mass range \logm\ $=$ 10.6.
-In this work, we find that $\Delta$log(sSFR) has no dependence on the stellar mass of the galaxy.
-The source of the difference is unclear; between our works we utilize different methods for determining the sSFR enhancement in galaxy pairs.
-\citet{Li:2008} defines their enhancement function as the average sSFR of the paired galaxies at a given separation, weighted by the number of companions, subtracted by the average sSFR of the whole sample.
-While we don't find the same dependency between the sSFR enhancement and stellar mass, the sSFR enhancement as a function of projected separation between our studies is in good agreement.
-
-The dependency of the SFR enhancement on the mass ratio was studied in \citet{Ellison:2008}.
-They found that pairs with mass ratios of 2:1 have higher SFR enhancements of $\sim$0.1 dex over pairs with wider 10:1 mass ratios.
-We find that pairs with mass ratios of $\Delta$log($M$) $=$ 0.25 (1.8:1) are 0.2 dex over pairs with mass ratios of $\Delta$log($M$) $=$ 1.0 (10:1).
-\citet{Ellison:2008} also saw tentative evidence for SFR enhancement in the secondary companions of minor pairs.
-We not only confirm that secondary companions of minor pairs feature SFR enhancement, but also that the enhancement is higher than the primary component of pairs at the same mass ratios.
-
-In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
-The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 dex higher than our sample of paired galaxies.
-The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
-The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 \reff\ of $\sim$0.1$-$0.15 dex.
-The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
-
-The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughly $\sim$0.1$-$0.2 dex higher than our sample.
-Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
-The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of post-merger galaxies while our sample has no post-merger galaxies.
-These post-merger galaxies are predicted to have higher levels of star formation over other paired galaxies due to a second larger burst of star formation which is triggered as the merging galaxies coalesce and may be able to increase the sample's average sSFR enhancement .
-
-\citet{Barrera-Ballesteros:2015} studied the sSFR in paired galaxies in the CALIFA IFS survey using the H$\alpha$ equivalent width (\ewha) as a proxy for the sSFR.
-They compared the sSFR in the centers of paired galaxies to their disks by varying the aperture diameters from which they extract the \ewha.
-They found that the sSFR is enhanced in the centers of the paired galaxies but suppressed in their disks, which is similar to what we find.
-
-\citet{Moreno:2015} used {\sc Gadget}-3, a smoothed particle hydrodynamics code, to study the spatial extent of the star formation enhancement.
-The merger simulations showed that the star formation enhancement was largely concentrated in the centers (R $<$ 1 kpc) of the paired galaxies and that the off-nuclear regions (1 $<$ R $<$ 10 kpc) showed a suppression to the star formation.
-\citet{Moreno:2015} also found that lower mass secondary galaxies (in mergers with stellar mass ratios of 2.5:1) have higher levels of sSFR enhancement in their centers and have stronger levels of sSFR suppression in their disks.
-This is in good agreement with our work, we found that secondary companions show moderately higher levels of sSFR enhancement in their centers in comparison to primary companions at the same mass ratio.
-Further, the outskirts of the primary companions feature positive to zero enhancement to their sSFR while the secondary companions show a strong suppression to the sSFR in their outskirts.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
-\label{fig:prof_comp}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In this work.
-we have made a sample of 175 star forming galaxy pairs along with a set of 1888 star forming control galaxies in the MaNGA IFS survey.
-We compared the radial profiles of sSFR between the paired galaxies and controls galaxies and found the following;
+In this paper, we have demonstrated the power of a massive integral-field spectroscopic survey in comparison studies of galaxy properties.
+The nearby galaxy populations show consistent behaviors despite of their large diversity in star formation properties.
+Stacking was able to detect the signal buried in the noise by averaging, in the time domain, the likely stochastic star forming histories of galaxies (which drives the scatter in the sample).
+We focused on comparing the azimuthally averaged radial profiles of sSFR between galaxies in close pairs and a control sample of isolated galaxies.
+In agreement with previous studies, we found that, on average, star formation is elevated in close galaxy pairs.
+The properties of these purported merger-induced differences in sSFR can be summarized as follows:
 
 \begin{enumerate}
-\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.25 $\pm$ 0.1 dex. 
-\item The outskirts of the paired galaxies, \reff\ $=$ 1.0$-$2.5, show limited suppression in their disks of $\sim$0.1 dex.
-\item The sSFR enhancement in paired galaxies is independent of their total stellar mass.
-\item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies.
-Galaxies with small mass ratios, $|\Delta$log($M$)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.35 dex, which is 0.1 dex higher than the average paired galaxies in the survey.
-Paired galaxies with large mass ratios, $|\Delta$log($M$)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex.
-\item The secondary companions of a galaxy pair, the less massive galaxy, show higher sSFR enhancements, by $\sim$0.1 dex in comparison to primary companions at the same mass ratio.
-Further, primary companions have zero to positive sSFR offsets in their ouskirts, $\Delta$log(sSFR) $=$ 0.0$-$0.4 dex.
-Secondary companions feature a sSFR suppression in their outskirts of 0.1$-$0.4 dex.
-\item The sSFR enhancement increases with closer projected separations where galaxies within 20 kpc have their sSFR enhanced by 0.3$-$0.4. 
+
+\item Star formation is enhanced within the inner 1.0 \reff\ and it peaks at a level of 0.25 $\pm$ 0.1 dex (i.e., $\sim$2$\times$ faster star formation).
+On the other hand, the outskirts of the paired galaxies (\reff\ $=$ 1.0$-$2.5) show a moderate amount of suppression in sSFR at a level of $\sim$0.1 dex.
+
+\item The sSFR difference profile is largely independent of the stellar mass.
+
+\item The level of central sSFR enhancement increases as the projected separation of the pair decreases.
+
+\item The level of central sSFR enhancement depends on the mass ratio of the galaxy pair.
+Galaxies with small mass ratios, $|\Delta$log($M$)$|$ $=$ 0.0$-$0.5, see an enhancement $\sim$0.1 dex higher than the average.
+But the enhancement is still present in pairs with mass ratios as large as $|\Delta$log($M$)$|$ $=$ 1.0.
+
+\item The merger-induced changes in sSFR also seem to differ between the more massive and the less massive member of a galaxy pair.
+At the same mass ratio, the less massive member in a galaxy pair shows a higher sSFR enhancement (by $\sim$0.1 dex) in comparison to the more massive member.
+And in the galactic outskirt (R/\reff\ $=$ 1.0$-$2.5), the more massive member shows a general enhancement in sSFR, while the less massive member features a general suppression.
+
 \end{enumerate}
 
-There is still much to be understood about these galaxy pairs.
-We see that there is a great diversity in the difference profiles of individual galaxies.
-In particular there are galaxy pairs which feature a strong suppression to the sSFR in their centers while others feature a central enhancement to the sSFR which is much greater than the median enhancement.
-The depth of our analysis here would benefit by studying other merger parameters like the interaction stage or the gas fraction.
-
-As of August 24, 2020, MaNGA has finished observing its goal of 10,000 galaxies.
-The completion of the final sample will mean that we will have access to a larger sample of paired and control galaxies.
-We also plan to fit the light profiles of the inside-IFU companion galaxies which will allow us to roughly double the size of the inside-IFU sample.
-With this and the completion of MaNGA's observations, we may be able to expand our pair sample to include nearly 500 galaxy pairs.
-
-With the larger sample size we will be better able to separate how the stellar mass, mass ratio, and projected separation effect the enhancement profile along with new parameters like the merger stage and gas fraction.
-Also, by constructing enhancement profiles for the inside-IFU companions to the MaNGA targets, we can better study how primary companions behave in comparison to their secondary companions.
+As of 2020 August 24, MaNGA has completed its observations of $\sim$10,000 galaxies.
+This final sample gives us access to an unprecedentedly large sample of paired and control galaxies with 2\arcsec\ spatial sampling up to 2-3~\reff, which will undoubtedly improve the results presented here.
+In addition, the less massive members of the inside-IFU pairs can be included in such a comparison study once we build a better deblended photometric catalog using SDSS images.
 
@@
 
-% funding
 We thank Cheng Li for our useful discussion on how the sSFR enhancement in galaxy pairs relates to their stellar mass and mass ratio.

### 2020-10-23 authors.tex
Fixing more typos

@@
 \author{
-Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, and Rui~Xue\altaffilmark{1}
+Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Arran~C.~Gross\altaffilmark{1}, and Rui~Xue\altaffilmark{1}
 }

### 2020-10-23 maintex.tex
Fixing more typos

@@
 In fact, cosmological hydrodynamical simulations have shown that repeated merger events may be responsible for as much as $\sim$60\% of stellar mass in massive galaxies like M87 \citep[e.g.,][]{Rodriguez-Gomez:2016,Pillepich:2018}.
-As the galaxies undergo the merging process, the gas within the galaxies are subject to gravitational torques which perturb the morphology of the galaxies.
+As the galaxies undergo the merging process, the gas within the galaxies are subjected to gravitational torques which perturb the morphology of the galaxies.
 
@@
 Since then, hydrodynamical simulations have expanded upon the N-body simulations of \citet{Toomre:1972} by modeling gas-dynamics within the galaxies.
-These simulations show how barred structures develop within the disks of the interacting galaxies due to the tidal torques between them \citep{Barnes:1991}.
+These simulations show the process by which barred structures develop within the disks of the interacting galaxies due to the tidal torques between them \citep{Barnes:1991}.
 As the bars form, the gases within the galaxy's disk lose angular momentum and get funneled into the centers of the galaxies.
 
-When the gas-inflows impact upon the gases in the nucleus of galaxy a burst of new star formation in triggered \citep{Barnes:1996, Mihos:1996}.
+When the gas-inflows impact upon the gases in the nucleus of the galaxy, a burst of new star formation in triggered \citep{Barnes:1996, Mihos:1996}.
 These gas inflows will also bring metal-poor gases from the disk into the center of the galaxy which can dilute the central metallicity \citep{Rupke:2010, Perez:2011, Scudder:2012}.
-The gas-inflows may also be able to reach the very center of the galaxy and trigger supermassive black hole (SMBH) accretion \citep{Capelo:2017}.
+The gas-inflows may also be able to reach into the very center of the galaxy and trigger an episode of supermassive black hole (SMBH) accretion \citep{Capelo:2017}.
 
@@
 Interaction induced star formation was first seen observationally in the bluer colors of peculiar galaxies in \citet{Larson:1978}.
-This observation has also been shown in more recent works using the single-fiber spectroscopic survey, SDSS (Sloan Digital Sky Survey) \citep{Ellison:2008, Li:2008, Scudder:2012, Patton:2013, Bustamante:2020}.
+Similar observations have has also been shown in more recent works using the single-fiber spectroscopic survey, SDSS (Sloan Digital Sky Survey) \citep{Ellison:2008, Li:2008, Scudder:2012, Patton:2013, Bustamante:2020}.
 From these previous works it has been shown that the strength of the star formation enhancement in the centers of paired galaxies is dependent on the stellar mass of the pairs \citep{Li:2008}, the projected separation between the pairs \citep{Ellison:2008, Li:2008, Scudder:2012}, and the mass ratio between the pairs \citep{Ellison:2008}.
@@
 %%%Integral Field Spectroscopy%%%
-The previous mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 2\arcsec\ diameter optical fibers.
+The previously mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 2\arcsec\ diameter optical fibers.
 With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail.
@@
 
-Indeed, \citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted from.
+Indeed, \citet{Barrera-Ballesteros:2015} used the CALIFA (Calar Alto Legacy Integral Field Area) survey to study a sample of 103 paired galaxies by varying the size of the aperture through which the \ewha\ is extracted.
 In this study, they found a moderate enhancement to the sSFR in the centers of paired galaxies and a moderate suppression to the sSFR in outskirts of the paired galaxies.
@@
 The enhancement to the sSFR was shown to be the strongest in the centers of the paired galaxies.
-This central enhancement linearly fell with increasing galactocentric radii; however, a moderate enhancement to the sSFR remain in the outskirts of the galaxies.
-\citet{Pan:2019} further studied the paired galaxies as a function of merger stage; from well separated pairs to post-merger galaxies.
+This central enhancement linearly fell with increasing galactocentric radii; however, a moderate enhancement to the sSFR remains in the outskirts of the galaxies.
+\citet{Pan:2019} further studied the paired galaxies as a function of merger stage, from well separated pairs to post-merger galaxies.
 Across the different merger stages, the sSFR enhancement was greatest in close pairs with tidal features and in post-merger galaxies.
@@
 With the MaNGA survey, we will be able to expand upon these previous studies in greater spatial detail.
-We will be able to see how these three parameters affect both the level of the sSFR offsets in the centers of the paired galaxies and the offsets in the outskirts of the galaxies.
-We will also be able to study if any of three parameters influence the gradient of the sSFR enhancement profiles or if the gradient is preserved between different configurations.
+We will be able to analyze how these three parameters affect both the level of the sSFR offsets in the centers of the paired galaxies and the offsets in the outskirts of the galaxies.
+We will also be able to study whether any of the three parameters influence the gradient of the sSFR enhancement profiles or if the gradient is preserved between different configurations.
 
@@
 \caption[]{Color-magnitude diagram for MaNGA galaxies.
-The grey circles represent the whole MaNGA sample and reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
 Inside-IFU pairs are marked with red diamonds and the outside-IFU pairs are marked with red squares.
@@
 
-MaNGA is an IFS survey at the Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}.
-MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citep{Law:2015}.
+MaNGA is an IFS survey at the Apache Point Observatory (APO) which uses the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}.
+MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers: 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citep{Law:2015}.
 MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a PSF of 2.5\arcsec\ FWHM \citep{Bundy:2015}.
@@
 \begin{equation}\label{eq:red}
-NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18)
+NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18),
 \end{equation}
-
 Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_i$ is the $i$-band magnitude from the NSA catalog.
@@
 
-The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories; ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects.
+The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories: ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects.
 The ``good" galaxy spectra are the objects whose spectra are well modeled by {\sc spfit} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
@@
 
-Among 6142 MaNGA IFUs considered here, 404 have multiple galaxy objects within the IFU.
+Among the 6142 MaNGA IFUs considered here, 404 have multiple galaxy objects within the IFU.
 We further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected companions.
-Given redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc.
+Given the redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc.
 Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples.
@@
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-This give use a total of 175 MaNGA targets in our pair sample.
+This gives us a total of 175 MaNGA targets in our pair sample.
 
@@
 The pairs are then compared to their respective controls within each stellar mass bin.
-While the redshift in not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
+While the redshift is not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
 
@@
 We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
-The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.
+The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.
 
@@
 \begin{equation}
-{\rm sSFR} = \frac{\rm SFR}{M}
+{\rm sSFR} = \frac{\rm SFR}{M}.
 \end{equation}
-The local stellar masses used here is derived from {\sc SPFIT}'s best-fit stellar continuum.
+The local stellar masses used here is derived from {\sc spfit}'s best-fit stellar continuum.
 Utilizing sSFR, instead of SFR, allows us to compare regions of high mass surface density to regions of low mass surface density.
@@
 When making the comparison with the second tailored control method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
-Further, when defining the a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
+Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
 
@@
 \begin{equation}
-{\rm cos^2}(i) = \frac{(b/a)^2 - q^2}{1 - q^2}
+{\rm cos^2}(i) = \frac{(b/a)^2 - q^2}{1 - q^2},
 \end{equation}
-
 Where $b/a$ is the major-to-minor axis ratio and $q$ is the intrinsic oblateness. We use the empirically determined oblateness of $q = 0.13$, from \citet{Giovanelli:1994}.
@@
 The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies.
-We use the 50\% half light radius (i.e.
-the effective radius, \reff) to scale the sizes of the galaxies.
+We use the 50\% half light radius ({\it i.e}, the effective radius, \reff) to scale the sizes of the galaxies.
 Doing this will allow us to compare galaxies of different sizes against each other.
 
-Once the geometry of the galaxies are set, we can build azimuthally averaged radial profiles.
+Once the geometries of the galaxies are set, we can build azimuthally averaged radial profiles.
 The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
@@
 The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.
-The parts of the profiles with dashed lines represent regions where less than 50\% of the galaxies in the bin are covered at that radii.
 }
@@
 With the individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies.
-The first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins.
+In the first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins.
 In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which are matched in stellar mass and redshift.
@@
 
-{\bf COMMENT: I am not sure the trimmed regions could be so limited.
+%{\bf COMMENT: I am not sure the trimmed regions could be so limited.
 If this is indeed correct, then we don't need to spend a paragraph on something so negligible and not to highlight the trimed regions in the plots.}
-The radial extent of our profiles reaches 2.6 \reff; however, 67\% of the MaNGA sample (i.e., the Primary subsample) is designed to cover only 1.5 \reff\ of the galaxy.
+%The radial extent of our profiles reaches 2.6 \reff; however, 67\% of the MaNGA sample (i.e., the Primary subsample) is designed to cover only 1.5 \reff\ of the galaxy.
 Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall outside of the innermost radii bin.
@@
 We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space).
-This gives us difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
+This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
 Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.35$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff.
@@
 In Figure \ref{fig:nuc_sep} we show the $\Delta$log(sSFR) enhancements across 2D separation (projected separation) from the TNG300-1 simulation.
-\citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2d separation of $\sim$250 kpc.
+\citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2D separation of $\sim$250 kpc.
 This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in Figure \ref{fig:nuc_sep} was extracted from a 0.5 \reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius.

### 2020-10-23 maintex.tex
Minor revisions

@@
 The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-Inside-IFU pairs are marked with red diamonds and the outside-IFU pairs are marked with red squares.
+The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic).
 From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
@@
 The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
+While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the inclination angle, sin($i$).
+
 Within each radius bin we take the median of the specific star formation rate.
@@
 In contrast, the paired galaxies show flatter sSFR profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5, which still show some central quenching.
-
-%{\bf COMMENT: I am not sure the trimmed regions could be so limited.
-If this is indeed correct, then we don't need to spend a paragraph on something so negligible and not to highlight the trimed regions in the plots.}
-%The radial extent of our profiles reaches 2.6 \reff; however, 67\% of the MaNGA sample (i.e., the Primary subsample) is designed to cover only 1.5 \reff\ of the galaxy.
-Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall outside of the innermost radii bin.
-Because of these issues, the centers or the outskirts of the stacked profiles may only represent a small subset of the galaxies in that mass bin.
-To account for this, we ``trim" the stacked profiles where a radius bin contains data for less than 50\% of the total set of galaxies.
-We represent the trimmed regions in our figures with dashed lines.
-In Figure \ref{fig:ssfr_prof}, galaxies below \logm\ $\le$ 10.0 have their innermost radii bin trimmed due to insufficient coverage.
 
@@
 where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
+We emphasize that the MaNGA target is not always the more massive component of the pair.
 We will define the more massive galaxy of a pair the primary companion and the less massive one the secondary companion.
@@
 \includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}) and \citet{Thorp:2019} ({\it Blue}).}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair survey, and \citet{Thorp:2019} ({\it Blue}), a post-merger survey.}
 \label{fig:prof_comp}

### 2020-10-23 maintex.tex
Updated language for the mass ratio equation

@@
 where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
-We emphasize that the MaNGA target is not always the more massive component of the pair.
-We will define the more massive galaxy of a pair the primary companion and the less massive one the secondary companion.
+In the sample, the MaNGA target is not always the more massive component of the pair.
+We split the sample into two groups based on their mass ratios; primary companions in which the MaNGA target is the more massive galaxy and secondary companions in which the MaNGA target is the less massive galaxy.
 
@@
 \includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair survey, and \citet{Thorp:2019} ({\it Blue}), a post-merger survey.}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
 \label{fig:prof_comp}

### 2020-10-26 maintex.tex
Removed a couple of duplicate paragrphs

@@
 
-The MaNGA survey targets galaxies from a subset of 41,154 galaxies in the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_i}$ $<$ -24.0, where $\mathcal{M_i}$ is the rest frame $i$-band magnitude within the survey's elliptical Petrosian apertures.
+The MaNGA survey targets galaxies from a subset of 41,154 galaxies in the NASA-Sloan Atlas (NSA v1\_0\_1; \url{http://www.nsatlas.org}) with a redshift range of 0.01 $< z <$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M}_{\rm i}$ $<$ -24.0, where $\mathcal{M}_{\rm i}$ is the rest frame $i$-band magnitude within the survey's elliptical Petrosian apertures.
 MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light).
@@
 \begin{equation}\label{eq:blue}
-NUV-r = 3.1682 - 0.16 (\mathcal{M}_i+18)
+NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
 \end{equation}
 \begin{equation}\label{eq:red}
-NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18),
+NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18),
 \end{equation}
-Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_i$ is the $i$-band magnitude from the NSA catalog.
+Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog.
 We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
@@
 From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets.
-After restricting the sample to SFGs, we have 133 MaNGA targets with paired galaxies outside of the IFU.
-MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-This gives us a total of 175 MaNGA targets in our pair sample.
-
-From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets.
 After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU.
@@
 This gives us a control sample of 1888 star forming control galaxies.
-
-It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep{Noeske:2007}.
-We will compare our interacting galaxies with isolated galaxies of a similar stellar mass and redshift, to account for these other dependencies.
-To do this, we will use two different methods of pair - control comparison.
-
-In the first method, we only control for the stellar mass between the pairs and controls.
-We split both the pair and control samples into five evenly spaced stellar mass bins over the range, \logm\ $=$ 9.0$-$11.5.
-The pairs are then compared to their respective controls within each stellar mass bin.
-While the redshift is not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
 
@@
 When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
-When making the comparison with the second tailored control method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
-Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
-
-We fit the geometry with apertures from both catalogs when available.
-When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures.
-When making the comparison with the second method, paired galaxies fitted with the NSA aperture are compared against controls fitted with the NSA aperture and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
+When making the comparison with the second method, paired galaxies fitted with the NSA apertures are compared against controls fitted with the NSA apertures and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures.
 Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
@@
 The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
-While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the inclination angle, sin($i$).
+While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).
 
@@
 For our data points, we use the mean $\Delta\log{\rm SFR}$ and $\Delta\log{\rm sSFR}$ measured within a deprojected radius of 0.5~\reff\ (i.e., the black data points in the right side panel of Figure~\ref{fig:ssfr_sep}).
-The literature data are either measured from single 1-1.5\arcsec-radius SDSS fibers \citep{Ellison:2008,Scudder:2012,Patton:2013} or XX\arcsec-radius apertures from CALIFA IFS data \citep{Bustamante:2020}.
-%The $\Delta$log(SFR) as a function of projected separation has been studied before with the SDSS survey \citep{Ellison:2008, Li:2008, Patton:2013, Scudder:2012, Bustamante:2020}.
-We compare the mentioned surveys with our own work in Figure \ref{fig:nuc_sep}.
+The literature data is measured from single 1-1.5\arcsec-radius SDSS fibers \citep{Ellison:2008,Scudder:2012,Patton:2013,Bustamante:2020}.
 We find that our central SFR enhancements for closely separated pairs are higher than many of the previous studies, our sSFR enhancement is $\sim$0.2 dex higher than \citet{Scudder:2012} and $\sim$0.3 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}.

### 2020-10-26 maintex.tex
replaced Section with \S

@@
 % Organization
-This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we study the radial profiles as a function of stellar mass, projected separation, and the mass ratio, in Section \ref{sec:disc} we compare our work against previous works, and in Section \ref{sec:sum} we summarize the findings of the work.
+This paper is organized as follows; in \S~\ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in \S~\ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in \S~\ref{sec:results} we study the radial profiles as a function of stellar mass, projected separation, and the mass ratio, in \S~\ref{sec:disc} we compare our work against previous works, and in \S~\ref{sec:sum} we summarize the findings of the work.
 % cosmology
@@
 Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples.
-We also require that the galaxies are classified as star forming as described in Section \ref{sec:data}.
+We also require that the galaxies are classified as star forming as described in \S~\ref{sec:data}.
 These requirements reduce our sample down to 87 star forming MaNGA targets with inside-IFU companions.
@@
 The pairs are then compared to their respective controls within each stellar mass bins.
-While the redshift is not constrained in this method, we will show in Section \ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
+While the redshift is not constrained in this method, we will show in \S~\ref{sec:mass-bin} that this method is sufficient to reveal the merger induced star formation.
 
@@
 With the individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies.
-In the first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins.
-In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which are matched in stellar mass and redshift.
+In the first method, in \S~\ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins.
+In the second method, in \S~\ref{sec:tailored}, paired galaxies are compared to a subset of 20 control galaxies which are matched in stellar mass and redshift.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}.
+In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}.
 We then take the median of the azimuthally averaged profiles of the tailored control sample.
@@
 The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
-Similar to what was seen in Section \ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.15$-$0.25 dex higher than the sample average.
+Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.15$-$0.25 dex higher than the sample average.
 
@@
 The paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, feature enhanced sSFR in their disks of 0.1$-$0.2 dex.
-As we will show in the next section, Section \ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.
+As we will show in the next section, \S~\ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.
 
@@
 The highest mass galaxies in the sample are at closer projected separations in comparison to the rest of the sample with 70\% of the highest mass galaxies being within 20 kpc.
-As we will show in Section \ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.
+As we will show in \S~\ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.
 
@@
 Between the two methods we see that the $\Delta$log(sSFR) profile is independent of the total stellar mass of the galaxies.
-In the next two sections, we will use the tailored-control method to study how the difference profiles behave as a function of the mass ratio (Section \ref{sec:dm}) and projected separation (Section \ref{sec:sep}).
+In the next two sections, we will use the tailored-control method to study how the difference profiles behave as a function of the mass ratio (\S~\ref{sec:dm}) and projected separation (\S~\ref{sec:sep}).
 

### 2020-10-26 maintex.tex
fixed typo in figure caption

@@
 The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic).
+The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic).
 From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.

### 2020-12-08 build/submit_v1/maintex.tex
added build folder

--- 2020-10-26 maintex.tex
@@
 %%%Integral Field Spectroscopy%%%
-The previously mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 2\arcsec\ diameter optical fibers.
+The previously mentioned works using SDSS were restricted to studying the centers of the paired galaxies through 1-1.5\arcsec-radius optical fibers.
 With the recent large integral field spectroscopic (IFS) surveys, interacting galaxies can now be studied with unprecedented spatial detail.
@@
 This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
-Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.35$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff.
+Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.3$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff.
 In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex.
@@
 The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations.
-The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.05$-$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.
+The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.1$-$0.15 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.
 
@@
 
+\subsection{Dependency on Merger Parameters}
+
 While in this work we find that $\Delta$log(sSFR) has essentially no dependence on the stellar mass of the galaxy, \citet{Li:2008} found that lower mass galaxies experience greater levels of enhancement than higher mass galaxies.
@@
 While we do not find the same dependency between the sSFR enhancement and stellar mass, the sSFR enhancement as a function of projected separation between our studies is in good agreement (see Figure~\ref{fig:nuc_sep}).
-
-\subsection{Dependency on Merger Parameters}
 

### 2020-12-14 maintex.tex
added table

@@
 
-\include{authors}
+\author{
+Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Arran~C.~Gross\altaffilmark{1}, and Rui~Xue\altaffilmark{1}
+}
+\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
+\altaffiltext{2}{Insititute for Astronomy, University of Hawaii, Honolulu, HI 96822}
+\altaffiltext{3}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
+\altaffiltext{4}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
+\altaffiltext{5}{Department of Physics, Hebei Normal University, 20 South Erhuan Road, Shijiazhuang, 050024, China}
+\altaffiltext{6}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical Observatory, Chinese Academy of Sciences, 80 Nandan Road, Shanghai 200030, China}
+\altaffiltext{7}{University of the Chinese Academy of Sciences, No.19A Yuquan Road, Beijing 100049, China}
 
@@
 
-When the gas-inflows impact upon the gases in the nucleus of the galaxy, a burst of new star formation in triggered \citep{Barnes:1996, Mihos:1996}.
+When the gas-inflows impact upon the gases in the nucleus of the galaxy, a burst of new star formation is triggered \citep{Barnes:1996, Mihos:1996}.
 These gas inflows will also bring metal-poor gases from the disk into the center of the galaxy which can dilute the central metallicity \citep{Rupke:2010, Perez:2011, Scudder:2012}.
@@
 \centering
-\includegraphics[width=\linewidth]{fig/color-mag.pdf}
+\includegraphics[width=\linewidth]{color-mag.pdf}
 \caption[]{Color-magnitude diagram for MaNGA galaxies.
@@
 Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog.
-We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
+We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
 Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers.
@@
 The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
-While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).
+\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).} While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).
 
@@
 \centering
-\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
+\includegraphics[width=\linewidth]{ssfr_comb.pdf}
 \caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
@@
 \centering
-\includegraphics[width=0.8\linewidth]{fig/ssfr_mass.pdf}
+\includegraphics[width=0.8\linewidth]{ssfr_mass.pdf}
 \caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
@@
 \centering
-\includegraphics[width=0.8\linewidth]{fig/sep_hist.pdf}
+\includegraphics[width=0.8\linewidth]{sep_hist.pdf}
 \caption[]{The projected separation distribution of the whole sample (blue) against the projected separation distribution for the highest mass galaxies, \logm\ $=$ 11.0$-$11.5 (Red). }
@@
 \centering
-\includegraphics[width=0.8\linewidth]{fig/ssfr_dm.pdf}
+\includegraphics[width=0.8\linewidth]{ssfr_dm.pdf}
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair.
@@
 \centering
-\includegraphics[width=0.8\linewidth]{fig/ssfr_sep.pdf}
+\includegraphics[width=0.8\linewidth]{ssfr_sep.pdf}
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by projected separation. }
@@
 \centering
-\includegraphics[width=3in]{fig/prof_comp.pdf}
+\includegraphics[width=3in]{prof_comp.pdf}
 \caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
@@
 \centering
-\includegraphics[width=3in]{fig/nuc_sep.pdf}
+\includegraphics[width=3in]{nuc_sep.pdf}
 \caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
@@
 
+\appendix
+
+\begin{deluxetable*}{lcccccccccc}
+
+\tablestypesize{\small} \tablewidth{0pt}
+\tablecaption{Pair Catalog}
+\centering
+\tablehead{\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
+\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
+\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}}
+
+\startdata
+%\begin{tabular}{cccccccccc}
+%Plate & IFU & Sample & Sep_arc & Sep_kpc & d_logm & RAdeg & Decdeg & z & logm \\
+7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.0 & 10.8 \\
+7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.0 & 10.1 \\
+7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.0 & 9.2 \\
+7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.1 & 11.1 \\
+7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.1 & 10.8 \\
+8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.0 & 10.1 \\
+8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.0 & 10.8 \\
+8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.0 & 9.5 \\
+8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.0 & 10.3 \\
+8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.0 & 9.9 \\
+%\end{tabular}
+%\end{table*}
+
+\enddata
+\end{deluxetable*}
+
 \end{document}

### 2020-12-16 maintex.tex
text revisions

@@
 
-\usepackage{epstopdf}
+%\usepackage{epstopdf}
 
@@
 \begin{abstract}
-We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 175 star-forming galaxies in close pairs with those of mass-matched isolated galaxies in the SDSS-IV MaNGA survey.
+We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 175 star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey.
 We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
@@
 
+\textbf{Broad-line AGN comprise $\sim$0.9\% of MaNGA's galaxy sample where \citet{Lacerda:2020} found a fraction of $\sim$2.8\% from the CALIFA survey and \citet{Sanchez:2018} found a fraction of $\sim$1.33\% from the MaNGA's MPL-5 sample (which observed $\sim$2700 galaxies).
+}
+
 Among the 6142 MaNGA IFUs considered here, 404 have multiple galaxy objects within the IFU.
@@
 We leave out the identified companions from the analysis because the MaNGA targets are covered by the NSA catalog with geometries and total stellar masses while the companions are not covered by the NSA catalog.
+\textbf{While we use the identified companions to select galaxy pairs, we only build radial profiles for the MaNGA target galaxies.
+We do this because the identified companions are not included in the NSA catalog which we use to build the radial profiles for the galaxies.}
 
@@
 
-To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of isolated galaxies in the MaNGA survey.
+To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of \textbf{control} galaxies in the MaNGA survey.
 We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_{\rm p}$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
@@
 It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep[e.g.,][]{Noeske:2007}.
-We will compare our interacting galaxies with isolated galaxies of a similar stellar mass and redshift, to account for these other dependencies.
+We will compare our interacting galaxies with \textbf{control} galaxies of a similar stellar mass and redshift, to account for these other dependencies.
 To do this, we will use two different methods of pair - control comparison.
@@
 Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
-Note that although we carefully treat the two catalogs separately whenever possible, we find excellent agreement in the geometry parameters of isolated galaxies in both catalogs.
+Note that although we carefully treat the two catalogs separately whenever possible, we find excellent agreement in the geometry parameters of \textbf{control} galaxies in both catalogs.
 
@@
 The profiles' errors are the standard error of the mean of the data within each radius bin.
-We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.
+\textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
+\begin{equation}
+\sigma_{\overline{x}} = \frac{\sigma}{\sqrt{n}},
+\end{equation}
+where $\sigma$ is the standard deviation and $n$ is the sample size.} We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.
 
@@
 
-\begin{deluxetable*}{lcccccccccc}
-
-\tablestypesize{\small} \tablewidth{0pt}
+\begin{deluxetable*}{cccccccccc}
+%\tablestypesize{\small} \tablewidth{0pt}
 \tablecaption{Pair Catalog}
-\centering
-\tablehead{\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
+\tablehead{
+\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
 \colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
-\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}}
-
+\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
+}
+\decimals
 \startdata
-%\begin{tabular}{cccccccccc}
-%Plate & IFU & Sample & Sep_arc & Sep_kpc & d_logm & RAdeg & Decdeg & z & logm \\
-7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.0 & 10.8 \\
-7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.0 & 10.1 \\
-7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.0 & 9.2 \\
-7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.1 & 11.1 \\
-7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.1 & 10.8 \\
-8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.0 & 10.1 \\
-8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.0 & 10.8 \\
-8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.0 & 9.5 \\
-8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.0 & 10.3 \\
-8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.0 & 9.9 \\
-%\end{tabular}
-%\end{table*}
-
+7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
+7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
+7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
+7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
+7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
+8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
+8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
+8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
+8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
+8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
 \enddata

### 2020-12-22 maintex.tex
updated figures

@@
 \begin{abstract}
-We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 175 star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey.
+We compare the radial profiles of the specific star formation rate (sSFR) in a sample of \textbf{169} star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey.
 We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
@@
 In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy.
-We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair.
-The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.
+{\it We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair.
+The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.} \textbf{Our results indicate that merger induced gas-inflows are responsible for elevating the central sSFR in galaxy pairs.
+}
 \end{abstract}
@@
 \centering
-\includegraphics[width=\linewidth]{color-mag.pdf}
+\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
 \caption[]{Color-magnitude diagram for MaNGA galaxies.
@@
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-This give us a total of 175 close pairs.
+This give us a total of \textbf{169} close pairs.
 
@@
 \centering
-\includegraphics[width=\linewidth]{ssfr_comb.pdf}
+\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
 \caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
@@
 \centering
-\includegraphics[width=0.8\linewidth]{ssfr_mass.pdf}
+\includegraphics[width=0.8\linewidth]{fig/ssfr_mass.pdf}
 \caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
@@
 \centering
-\includegraphics[width=0.8\linewidth]{sep_hist.pdf}
+\includegraphics[width=0.8\linewidth]{fig/sep_hist.pdf}
 \caption[]{The projected separation distribution of the whole sample (blue) against the projected separation distribution for the highest mass galaxies, \logm\ $=$ 11.0$-$11.5 (Red). }
@@
 \centering
-\includegraphics[width=0.8\linewidth]{ssfr_dm.pdf}
+\includegraphics[width=0.8\linewidth]{fig/ssfr_dm.pdf}
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair.
@@
 We then take the median of the azimuthally averaged profiles of the tailored control sample.
-Finally, we obtain the $\Delta\log$sSFR profile for each of the 175 paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.
+Finally, we obtain the $\Delta\log$sSFR profile for each of the \textbf{169} paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.
 
@@
 \centering
-\includegraphics[width=0.8\linewidth]{ssfr_sep.pdf}
+\includegraphics[width=0.8\linewidth]{fig/ssfr_sep.pdf}
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by projected separation. }
@@
 \centering
-\includegraphics[width=3in]{prof_comp.pdf}
+\includegraphics[width=3in]{fig/prof_comp.pdf}
 \caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
@@
 \centering
-\includegraphics[width=3in]{nuc_sep.pdf}
+\includegraphics[width=3in]{fig/nuc_sep.pdf}
 \caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).

### 2020-12-23 maintex.tex
more text edits to sections 2-3

@@
 
+\subsection{\textbf{Emission Line Extraction}}\label{sec:spfit}
+
+\textbf{
+We use our own {\sc idl} based spectral fitting code, {\sc spfit}\footnote{\url{https://github.com/fuhaiastro/spfit}}, to model the spectra from the MaNGA datacubes.
+{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}.
+Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
+The code used the SSP templates from the MUISCAT library \citep{Vazdekis:2012} which allows a spectral range of 3465$-$9469 \AA\ with a uniform spectral resolution of FWHM $=$ 2.5 \AA.
+}
+
+\textbf{
+For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
+}
+
+MaNGA DAP \citep{Belfiore:2019}, Pipe3D \citep{Sanchez:2016a, Sanchez:2016b}
+
+\subsection{\textbf{Selecting Star Forming Galaxies}}\label{sec:sf}
+
 We classify galaxies in this survey as star forming galaxies by selecting galaxies in the blue cloud on the color-magnitude diagram (CMD).
@@
 Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog.
-We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
-Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers.
+We further apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
+\textbf{This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in the centers of our galaxies.} Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers.
 Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.
+\textbf{}
 
@@
 To select paired galaxies out of our object catalog, we inspect the spectra of each object.
-We use our own {\sc idl} based spectral fitting code, {\sc spfit}, to model the spectra from the MaNGA datacubes.
-{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}.
-Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
 
@@
 
-For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
-
-We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
+We correct the emission lines extracted by {\sc spfit} for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
 The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.
+\textbf{To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line.}
 
@@
 \label{fig:ssfr_prof}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering
+\includegraphics[width=\linewidth]{fig/ewha_comb.pdf}
+\caption[]{Same as Figure \ref{fig:ssfr_prof} but for EW(H$\alpha$). }
+\label{fig:ewha_prof}
 \end{figure*}
@@
 \enddata
+\tablecomments{
+(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) stellar mass.
+\\ \\
+(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
+}
 \end{deluxetable*}

### 2020-12-23 maintex.tex
more text revisions

@@
 The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
-\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).} While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).
+\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).} {\it While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).
+}
 
@@
 The number of paired galaxies in each mass range is given in the legend in parentheses.
-In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown.
+The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) \textbf{extracted from a 0.5\reff\ aperture}.
 The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
@@
 \end{equation}
-where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.
-In the sample, the MaNGA target is not always the more massive component of the pair.
-We split the sample into two groups based on their mass ratios; primary companions in which the MaNGA target is the more massive galaxy and secondary companions in which the MaNGA target is the less massive galaxy.
+where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of \textbf{its identified} companion galaxy.
+\textbf{We not only use the mass ratio to study how a major merger behaves differently from a minor merger but also to study how the more massive galaxy of a pair behaves differently from the less massive galaxy of the pair.
+We expect that either component of a similar mass pair will behave in a similar fashion; however, in a minor merger the large central galaxy may not respond to the merger event in the same way than its companion dwarf galaxy.
+The two different scenarios can be differentiated with our definition of the mass ratio; when the MaNGA target is the more massive companion of the pair, its mass ratio is positive and when MaNGA target is the less massive companion of pair the mass ratio is negative.}
+
+%{\it In the sample, the MaNGA target is not always the more massive component of the pair.
+We split the sample into two groups based on their mass ratios; primary companions in which the MaNGA target is the more massive galaxy and secondary companions in which the MaNGA target is the less massive galaxy.}
 
@@
 
-In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log($M$)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log($M$)$|$ $>$ 0.5.
+In \textbf{left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log($M$)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log($M$)$|$ $>$ 0.5.
 Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex over minor mergers.
@@
 
-In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
+In \textbf{right panel} of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
 These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
@@
 Figure \ref{fig:ssfr_sep} shows the profile and the central level of sSFR enhancement as a function of the projected separation ($r_{\rm p}$) from our MaNGA data.
-The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations.
+\textbf{The $\Delta$log(sSFR) profiles show only a weak dependency on the projected separation.
+The pairs below a separation of 12.5 kpc have a sSFR enhancement which is roughly 0.1 dex above pairs with wider separations within 0.2 \reff.
+}
+
+%{\it The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations.
 The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.1$-$0.15 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.
+}
 

### 2021-01-07 maintex.tex
updated SPFIT seciton

@@
 
-MaNGA DAP \citep{Belfiore:2019}, Pipe3D \citep{Sanchez:2016a, Sanchez:2016b}
+\textbf{
+The are a few differences between {\sc SPFIT} and the previous spectral fitting codes designed for the MaNGA project; the MaNGA {\sc DAP} \citep{Belfiore:2019} and {\sc Pipe3D} \citep{Sanchez:2016a, Sanchez:2016b}.
+{\sc SPFIT} re-bins the MaNGA datacubes into 1\arcsec $\times$ 1\arcsec\ pixels to remove the covariances between neighboring pixels while the {\sc DAP} and {\sc Pipe3D} leaves the data in its original 0.5\arcsec $\times$ 0.5\arcsec\ format.
+Each code uses a slightly different SSP library.
+The {\sc DAP} uses the MILES-HC (Hierarchically Clustered MILES templates) library \citep{Westfall:2019}, {\sc PIPE3D} library uses the GSD156 library \citep{Cid-Fernandes:2013} which is built from the GRANADA \citep{Martins:2005} and MILES \citep{Sanchez-Blazquez:2006} libraries, and {\sc SPFIT} uses the MIUSCAT library which is the combination of the MILES, CaT \citep{Cenarro:2001}, and Indo-U.S.
+stellar libraries \citep{Valdes:2004}.
+Both {\sc SPFIT} and the {\DAP} simultaneously fits emission lines and the stellar continuum while {\sc PIPE3D} only fits the emission lines.
+}
 
@@
 \includegraphics[width=3in]{fig/nuc_sep.pdf}
-\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
-(\textbf{Bottom}) $\Delta$log(sSFR) over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).}
+\caption[]{(\textbf{Top}) $\Delta$log(SFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
+(\textbf{Bottom}) $\Delta$log(sSFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).}
 \label{fig:nuc_sep}

### 2021-01-09 maintex.tex
updated sections 2-3

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
-\caption[]{Color-magnitude diagram for MaNGA galaxies.
+\caption[]{(\textbf{Top}) Color-magnitude diagram for MaNGA galaxies.
 The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
@@
 From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
-The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
+The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.
+(\textbf{Bottom}) BPT diagram for the MaNGA galaxies.
+}
 \label{fig:cmd}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 To select paired galaxies out of our object catalog, we inspect the spectra of each object.
-
 The spectra of the identified objects is extracted through a 1\arcsec\ circular aperture and fitted assuming the MaNGA target's redshift and then manually sorted into the following categories: ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects.
@@
 \subsection{Specific Star Formation Rate}
-
-We correct the emission lines extracted by {\sc spfit} for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
+\textbf{We calculate the star formation rates in the pair and control galaxies with the emission lines extracted with our spectra fitting code, {\sc SPFIT} (described in Section \ref{sec:spfit}).} We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
 The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.
-\textbf{To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line.}
 
@@
 
-Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the stellar mass in the same spaxel, giving us the specific star formation rate (sSFR):
+Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the stellar mass in the same spaxel, $M$, giving us the specific star formation rate (sSFR):
 \begin{equation}
@@
 Utilizing sSFR, instead of SFR, allows us to compare regions of high mass surface density to regions of low mass surface density.
+
+\textbf{
+We check our measurement of the specific star formation rate with the equivalent width of the H$\alpha$ line, \ewha, since it is a known proxy for the sSFR.
+This is useful as the sSFR is dependent on {\sc SPFIT}'s measurement of the stellar mass while \ewha\ is an observable.
+As we will show in Section \ref{sec:results}, the \ewha\ is consistent with our measurement of the sSFR.
+}
+
+\textbf{
+The signal to noise ratio of the data will fall with wide galactocentric radii.
+MaNGA is designed to cover 1.5 \reff\ for galaxies in the Primary sample and 2.5 \reff\ in the secondary sample.
+These are not hard limits, data will exist beyond these radii, especially along the semi-minor axis of galaxy; however, the data beyond these limits may be unreliable due to low signal to noise.
+To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line.
+}
 
@@
 The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff.
-\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).} {\it While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).
-}
+Within each radius bin we take the median of the specific star formation rate.
 
-Within each radius bin we take the median of the specific star formation rate.
-The profiles' errors are the standard error of the mean of the data within each radius bin.
-\textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
+The profiles' errors are the standard error of the mean of the data within each radius bin. \textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
 \begin{equation}
@@
 where $\sigma$ is the standard deviation and $n$ is the sample size.} We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.
+
+\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).} {\it While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).}
 

### 2021-01-16 maintex.tex
updated Results section

@@
 \includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
-\caption[]{(\textbf{Top}) Color-magnitude diagram for MaNGA galaxies.
+\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies.
 The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
@@
 The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.
-(\textbf{Bottom}) BPT diagram for the MaNGA galaxies.
+(\textbf{Center}) BPT diagram for the MaNGA galaxies.
+(\textbf{Right}) The WHAN diagram for the MaNGA galaxies.
 }
@@
 Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog.
-We further apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
-\textbf{This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in the centers of our galaxies.} Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers.
+
+We use the BPT diagnostic \citep{Baldwin:1981}, shown in the center of Figure \ref{fig:cmd}, to remove galaxies with possible AGN in their centers.
 Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.
-\textbf{}
+
+\textbf{Based on the WHAN diagram, shown in the right panel of Figure \ref{fig:cmd}, we apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.}
 
@@
 \subsection{Inside-IFU Sample}\label{sec:inside}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{deluxetable*}{cccccccccc}
+%\tablestypesize{\small} \tablewidth{0pt}
+\tablecaption{Pair Catalog}
+\tablehead{
+\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
+\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
+\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
+}
+\decimals
+\startdata
+7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
+7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
+7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
+7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
+7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
+8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
+8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
+8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
+8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
+8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
+\enddata
+\tablecomments{
+(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) stellar mass.
+\\ \\
+(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
+}
+\label{tab:pair}
+\end{deluxetable*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-This give us a total of \textbf{169} close pairs.
+This gives us a total of \textbf{169} close pairs, shown in Table \ref{tab:pair}.
 
@@
 We select a subsample of 20 control galaxies for each paired galaxy.
-We first select all of the control galaxies which are within a 0.1~dex stellar mass limit and within the same MaNGA subsample (e.g.
+We first select all of the control galaxies which are within 0.1 dex in stellar mass limit, \textbf{0.025 in redshift, 20\% \reff}, and within the same MaNGA subsample (e.g.
 Primary or Secondary) as the paired galaxy.
-Since the MaNGA sample has a tight distribution in stellar mass and redshift, the stellar mass and MaNGA subsample restriction effectively sets a $\Delta z$ $\lesssim$ $\sim$0.025 redshift tolerance.
 With these requirements, most paired galaxies will find between 20$-$100 control galaxies.
@@
 \begin{equation}\label{eq:sfr}
-\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}.
+\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1} kpc^{-2}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}.
 \end{equation}
@@
 To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line.
+}
+
+\textbf{
+We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}.
+This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
 }
@@
 
+\textbf{ 
+We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}.
+We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc SPFIT}'s measurement of the sSFR.
+We do see that the pair-control offsets are lightly suppressed using the \ewha.
+}
+
 This method of stacking sSFR profiles by a single parameter (stellar mass) has the advantage of simplicity and large statistical samples.
@@
 The horizontal, dashed black line represents the median central enhancement of the pair sample.
-Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
+Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.
+}
 \label{fig:ssfr_mass}
@@
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair.
+The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the plain mass ratio.
+Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from less massive companions from pairs.
 The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
@@
 
-To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff.
-We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
+\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff.
+The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels.
+Once this is done we calculate the $\Delta$log(sSFR) using the same method as the $\Delta$log(sSFR) radial profiles are made.
+The central sSFR of a paired galaxy is compared against the sSFR of a set of 20 similar control galaxies, the same set of controls which were used for the $\Delta$log(sSFR) profiles, by taking the difference between the central sSFR of the paired galaxy and the median sSFR of the 20 selected control galaxies.
+We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.}
 
-The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex.
-Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.15$-$0.25 dex higher than the sample average.
+The difference profiles are shown to be centrally enhanced by $\sim$0.3 $\pm$ 0.1 dex.
+Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.10$-$0.15 dex higher than the sample average.
 
 The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex.
-The paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, feature enhanced sSFR in their disks of 0.1$-$0.2 dex.
 As we will show in the next section, \S~\ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.
 
-To understand why these high mass galaxies behave differently from the rest of the sample, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.
-The whole sample has a v-shaped separation distribution.
+\textbf{To understand why the profiles of high mass galaxies behave differently from the rest of the sample in Figures \ref{fig:ssfr_prof}, \ref{fig:ewha_prof}, and \ref{fig:ssfr_mass}, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.} The whole sample has a v-shaped separation distribution.
 This is the result of the combination of the two different samples, the inside-IFU and outside-IFU samples.
@@
 The separation distribution of the inside-IFU sample is limited by MaNGA's IFU sizes and the sample's redshift distribution; the maximum possible projected separation for a MaNGA target with $z$ $=$ 0.15 and a 127 spaxel IFU is about 40 kpc.
+
 The highest mass galaxies in the sample are at closer projected separations in comparison to the rest of the sample with 70\% of the highest mass galaxies being within 20 kpc.
+\textbf{ The cause of this may be due to clustering effects where high mass galaxies tend to be at the centers of galaxy clusters \citep{Cooray:2002, Zehavi:2002}}.
 As we will show in \S~\ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.
@@
 The mass ratio here is defined as, 
-\begin{equation}
+\begin{equation}\label{eq:dm}
 \Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
@@
 where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of \textbf{its identified} companion galaxy.
+\textbf{In the inside-IFU sample, we have stellar masses for the MaNGA target galaxy but not the other identified pairs.
+Because of this, we leave the inside-IFU companions out of this analysis.}
+
+\textbf{In the top left of Figure \ref{fig:ssfr_dm}, we split difference profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0.
+Here, $|\Delta$log(M)$|$ $\le$ 0.5, represents equal mass major mergers while $|\Delta$log(M)$|$ $\ge$ 0.5 represents minor mergers.
+We see that there is a clear preference for pairs in major merger to have higher sSFR enhancements in their centers, $\sim$0.4 dex, while minor mergers show a weaker sSFR enhancement of $\sim$0.0$-$0.2 dex.
+The effect can be seen more clearly with the data extracted from the central 0.5 \reff\ in the top right panel.
+Here the $\Delta$log(sSFR) falls linearly with wider mass ratios, reaching zero enhancement to the sSFR at $|\Delta$log(M)$|$ $=$ 1.5$-$1.75.}
+
 \textbf{We not only use the mass ratio to study how a major merger behaves differently from a minor merger but also to study how the more massive galaxy of a pair behaves differently from the less massive galaxy of the pair.
-We expect that either component of a similar mass pair will behave in a similar fashion; however, in a minor merger the large central galaxy may not respond to the merger event in the same way than its companion dwarf galaxy.
-The two different scenarios can be differentiated with our definition of the mass ratio; when the MaNGA target is the more massive companion of the pair, its mass ratio is positive and when MaNGA target is the less massive companion of pair the mass ratio is negative.}
+We expect that either component of a similar mass pair will behave in a similar fashion; however, in a minor merger the large central galaxy may not respond to the merger event in the same way as its less massive companion.
+The two different scenarios can be differentiated with our definition of the mass ratio in equation \ref{eq:dm}; when the MaNGA target is the more massive companion of the pair, its mass ratio is positive and when MaNGA target is the less massive companion of pair the mass ratio is negative.
+To distinguish between these scenarios, we refer to the more massive galaxy of a pair as the primary companion and the less massive galaxy of a pair the secondary companion.}
 
-%{\it In the sample, the MaNGA target is not always the more massive component of the pair.
-We split the sample into two groups based on their mass ratios; primary companions in which the MaNGA target is the more massive galaxy and secondary companions in which the MaNGA target is the less massive galaxy.}
+In \textbf{bottom left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins.
+\textbf{The primary companions are the pairs with $\Delta$log(M) $\ge$ 0.0 and the secondary companions are the pairs with $\Delta$log(M) $\le$ 0.0.
+When splitting the mass ratio like this we see that major mergers still higher levels of sSFR enhancement in comparison to minor mergers; however, we also see that the less massive companion of the pair sees a higher $\Delta$log(sSFR) in comparison to the more massive companion of a pair.
+In major mergers, the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions and in minor mergers the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions.}
 
-For the outside-IFU pair sample we use the stellar masses enclosed by the $r$-band elliptical Petrosian apertures from the NSA catalog.
-The inside-IFU pair sample is left out of this analysis, because most of the secondary companions in these pairs are missing in the NSA catalog and the \citet{Simard:2011} catalog.
-
-In \textbf{left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log($M$)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log($M$)$|$ $>$ 0.5.
-Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex over minor mergers.
-Secondary companions also feature slightly higher levels of enhancement in their centers than primary companions at the same mass ratios by $\sim$0.1 dex.
-
-The sSFR offsets in the outskirts of the galaxy pairs show a dependence on the mass ratio.
-Primary companions show a zero to positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts.
-Secondary companions feature a suppression to the sSFR in their outskirts of about 0.1$-$0.4 dex.
-
-In \textbf{right panel} of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
+In \textbf{bottom right panel} of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
 These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
@@
 We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.
+
+\textbf{We also see that the $\Delta$log(sSFR) in the outskirts ($R$ $>$ 1.5 \reff) of the pairs have a dependence on the mass ratio in the bottom right of Figure \ref{fig:ssfr_dm}.
+Primary companions show a zero to positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts, while secondary companions feature a suppression to the sSFR in their outskirts of about 0.0$-$0.4 dex.
+Again we note that only 37\% of the MaNGA sample is designed to extend beyond 1.5 \reff; however, a similar result has been observed in the hydrodynamical simulations of \citet{Moreno:2015}.
+}
 
@@
 Our data shows that the sSFR enhancement persists out to at least $r_{\rm p} = 50$~kpc, which is the limit of our pair selection.
-In the next section, we will compare our results with those from previous studies.
+
+\textbf{There is also v-shaped dip in the data at 30$-$40 kpc.
+The dip is partially due to the mixing of the inside-IFU and outside-IFU samples.
+If we mask out the inside-IFU pairs, the $\Delta$log(sSFR) over projected separation curve becomes smoother; however, a weak dip still exist at 30$-$40 kpc.
+In the next section, we will compare our results with those from previous studies.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison with Previous Work}\label{sec:disc}
+\section{Discussion}\label{sec:disc}
 
-\subsection{Difference Radial Profiles}
+\section{Physical Scenario}
+
+\subsection{Comparison with Previous Work}
+
+\subsubsection{Radial Difference Profiles}
 
@@
 \includegraphics[width=3in]{fig/prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) (\textbf{Top}) and $\Delta$log(SFR) (\textbf{Bottom}) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
 \label{fig:prof_comp}
@@
 
-In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works.
-The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 dex higher than our sample of paired galaxies.
-The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies.
-The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 \reff\ of $\sim$0.1$-$0.15 dex.
-The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
+In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile \textbf{and $\Delta$log(SFR)} as a function of galactocentric radius between our work and previous works.
+\textbf{\citet{Thorp:2019} studies a sample of 36 post-mergers from the MaNGA sample.
+The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(SFR) $=$ 0.40$-$0.45, roughly 0.2 dex higher than our paired galaxies.
+Between 0.4$-$1.0\reff\ the post-merger galaxies and our pairs are in closer agreement, being 0.05$-$0.1 dex higher than our paired galaxies.
+Beyond 1.0 \reff\ the post-merger galaxies have a higher $\Delta$log(SFR) by about 0.1$-$0.2 dex.} The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
 
-The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughly $\sim$0.1$-$0.2 dex higher than our sample.
-Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
-The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of post-merger galaxies while our sample has no post-merger galaxies.
-These post-merger galaxies are predicted to have higher levels of star formation over other paired galaxies due to a second larger burst of star formation which is triggered as the merging galaxies coalesce and may be able to increase the sample's average sSFR enhancement.
+\textbf{\citet{Pan:2019} studies a set of 205 paired galaxies in the MaNGA sample, focusing on the sSFR enhancement as a function of the merger interaction stage.
+The $\Delta$log(sSFR) profiles of the galaxies pairs in \citet{Pan:2019} are $\sim$0.10$-$0.15 dex above the profiles in our sample.} Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+
+The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of \textbf{96 pairs which are too close to be separately de-blended by SDSS, 82 of which are post-merger galaxies.
+\citet{Pan:2019} shows that pairs with morphological distortions show higher $\Delta$log(SFR) when compared to pairs without morphological distortions.
+Further, \citet{Thorp:2019} showed that post-merger galaxies have $\Delta$log(SFR) profiles which are higher than our sample's profiles.
+From this, infer that these 96 morphologically identified close pairs and post-mergers are the primary reason why the $\Delta$log(sSFR) profile from \citet{Pan:2019} is higher than our profile.
+}
 
@@
 While in this work we find that $\Delta$log(sSFR) has essentially no dependence on the stellar mass of the galaxy, \citet{Li:2008} found that lower mass galaxies experience greater levels of enhancement than higher mass galaxies.
-Galaxies in the mass range \logm\ $=$ 9.72 were shown to experience an enhancement $\sim$0.4 dex higher than galaxies in the mass range \logm\ $=$ 10.6.
+Galaxies in the mass range \logm\ $\ge$ 9.72 were shown to experience an enhancement $\sim$0.4 dex higher than galaxies in the mass range \logm\ $\ge$ 10.6.
+
 The source of the difference is unclear; between our works we utilize different methods for determining the sSFR enhancement in galaxy pairs.
@@
 \caption[]{(\textbf{Top}) $\Delta$log(SFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
-(\textbf{Bottom}) $\Delta$log(sSFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).}
+(\textbf{Bottom}) $\Delta$log(sSFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
+
+{\it mention robust statistics}}
 \label{fig:nuc_sep}
@@
 
-\appendix
-
-\begin{deluxetable*}{cccccccccc}
-%\tablestypesize{\small} \tablewidth{0pt}
-\tablecaption{Pair Catalog}
-\tablehead{
-\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
-\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
-\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
-}
-\decimals
-\startdata
-7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
-7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
-7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
-7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
-7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
-8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
-8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
-8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
-8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
-8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
-\enddata
-\tablecomments{
-(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) stellar mass.
-\\ \\
-(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
-}
-\end{deluxetable*}
+%\appendix
 

### 2021-01-20 maintex.tex
edits to the discussion

@@
 In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy.
-{\it We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair.
-The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.} \textbf{Our results indicate that merger induced gas-inflows are responsible for elevating the central sSFR in galaxy pairs.
+We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair.
+The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.
+\textbf{Our results are consistent with the idea that merger induced gas-inflows are capable of triggering elevated star formation in paired galaxies.
 }
@@
 \caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies.
-The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic).
-From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud.
-The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.
-(\textbf{Center}) BPT diagram for the MaNGA galaxies.
-(\textbf{Right}) The WHAN diagram for the MaNGA galaxies.
-}
+\textbf{(\textbf{Center}) BPT diagram for the MaNGA galaxies.
+(\textbf{Right}) The WHAN diagram for the MaNGA galaxies.} The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic).}
 \label{fig:cmd}
@@
 \textbf{
-We use our own {\sc idl} based spectral fitting code, {\sc spfit}\footnote{\url{https://github.com/fuhaiastro/spfit}}, to model the spectra from the MaNGA datacubes.
-{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}.
+We use our own {\sc idl} based spectral fitting code, {\sc spfit}\footnote{\url{https://github.com/fuhaiastro/spfit}}, to model the spectra from the MaNGA datacubes \citepalias{Fu:2018}.
+{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm.
 Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
-The code used the SSP templates from the MUISCAT library \citep{Vazdekis:2012} which allows a spectral range of 3465$-$9469 \AA\ with a uniform spectral resolution of FWHM $=$ 2.5 \AA.
 }
@@
 \textbf{
-For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
+{\sc SPFIT} re-bins the MaNGA datacubes into 1\arcsec $\times$ 1\arcsec\ pixels to remove the covariances between neighboring pixels.
+This is in contrast with previous spectral fitting codes designed for the MaNGA survey like the MaNGA {\sc DAP} \citep{Belfiore:2019} and {\sc PIPE3D} \citep{Sanchez:2016a, Sanchez:2016b} which uses the original 0.5\arcsec $\times$ 0.5\arcsec\ grid.
+Within each 1\arcsec$\times$1\arcsec\ pixel, we use {\sc spfit} to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
 }
@@
 \textbf{
-The are a few differences between {\sc SPFIT} and the previous spectral fitting codes designed for the MaNGA project; the MaNGA {\sc DAP} \citep{Belfiore:2019} and {\sc Pipe3D} \citep{Sanchez:2016a, Sanchez:2016b}.
-{\sc SPFIT} re-bins the MaNGA datacubes into 1\arcsec $\times$ 1\arcsec\ pixels to remove the covariances between neighboring pixels while the {\sc DAP} and {\sc Pipe3D} leaves the data in its original 0.5\arcsec $\times$ 0.5\arcsec\ format.
-Each code uses a slightly different SSP library.
-The {\sc DAP} uses the MILES-HC (Hierarchically Clustered MILES templates) library \citep{Westfall:2019}, {\sc PIPE3D} library uses the GSD156 library \citep{Cid-Fernandes:2013} which is built from the GRANADA \citep{Martins:2005} and MILES \citep{Sanchez-Blazquez:2006} libraries, and {\sc SPFIT} uses the MIUSCAT library which is the combination of the MILES, CaT \citep{Cenarro:2001}, and Indo-U.S.
+The code uses the SSP templates from the MUISCAT library \citep{Vazdekis:2012} which allows a spectral range of 3465$-$9469 \AA\ with a uniform spectral resolution of FWHM $=$ 2.5 \AA.
+This MIUSCAT library is the combination of the MILES \citep{Sanchez-Blazquez:2006}, CaT \citep{Cenarro:2001}, and Indo-U.S.
 stellar libraries \citep{Valdes:2004}.
-Both {\sc SPFIT} and the {\DAP} simultaneously fits emission lines and the stellar continuum while {\sc PIPE3D} only fits the emission lines.
+The MaNGA {\sc DAP} uses the MILES-HC (Hierarchically Clustered MILES templates) library \citep{Westfall:2019} and {\sc PIPE3D} library uses the GSD156 library \citep{Cid-Fernandes:2013} which is built from the GRANADA \citep{Martins:2005} and MILES libraries.
 }
 
-\subsection{\textbf{Selecting Star Forming Galaxies}}\label{sec:sf}
+\subsection{Selecting Star Forming Galaxies}\label{sec:sf}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{deluxetable*}{cccccccccc}
+%\begin{deluxetable*}{cccccccccc}
 %\tablestypesize{\small} \tablewidth{0pt}
-\tablecaption{Pair Catalog}
-\tablehead{
-\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
-\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
-\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
-}
-\decimals
-\startdata
-7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
-7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
-7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
-7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
-7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
-8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
-8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
-8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
-8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
-8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
-\enddata
-\tablecomments{
-(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) stellar mass.
-\\ \\
-(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
-}
-\label{tab:pair}
-\end{deluxetable*}
+%\tablecaption{Pair Catalog}
+%\tablehead{
+%\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
+%\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
+%\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
+%}
+%\decimals
+%\startdata
+%7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
+%7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
+%7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
+%7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
+%7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
+%8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
+%8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
+%8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
+%8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
+%8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
+%\enddata
+%\tablecomments{
+%(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10)
+%stellar mass. \\ \\
+%(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
+%}
+%\label{tab:pair}
+%\end{deluxetable*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{table1.tex}
 
@@
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-This gives us a total of \textbf{169} close pairs, shown in Table \ref{tab:pair}.
+This gives us a total of \textbf{169} close pairs, shown in Table \ref{tab:coords}.
 
@@
 A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times.
-In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.
-Only 5 of the paired galaxies required an extra iteration to find 20 controls.
+In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex, the redshift by 0.025, and the \reff\ by 5\% until at least 20 control galaxies are found.
+\textbf{39 pairs required 1 extra iteration, 15 pairs required 2 extra iterations, 5 pairs required 3 extra iterations, and 2 pairs required 4 extra iterations.
+}
 
@@
 \textbf{
-The signal to noise ratio of the data will fall with wide galactocentric radii.
+The signal to noise ratio of the data will decrease with wide galactocentric radii.
 MaNGA is designed to cover 1.5 \reff\ for galaxies in the Primary sample and 2.5 \reff\ in the secondary sample.
@@
 To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line.
-}
-
-\textbf{
-We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}.
-This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
+We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}, which effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
 }
@@
 Within each radius bin we take the median of the specific star formation rate.
+We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.
 
-The profiles' errors are the standard error of the mean of the data within each radius bin. \textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
-\begin{equation}
-\sigma_{\overline{x}} = \frac{\sigma}{\sqrt{n}},
-\end{equation}
-where $\sigma$ is the standard deviation and $n$ is the sample size.} We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.
-
-\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).} {\it While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).}
+\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).
+This means that there will be fewer selected spaxel beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff.
+We decide to still extend our radial profiles out to 2.5 \reff, but emphasize that the data beyond 1.5 \reff\ is lower in quality.
+}
 
@@
 The error associated with the ``stacked'' profile is the standard error of mean of the data at each radius bin.
+\textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
+\begin{equation}
+\sigma_{\overline{x}} = \frac{\sigma}{\sqrt{n}},
+\end{equation}
+where $\sigma$ is the standard deviation and $n$ is the sample size.}
+
 We show these stacked profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}.
@@
 This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}).
-Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.3$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff.
-In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex.
+Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.3$\pm$0.1~dex, which gradually falls to zero around $\sim$1.5 \reff.
+In the outskirts of the pairs beyond 1.5 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex.
 All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile.
@@
 We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc SPFIT}'s measurement of the sSFR.
-We do see that the pair-control offsets are lightly suppressed using the \ewha.
+We do see that the pair-control offsets are lightly suppressed using the \ewha\ as the $\Delta$log(\ewha) is only enhanced by 0.25 dex where the $\Delta$log(sSFR) was enhanced by 0.30 dex.
 }
@@
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair.
-The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the plain mass ratio.
+The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the mass ratio without taking the absolute value.
 Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from less massive companions from pairs.
@@
 
-\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff.
+\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample within the central 0.5~\reff.
 The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels.
@@
 
-The difference profiles are shown to be centrally enhanced by $\sim$0.3 $\pm$ 0.1 dex.
-Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.10$-$0.15 dex higher than the sample average.
+The difference profiles are shown to be centrally enhanced by $\sim$0.20$-$0.25 $\pm$ 0.1 dex.
+Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.4 dex higher than the sample average.
 
-The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex.
-As we will show in the next section, \S~\ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.
+The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.0$-$0.1 dex.
+\textbf{Within individual mass ranges, there are some mass ranges which feature large enhancements to the sSFR at large radii while other mass ranges show a strong suppression to the sSFR.
+There appears to be no dependence on the stellar mass of the pair but, as we will show in the next section, \S~\ref{sec:dm}, these offsets at large radii may be dependent on the mass ratio between the galaxy pairs.}
 
@@
 Here, $|\Delta$log(M)$|$ $\le$ 0.5, represents equal mass major mergers while $|\Delta$log(M)$|$ $\ge$ 0.5 represents minor mergers.
-We see that there is a clear preference for pairs in major merger to have higher sSFR enhancements in their centers, $\sim$0.4 dex, while minor mergers show a weaker sSFR enhancement of $\sim$0.0$-$0.2 dex.
+We see that there is a clear preference for pairs in major merger to have higher sSFR enhancements in their centers, $\sim$0.3$-$0.4 dex, while minor mergers show a weaker sSFR enhancement of $\sim$0.0$-$0.2 dex.
 The effect can be seen more clearly with the data extracted from the central 0.5 \reff\ in the top right panel.
@@
 When splitting the mass ratio like this we see that major mergers still higher levels of sSFR enhancement in comparison to minor mergers; however, we also see that the less massive companion of the pair sees a higher $\Delta$log(sSFR) in comparison to the more massive companion of a pair.
-In major mergers, the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions and in minor mergers the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions.}
+In major mergers, the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions and in minor mergers the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions.}
 
 In \textbf{bottom right panel} of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
-These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample.
-This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0.
-We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.
+These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.2 dex higher than the average central enhancement of the whole sample.
+\textbf{This enhancement falls with wider mass ratios with a different slope for primary and secondary companions.
+At $\Delta$log($M$) $=$ -1.0, the sSFR is enhanced by 0.2 dex while at $\Delta$log($M$) $=$ 1.0 the sSFR enhancement is zero.}
 
@@
 Second, we see that secondary companions show steeper enhancement profiles with higher levels of sSFR enhancement in their centers and stronger levels of sSFR suppression in their disks with respect to primary companions.
-It is interesting to note that the central enhancement to sSFR is dependent on both the mass ratio and the projected separation (which we will demonstrate in the next section) while the sSFR offsets in their outskirts primarily depends on whether the galaxy is the primary or secondary companion of the pair.
+\textbf{Finally, we see that primary companions feature sSFR enhancement at wide radii while secondary companions feature sSFR suppression at wide radii.}
 
@@
 \textbf{The $\Delta$log(sSFR) profiles show only a weak dependency on the projected separation.
-The pairs below a separation of 12.5 kpc have a sSFR enhancement which is roughly 0.1 dex above pairs with wider separations within 0.2 \reff.
+The pairs below a separation of 25 kpc have $\Delta$log(sSFR) profiles which lie $\sim$0.1 dex above the sample median while the profiles of the pairs beyond 25 kpc are $\sim$ 0.1 dex below the sample median.
 }
 
-%{\it The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations.
-The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.1$-$0.15 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.
-}
-
-This effect can be seen more clearly in the plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation.
+A dependence on the projected separation can be seen more clearly when looking at the data extracted from the inner 0.5 \reff.
 The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc.
-While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex.
-Within 20 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex.
+While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.15 dex.
+Within 10 kpc, the $\Delta$log(sSFR) enhancement jumps to $\sim$0.3 dex.
 Our data shows that the sSFR enhancement persists out to at least $r_{\rm p} = 50$~kpc, which is the limit of our pair selection.
-
-\textbf{There is also v-shaped dip in the data at 30$-$40 kpc.
-The dip is partially due to the mixing of the inside-IFU and outside-IFU samples.
-If we mask out the inside-IFU pairs, the $\Delta$log(sSFR) over projected separation curve becomes smoother; however, a weak dip still exist at 30$-$40 kpc.
-In the next section, we will compare our results with those from previous studies.}
 
@@
 \section{Discussion}\label{sec:disc}
-
-\section{Physical Scenario}
 
@@
 
-The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of \textbf{96 pairs which are too close to be separately de-blended by SDSS, 82 of which are post-merger galaxies.
-\citet{Pan:2019} shows that pairs with morphological distortions show higher $\Delta$log(SFR) when compared to pairs without morphological distortions.
+The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of \textbf{96 pairs which are too close to be separately de-blended by SDSS and instead were visually identified by their morphology.
+82 of these pairs are post-merger galaxies.
+\citet{Pan:2019} shows that pairs with morphological features show higher $\Delta$log(SFR) when compared to pairs without morphological distortions.
 Further, \citet{Thorp:2019} showed that post-merger galaxies have $\Delta$log(SFR) profiles which are higher than our sample's profiles.
-From this, infer that these 96 morphologically identified close pairs and post-mergers are the primary reason why the $\Delta$log(sSFR) profile from \citet{Pan:2019} is higher than our profile.
+From this, infer that the lower $\Delta$log(sSFR) seen in our sample is due to our sample's lack of post-merger galaxies.
 }
@@
 This is in good agreement with our work, we found that secondary companions show moderately higher levels of sSFR enhancement in their centers in comparison to primary companions at the same mass ratio.
-Further, the outskirts of the primary companions feature positive to zero enhancement to their sSFR while the secondary companions show a strong suppression to the sSFR in their outskirts.
+Further, the outskirts of our primary companions feature positive enhancement to their sSFR while the secondary companions show a strong suppression to the sSFR in their outskirts.
 
@@
 (\textbf{Bottom}) $\Delta$log(sSFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
-
-{\it mention robust statistics}}
+}
 \label{fig:nuc_sep}
@@
 The literature data is measured from single 1-1.5\arcsec-radius SDSS fibers \citep{Ellison:2008,Scudder:2012,Patton:2013,Bustamante:2020}.
-We find that our central SFR enhancements for closely separated pairs are higher than many of the previous studies, our sSFR enhancement is $\sim$0.2 dex higher than \citet{Scudder:2012} and $\sim$0.3 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}.
-The central enhancement to the sSFR for closely separated pairs in our sample is $\sim$0.1 dex higher than \citet{Patton:2013}.
-The sSFR enhancement function from \citet{Li:2008} follows closely to our own and remains $\sim$0.05 dex above our sample out to 40 kpc.
+We find that our central SFR enhancements for closely separated pairs are higher than many of the previous studies, our sSFR enhancement is $\sim$0.1 dex higher than \citet{Scudder:2012} and $\sim$0.2 dex higher than \citet{Ellison:2008} and \citet{Bustamante:2020}.
+The central enhancement to the sSFR for closely separated pairs in our sample is $\sim$0.05 dex lower than \citet{Patton:2013}.
+The sSFR enhancement function from \citet{Li:2008} is 0.05$-$0.10 dex above our sample at close separations.
 
@@
 \citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2D separation of $\sim$250 kpc.
-This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in Figure \ref{fig:nuc_sep} was extracted from a 0.5 \reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius.
+This enhancement is $\sim$0.05 dex lower than ours; however, our sSFR enhancement shown in Figure \ref{fig:nuc_sep} was extracted from a 0.5 \reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius.
 This means that our extraction radius is effectively twice a small and is more restricted to the central burst of star formation.
@@
 Our sample only covers projected separations within 50 kpc, while previous surveys cover out to 100$-$200 kpc.
-While our sample covers a smaller separation range, the $\Delta$log(SFR) of our sample at 50 kpc is roughly the same level as \citet{Scudder:2012} and \citet{Patton:2013} at the same projected separation.
+While our sample covers a smaller separation range, the $\Delta$log(SFR) of our sample at 50 kpc is roughly the same level as \citet{Ellison:2008} and \citet{Bustamante:2020} at the same projected separation.
 From this we see that our sSFR enhancement as a function of projected separation is consistent with with what has been found in previous works.
 
+\section{Physical Scenario}
+% General Merger-SFR enhancement
+\textbf{
+Our results are consistent with the idea that galaxy merger events trigger a burst of star formation in the centers of the paired galaxies.
+When two galaxy pairs undergo their first pericenter, the tidal torques exerted on the disks of interacting galaxies form barred structures.
+These barred structures funnel gases into the centers of the galaxies which triggers a burst of new star formation.
+Eventually, as the pairs separate from each other after the first pericenter, the burst of star formation begins to subside.
+This is shown in our work and many previous works in Figure \ref{fig:nuc_sep} where the sSFR enhancement is greatest for close separations and falls with wider separations.
+}
+
+ % Consant DelSSFR at different Masses
+\textbf{
+We also found that the $\Delta$log(sSFR) is independent of the stellar mass.
+This means that the merger event will produce the same amount of new stellar mass for low mass galaxies as it produces for high mass galaxies.
+This also means that the low mass galaxies will experience a greater change in total stellar mass before and after the merger event so the merger event will have a greater impact on the mass evolution of low mass galaxies as opposed to high mass galaxies.
+}
+
+% Mass ratio stuff
+\textbf{
+In agreement with previous works, we find that the strength of the central burst of merger induced star formation is dependent on the relative masses of the two galaxies.
+Equal mass galaxies see the strongest bursts of star formation while wide mass ratios see weaker bursts of star formation.
+We further find that the strength of the central burst of star formation differs between the primary and secondary companion of a pair where the less massive secondary companion features a higher level of sSFR enhancement in comparison to its higher mass primary companion.
+}
+
+\textbf{
+We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions.
+The primary companion features an enhancement to their sSFR at wide radii while the secondary companion features a suppression to their sSFR at wide radii.
+The reason for this is unclear; however, this means that the primary companions will experience mass growth across their disks while the secondary companions will see only see substantial mass growth in their centers which will result in more bulge dominated galaxies.
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\item Star formation is enhanced within the inner 1.0 \reff\ and it peaks at a level of 0.25 $\pm$ 0.1 dex (i.e., $\sim$2$\times$ faster star formation).
+\item Star formation is enhanced within the inner 1.0 \reff\ and it peaks at a level of 0.20$-$0.25 $\pm$ 0.1 dex (i.e., $\sim$2$\times$ faster star formation).
 On the other hand, the outskirts of the paired galaxies (\reff\ $=$ 1.0$-$2.5) show a moderate amount of suppression in sSFR at a level of $\sim$0.1 dex.
@@
 
-\item The level of central sSFR enhancement increases as the projected separation of the pair decreases.
+\item The level of central sSFR enhancement increases smaller projected separations.
 
 \item The level of central sSFR enhancement depends on the mass ratio of the galaxy pair.
-Galaxies with small mass ratios, $|\Delta$log($M$)$|$ $=$ 0.0$-$0.5, see an enhancement $\sim$0.1 dex higher than the average.
+Galaxies with small mass ratios, $|\Delta$log($M$)$|$ $=$ 0.0$-$0.5, see an enhancement $\sim$0.1$-$0.2 dex higher than the average.
 But the enhancement is still present in pairs with mass ratios as large as $|\Delta$log($M$)$|$ $=$ 1.0.
@@
 \item The merger-induced changes in sSFR also seem to differ between the more massive and the less massive member of a galaxy pair.
-At the same mass ratio, the less massive member in a galaxy pair shows a higher sSFR enhancement (by $\sim$0.1 dex) in comparison to the more massive member.
-And in the galactic outskirt (R/\reff\ $=$ 1.0$-$2.5), the more massive member shows a general enhancement in sSFR, while the less massive member features a general suppression.
+At the same mass ratio, the less massive member in a galaxy pair shows a higher sSFR enhancement (by $\sim$0.1$-$0.2 dex) in comparison to the more massive member.
+
+\item At large radii (R/\reff\ $>$ 1.5), the more massive companion of pairs show a enhancement to the sSFR while the less massive companion of pairs show a suppression to the sSFR.
 

### 2021-01-20 table1.tex
edits to the discussion

% ApJ Format
%\documentclass[apj,twocolumn]{emulateapj}
%\usepackage{apjfonts}

%\begin{document}

\begin{table}
\begin{center}
\caption{Close Galaxy Pairs and Multiples in MaNGA IFUs}
\label{tab:coords}
\begin{tabular}{lc ccc}
\hline
\hline
Plate-IFU & Index & R.A. (J2000) & Decl. (J2000) & Redshift \\
          &           & (deg)        & (deg)         &     \\
\hline
\input{table1_data.tex}
\hline
\end{tabular}
\end{center}
\tablecomments{
This table lists a total of 404 plate-IFUs that contain close galaxy pairs and multiples in the eighth MaNGA Product Launch (MPL-8). The second column lists the component index, where ``0'' indicates the primary target of the MaNGA observation. For each IFU, all components within $\pm$2000\,km~s$^{-1}$ of the primary are listed, sorted in ascending angular distance from the primary.\\
(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
}
\end{table}

%\end{document}

### 2021-01-21 maintex.tex
final edits

@@
 We also require that the galaxies are classified as star forming as described in \S~\ref{sec:data}.
-These requirements reduce our sample down to 87 star forming MaNGA targets with inside-IFU companions.
-While the companions to the inside-IFU MaNGA targets contained are within the MaNGA IFUs, we only use the MaNGA targets when building radial profiles.
-We leave out the identified companions from the analysis because the MaNGA targets are covered by the NSA catalog with geometries and total stellar masses while the companions are not covered by the NSA catalog.
+These requirements reduce our sample down to 54 star forming MaNGA targets with inside-IFU companions.
 \textbf{While we use the identified companions to select galaxy pairs, we only build radial profiles for the MaNGA target galaxies.
@@
 In cases where a MaNGA target has multiple viable companions galaxies, we chose the closest companion when measuring the pair's mass ratio and projected separation.
+\textbf{We show the whole 404 inside-IFU pair sample in Table \ref{tab:coords}.}
 
@@
 From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets.
-After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU.
+After restricting the sample to SFGs, we have another 115 MaNGA targets with paired galaxies outside of the IFU.
 MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample.
-This gives us a total of \textbf{169} close pairs, shown in Table \ref{tab:coords}.
 
@@
 We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_{\rm p}$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
-This gives us a control sample of 1888 star forming control galaxies.
+This gives us a control sample of 1830 star forming control galaxies.
 
 It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep[e.g.,][]{Noeske:2007}.
-We will compare our interacting galaxies with \textbf{control} galaxies of a similar stellar mass and redshift, to account for these other dependencies.
+We will compare our interacting galaxies with \textbf{control} galaxies of a similar stellar mass, redshift, and radial size, to account for these other dependencies.
 To do this, we will use two different methods of pair - control comparison.
@@
 We select a subsample of 20 control galaxies for each paired galaxy.
-We first select all of the control galaxies which are within 0.1 dex in stellar mass limit, \textbf{0.025 in redshift, 20\% \reff}, and within the same MaNGA subsample (e.g.
+We first select all of the control galaxies which are within 0.1 dex in stellar mass, \textbf{0.025 in redshift, 20\% in effective radii}, and within the same MaNGA subsample (e.g.
 Primary or Secondary) as the paired galaxy.
-With these requirements, most paired galaxies will find between 20$-$100 control galaxies.
+With these requirements, most paired galaxies will find between 20$-$60 control galaxies.
 Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20.
-A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times.
+A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 2$-$4 times.
 In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex, the redshift by 0.025, and the \reff\ by 5\% until at least 20 control galaxies are found.
@@
 \begin{equation}\label{eq:sfr}
-\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1} kpc^{-2}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}.
+\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}.
 \end{equation}
@@
 This is useful as the sSFR is dependent on {\sc SPFIT}'s measurement of the stellar mass while \ewha\ is an observable.
-As we will show in Section \ref{sec:results}, the \ewha\ is consistent with our measurement of the sSFR.
+As we will show in Section \ref{sec:results}, the radial profiles of \ewha\ is consistent with radial profiles of the sSFR.
 }
@@
 The two different scenarios can be differentiated with our definition of the mass ratio in equation \ref{eq:dm}; when the MaNGA target is the more massive companion of the pair, its mass ratio is positive and when MaNGA target is the less massive companion of pair the mass ratio is negative.
-To distinguish between these scenarios, we refer to the more massive galaxy of a pair as the primary companion and the less massive galaxy of a pair the secondary companion.}
+To distinguish between these scenarios, we refer to the more massive galaxy of a pair as the primary companion and the less massive galaxy of a pair as the secondary companion.}
 
@@
 Primary companions show a zero to positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts, while secondary companions feature a suppression to the sSFR in their outskirts of about 0.0$-$0.4 dex.
-Again we note that only 37\% of the MaNGA sample is designed to extend beyond 1.5 \reff; however, a similar result has been observed in the hydrodynamical simulations of \citet{Moreno:2015}.
+Again we note that only 37\% of the MaNGA sample is designed to extend beyond 1.5 \reff; however, a similar result has been observed in the hydrodynamical simulations of \citet{Moreno:2015} and \citet{Moreno:2020}.
 }
@@
 
+\section{Physical Scenario}
+% General Merger-SFR enhancement
+\textbf{
+Our results are consistent with the idea that galaxy merger events trigger a burst of star formation in the centers of the paired galaxies.
+In this model, when two galaxy pairs undergo their first pericenter, the tidal torques exerted on the disks of interacting galaxies form barred structures.
+These barred structures funnel gases into the centers of the galaxies which triggers a burst of new star formation.
+Eventually, as the pairs separate from each other after the first pericenter, the burst of star formation begins to subside.
+This is shown in our work and many previous works in Figure \ref{fig:nuc_sep} where the sSFR enhancement is greatest for close separations and falls with wider separations.
+}
+
+ % Consant DelSSFR at different Masses
+\textbf{
+We also found that the $\Delta$log(sSFR) is independent of the stellar mass.
+This means that the merger event will produce the same amount of new stellar mass for low mass galaxies as it produces for high mass galaxies.
+This also means that the low mass galaxies will experience a greater change in total stellar mass before and after the merger event so the merger event will have a greater impact on the mass evolution of low mass galaxies as opposed to high mass galaxies.
+}
+
+% Mass ratio stuff
+\textbf{
+We find that the strength of the central burst of merger induced star formation is dependent on the relative masses between the two galaxies.
+Equal mass galaxies see the strongest bursts of star formation while wide mass ratios see weaker bursts of star formation.
+We further find that the strength of the central burst of star formation differs between the primary and secondary companion of a pair where the less massive secondary companion features a higher level of sSFR enhancement in comparison to its higher mass primary companion.
+}
+
+\textbf{
+\citet{Moreno:2020} uses galaxy merger simulations to study the origin of the enhanced star formation in galaxy pairs, whether its an increase in the star formation efficiency, defined as the ratio between the SFR and the mass of cold-dense gas, or its an increase in the availability of cold dense gas.
+They find that the star formation in secondary galaxies is evenly split between being efficiency driven or fuel driven systems while primary galaxies are more likely to be fuel driven systems (71\%).
+\citet{Moreno:2020} also finds that that secondary galaxies feature higher levels of star formation enhancement in comparison to primary galaxies, which is in agreement with what we find in this work.
+This indicates that the reason why primary galaxies behave differently from secondary galaxies may be due to a difference in the physical mechanism which drives the enhanced star formation.
+}
+
+\textbf{
+We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions.
+The primary companion features an enhancement to their sSFR at wide radii while the secondary companion features a suppression to their sSFR at wide radii.
+The reason for this is unclear; however, this means that the primary companions will experience enhanced stellar mass growth across their disks while the secondary companions will see only see substantial stellar mass growth in their centers which will result in more bulge dominated galaxies.
+}
+
 \subsection{Comparison with Previous Work}
@@
 
-In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile \textbf{and $\Delta$log(SFR)} as a function of galactocentric radius between our work and previous works.
+In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile and $\Delta$log(SFR) as a function of galactocentric radius between our work and previous works.
 \textbf{\citet{Thorp:2019} studies a sample of 36 post-mergers from the MaNGA sample.
@@
 
-\section{Physical Scenario}
-% General Merger-SFR enhancement
-\textbf{
-Our results are consistent with the idea that galaxy merger events trigger a burst of star formation in the centers of the paired galaxies.
-When two galaxy pairs undergo their first pericenter, the tidal torques exerted on the disks of interacting galaxies form barred structures.
-These barred structures funnel gases into the centers of the galaxies which triggers a burst of new star formation.
-Eventually, as the pairs separate from each other after the first pericenter, the burst of star formation begins to subside.
-This is shown in our work and many previous works in Figure \ref{fig:nuc_sep} where the sSFR enhancement is greatest for close separations and falls with wider separations.
-}
-
- % Consant DelSSFR at different Masses
-\textbf{
-We also found that the $\Delta$log(sSFR) is independent of the stellar mass.
-This means that the merger event will produce the same amount of new stellar mass for low mass galaxies as it produces for high mass galaxies.
-This also means that the low mass galaxies will experience a greater change in total stellar mass before and after the merger event so the merger event will have a greater impact on the mass evolution of low mass galaxies as opposed to high mass galaxies.
-}
-
-% Mass ratio stuff
-\textbf{
-In agreement with previous works, we find that the strength of the central burst of merger induced star formation is dependent on the relative masses of the two galaxies.
-Equal mass galaxies see the strongest bursts of star formation while wide mass ratios see weaker bursts of star formation.
-We further find that the strength of the central burst of star formation differs between the primary and secondary companion of a pair where the less massive secondary companion features a higher level of sSFR enhancement in comparison to its higher mass primary companion.
-}
-
-\textbf{
-We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions.
-The primary companion features an enhancement to their sSFR at wide radii while the secondary companion features a suppression to their sSFR at wide radii.
-The reason for this is unclear; however, this means that the primary companions will experience mass growth across their disks while the secondary companions will see only see substantial mass growth in their centers which will result in more bulge dominated galaxies.
-}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We thank Cheng Li for our useful discussion on how the sSFR enhancement in galaxy pairs relates to their stellar mass and mass ratio.
+\textbf{We thank the anonymous referee for the useful comments and suggestions.} We also thank Cheng Li for our useful discussion on how the sSFR enhancement in galaxy pairs relates to their stellar mass and mass ratio.
 J.S.

### 2021-01-21 maintex.tex
merged table1 into maintex

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{deluxetable*}{cccccccccc}
-%\tablestypesize{\small} \tablewidth{0pt}
-%\tablecaption{Pair Catalog}
-%\tablehead{
-%\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
-%\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
-%\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
-%}
-%\decimals
-%\startdata
-%7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
-%7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
-%7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
-%7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
-%7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
-%8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
-%8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
-%8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
-%8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
-%8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
-%\enddata
-%\tablecomments{
-%(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10)
-%stellar mass. \\ \\
-%(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
-%}
-%\label{tab:pair}
-%\end{deluxetable*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{table1.tex}
+\begin{table}
+\begin{center}
+\caption{Close Galaxy Pairs and Multiples in MaNGA IFUs}
+\label{tab:coords}
+\begin{tabular}{lc ccc}
+\hline
+\hline
+Plate-IFU & Index & R.A. (J2000) & Decl. (J2000) & Redshift \\
+          &           & (deg)        & (deg)         &     \\
+\hline
+ 7443-12703&0&229.5255758&+42.7458538&0.04043\\
+    \nodata&1&229.5265348&+42.7440666&0.04079\\
+  7958-3701&0&257.5338400&+33.5989046&0.11015\\
+    \nodata&1&257.5344200&+33.5984600&0.10920\\
+    \nodata&2&257.5326566&+33.5979470&0.11031\\
+  7960-3701&0&257.0857469&+31.7469109&0.10819\\
+    \nodata&1&257.0850100&+31.7470300&0.10800\\
+  7960-3702&0&258.2893316&+31.5820375&0.02961\\
+    \nodata&1&258.2913540&+31.5812244&0.02943\\
+  7962-3702&0&259.0637432&+28.0140065&0.10725\\
+    \nodata&1&259.0639447&+28.0130439&0.10753\\
+\hline
+\end{tabular}
+\end{center}
+\tablecomments{
+This table lists a total of 404 plate-IFUs that contain close galaxy pairs and multiples in the eighth MaNGA Product Launch (MPL-8).
+The second column lists the component index, where ``0'' indicates the primary target of the MaNGA observation.
+For each IFU, all components within $\pm$2000\,km~s$^{-1}$ of the primary are listed, sorted in ascending angular distance from the primary.\\
+(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
+}
+\end{table}
 

### 2021-01-21 maintex.tex
spfit section rewritten

@@
 We compare the radial profiles of the specific star formation rate (sSFR) in a sample of \textbf{169} star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey.
-We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
+We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.3 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
 We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass.
@@
 The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.
-\textbf{Our results are consistent with the idea that merger induced gas-inflows are capable of triggering elevated star formation in paired galaxies.
+\textbf{Our results illustrate the complex tidal effects on star formation in closely paired galaxies.
 }
@@
 
-\subsection{\textbf{Emission Line Extraction}}\label{sec:spfit}
+\subsection{Spectral Fitting}\label{sec:spfit}
 
-\textbf{
-We use our own {\sc idl} based spectral fitting code, {\sc spfit}\footnote{\url{https://github.com/fuhaiastro/spfit}}, to model the spectra from the MaNGA datacubes \citepalias{Fu:2018}.
-{\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm.
-Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
-}
+{\bf 
+We use {\sc spfit} to model the MaNGA datacubes.
+The IDL package is publicly available\footnote{\url{https://github.com/fuhaiastro/spfit}} and was first used in our previous study of close galaxy pairs in MaNGA \citepalias{Fu:2018}.
+While data products from the MaNGA Data Analysis Pipeline \citep[DAP;][]{Belfiore:2019} and {\sc PIPE3D} \citep{Sanchez:2016a, Sanchez:2016b} are available, {\sc spfit} allows us to combine spectra inside a given aperture before fitting the combined spectrum.
+The feature alone made it better suited for this project.
+Additional features of {\sc spfit} include: (1) simultaneously fitting emission lines and stellar continuum, (2) coadding spaxels with either a Voronoi tessellation or arbitrary polygons while accounting for covariances, (3) modeling asymmetric emission lines, broad AGN emission lines, AGN continuum, and various dust-extinction laws, and (4) utilizing multi-threading when processing a large number of datacubes.
 
-\textbf{
-{\sc SPFIT} re-bins the MaNGA datacubes into 1\arcsec $\times$ 1\arcsec\ pixels to remove the covariances between neighboring pixels.
-This is in contrast with previous spectral fitting codes designed for the MaNGA survey like the MaNGA {\sc DAP} \citep{Belfiore:2019} and {\sc PIPE3D} \citep{Sanchez:2016a, Sanchez:2016b} which uses the original 0.5\arcsec $\times$ 0.5\arcsec\ grid.
-Within each 1\arcsec$\times$1\arcsec\ pixel, we use {\sc spfit} to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
-}
+Here we provide a brief description of the fitting procedure of {\sc spfit}.
+Except for broad-line AGN, {\sc spfit} models the observed spectrum as a superposition of emission lines and simple stellar populations (SSPs).
+The SSP library of {\sc miuscat} \citep{Vazdekis:2012} is matched to the MaNGA spectral resolution and is convolved with the line-of-sight velocity distribution (LOSVD).
+Both the LOSVD and the profile of the emission lines are parameterized as separate Gauss-Hermite series \citep{van-der-Marel:1993} to the fourth order.
 
-\textbf{
-The code uses the SSP templates from the MUISCAT library \citep{Vazdekis:2012} which allows a spectral range of 3465$-$9469 \AA\ with a uniform spectral resolution of FWHM $=$ 2.5 \AA.
-This MIUSCAT library is the combination of the MILES \citep{Sanchez-Blazquez:2006}, CaT \citep{Cenarro:2001}, and Indo-U.S.
-stellar libraries \citep{Valdes:2004}.
-The MaNGA {\sc DAP} uses the MILES-HC (Hierarchically Clustered MILES templates) library \citep{Westfall:2019} and {\sc PIPE3D} library uses the GSD156 library \citep{Cid-Fernandes:2013} which is built from the GRANADA \citep{Martins:2005} and MILES libraries.
+For model optimization, we prefer a fast algorithm like the Levenberg-Marquardt nonlinear least-squares minimization algorithm implemented in {\sc mpfit} \citep{Markwardt:2009}.
+But for complex spectral models like ours, the success of the fitting routine relies on a good initial ``guess'' solution, which can be provided by the penalized pixel-fitting method \citep[pPXF;][]{Cappellari:2017}.
+The pPXF method is robust because it solves the weights of the templates with a linear algorithm \citep{Lawson:1974} {\it independently} from solving the Gauss-Hermite LOSVD with a nonlinear optimizer ({\sc mpfit}).
+The {\sc spfit} package implements a three-stage fitting procedure: First, it masks out spectral regions around emission lines from the input spectrum and use pPXF on the masked spectrum with SSP-only templates to obtain the initial ``best-fit'' parameters of the stellar continuum; Then, it subtracts the best-fit stellar continuum model from the spectrum and use pPXF to fit the residual emission-line-only spectrum with Gaussian emission-line templates to obtain the initial ``best-fit'' parameters of the emission lines; Finally, it uses {\sc mpfit} on the full input spectrum with the two sets of ``best-fit'' parameters from pPXF to simultaneously fit all of the parameters describing the emission lines and the stellar continuum.
+Saved in the final FITS file are the best-fit parameters and their uncertainties, including emission-line fluxes, equivalent widths, and kinematics and luminosity-weighted stellar masses, ages, metallicities, and kinematics.
 }
@@
 
-\item At large radii (R/\reff\ $>$ 1.5), the more massive companion of pairs show a enhancement to the sSFR while the less massive companion of pairs show a suppression to the sSFR.
+\item At large radii (R/\reff\ $>$ 1.5), the more massive companion of pairs show an enhancement to the sSFR while the less massive companion of pairs show a suppression to the sSFR.
 
@@
 
-%\appendix
-
 \end{document}

### 2021-01-21 maintex.tex
revised iniside-IFU sample section

@@
 The IDL package is publicly available\footnote{\url{https://github.com/fuhaiastro/spfit}} and was first used in our previous study of close galaxy pairs in MaNGA \citepalias{Fu:2018}.
-While data products from the MaNGA Data Analysis Pipeline \citep[DAP;][]{Belfiore:2019} and {\sc PIPE3D} \citep{Sanchez:2016a, Sanchez:2016b} are available, {\sc spfit} allows us to combine spectra inside a given aperture before fitting the combined spectrum.
+While data products from the MaNGA Data Analysis Pipeline \citep[DAP;][]{Belfiore:2019} and {\sc pipe3d} \citep{Sanchez:2016a, Sanchez:2016b} are available, {\sc spfit} allows us to combine spectra inside a given aperture before fitting the combined spectrum.
 The feature alone made it better suited for this project.
@@
 \caption{Close Galaxy Pairs and Multiples in MaNGA IFUs}
-\label{tab:coords}
+\label{tab:sample}
 \begin{tabular}{lc ccc}
@@
 The ``good" galaxy spectra are the objects whose spectra are well modeled by {\sc spfit} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy.
-This means that the companion galaxy can be within approximately $\pm$3000 km s$^{-1}$ of the MaNGA target.
+This means that the companion galaxy can be within approximately $\pm$2000 km s$^{-1}$ of the MaNGA target.
 We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.
@@
 
-Among the 6142 MaNGA IFUs considered here, 404 have multiple galaxy objects within the IFU.
-We further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected companions.
+{\bf Among the 6142 MaNGA IFUs considered here, 404 cover close galaxy pairs and multiples.
+The sample includes 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
+Table\,\ref{tab:sample} lists the coordinates and redshifts of these galaxy components in pairs/multiples.} When a MaNGA target has multiple companions galaxies, we chose the closest companion to define the pair's mass ratio and projected separation.
+
+For this study, we further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$.
 Given the redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc.
@@
 We do this because the identified companions are not included in the NSA catalog which we use to build the radial profiles for the galaxies.}
-
-Several of the target galaxies in our sample have multiple companions.
-From the whole set of 404 IFUs, there are 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
-In cases where a MaNGA target has multiple viable companions galaxies, we chose the closest companion when measuring the pair's mass ratio and projected separation.
-\textbf{We show the whole 404 inside-IFU pair sample in Table \ref{tab:coords}.}
 
@@
 \subsection{Specific Star Formation Rate}
-\textbf{We calculate the star formation rates in the pair and control galaxies with the emission lines extracted with our spectra fitting code, {\sc SPFIT} (described in Section \ref{sec:spfit}).} We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
+\textbf{We calculate the star formation rates in the pair and control galaxies with the emission lines extracted with our spectra fitting code, {\sc spfit} (described in Section \ref{sec:spfit}).} We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
 The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.
@@
 We check our measurement of the specific star formation rate with the equivalent width of the H$\alpha$ line, \ewha, since it is a known proxy for the sSFR.
-This is useful as the sSFR is dependent on {\sc SPFIT}'s measurement of the stellar mass while \ewha\ is an observable.
+This is useful as the sSFR is dependent on {\sc spfit}'s measurement of the stellar mass while \ewha\ is an observable.
 As we will show in Section \ref{sec:results}, the radial profiles of \ewha\ is consistent with radial profiles of the sSFR.
@@
 We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}.
-We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc SPFIT}'s measurement of the sSFR.
+We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc spfit}'s measurement of the sSFR.
 We do see that the pair-control offsets are lightly suppressed using the \ewha\ as the $\Delta$log(\ewha) is only enhanced by 0.25 dex where the $\Delta$log(sSFR) was enhanced by 0.30 dex.

### 2021-01-22 maintex.tex
rearranged discussion subsections
minor text edits

@@
 \usepackage{comment}
+
+%\usepackage{CJK}
+%\setCJKmainfont{SimSun}
 
@@
 
-%\usepackage{epstopdf}
-
 \begin{document}
-
 \title{
@@
 \author{
-Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Arran~C.~Gross\altaffilmark{1}, and Rui~Xue\altaffilmark{1}
+Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai \altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Arran~C.~Gross\altaffilmark{1}, and Rui~Xue\altaffilmark{1}
 }
+
 \altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
@@
 (\textbf{Right}) The WHAN diagram for the MaNGA galaxies.} The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
-The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic).}
+The {\it purple} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), the {\it blue} diamonds represent the star forming paired galaxies (by the BPT diagram), the {\it green} diamonds represent the composite star forming-AGN paired galaxies (by the BPT diagram), and the {\it Red} diamonds represent the paired galaxies containing an AGN (by the BPT diagram).}
 \label{fig:cmd}
@@
 The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the mass ratio without taking the absolute value.
-Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from less massive companions from pairs.
+Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from the less massive companions from pairs.
 The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
@@
 
-\textbf{In the top left of Figure \ref{fig:ssfr_dm}, we split difference profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0.
+\textbf{In the top left of Figure \ref{fig:ssfr_dm}, we split the $\Delta$log(sSFR) profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0.
 Here, $|\Delta$log(M)$|$ $\le$ 0.5, represents equal mass major mergers while $|\Delta$log(M)$|$ $\ge$ 0.5 represents minor mergers.
@@
 When splitting the mass ratio like this we see that major mergers still higher levels of sSFR enhancement in comparison to minor mergers; however, we also see that the less massive companion of the pair sees a higher $\Delta$log(sSFR) in comparison to the more massive companion of a pair.
-In major mergers, the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions and in minor mergers the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions.}
+In major mergers, the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions.
+In minor mergers the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions.}
 
@@
 \textbf{We also see that the $\Delta$log(sSFR) in the outskirts ($R$ $>$ 1.5 \reff) of the pairs have a dependence on the mass ratio in the bottom right of Figure \ref{fig:ssfr_dm}.
-Primary companions show a zero to positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts, while secondary companions feature a suppression to the sSFR in their outskirts of about 0.0$-$0.4 dex.
+Primary companions show a positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts, while secondary companions feature a suppression to the sSFR in their outskirts of about 0.0$-$0.3 dex.
 Again we note that only 37\% of the MaNGA sample is designed to extend beyond 1.5 \reff; however, a similar result has been observed in the hydrodynamical simulations of \citet{Moreno:2015} and \citet{Moreno:2020}.
@@
 
-\section{Physical Scenario}
-% General Merger-SFR enhancement
-\textbf{
-Our results are consistent with the idea that galaxy merger events trigger a burst of star formation in the centers of the paired galaxies.
-In this model, when two galaxy pairs undergo their first pericenter, the tidal torques exerted on the disks of interacting galaxies form barred structures.
-These barred structures funnel gases into the centers of the galaxies which triggers a burst of new star formation.
-Eventually, as the pairs separate from each other after the first pericenter, the burst of star formation begins to subside.
-This is shown in our work and many previous works in Figure \ref{fig:nuc_sep} where the sSFR enhancement is greatest for close separations and falls with wider separations.
-}
-
- % Consant DelSSFR at different Masses
-\textbf{
-We also found that the $\Delta$log(sSFR) is independent of the stellar mass.
-This means that the merger event will produce the same amount of new stellar mass for low mass galaxies as it produces for high mass galaxies.
-This also means that the low mass galaxies will experience a greater change in total stellar mass before and after the merger event so the merger event will have a greater impact on the mass evolution of low mass galaxies as opposed to high mass galaxies.
-}
-
-% Mass ratio stuff
-\textbf{
-We find that the strength of the central burst of merger induced star formation is dependent on the relative masses between the two galaxies.
-Equal mass galaxies see the strongest bursts of star formation while wide mass ratios see weaker bursts of star formation.
-We further find that the strength of the central burst of star formation differs between the primary and secondary companion of a pair where the less massive secondary companion features a higher level of sSFR enhancement in comparison to its higher mass primary companion.
-}
-
-\textbf{
-\citet{Moreno:2020} uses galaxy merger simulations to study the origin of the enhanced star formation in galaxy pairs, whether its an increase in the star formation efficiency, defined as the ratio between the SFR and the mass of cold-dense gas, or its an increase in the availability of cold dense gas.
-They find that the star formation in secondary galaxies is evenly split between being efficiency driven or fuel driven systems while primary galaxies are more likely to be fuel driven systems (71\%).
-\citet{Moreno:2020} also finds that that secondary galaxies feature higher levels of star formation enhancement in comparison to primary galaxies, which is in agreement with what we find in this work.
-This indicates that the reason why primary galaxies behave differently from secondary galaxies may be due to a difference in the physical mechanism which drives the enhanced star formation.
-}
-
-\textbf{
-We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions.
-The primary companion features an enhancement to their sSFR at wide radii while the secondary companion features a suppression to their sSFR at wide radii.
-The reason for this is unclear; however, this means that the primary companions will experience enhanced stellar mass growth across their disks while the secondary companions will see only see substantial stellar mass growth in their centers which will result in more bulge dominated galaxies.
-}
-
-\subsection{Comparison with Previous Work}
-
-\subsubsection{Radial Difference Profiles}
+\subsection{Radial Profiles of Enhancement}
 
@@
 
-In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile and $\Delta$log(SFR) as a function of galactocentric radius between our work and previous works.
+In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile and $\Delta$log(SFR) as a function of galactocentric radius between our work and previous works using the MaNGA data.
 \textbf{\citet{Thorp:2019} studies a sample of 36 post-mergers from the MaNGA sample.
@@
 82 of these pairs are post-merger galaxies.
-\citet{Pan:2019} shows that pairs with morphological features show higher $\Delta$log(SFR) when compared to pairs without morphological distortions.
-Further, \citet{Thorp:2019} showed that post-merger galaxies have $\Delta$log(SFR) profiles which are higher than our sample's profiles.
+\citet{Pan:2019} showed that pairs with disturbed morphology have higher $\Delta$log(SFR) when compared to pairs without morphological distortions.
+Further, \citet{Thorp:2019} showed that post-merger galaxies have $\Delta$log(SFR) profiles which are elevated over our sample's profiles.
 From this, infer that the lower $\Delta$log(sSFR) seen in our sample is due to our sample's lack of post-merger galaxies.
@@
 
-\subsection{Dependency on Merger Parameters}
+\subsection{Central Enhancement vs. Merger Parameters}
 
@@
 From this we see that our sSFR enhancement as a function of projected separation is consistent with with what has been found in previous works.
+
+\subsection{Comparison with Simulations}
+
+% General Merger-SFR enhancement
+\textbf{
+Our results are consistent with the idea that galaxy merger events trigger a burst of star formation in the centers of the paired galaxies.
+In this model, when two galaxy pairs undergo their first pericenter, the tidal torques exerted on the disks of interacting galaxies form barred structures.
+These barred structures funnel gases into the centers of the galaxies which triggers a burst of new star formation.
+Eventually, as the pairs separate from each other after the first pericenter, the burst of star formation begins to subside.
+This is shown in our work and many previous works in Figure \ref{fig:nuc_sep} where the sSFR enhancement is greatest for close separations and falls with wider separations.
+}
+
+ % Consant DelSSFR at different Masses
+\textbf{
+We also found that the $\Delta$log(sSFR) is independent of the stellar mass.
+This means that the merger event will produce the same amount of new stellar mass for low mass galaxies as it produces for high mass galaxies.
+This also means that the low mass galaxies will experience a greater change in total stellar mass before and after the merger event so the merger event will have a greater impact on the mass evolution of low mass galaxies as opposed to high mass galaxies.
+}
+
+% Mass ratio stuff
+\textbf{
+We find that the strength of the central burst of merger induced star formation is dependent on the relative masses between the two galaxies.
+Equal mass galaxies see the strongest bursts of star formation while wide mass ratios see weaker bursts of star formation.
+We further find that the strength of the central burst of star formation differs between the primary and secondary companion of a pair where the less massive secondary companion features a higher level of sSFR enhancement in comparison to its higher mass primary companion.
+}
+
+\textbf{
+\citet{Moreno:2020} uses galaxy merger simulations to study the origin of the enhanced star formation in galaxy pairs, whether its an increase in the star formation efficiency, defined as the ratio between the SFR and the mass of cold-dense gas, or its an increase in the availability of cold dense gas.
+They find that the star formation in secondary galaxies is evenly split between being efficiency driven or fuel driven systems while primary galaxies are more likely to be fuel driven systems (71\%).
+\citet{Moreno:2020} also finds that that secondary galaxies feature higher levels of star formation enhancement in comparison to primary galaxies, which is in agreement with what we find in this work.
+This indicates that the reason why primary galaxies behave differently from secondary galaxies may be due to a difference in the physical mechanism which drives the enhanced star formation.
+}
+
+\textbf{
+We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions.
+The primary companion features an enhancement to their sSFR at wide radii while the secondary companion features a suppression to their sSFR at wide radii.
+The reason for this is unclear; however, this means that the primary companions will experience enhanced stellar mass growth across their disks while the secondary companions will see only see substantial stellar mass growth in their centers which will result in more bulge dominated galaxies.
+}
 

### 2021-01-22 build/submit_v2/response.txt
removed fig folder

We thank the referee for the report. We hope that we have addressed the referee's concerns in the updated document. Our responses to the referee's comments are given below and the revised parts of the paper have been highlighted in bold.

#######################################################
### Reply to the Reviewer's Comments
#######################################################

MAJOR COMMENTS

I am concerned with the radial sampling at large distances, specifically at 1.5 < Reff < 2.5. The number of galaxies sampled by the primary and secondary sample are different. Therefore, for a given stellar mass bin the sampling in the inner 1.5 Reff is larger than in the outskirts. This could induce artificial slopes in the radial gradient of Delta_sSFR. The authors should discuss this, indicating the impact of having a sample with a non-homogeneous radial coverage.

> We have added a couple of paragraphs addressing this in sections 3.1 and 3.2. In section 3.1 we have added a S/N > 3 cut on the Ha line to remove spaxels with low signal, which are mostly going to be beyond 1.5 Reff and 2.5 Reff in the primary and secondary samples respectively. In section 3.2, we also mention how the number of usable spaxels will fall beyond 1.5 Reff and that the results here should be taken with a grain of salt.

Other than the comparison with the literature in Sec.5, the authors should make a deeper discussion of their results and give their physical interpretation of their results.

>   We have added a section discussing our physical interpretation of the results to the discussion section.

I also encourage the authors to please highlight the differences between their study and those derived from the same MaNGA dataset.

>   We have expanded the discussion of our results in comparison to Pan+2019 and Thorp+2019.

MINOR COMMENTS

ABSTRACT

The author should include a sentence at the end of the abstract in which they explain what is, in the light of their results, the most likely phsical scenario explaining their results.

>   We've added a sentence to the abstract describing the physical scenario.

SECTION 2.

In Sec. 2, the authors create selection lines that devide the red sequence, the green valley and the blue cloud in the CMD. The authors should compare their best separation lines with previous studies.

>   There is no standard way to way to split the CMD; however, we checked our cuts against those in Wake+2017 and find that they are consistent. We have also added the BPT diagram and WHAN diagram for our pair selection.

I strongly recommend the authors to use 6 Á, instead of 3A. This threshold has been used as selection criteria for selecting star-forming galaxies/regions (see Sanchez 2020). By the way, EW(Ha)>6A Is equivalent to the SSFR> ~ -10.8 yr^-1 The authors have to state that this is an intrinsic limit due to the Selection criteria.

>   We agree with the reviewer here and changed our EW(Ha) cut to 6 A. This limit reduces our total pair sample from 175 pairs to 169 pairs.

The authors use the EW(HA)>3A and the BPT diagram (emission line fluxes) to differentiate between passive and star forming galaxies. The authors have to Indicate how these properties have been derived using the MANGA data before they are used as selection criteria, or at least refer to the section where they show how these quantities are derived (see my next comment).

>   We have added a reference to a section describing our spectral fitting code, SPFIT.

The authors should give more details regarding SPFIT. Which SSPs did the authors used? Are the derived properties similar to those derived from other analysis pipelines such as DAP or PIPE3D? I recommend that the authors create a subsection in Sec.2 or 3 to address the main properties of their analysis pipeline.

>   We have created a new subsection describing SPFIT in more detail.

What is the fraction of broad-line AGNs compared to the one from previous studies using the MaNGA sample (Lacerda et al. 2020).

>   We've added a paragraph to Inside-IFU pair sample section comparing the number of BLAGN that we find in comparison to Lacerda+2020 and Sanchez+2018.

This sentence it is not clear to me: 'We leave out the identified companions from the analysis because the MaNGA targets are covered by the NSA catalog with geometries and total stellar masses while the companions are not covered by the NSA catalog'. Does the authors mean that they did not include in their analysis the companion galaxies they found within the MaNGA FoV? If this is the case, why make this selection in the first place?

>   We have rephrased this statement in the text. What we meant to say was that we only analyze the MaNGA target galaxies in our work and not the other galaxies found within the IFUs.

Is the list of galaxies in Sec. 2.1 and 2.2 available? Such lists are useful to the community. I encourage the authors to provide such a list.

>   We have added a machine readable table of our galaxy pairs to the paper.

I suggest the authors to restrain themselves to refer the Control Sample as the 'isolated sample' as these galaxies are not strictly isolated (as for example the galaxies selected in the AMIGA survey, e.g.,Verdes-Montenegro et al., 2015).

>   We have changed instances of "isolated sample" to "control sample"

SECTION 3

As in the previous Sec.2, I suggest that the authors provided a more detailed description of the analysis pipeline.

> We have expanded our description of the methodology.

In sec 3.1., Why not using the EW(Ha) instead of the SFR/M (which is actually surface densities) to estimate sSFR?

>   The surface density factor will be cancelled out with SFR/M since both SFR and M here are surface densities. We have also decided to show radial profiles of EW(Ha) to show that they are constant with each other.

In Sec. 3.2, the authors have to detail that the galaxy sampling is not the same from 0 to 1.5 Reff to 1.5 to 2.5 Reff this is due to the Primary and secondary samples inherit from the MaNGA sample.This is independent from the correction from inclination. The authors have also to discuss the impact of the FoV coverage in their results.

>   We have added a paragraph on the non-uniform radial coverage.

SECTION 4

Fig.3, left panel: It is difficult to visualize the different radial trends for different stellar mass bins. I suggest to make 5 subpanels for each mass bin.

>   We think that breaking the figures into 5 panel plots would take up too much space, instead we changed the bound of the plots to remove the extra white space.

Fig.3, right panel: The vertical error bars look rather small to be representative of the standard deviation of the sample in each stellar mass bin.

>   There was a typo in the caption, there error bars here are the standard error of the mean. We have fixed that typo.

In the sentence: 'To understand why these high mass galaxies behave differently from the rest of the sample, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure 4' The author refer to the radial gradient in left panel of Fig.3? If so, please clarify. This sentence and the previous paragraph are hard to read since in the previous paragraph the authors are referring to the low-mass bins.

>   We have rephrased this here and referred to the figures in question.

The authors mention:'The highest mass galaxies in the sample are at closer projected separations in comparison to the rest of the sample with 70% of the highest mass galaxies being within 20 kpc.' Has this been observed in other samples of interacting galaxies?

>   We think that this may be due to clustering effects, see Cooray&Sheth 2002 and Zehavi+2002. We have added a paragraph about this in the text.

Fig.5: There is a typo in the text. Those are only two panels not four as suggested in the description of this Fig. There are no bottom left and right panels, right?

>   We've fixed the typo

Fig.5: It is not clear if the right panel is the Delta_sSFR within a 0.5 aperture, please clarify.

>   We now clarify this in the caption.

Fig.5: The authors mention that there is a clear difference among the different profiles at large Reff. As mentioned above, this may depend on the galaxies being on the primary or secondary MaNGA sample.

>   We looked at Fig.5 (now Fig.6) without the secondary galaxies from the sample and find similar results.

It is a bit confusing what the authors refer to 'primary' and 'secondary' companion of major and minor mergers: abs(log(Delta_M)) < 0.5 is a major merger otherwise it is a minor merger, no? This is also making difficult to understand the results from left panel of Fig.5. Why is there a difference between the blue and red radial trends? In principle there should not be a difference between them since they both are referring to minor mergers. Please make clear in the figures the primary and secondary profiles/points in minor and major mergers.

>   Here we are studying how the more massive galaxy of a pair (the primary galaxy) may differ from the less massive galaxy of the pair (the secondary galaxy). We clarify this in the text. We also update Fig.6 to have a row for abs(Deltalog(M)), showing how major merger differ from minor mergers, and a row for Deltalog(M), showing how primary companions differ from secondary companions.

In Sec. 4.3 the authors mention: 'The ∆log(sSFR) profiles show a clear gradient with the projected separation with close galaxy pairs showing higher levels of sSFR enhancement compared to pairs with wide separations.'. This is not true from the figure, within the uncertainties the gradients are similar regardless of the projected separation of the pair. Please rectify.

>   The reviewer is correct here and we have updated the text.

Why do the authors find an increment in the central Delta_sSFR at large separations (~50 kpc)? Why do the authors find this 'V-shape' in the enhancement in the Delta_sSFR? Is due to the sample selection (inside outside IFU pairs)?

>   The dip was likely due to a few pairs with a strong sSFR suppression in their centers, these pairs seem to have been removed with the stricter EW(Ha)>6 A cut so that there is no longer a strong dip at 30-40 kpc.

SECTION 5

Fig 7.: This goes to my main concern. The authors can note that neither the Thorp et al or Pan et al. works go beyond 1.5 Reff. This could be due to the effect of the FoV coverage of the MaNGA survey. Please comment on this. I also encourage the authors to explore further the possible difference with the literature datasets. I find worrisome the difference between their radial profiles and those in the literature. I can understand the difference between the Thorp et al. work and the one with the authors, but Pan et al. work sample is similar, yet the enhancement is significantly larger for Pan et al. work.

>   Pan+2019 includes a large set of 82 post-merger galaxies. We think that this may be a major source of why their profiles are elevated over ours. We have also updated fig.8 as Thorp+2019 used the SFR and not sSFR. We have also updated our analysis to match pairs to controls based on stellar mass, redshift, and effective radius like what was done in Pan+2019.

Sec. 5.2: The authors have to further discuss what are the possible differences between the results from Li et al.(2008) and their results. Not only about differences in the methodology but also the samples and what is the impact of these differences in the physical interpretation of mergers in galaxy evolution.

>   We do not know why our results differ from Li+2008. We have discussed this with Cheng Li but we were unable to resolve this discrepancy.

Fig.8: Please include in the caption that this Delta_SFR and Delta_sSFR refers to the integrated values with 0.5 Reff.

>   We have updated the captions.

### 2021-01-22 build/submit_v2/maintex.tex
removed fig folder

--- 2021-01-22 maintex.tex
@@
 % ApJ Format
-\documentclass[iop,revtex4,twocolumn,apj,numberedappendix,appendixfloats]{emulateapj}
+\documentclass[apj,twocolumn]{emulateapj}
 \usepackage{apjfonts}
-% Hyperlinks & Bookmarks
 \usepackage[pagebackref=false,colorlinks=true,citecolor=blue,linkcolor=blue,breaklinks=true,bookmarks=true]{hyperref}
 \usepackage{amsmath}
-\usepackage{comment}
+\usepackage{lineno}
+\usepackage{CJKutf8}
 
-%\usepackage{CJK}
-%\setCJKmainfont{SimSun}
-
+\linenumbers
 % Units
@@
 % special 
-\newcommand{\nod}{\nodata}
-
-\newcommand{\angstrom}{\mbox{\normalfont\AA}}
 \newcommand{\reff}{$R_{\rm eff}$}
@@
 \newcommand{\logm}{log($M/M_{\odot}$)}
-%\newcommand{\arcsec}{\prime\prime}
-\newcommand{\simard}{Simard+11}
-
-% citations
 \defcitealias{Fu:2018}{Paper I}
@@
 \begin{document}
-\title{
-SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs
-}
+\begin{CJK*}{UTF8}{gbsn}
+\title{SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs}
 
 \author{
-Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai \altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Arran~C.~Gross\altaffilmark{1}, and Rui~Xue\altaffilmark{1}
+Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1,2}, J.~M.~Comerford\altaffilmark{3}, Y.~Sophia~Dai (戴昱)\altaffilmark{4}, Shuai~Feng\altaffilmark{5,6,7}, Arran~C.~Gross\altaffilmark{1}, and Rui~Xue\altaffilmark{1}
 }
@@
 
+\end{CJK*} 
 \end{document}

### 2021-01-22 maintex.tex
line number added
updated affiliations and acknowledgements

@@
 \altaffiltext{3}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
-\altaffiltext{4}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}
+\altaffiltext{4}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA)/National Astronomical Observatories of China (NAOC), 20A Datun Road, Beijing 100012, China}
 \altaffiltext{5}{Department of Physics, Hebei Normal University, 20 South Erhuan Road, Shijiazhuang, 050024, China}
@@
 \centering
-\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
+\includegraphics[width=\linewidth]{bpt-cmd.pdf}
 \caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies.
@@
 \centering
-\includegraphics[width=\linewidth]{fig/ewha_comb.pdf}
+\includegraphics[width=\linewidth]{ewha_comb.pdf}
 \caption[]{Same as Figure \ref{fig:ssfr_prof} but for EW(H$\alpha$). }
@@
 \centering
-\includegraphics[width=3in]{fig/prof_comp.pdf}
+\includegraphics[width=3in]{prof_comp.pdf}
 \caption[]{The mean radial profile of $\Delta$log(sSFR) (\textbf{Top}) and $\Delta$log(SFR) (\textbf{Bottom}) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
@@
 \centering
-\includegraphics[width=3in]{fig/nuc_sep.pdf}
+\includegraphics[width=3in]{nuc_sep.pdf}
 \caption[]{(\textbf{Top}) $\Delta$log(SFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
@@
 acknowledge support from the National Science Foundation (NSF) grant AST-1614326.
+{\bf YSD would like to acknowledge support from NSFC grant number 10878003}.
 Funding for the Sloan Digital Sky Survey IV has been provided by the Alfred P.
@@
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+\end{CJK*} 
 \bibliographystyle{aasjournal}

### 2021-01-29 maintex.tex
updated paper for second revision

@@
 \begin{abstract}
-We compare the radial profiles of the specific star formation rate (sSFR) in a sample of \textbf{169} star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey.
+We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 169 star-forming galaxies in close pairs with those of mass-matched control galaxies in the SDSS-IV MaNGA survey.
 We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.3 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex.
@@
 The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.
-\textbf{Our results illustrate the complex tidal effects on star formation in closely paired galaxies.
-}
+Our results illustrate the complex tidal effects on star formation in closely paired galaxies.
 \end{abstract}
@@
 \caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies.
-\textbf{(\textbf{Center}) BPT diagram for the MaNGA galaxies.
-(\textbf{Right}) The WHAN diagram for the MaNGA galaxies.} The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
+(\textbf{Center}) BPT diagram for the MaNGA galaxies.
+(\textbf{Right}) The WHAN diagram for the MaNGA galaxies.
+The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
 The {\it purple} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), the {\it blue} diamonds represent the star forming paired galaxies (by the BPT diagram), the {\it green} diamonds represent the composite star forming-AGN paired galaxies (by the BPT diagram), and the {\it Red} diamonds represent the paired galaxies containing an AGN (by the BPT diagram).}
@@
 
-{\bf 
 We use {\sc spfit} to model the MaNGA datacubes.
@@
 Saved in the final FITS file are the best-fit parameters and their uncertainties, including emission-line fluxes, equivalent widths, and kinematics and luminosity-weighted stellar masses, ages, metallicities, and kinematics.
-}
 
@@
 
-\textbf{Based on the WHAN diagram, shown in the right panel of Figure \ref{fig:cmd}, we apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.}
+Based on the WHAN diagram, shown in the right panel of Figure \ref{fig:cmd}, we apply an \ewha\ $\ge$ 6\AA cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all retired galaxies are removed from the sample \citep{Cid-Fernandes:2011}.
 
@@
 
-\textbf{Broad-line AGN comprise $\sim$0.9\% of MaNGA's galaxy sample where \citet{Lacerda:2020} found a fraction of $\sim$2.8\% from the CALIFA survey and \citet{Sanchez:2018} found a fraction of $\sim$1.33\% from the MaNGA's MPL-5 sample (which observed $\sim$2700 galaxies).
-}
+Broad-line AGN comprise $\sim$0.9\% of MaNGA's galaxy sample where \citet{Lacerda:2020} found a fraction of $\sim$2.8\% from the CALIFA survey and \citet{Sanchez:2018} found a fraction of $\sim$1.33\% from the MaNGA's MPL-5 sample (which observed $\sim$2700 galaxies).
 
-{\bf Among the 6142 MaNGA IFUs considered here, 404 cover close galaxy pairs and multiples.
+Among the 6142 MaNGA IFUs considered here, 404 cover close galaxy pairs and multiples.
 The sample includes 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet.
-Table\,\ref{tab:sample} lists the coordinates and redshifts of these galaxy components in pairs/multiples.} When a MaNGA target has multiple companions galaxies, we chose the closest companion to define the pair's mass ratio and projected separation.
+Table\,\ref{tab:sample} lists the coordinates and redshifts of these galaxy components in pairs/multiples.
+When a MaNGA target has multiple companions galaxies, we chose the closest companion to define the pair's mass ratio and projected separation.
 
@@
 These requirements reduce our sample down to 54 star forming MaNGA targets with inside-IFU companions.
-\textbf{While we use the identified companions to select galaxy pairs, we only build radial profiles for the MaNGA target galaxies.
-We do this because the identified companions are not included in the NSA catalog which we use to build the radial profiles for the galaxies.}
+While we use the identified companions to select galaxy pairs, we only build radial profiles for the MaNGA target galaxies.
+We do this because the identified companions are not included in the NSA catalog which we use to build the radial profiles for the galaxies.
 
@@
 
-To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of \textbf{control} galaxies in the MaNGA survey.
+To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of control galaxies in the MaNGA survey.
 We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_{\rm p}$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU.
@@
 It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep[e.g.,][]{Noeske:2007}.
-We will compare our interacting galaxies with \textbf{control} galaxies of a similar stellar mass, redshift, and radial size, to account for these other dependencies.
+We will compare our interacting galaxies with control galaxies of a similar stellar mass, redshift, and radial size, to account for these other dependencies.
 To do this, we will use two different methods of pair - control comparison.
@@
 We select a subsample of 20 control galaxies for each paired galaxy.
-We first select all of the control galaxies which are within 0.1 dex in stellar mass, \textbf{0.025 in redshift, 20\% in effective radii}, and within the same MaNGA subsample (e.g.
+We first select all of the control galaxies which are within 0.1 dex in stellar mass, 0.025 in redshift, 20\% in effective radii, and within the same MaNGA subsample (e.g.
 Primary or Secondary) as the paired galaxy.
@@
 In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex, the redshift by 0.025, and the \reff\ by 5\% until at least 20 control galaxies are found.
-\textbf{39 pairs required 1 extra iteration, 15 pairs required 2 extra iterations, 5 pairs required 3 extra iterations, and 2 pairs required 4 extra iterations.
-}
+39 pairs required 1 extra iteration, 15 pairs required 2 extra iterations, 5 pairs required 3 extra iterations, and 2 pairs required 4 extra iterations.
 
@@
 \subsection{Specific Star Formation Rate}
-\textbf{We calculate the star formation rates in the pair and control galaxies with the emission lines extracted with our spectra fitting code, {\sc spfit} (described in Section \ref{sec:spfit}).} We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
+We calculate the star formation rates in the pair and control galaxies with the emission lines extracted with our spectra fitting code, {\sc spfit} (described in Section \ref{sec:spfit}).
+We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}.
 The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.
@@
 
-\textbf{
 We check our measurement of the specific star formation rate with the equivalent width of the H$\alpha$ line, \ewha, since it is a known proxy for the sSFR.
@@
 As we will show in Section \ref{sec:results}, the radial profiles of \ewha\ is consistent with radial profiles of the sSFR.
-}
 
-\textbf{
 The signal to noise ratio of the data will decrease with wide galactocentric radii.
@@
 We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}, which effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
-}
 
@@
 Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy.
-Note that although we carefully treat the two catalogs separately whenever possible, we find excellent agreement in the geometry parameters of \textbf{control} galaxies in both catalogs.
+Note that although we carefully treat the two catalogs separately whenever possible, we find excellent agreement in the geometry parameters of control galaxies in both catalogs.
 
@@
 
-\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).
-This means that there will be fewer selected spaxel beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff.
-We decide to still extend our radial profiles out to 2.5 \reff, but emphasize that the data beyond 1.5 \reff\ is lower in quality.
+The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).
+This means that there will be fewer selected spaxels beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff.
+{\bf We decide to still extend our radial profiles out to 2.5 \reff\ to make full use of the MaNGA data; however, we emphasize that the difference in the sampling of the data within 1.5 \reff\ and the data beyond 1.5 \reff\ may create artificial slopes in the data.
 }
@@
 The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.
-}
+{\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.}}
 \label{fig:ssfr_prof}
@@
 The error associated with the ``stacked'' profile is the standard error of mean of the data at each radius bin.
-\textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
+Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
 \begin{equation}
@@
 \end{equation}
-where $\sigma$ is the standard deviation and $n$ is the sample size.}
+where $\sigma$ is the standard deviation and $n$ is the sample size.
 
@@
 
-\textbf{ 
 We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}.
@@
 We do see that the pair-control offsets are lightly suppressed using the \ewha\ as the $\Delta$log(\ewha) is only enhanced by 0.25 dex where the $\Delta$log(sSFR) was enhanced by 0.30 dex.
-}
 
@@
 The number of paired galaxies in each mass range is given in the legend in parentheses.
-The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) \textbf{extracted from a 0.5\reff\ aperture}.
+The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) extracted from a 0.5\reff\ aperture.
 The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
@@
 Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.
+{\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.
+}
 }
@@
 We then take the median of the azimuthally averaged profiles of the tailored control sample.
-Finally, we obtain the $\Delta\log$sSFR profile for each of the \textbf{169} paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.
+Finally, we obtain the $\Delta\log$sSFR profile for each of the 169 paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.
 
@@
 
-\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample within the central 0.5~\reff.
+To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample within the central 0.5~\reff.
 The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels.
@@
 The central sSFR of a paired galaxy is compared against the sSFR of a set of 20 similar control galaxies, the same set of controls which were used for the $\Delta$log(sSFR) profiles, by taking the difference between the central sSFR of the paired galaxy and the median sSFR of the 20 selected control galaxies.
-We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.}
+We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.
 
@@
 The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.0$-$0.1 dex.
-\textbf{Within individual mass ranges, there are some mass ranges which feature large enhancements to the sSFR at large radii while other mass ranges show a strong suppression to the sSFR.
-There appears to be no dependence on the stellar mass of the pair but, as we will show in the next section, \S~\ref{sec:dm}, these offsets at large radii may be dependent on the mass ratio between the galaxy pairs.}
+Within individual mass ranges, there are some mass ranges which feature large enhancements to the sSFR at large radii while other mass ranges show a strong suppression to the sSFR.
+There appears to be no dependence on the stellar mass of the pair but, as we will show in the next section, \S~\ref{sec:dm}, these offsets at large radii may be dependent on the mass ratio between the galaxy pairs.
 
-\textbf{To understand why the profiles of high mass galaxies behave differently from the rest of the sample in Figures \ref{fig:ssfr_prof}, \ref{fig:ewha_prof}, and \ref{fig:ssfr_mass}, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.} The whole sample has a v-shaped separation distribution.
+To understand why the profiles of high mass galaxies behave differently from the rest of the sample in Figures \ref{fig:ssfr_prof}, \ref{fig:ewha_prof}, and \ref{fig:ssfr_mass}, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.
+The whole sample has a v-shaped separation distribution.
 This is the result of the combination of the two different samples, the inside-IFU and outside-IFU samples.
@@
 The highest mass galaxies in the sample are at closer projected separations in comparison to the rest of the sample with 70\% of the highest mass galaxies being within 20 kpc.
-\textbf{ The cause of this may be due to clustering effects where high mass galaxies tend to be at the centers of galaxy clusters \citep{Cooray:2002, Zehavi:2002}}.
+The cause of this may be due to clustering effects where high mass galaxies tend to be at the centers of galaxy clusters \citep{Cooray:2002, Zehavi:2002}.
 As we will show in \S~\ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.
@@
 \end{equation}
-where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of \textbf{its identified} companion galaxy.
-\textbf{In the inside-IFU sample, we have stellar masses for the MaNGA target galaxy but not the other identified pairs.
-Because of this, we leave the inside-IFU companions out of this analysis.}
+where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of its identified companion galaxy.
+In the inside-IFU sample, we have stellar masses for the MaNGA target galaxy but not the other identified pairs.
+Because of this, we leave the inside-IFU companions out of this analysis.
 
-\textbf{In the top left of Figure \ref{fig:ssfr_dm}, we split the $\Delta$log(sSFR) profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0.
+In the top left of Figure \ref{fig:ssfr_dm}, we split the $\Delta$log(sSFR) profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0.
 Here, $|\Delta$log(M)$|$ $\le$ 0.5, represents equal mass major mergers while $|\Delta$log(M)$|$ $\ge$ 0.5 represents minor mergers.
@@
 The effect can be seen more clearly with the data extracted from the central 0.5 \reff\ in the top right panel.
-Here the $\Delta$log(sSFR) falls linearly with wider mass ratios, reaching zero enhancement to the sSFR at $|\Delta$log(M)$|$ $=$ 1.5$-$1.75.}
+Here the $\Delta$log(sSFR) falls linearly with wider mass ratios, reaching zero enhancement to the sSFR at $|\Delta$log(M)$|$ $=$ 1.5$-$1.75.
 
-\textbf{We not only use the mass ratio to study how a major merger behaves differently from a minor merger but also to study how the more massive galaxy of a pair behaves differently from the less massive galaxy of the pair.
+We not only use the mass ratio to study how a major merger behaves differently from a minor merger but also to study how the more massive galaxy of a pair behaves differently from the less massive galaxy of the pair.
 We expect that either component of a similar mass pair will behave in a similar fashion; however, in a minor merger the large central galaxy may not respond to the merger event in the same way as its less massive companion.
 The two different scenarios can be differentiated with our definition of the mass ratio in equation \ref{eq:dm}; when the MaNGA target is the more massive companion of the pair, its mass ratio is positive and when MaNGA target is the less massive companion of pair the mass ratio is negative.
-To distinguish between these scenarios, we refer to the more massive galaxy of a pair as the primary companion and the less massive galaxy of a pair as the secondary companion.}
+To distinguish between these scenarios, we refer to the more massive galaxy of a pair as the primary companion and the less massive galaxy of a pair as the secondary companion.
 
-In \textbf{bottom left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins.
-\textbf{The primary companions are the pairs with $\Delta$log(M) $\ge$ 0.0 and the secondary companions are the pairs with $\Delta$log(M) $\le$ 0.0.
+In bottom left panel of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins.
+The primary companions are the pairs with $\Delta$log(M) $\ge$ 0.0 and the secondary companions are the pairs with $\Delta$log(M) $\le$ 0.0.
 When splitting the mass ratio like this we see that major mergers still higher levels of sSFR enhancement in comparison to minor mergers; however, we also see that the less massive companion of the pair sees a higher $\Delta$log(sSFR) in comparison to the more massive companion of a pair.
 In major mergers, the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions.
-In minor mergers the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions.}
+In minor mergers the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions.
 
-In \textbf{bottom right panel} of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
+In bottom right panel of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0).
 These galaxies feature a central enhancement of $\sim$0.4 dex which is 0.2 dex higher than the average central enhancement of the whole sample.
-\textbf{This enhancement falls with wider mass ratios with a different slope for primary and secondary companions.
-At $\Delta$log($M$) $=$ -1.0, the sSFR is enhanced by 0.2 dex while at $\Delta$log($M$) $=$ 1.0 the sSFR enhancement is zero.}
+This enhancement falls with wider mass ratios with a different slope for primary and secondary companions.
+At $\Delta$log($M$) $=$ -1.0, the sSFR is enhanced by 0.2 dex while at $\Delta$log($M$) $=$ 1.0 the sSFR enhancement is zero.
 
-\textbf{We also see that the $\Delta$log(sSFR) in the outskirts ($R$ $>$ 1.5 \reff) of the pairs have a dependence on the mass ratio in the bottom right of Figure \ref{fig:ssfr_dm}.
+We also see that the $\Delta$log(sSFR) in the outskirts ($R$ $>$ 1.5 \reff) of the pairs have a dependence on the mass ratio in the bottom right of Figure \ref{fig:ssfr_dm}.
 Primary companions show a positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts, while secondary companions feature a suppression to the sSFR in their outskirts of about 0.0$-$0.3 dex.
 Again we note that only 37\% of the MaNGA sample is designed to extend beyond 1.5 \reff; however, a similar result has been observed in the hydrodynamical simulations of \citet{Moreno:2015} and \citet{Moreno:2020}.
-}
 
@@
 Second, we see that secondary companions show steeper enhancement profiles with higher levels of sSFR enhancement in their centers and stronger levels of sSFR suppression in their disks with respect to primary companions.
-\textbf{Finally, we see that primary companions feature sSFR enhancement at wide radii while secondary companions feature sSFR suppression at wide radii.}
+Finally, we see that primary companions feature sSFR enhancement at wide radii while secondary companions feature sSFR suppression at wide radii.
 
@@
 Figure \ref{fig:ssfr_sep} shows the profile and the central level of sSFR enhancement as a function of the projected separation ($r_{\rm p}$) from our MaNGA data.
-\textbf{The $\Delta$log(sSFR) profiles show only a weak dependency on the projected separation.
+The $\Delta$log(sSFR) profiles show only a weak dependency on the projected separation.
 The pairs below a separation of 25 kpc have $\Delta$log(sSFR) profiles which lie $\sim$0.1 dex above the sample median while the profiles of the pairs beyond 25 kpc are $\sim$ 0.1 dex below the sample median.
-}
 
@@
 In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile and $\Delta$log(SFR) as a function of galactocentric radius between our work and previous works using the MaNGA data.
-\textbf{\citet{Thorp:2019} studies a sample of 36 post-mergers from the MaNGA sample.
+\citet{Thorp:2019} studies a sample of 36 post-mergers from the MaNGA sample.
 The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(SFR) $=$ 0.40$-$0.45, roughly 0.2 dex higher than our paired galaxies.
 Between 0.4$-$1.0\reff\ the post-merger galaxies and our pairs are in closer agreement, being 0.05$-$0.1 dex higher than our paired galaxies.
-Beyond 1.0 \reff\ the post-merger galaxies have a higher $\Delta$log(SFR) by about 0.1$-$0.2 dex.} The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
+Beyond 1.0 \reff\ the post-merger galaxies have a higher $\Delta$log(SFR) by about 0.1$-$0.2 dex.
+The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.
 
-\textbf{\citet{Pan:2019} studies a set of 205 paired galaxies in the MaNGA sample, focusing on the sSFR enhancement as a function of the merger interaction stage.
-The $\Delta$log(sSFR) profiles of the galaxies pairs in \citet{Pan:2019} are $\sim$0.10$-$0.15 dex above the profiles in our sample.} Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
+\citet{Pan:2019} studies a set of 205 paired galaxies in the MaNGA sample, focusing on the sSFR enhancement as a function of the merger interaction stage.
+The $\Delta$log(sSFR) profiles of the galaxies pairs in \citet{Pan:2019} are $\sim$0.10$-$0.15 dex above the profiles in our sample.
+Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.
 
-The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of \textbf{96 pairs which are too close to be separately de-blended by SDSS and instead were visually identified by their morphology.
+The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of 96 pairs which are too close to be separately de-blended by SDSS and instead were visually identified by their morphology.
 82 of these pairs are post-merger galaxies.
@@
 From this, infer that the lower $\Delta$log(sSFR) seen in our sample is due to our sample's lack of post-merger galaxies.
-}
 
@@
 \caption[]{(\textbf{Top}) $\Delta$log(SFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
-(\textbf{Bottom}) $\Delta$log(sSFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
+(\textbf{Bottom}) $\Delta$log(sSFR) extracted from the inner 0.5 \reff over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
 }
@@
 % General Merger-SFR enhancement
-\textbf{
 Our results are consistent with the idea that galaxy merger events trigger a burst of star formation in the centers of the paired galaxies.
@@
 This is shown in our work and many previous works in Figure \ref{fig:nuc_sep} where the sSFR enhancement is greatest for close separations and falls with wider separations.
-}
 
  % Consant DelSSFR at different Masses
-\textbf{
 We also found that the $\Delta$log(sSFR) is independent of the stellar mass.
@@
 This also means that the low mass galaxies will experience a greater change in total stellar mass before and after the merger event so the merger event will have a greater impact on the mass evolution of low mass galaxies as opposed to high mass galaxies.
-}
 
 % Mass ratio stuff
-\textbf{
 We find that the strength of the central burst of merger induced star formation is dependent on the relative masses between the two galaxies.
@@
 We further find that the strength of the central burst of star formation differs between the primary and secondary companion of a pair where the less massive secondary companion features a higher level of sSFR enhancement in comparison to its higher mass primary companion.
-}
 
-\textbf{
 \citet{Moreno:2020} uses galaxy merger simulations to study the origin of the enhanced star formation in galaxy pairs, whether its an increase in the star formation efficiency, defined as the ratio between the SFR and the mass of cold-dense gas, or its an increase in the availability of cold dense gas.
@@
 This indicates that the reason why primary galaxies behave differently from secondary galaxies may be due to a difference in the physical mechanism which drives the enhanced star formation.
-}
 
-\textbf{
 We also find that there is a difference in the $\Delta$log(sSFR) offsets at wide radii between primary and secondary companions.
@@
 The reason for this is unclear; however, this means that the primary companions will experience enhanced stellar mass growth across their disks while the secondary companions will see only see substantial stellar mass growth in their centers which will result in more bulge dominated galaxies.
-}
+{\bf Differences in the bulge-to-total ratio, (B/T), has been observed in previous works like \citet{Bluck:2019} who found that satellites tend to have slighter higher (B/T) ratios in comparison to central galaxies at the same stellar mass.}
 
@@
 
-\textbf{We thank the anonymous referee for the useful comments and suggestions.} We also thank Cheng Li for our useful discussion on how the sSFR enhancement in galaxy pairs relates to their stellar mass and mass ratio.
+We thank the anonymous referee for the useful comments and suggestions.
+We also thank Cheng Li for our useful discussion on how the sSFR enhancement in galaxy pairs relates to their stellar mass and mass ratio.
 J.S.
@@
 acknowledge support from the National Science Foundation (NSF) grant AST-1614326.
-{\bf YSD would like to acknowledge support from NSFC grant number 10878003}.
+YSD would like to acknowledge support from NSFC grant number 10878003.
 Funding for the Sloan Digital Sky Survey IV has been provided by the Alfred P.

### 2021-02-04 build/final_submit_v3/maintex.tex
added final submit folder

--- 2021-01-29 maintex.tex
@@
 
-\linenumbers
+%\linenumbers
 % Units
@@
 \includegraphics[width=\linewidth]{bpt-cmd.pdf}
-\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies.
-(\textbf{Center}) BPT diagram for the MaNGA galaxies.
-(\textbf{Right}) The WHAN diagram for the MaNGA galaxies.
+\caption[]{(Left) Color-magnitude diagram for MaNGA galaxies.
+(Center) BPT diagram for the MaNGA galaxies.
+(Right) The WHAN diagram for the MaNGA galaxies.
 The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top.
@@
 This means that there will be fewer selected spaxels beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff.
-{\bf We decide to still extend our radial profiles out to 2.5 \reff\ to make full use of the MaNGA data; however, we emphasize that the difference in the sampling of the data within 1.5 \reff\ and the data beyond 1.5 \reff\ may create artificial slopes in the data.
-}
+We decide to still extend our radial profiles out to 2.5 \reff\ to make full use of the MaNGA data; however, we emphasize that the difference in the sampling of the data within 1.5 \reff\ and the data beyond 1.5 \reff\ may create artificial slopes in the data.
 
@@
 \includegraphics[width=\linewidth]{ssfr_comb.pdf}
-\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}).
-The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel.
+\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (Left) and galaxy pairs (Middle).
+The difference between the profiles of the paired galaxies and the control galaxies are shown in the Right panel.
 The dashed black profile represents the mean of the difference profiles.
@@
 The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.
-{\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.}}
+The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.}
 \label{fig:ssfr_prof}
@@
 \includegraphics[width=0.8\linewidth]{ssfr_mass.pdf}
-\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
+\caption[]{The Left panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies.
 The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile.
@@
 The number of paired galaxies in each mass range is given in the legend in parentheses.
-The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) extracted from a 0.5\reff\ aperture.
+The Right panel shows the nuclear $\Delta$log(sSFR) extracted from a 0.5\reff\ aperture.
 The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars).
@@
 Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.
-{\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.
-}
+The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.
 }
@@
 \caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair.
-The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the mass ratio without taking the absolute value.
+The top row is the absolute value of the mass ratio and the bottom row is the mass ratio without taking the absolute value.
 Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from the less massive companions from pairs.
@@
 \includegraphics[width=3in]{prof_comp.pdf}
-\caption[]{The mean radial profile of $\Delta$log(sSFR) (\textbf{Top}) and $\Delta$log(SFR) (\textbf{Bottom}) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
+\caption[]{The mean radial profile of $\Delta$log(sSFR) (Top) and $\Delta$log(SFR) (Bottom) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
 \label{fig:prof_comp}
@@
 \includegraphics[width=3in]{nuc_sep.pdf}
-\caption[]{(\textbf{Top}) $\Delta$log(SFR) \textbf{extracted from the inner 0.5 \reff} over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
-(\textbf{Bottom}) $\Delta$log(sSFR) extracted from the inner 0.5 \reff over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
+\caption[]{(Top) $\Delta$log(SFR) extracted from the inner 0.5 \reff over projected separation from this study ({\it Black}), \citet{Ellison:2008} ({\it Red}), \citet{Scudder:2012} ({\it Blue}), \citet{Patton:2013} ({\it Green}), and \citet{Bustamante:2020} ({\it Purple}).
+(Bottom) $\Delta$log(sSFR) extracted from the inner 0.5 \reff over projected separation from this study ({\it Black}), \citet{Li:2008} ({\it Red}), and \citet{Patton:2020} ({\it Blue}).
 }
@@
 The reason for this is unclear; however, this means that the primary companions will experience enhanced stellar mass growth across their disks while the secondary companions will see only see substantial stellar mass growth in their centers which will result in more bulge dominated galaxies.
-{\bf Differences in the bulge-to-total ratio, (B/T), has been observed in previous works like \citet{Bluck:2019} who found that satellites tend to have slighter higher (B/T) ratios in comparison to central galaxies at the same stellar mass.}
+Differences in the bulge-to-total ratio, (B/T), has been observed in previous works like \citet{Bluck:2019} who found that satellites tend to have slighter higher (B/T) ratios in comparison to central galaxies at the same stellar mass.
 
